### 2022-03-18 tgispine_hypotheses.Rmd
hypothesis simulation script added by FF

---
title: "TGI-spine"
author: "Francesca Fardo"
date: "18/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
## Simulate results for one participant
```{r}
simulate_subj <- function(subid) {
trialN = 10
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

# The following intervals and mean can be changed to reflect hypotheses
# Cold ratigs: simulation
w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:35,1), sd=10)
w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:35,1), sd=10)
a_dr_tgi_cold <- rnorm(trialN, mean=sample(10:40,1), sd=10)
a_pc_tgi_cold <- rnorm(trialN, mean=sample(10:45,1), sd=10)
w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)

# Warm ratigs: simulation
w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:65,1), sd=15)
a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:50,1), sd=15)
w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)

# Burning ratigs: simulation
 w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:80,1), sd=15)
 w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:80,1), sd=15)
 a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:65,1), sd=15)
 a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:50,1), sd=15)
# 
 w_dr_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
 w_pc_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
 a_dr_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
 a_pc_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)

df$rating <- c(w_dr_tgi_cold, w_pc_tgi_cold, a_dr_tgi_cold, a_pc_tgi_cold, w_dr_nontgi_cold, w_pc_nontgi_cold, a_dr_nontgi_cold, a_pc_nontgi_cold,
               w_dr_tgi_warm, w_pc_tgi_warm, a_dr_tgi_warm, a_pc_tgi_warm, w_dr_nontgi_warm, w_pc_nontgi_warm, a_dr_nontgi_warm, a_pc_nontgi_warm,
               w_dr_tgi_burn, w_pc_tgi_burn, a_dr_tgi_burn, a_pc_tgi_burn, w_dr_nontgi_burn, w_pc_nontgi_burn, a_dr_nontgi_burn, a_pc_nontgi_burn)
return(df)}
```

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:30) {
  df <- simulate_subj(i)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

## Summary stats: subject-level
```{r}
# Subject-level
df <- df30
df_subj <- aggregate(df$rating, by = list(id = df$id, conditionN = df$conditionN, dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = mean)
#df_subj$dermatome <- factor(df_subj$dermatome, levels = c('within','across')) # re-order conditions
df_subj
```
## Summary stats: group-level
```{r}
# Group-level stats
df <- df_subj
group_mean   <- aggregate(df$x, by = list(conditionN = df$conditionN, dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = mean)
group_median <- aggregate(df$x, by = list(conditionN = df$conditionN,dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = median)
group_sd     <- aggregate(df$x, by = list(conditionN = df$conditionN,dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = sd)
group_se     <- group_sd$x/sqrt(length(unique(df$id)))

df_group <- data.frame(group_mean, mean = group_mean$x, median = group_median$x, sd = group_sd$x, se = group_se)
df_group
```

## Settings for plots

```{r, echo = FALSE}
# Load libraries
library("ggplot2")
library("gghalves")
library("RColorBrewer")

# Define colors
reds <- brewer.pal(6, "Reds")
blues <- brewer.pal(6, "Blues")
purps <- brewer.pal(6, "Purples")

col_cold_n <- blues[5]
col_cold_w <- blues[3]
col_warm_n <- reds[3]
col_warm_w <- reds[5]
col_unpl_n <- purps[3]
col_unpl_w <- purps[5]

# Parameters for plots
tgi_theme = theme( 
    text = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title=element_text(size=12), 
    legend.text=element_text(size=12),
    plot.title = element_text(lineheight=.8, face="bold", size = 12),
    panel.border = element_rect(size=1),
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(),
    axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
    legend.key = element_blank(),
    axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

# Other parameters
nudge1 = .2
nudge2 = .3
nudge3 = .4

# Define how to plot half violins
tgi_half_violin <- function(df_subj, tgi_dermatome, tgi_cold_location, tgi_stimuli, nudge, color) {
v1 <- geom_half_violin(
   data = df_subj %>% filter(dermatome == tgi_dermatome & cold_location == tgi_cold_location & stimuli == tgi_stimuli), 
   aes(x = conditionN, y = x), position = position_nudge(x = nudge), side = "r", fill = color, alpha = .8)
return(v1)}

# Define how to plot group means and error bars
tgi_group_mean <- function(df_group, tgi_dermatome, tgi_cold_location, tgi_stimuli, nudge, color, shape) {
m1 <- geom_point(
  data = df_group %>% filter(dermatome == tgi_dermatome & cold_location == tgi_cold_location & stimuli == tgi_stimuli), 
  aes(x = conditionN, y = mean), position = position_nudge(x = nudge + .05), size = 3, shape = shape)
return(m1)}

# Define how to plot error bars
tgi_group_error <- function(df_group, tgi_dermatome, tgi_cold_location, tgi_stimuli, tgi_nudge, tgi_color) {
e1 <- geom_errorbar(
  data = df_group %>% filter(dermatome == tgi_dermatome & cold_location == tgi_cold_location & stimuli == tgi_stimuli), 
  aes(x = conditionN, y = mean, ymin = mean - se, ymax = mean + se), position = position_nudge(tgi_nudge + .05), width = 0)
return(e1)}

```

## Plot cold ratings

```{r, echo=FALSE}
# Subset of data corresponding to cold ratings
df_subj_cold  <- subset(df_subj, quality == "cold")
df_group_cold <- subset(df_group, quality == "cold")

# Set jitter for geom_point
set.seed(321)
df_subj_cold$xj <- jitter(df_subj_cold$conditionN, amount=.1)

c1 <- ggplot(data = df_subj_cold, mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +

   # Add theme
   theme_bw()+
   tgi_theme +
   geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +

   # Add points (for each subject and condition)
   geom_point(aes(x = xj), size = 2, alpha = .8) +

   # Add half violin plots
   tgi_half_violin(df_subj_cold, "within", "dist_rostr", "non-tgi", nudge2, col_cold_n) +
   tgi_half_violin(df_subj_cold, "within", "prox_caud", "non-tgi", nudge2, col_cold_n) +
   tgi_half_violin(df_subj_cold, "across", "dist_rostr", "non-tgi", nudge2, col_cold_n) +
   tgi_half_violin(df_subj_cold, "across", "prox_caud", "non-tgi", nudge2, col_cold_n) +
   tgi_half_violin(df_subj_cold, "within", "dist_rostr", "tgi", nudge1, col_cold_w) +
   tgi_half_violin(df_subj_cold, "within", "prox_caud", "tgi", nudge1, col_cold_w) +
   tgi_half_violin(df_subj_cold, "across", "dist_rostr", "tgi", nudge1, col_cold_w) +
   tgi_half_violin(df_subj_cold, "across", "prox_caud", "tgi", nudge1, col_cold_w) +

   # Add group summary stats (between-condition lines, errors bars, and means)
   geom_line(data = df_group_cold %>% filter(stimuli == "non-tgi"), aes(x = conditionN + .45, y = mean)) +
   geom_line(data = df_group_cold %>% filter(stimuli == "tgi"), aes(x = conditionN + .35, y = mean)) +

   tgi_group_error(df_group_cold, "within", "dist_rostr", "non-tgi", nudge3, col_cold_n) +
   tgi_group_error(df_group_cold, "within", "prox_caud", "non-tgi", nudge3, col_cold_n) +
   tgi_group_error(df_group_cold, "across", "dist_rostr", "non-tgi", nudge3, col_cold_n) +
   tgi_group_error(df_group_cold, "across", "prox_caud", "non-tgi", nudge3, col_cold_n) +
   tgi_group_error(df_group_cold, "within", "dist_rostr", "tgi", nudge2, col_cold_w) +
   tgi_group_error(df_group_cold, "within", "prox_caud", "tgi", nudge2, col_cold_w) +
   tgi_group_error(df_group_cold, "across", "dist_rostr", "tgi", nudge2, col_cold_w) +
   tgi_group_error(df_group_cold, "across", "prox_caud", "tgi", nudge2, col_cold_w) +

   tgi_group_mean(df_group_cold, "within", "dist_rostr", "non-tgi", nudge3, col_cold_n, 22) +
   tgi_group_mean(df_group_cold, "within", "prox_caud", "non-tgi", nudge3, col_cold_n, 22) +
   tgi_group_mean(df_group_cold, "across", "dist_rostr", "non-tgi", nudge3, col_cold_n, 22) +
   tgi_group_mean(df_group_cold, "across", "prox_caud", "non-tgi", nudge3, col_cold_n, 22) +
   tgi_group_mean(df_group_cold, "within", "dist_rostr", "tgi", nudge2, col_cold_w, 21) +
   tgi_group_mean(df_group_cold, "within", "prox_caud", "tgi", nudge2, col_cold_w, 21) +
   tgi_group_mean(df_group_cold, "across", "dist_rostr", "tgi", nudge2, col_cold_w, 21) +
   tgi_group_mean(df_group_cold, "across", "prox_caud", "tgi", nudge2, col_cold_w, 21) +

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "caudal", "rostral"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(blues[6],blues[3])) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c(blues[6], "gray25")) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Cold ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 1: Cold perception')

c1
```
## Plot warm ratings

```{r, echo=FALSE}
# Subset of data corresponding to cold ratings
df_subj_warm  <- subset(df_subj, quality == "warm")
df_group_warm <- subset(df_group, quality == "warm")

# Set jitter for geom_point
set.seed(321)
df_subj_warm$xj <- jitter(df_subj_warm$conditionN, amount=.1)

w1 <- ggplot(data = df_subj_warm, mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +

   # Add theme
   theme_bw()+
   tgi_theme +
   geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +

   # Add points (for each subject and condition)
   geom_point(aes(x = xj), size = 2, alpha = .8) +

   # Add half violin plots
   tgi_half_violin(df_subj_warm, "within", "dist_rostr", "non-tgi", nudge2, col_warm_n) +
   tgi_half_violin(df_subj_warm, "within", "prox_caud", "non-tgi", nudge2, col_warm_n) +
   tgi_half_violin(df_subj_warm, "across", "dist_rostr", "non-tgi", nudge2, col_warm_n) +
   tgi_half_violin(df_subj_warm, "across", "prox_caud", "non-tgi", nudge2, col_warm_n) +
   tgi_half_violin(df_subj_warm, "within", "dist_rostr", "tgi", nudge1, col_warm_w) +
   tgi_half_violin(df_subj_warm, "within", "prox_caud", "tgi", nudge1, col_warm_w) +
   tgi_half_violin(df_subj_warm, "across", "dist_rostr", "tgi", nudge1, col_warm_w) +
   tgi_half_violin(df_subj_warm, "across", "prox_caud", "tgi", nudge1, col_warm_w) +

   # Add group summary stats (between-condition lines, errors bars, and means)
   geom_line(data = df_group_warm %>% filter(stimuli == "non-tgi"), aes(x = conditionN + .45, y = mean)) +
   geom_line(data = df_group_warm %>% filter(stimuli == "tgi"), aes(x = conditionN + .35, y = mean)) +

   tgi_group_error(df_group_warm, "within", "dist_rostr", "non-tgi", nudge3, col_warm_n) +
   tgi_group_error(df_group_warm, "within", "prox_caud", "non-tgi", nudge3, col_warm_n) +
   tgi_group_error(df_group_warm, "across", "dist_rostr", "non-tgi", nudge3, col_warm_n) +
   tgi_group_error(df_group_warm, "across", "prox_caud", "non-tgi", nudge3, col_warm_n) +
   tgi_group_error(df_group_warm, "within", "dist_rostr", "tgi", nudge2, col_warm_w) +
   tgi_group_error(df_group_warm, "within", "prox_caud", "tgi", nudge2, col_warm_w) +
   tgi_group_error(df_group_warm, "across", "dist_rostr", "tgi", nudge2, col_warm_w) +
   tgi_group_error(df_group_warm, "across", "prox_caud", "tgi", nudge2, col_warm_w) +

   tgi_group_mean(df_group_warm, "within", "dist_rostr", "non-tgi", nudge3, col_warm_n, 22) +
   tgi_group_mean(df_group_warm, "within", "prox_caud", "non-tgi", nudge3, col_warm_n, 22) +
   tgi_group_mean(df_group_warm, "across", "dist_rostr", "non-tgi", nudge3, col_warm_n, 22) +
   tgi_group_mean(df_group_warm, "across", "prox_caud", "non-tgi", nudge3, col_warm_n, 22) +
   tgi_group_mean(df_group_warm, "within", "dist_rostr", "tgi", nudge2, col_warm_w, 21) +
   tgi_group_mean(df_group_warm, "within", "prox_caud", "tgi", nudge2, col_warm_w, 21) +
   tgi_group_mean(df_group_warm, "across", "dist_rostr", "tgi", nudge2, col_warm_w, 21) +
   tgi_group_mean(df_group_warm, "across", "prox_caud", "tgi", nudge2, col_warm_w, 21) +

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "caudal", "rostral"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_warm_n, col_warm_w)) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", reds[6])) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Warm ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 1: Warm perception')

w1
```

### 2022-03-21 tgispine_hypotheses.Rmd
adding anovas to estimate required sample size, will be more informative when we have pilot data

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(dplyr)
 
@@
 simulate_subj <- function(subid) {
-trialN = 10
+trialN = 9
 conditionN = 8
@@
 df30 <- data.frame()
-for (i in 1:30) {
+for (i in 1:50) {
   df <- simulate_subj(i)
@@
 ```
+
+# running ANOVA on simulated data - to gain idea of effect size
+
+```{r, echo=FALSE}
+library(ez)
+library(psychReport)
+# burning VAS
+burn_anova <- ezANOVA(
+  data = df_subj[df_subj$quality == 'burn' ,]
+  , dv = .(x)
+  , wid = .(id)
+  , within = .(dermatome, cold_location, stimuli),
+  return_aov = TRUE,
+  detailed = TRUE
+)
+
+# warm VAS
+warm_anova <- ezANOVA(
+  data = df_subj[df_subj$quality == 'warm' ,]
+  , dv = .(x)
+  , wid = .(id)
+  , within = .(dermatome, cold_location, stimuli),
+  return_aov = TRUE,
+  detailed = TRUE
+)
+
+# cold VAS
+cold_anova <- ezANOVA(
+  data = df_subj[df_subj$quality == 'cold' ,]
+  , dv = .(x)
+  , wid = .(id)
+  , within = .(dermatome, cold_location, stimuli),
+  return_aov = TRUE,
+  detailed = TRUE
+)
+
+```{r}
+burn_anova
+```
+```{r}
+warm_anova
+```
+``` {r}
+cold_anova
+```

### 2022-03-21 VAS_loadParams.m
adding counterbalancing procedures to the results file

@@ -19,7 +19,7 @@ vars.filename.path = "/Users/au706616/Documents/Experiments/SPINALTGI/"; % this 
 vars.ViewDist = 56;
 
 %Trials
-vars.task.NTrialsTotal       = 12; % Total number of trials
+vars.task.NBlocksTotal       = 1; %Total number of blocks per pseudorandom procedure (n x 8 trials)
 vars.task.NTrialsChange      = 4; % The frequency of thermode change per trial (if thermode is changed every trial, set to 1)
 
 %Times

### 2022-03-21 VAS_run.m

@@ -65,44 +65,59 @@ end
     vars.control.abortFlag = 0;
     [~, ~, keys.KeyCode] = KbCheck;
 
-for trial_idx=1:vars.task.NTrialsTotal
-    %% Open start screen
-    % to control when each trial starts - can remove this if VAS questions
-    % need to be continuous  
+    %% Pseudorandomise information
+    % get specific procedure order from main file
+    order = str2double(vars.filename.ID(2));
+    % extract trials associated with specific counterbalancing procedure
+    procedure = vars.task.randomise(vars.task.randomise.procedure==order, :);
 
-    Screen('TextSize', scr.win, scr.TextSize);
-    DrawFormattedText(scr.win, vars.instructions.StartVas, 'center', 'center', scr.TextColour);
-    [~, ~] = Screen('Flip', scr.win);
-    KbStrokeWait;
-
-    % run countdown during TGI stimulation - number of seconds defined in
-    % VAS_loadParams.m
-    StimCount(scr, vars);  
-
-    %% Run VAS
-    % Will loop through the number of VAS questions
-    % for each trial (both params are set in VAS_load.params.m)
-    % Currently set to 3 VAS questions - burning, warm, cold
-    % this is used to index which question was addressed in output (see
-    % VAS_loadParams.m for details)
-    randQuestion = vars.instructions.QuestionCode(randperm(length(vars.instructions.whichQuestion)));
-
-    Screen('TextSize', scr.win, scr.TextSize); % resetting text size
-    for rand_idx=1:length(randQuestion)
-        question_type_idx = randQuestion(rand_idx);
-        [results.vasResponse(trial_idx, question_type_idx), ...
-            results.vasReactionTime(trial_idx, question_type_idx)] = ...
-            getVasRatings(keys, scr, vars, question_type_idx); 
-        % making sure that VAS ratings are saved in correct column for each
-        % question (sanity check)
-        results.QuestionType(trial_idx, question_type_idx) = vars.instructions.Question(question_type_idx); 
-    end 
-
-    % display thermode switch text - atm not needed
-    if trial_idx == vars.instructions.ThermodeSwitch(trial_idx)
-        DrawFormattedText(scr.win, vars.instructions.Thermode, 'center', 'center', scr.TextColour);
+trial_idx = []; %create a seperate index for individual trials
+for block_idx=1:vars.task.NBlocksTotal
+    for pseudo_idx=1:length(procedure.trials)
+        % record number of total trials per participant
+        trial_idx = trial_idx+1;
+        %% Open start screen
[…]

### 2022-03-21 pseudo_thermodes.m

@@ -6,17 +6,16 @@
 % Last edited:
 
 % NB: this functions runs with an associated 'counterbalancing' file, where
-% specific procedures are indicated by a number
-
-% get specific procedure order from main file
-order = str2double(vars.filename.ID(2));
+% specific procedures are indicated by a number - loaded in
+% VAS_loadParams.m
 
 switch order
     case 1
-        % extract trials associated with specific counterbalancing procedure
-        procedure = vars.task.randomise(vars.task.randomise.procedure==order, :);
+        
     case 2
+        
     case 3
+
     case 4
 end
 %end

### 2022-03-21 VAS_loadParams.m
debugging counterbalancing addition, and making sure all results are saved logically

@@ -19,8 +19,8 @@ vars.filename.path = "/Users/au706616/Documents/Experiments/SPINALTGI/"; % this 
 vars.ViewDist = 56;
 
 %Trials
-vars.task.NBlocksTotal       = 1; %Total number of blocks per pseudorandom procedure (n x 8 trials)
-vars.task.NTrialsChange      = 4; % The frequency of thermode change per trial (if thermode is changed every trial, set to 1)
+vars.task.NBlocksTotal       = 1; %Total number of blocks per pseudorandom procedure (n x 16 trials)
+vars.task.NTrialsChange      = 2; % The frequency of thermode change per trial (if thermode is changed every trial, set to 1)
 
 %Times
 %vars.task.jitter             = randInRange(1,3,[1,vars.task.NTrialsTotal]); % time between the beginning of the trial and the beginning of the stimulation
@@ -49,10 +49,10 @@ vars.instructions.whichQuestion = [1 1 1]; %Enable or disable question (1 = enab
 
 vars.instructions.whichKey = {'LR','UD'}; % Left/Right. Up/Down. If you are using the mouse as an input device let this entirely as LR
       
-vars.instructions.ThermodeSwitch = 1:vars.task.NTrialsChange:vars.task.NTrialsTotal; %When to ask participant to change thermode position
-vars.instructions.Thermode = 'Thank you. Please wait whilst we change the thermode location';
+vars.instructions.ThermodeSwitch = 2:vars.task.NTrialsChange:(vars.task.NBlocksTotal*16); %When to ask participant to change thermode position (starting from 2)
+vars.instructions.Thermode = 'Please wait whilst we change the thermode location. Press a key when done.';
 
-vars.instructions.ConfEndPoints = {'Not at all', 'Extreme'};
+vars.instructions.ConfEndPoints = {'Not at all', 'Extreme'};    
 %% Waiting during stimulation
 vars.waitStim.text = 'When the countdown ends, please rate your experience';
 vars.waitStim.secs = 5; %the number of seconds you want to stimulate TGI for

### 2022-03-21 VAS_run.m
fixing some saving issues and thermode switch text issues

@@ -36,9 +36,11 @@ vars.filename.ID = string(inputdlg({'Participant number:','Conterbalance procedu
 formatout = 'yymmdd';
 vars.filename.date = datestr(now, formatout);
 
-matName = sprintf('%s_%s_VAS_sTGI.mat', vars.filename.ID, vars.filename.date);
-csv_ratName = sprintf('%s_%s_VASratings_sTGI.csv', vars.filename.ID, vars.filename.date);
-csv_respName = sprintf('%s_%s_VASresp_sTGI.csv', vars.filename.ID, vars.filename.date);
+% saving file name with participantID_pseudorandomProcedure_Date
+matName = sprintf('%s_%s_%s_VAS_sTGI.mat', vars.filename.ID, vars.filename.date);
+csv_ratName = sprintf('%s_%s_%s_VASratings_sTGI.csv', vars.filename.ID, vars.filename.date);
+csv_respName = sprintf('%s_%s_%s_VASrespTime_sTGI.csv', vars.filename.ID, vars.filename.date);
+csv_trialName = sprintf('%s_%s_%s_VAStrialInfo_sTGI.csv', vars.filename.ID, vars.filename.date);
 
 %% Psychtoolbox settings
 PsychDefaultSetup(2);
@@ -70,11 +72,11 @@ vars.control.abortFlag = 0;
 order = str2double(vars.filename.ID(2));
 % extract trials associated with specific counterbalancing procedure
 procedure = vars.task.randomise(vars.task.randomise.procedure==order, :);
-
+    
 trial_idx = 0 ; %create a seperate index for individual trials
 
 for block_idx=1:vars.task.NBlocksTotal
-    for pseudo_idx=1:length(procedure.trial_  type)
+    for pseudo_idx=1:length(procedure.trial_type)
         % record number of total trials per participant
         trial_idx = trial_idx+1;
         %% Open start screen
@@ -118,7 +120,8 @@ for block_idx=1:vars.task.NBlocksTotal
         results.trialInfo.trial_tot(trial_idx) = trial_idx;
         % display text for thermode location switch, need to refine this
         % step when counterbalancing procedure is finalised
-        if trial_idx == vars.instructions.ThermodeSwitch(trial_idx)
+        if bitget(trial_idx,1) %if the trial index is odd, no thermode switch
+        else
             DrawFormattedText(scr.win, vars.instructions.Thermode, 'center', 'center', scr.TextColour);
[…]

### 2022-04-07 VAS_loadParams.m
changing counterbalance order to be more flexible

@@ -20,6 +20,7 @@ vars.filename.path = "/Users/au706616/Documents/Experiments/SPINALTGI/"; % this 
 vars.ViewDist = 56;
 
 %Trials
+vars.task.NTrialReps         = 4; %number of repeat trials per condition (i.e. thermode in right place)ds
 vars.task.NBlocksTotal       = 1; %Total number of blocks per pseudorandom procedure (n x 16 trials)
 vars.task.NTrialsChange      = 4; % The frequency of thermode change per trial (if thermode is changed every trial, set to 1)
 
@@ -51,7 +52,7 @@ vars.instructions.whichQuestion = [1 1 1]; %Enable or disable question (1 = enab
 vars.instructions.whichKey = {'LR','UD'}; % Left/Right. Up/Down. If you are using the mouse as an input device let this entirely as LR
       
 vars.instructions.ThermodeSwitch = 2:vars.task.NTrialsChange:(vars.task.NBlocksTotal*16); %When to ask participant to change thermode position (starting from 2)
-vars.instructions.Thermode = 'Please wait whilst we change the thermode location. Press a key when done.';
+vars.instructions.Thermode = 'Please wait whilst we change the location of the thermode. Press a key when done.';
 
 vars.instructions.ConfEndPoints = {'Not at all', 'Extreme'};    
 %% Waiting during stimulation

### 2022-04-07 VAS_loadParams.m
changing instructions for the VAS

@@ -40,7 +40,15 @@ vars.task.randomise = readtable('counterbalancing.csv');
 %% Instructions
 vars.instructions.textSize = 32;
 
-vars.instructions.StartVas = 'Press a key when stimulation begins';
+vars.instructions.StartScreen = ['For each trial, you will experience thermal stimulation on your skin.\n\n' ...
+    'You will then be asked to rate how much a specific thermode\n' ...
+    'is BURNING, feels WARM or feels COLD on a scale of 0 - 100.\n' ...
+    'Where 0 represents no burning/warm/cold sensation,\n' ...
+    'and 100 an extreme burning/warm/cold sensation.\n\n'...
+    'It is important that you only rate the sensation coming from ONE thermode.\n\n' ...
+    'When you are ready, press and key to begin.'];
+
+vars.instructions.StartVas = 'When instructed by the experimenter, press a key to start rating';
 
 vars.instructions.Question = {'At the moment, how much is the stimulus BURNING?',...
                                'At the moment, how WARM is the stimulus?',...
@@ -56,7 +64,7 @@ vars.instructions.Thermode = 'Please wait whilst we change the location of the t
 
 vars.instructions.ConfEndPoints = {'Not at all', 'Extreme'};    
 %% Waiting during stimulation
-vars.waitStim.text = 'When the countdown ends, please rate your experience';
+vars.waitStim.text = 'When the countdown ends, please rate your experience. Press SPACE when done.';
 vars.waitStim.secs = 5; %the number of seconds you want to stimulate TGI for
 vars.waitStim.textSize = 65;
 

### 2022-04-07 VAS_run.m

@@ -14,18 +14,17 @@
 %% Load parameters
 clear all % clearing all old data
 
+% Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
+vars.control.devFlag  = 0; 
+
 VAS_loadParams;
 addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
-% path to save data to - should be changed depending on laptop
-% (VAS_loadParams.m)
+% path to save data to - should be changed depending on laptop (VAS_loadParams.m)
 datPath = vars.filename.path;
 runPath = pwd;
 
 % Reseed the random-number generator
 SetupRand;   
-
-vars.control.devFlag  = 1; % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
-
 %% Path
 if vars.control.devFlag == 0 %only run if not debugging
     % input participant details for filename
@@ -75,6 +74,12 @@ vars.control.thisTrial = 1;
 vars.control.abortFlag = 0;
 [~, ~, keys.KeyCode] = KbCheck;
 
+%% Start screen
+Screen('TextSize', scr.win, scr.TextSize);
+DrawFormattedText(scr.win, vars.instructions.StartScreen, 'center', 'center', scr.TextColour);
+[~, ~] = Screen('Flip', scr.win);
+KbStrokeWait;
+
 %% Pseudorandomise information
 % get specific procedure order from main file - if in development mode then
 % just get the first order
@@ -93,11 +98,10 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
         for rep_idx = 1:vars.task.NTrialReps %loop through trial repeats, 4 trials per thermode location
             % record number of total trials per participant
             trial_idx = trial_idx+1;
-            %% Open start screen
+            %% Open VAS screen
             % to control when each trial starts - can remove this if VAS questions
             % need to be continuous  
-        
-            Screen('TextSize', scr.win, scr.TextSize);
+
             DrawFormattedText(scr.win, vars.instructions.StartVas, 'center', 'center', scr.TextColour);
             [~, ~] = Screen('Flip', scr.win);
             KbStrokeWait;
@@ -133,8 +137,8 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
             results.trialInfo(trial_idx, 1:6) = procedure(pseudo_idx, 1:6);
[…]

### 2022-04-07 getVasRatings.m

@@ -45,8 +45,8 @@ function [vasResp, RT] = getVasRatings(keys, scr, vars, instruction_n)
         case 2 % Keyboard response
             vars.control.vasOnset = GetSecs;
             % The avaliable keys to press
-            returnKeys = KbName('return');
-            returnKey = returnKeys(1);
+            returnKey = KbName('space');
+            %returnKey = returnKeys(1);
             leftKey = KbName('LeftArrow');
             rightKey = KbName('RightArrow');
 

### 2022-04-07 analysis/tgispine_hypotheses.Rmd
adding pilot data to shape hypotheses, and correcting labelling error

--- 2022-03-21 tgispine_hypotheses.Rmd
@@
 # Cold ratigs: simulation
-w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:35,1), sd=10)
-w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:35,1), sd=10)
-a_dr_tgi_cold <- rnorm(trialN, mean=sample(10:40,1), sd=10)
-a_pc_tgi_cold <- rnorm(trialN, mean=sample(10:45,1), sd=10)
-w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
-w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
-a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
-a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
+w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
+w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
+a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
+a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
+w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
+w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
+a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
+a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
 
 # Warm ratigs: simulation
-w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
-w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
-a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:65,1), sd=15)
-a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:50,1), sd=15)
-w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
-w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
-a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
-a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
+w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
+w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
+a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
+a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
+w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
+w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
+a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
+a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
 
-# Burning ratigs: simulation
- w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:80,1), sd=15)
- w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:80,1), sd=15)
- a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:65,1), sd=15)
- a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:50,1), sd=15)
+# Burning ratings: simulation
+ w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
+ w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
+ a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:40,1), sd=15)
+ a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:30,1), sd=15)
 # 
- w_dr_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
- w_pc_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
- a_dr_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
- a_pc_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
+ w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
+ w_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
+ a_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
+ a_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 
@@
 col_warm_w <- reds[5]
-col_unpl_n <- purps[3]
-col_unpl_w <- purps[5]
+col_burn_n <- purps[3]
+col_burn_w <- purps[5]
 
@@
    scale_shape_manual(values = c(22, 21)) +
-   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "caudal", "rostral"), limits=c(0.6, 5)) +
+   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "rostral", "caudal"), limits=c(0.6, 5)) +
    scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(blues[6],blues[3])) +
@@
 ```{r, echo=FALSE}
-# Subset of data corresponding to cold ratings
+# Subset of data corresponding to warm ratings
 df_subj_warm  <- subset(df_subj, quality == "warm")
@@
    scale_shape_manual(values = c(22, 21)) +
-   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "caudal", "rostral"), limits=c(0.6, 5)) +
+   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "rostral", "caudal"), limits=c(0.6, 5)) +
    scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_warm_n, col_warm_w)) +
@@
    labs(title = "", x = "", y = "Warm ratings", fill = "Stimuli", color = "Stimuli") +
-   ggtitle('Figure 1: Warm perception')
+   ggtitle('Figure 2: Warm perception')
 
 w1
+```
+## Plot burn ratings
+
+```{r, echo=FALSE}
+# Subset of data corresponding to warm ratings
+df_subj_burn  <- subset(df_subj, quality == "burn")
+df_group_burn <- subset(df_group, quality == "burn")
+
+# Set jitter for geom_point
+set.seed(321)
+df_subj_burn$xj <- jitter(df_subj_burn$conditionN, amount=.1)
+
+b1 <- ggplot(data = df_subj_burn, mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +
+
+   # Add theme
+   theme_bw()+
+   tgi_theme +
+   geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
+
+   # Add points (for each subject and condition)
+   geom_point(aes(x = xj), size = 2, alpha = .8) +
+
+   # Add half violin plots
+   tgi_half_violin(df_subj_burn, "within", "dist_rostr", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "within", "prox_caud", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "across", "dist_rostr", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "across", "prox_caud", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "within", "dist_rostr", "tgi", nudge1, col_burn_w) +
+   tgi_half_violin(df_subj_burn, "within", "prox_caud", "tgi", nudge1, col_burn_w) +
+   tgi_half_violin(df_subj_burn, "across", "dist_rostr", "tgi", nudge1, col_burn_w) +
+   tgi_half_violin(df_subj_burn, "across", "prox_caud", "tgi", nudge1, col_burn_w) +
+
+   # Add group summary stats (between-condition lines, errors bars, and means)
+   geom_line(data = df_group_burn %>% filter(stimuli == "non-tgi"), aes(x = conditionN + .45, y = mean)) +
+   geom_line(data = df_group_burn %>% filter(stimuli == "tgi"), aes(x = conditionN + .35, y = mean)) +
+
+   tgi_group_error(df_group_burn, "within", "dist_rostr", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "within", "prox_caud", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "across", "dist_rostr", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "across", "prox_caud", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "within", "dist_rostr", "tgi", nudge2, col_burn_w) +
+   tgi_group_error(df_group_burn, "within", "prox_caud", "tgi", nudge2, col_burn_w) +
+   tgi_group_error(df_group_burn, "across", "dist_rostr", "tgi", nudge2, col_burn_w) +
+   tgi_group_error(df_group_burn, "across", "prox_caud", "tgi", nudge2, col_burn_w) +
+
+   tgi_group_mean(df_group_burn, "within", "dist_rostr", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "within", "prox_caud", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "across", "dist_rostr", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "across", "prox_caud", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "within", "dist_rostr", "tgi", nudge2, col_burn_w, 21) +
+   tgi_group_mean(df_group_burn, "within", "prox_caud", "tgi", nudge2, col_burn_w, 21) +
+   tgi_group_mean(df_group_burn, "across", "dist_rostr", "tgi", nudge2, col_burn_w, 21) +
+   tgi_group_mean(df_group_burn, "across", "prox_caud", "tgi", nudge2, col_burn_w, 21) +
+
+   # Define additional settings
+   scale_shape_manual(values = c(22, 21)) +
+   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "rostral", "caudal"), limits=c(0.6, 5)) +
+   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_burn_n, col_burn_w)) +
+   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", purps[6])) +
+   guides(shape = FALSE) +
+   labs(title = "", x = "", y = "Burn ratings", fill = "Stimuli", color = "Stimuli") +
+   ggtitle('Figure 3: Burn perception')
+
+b1
 ```

### 2022-04-07 VAS_run.m

@@ -24,7 +24,8 @@ datPath = vars.filename.path;
 runPath = pwd;
 
 % Reseed the random-number generator
-SetupRand;   
+SetupRand;
+
 %% Path
 if vars.control.devFlag == 0 %only run if not debugging
     % input participant details for filename

### 2022-04-07 analysis/tgispine_analysis.R

@@ -75,8 +75,12 @@ ggplot(AGM, aes(group = trial_tot, colour = cold_probe)) +
   theme_classic()
 
 
-# get median VAS responses for each condition
-# burning
-VASburn <- aggregate(VASburning~manipulation*condition*cold_probe*ID, median, data = AGM)
-VASwarm <- aggregate(VASwarm~manipulation*condition*cold_probe*ID, median, data = AGM)
-VAScold <- aggregate(VAScold~manipulation*condition*cold_probe*ID, median, data = AGM)
+# get mean VAS responses for each condition
+VASburn <- aggregate(VASburning~manipulation*condition*cold_probe*dermatome*ID, mean, data = AGM)
+VASwarm <- aggregate(VASwarm~manipulation*condition*cold_probe*dermatome*ID, mean, data = AGM)
+VAScold <- aggregate(VAScold~manipulation*condition*cold_probe*dermatome*ID, mean, data = AGM)
+# standard deviations
+SDburn <- aggregate(VASburning~manipulation*condition*cold_probe*dermatome*ID, sd, data = AGM)
+SDwarm <- aggregate(VASwarm~manipulation*condition*cold_probe*dermatome*ID, sd, data = AGM)
+SDcold <- aggregate(VAScold~manipulation*condition*cold_probe*dermatome*ID, sd, data = AGM)
+

### 2022-04-07 analysis/tgispine_hypotheses.Rmd
informing simulations with pilot data

@@
 w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
-a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
-a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
+a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
+a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
 w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
@@
 w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
-a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
-a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
+a_dr_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
+a_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
 w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
@@
  w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
- a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:40,1), sd=15)
- a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:30,1), sd=15)
+ a_dr_tgi_burn <- rnorm(trialN, mean=sample(5:40,1), sd=15)
+ a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:50,1), sd=15)
 # 
@@
 library(psychReport)
+# isolate just TGI for purposes of determining effect size
+df_tgi <- df_subj[df_subj$stimuli == 'tgi' ,]
+
 # burning VAS
 burn_anova <- ezANOVA(
-  data = df_subj[df_subj$quality == 'burn' ,]
+  data = df_tgi[df_tgi$quality == 'burn' ,]
   , dv = .(x)
   , wid = .(id)
-  , within = .(dermatome, cold_location, stimuli),
+  , within = .(dermatome, cold_location),
   return_aov = TRUE,
@@
 warm_anova <- ezANOVA(
-  data = df_subj[df_subj$quality == 'warm' ,]
+  data = df_tgi[df_tgi$quality == 'warm' ,]
   , dv = .(x)
   , wid = .(id)
-  , within = .(dermatome, cold_location, stimuli),
+  , within = .(dermatome, cold_location),
   return_aov = TRUE,
@@
 cold_anova <- ezANOVA(
-  data = df_subj[df_subj$quality == 'cold' ,]
+  data = df_tgi[df_tgi$quality == 'cold' ,]
   , dv = .(x)
   , wid = .(id)
-  , within = .(dermatome, cold_location, stimuli),
+  , within = .(dermatome, cold_location),
   return_aov = TRUE,
@@
 )
-
-```{r}
-burn_anova
-```
-```{r}
-warm_anova
-```
-``` {r}
-cold_anova
-```

### 2022-04-11 analysis/tgispine_analysis.R
still finalising plots

@@ -202,46 +202,43 @@ VAS_H1 <- merge(VAS_H1, VAS_H1_SD)
 # plotting - TGI
 H1TGI <- ggplot(VAS_H1[VAS_H1$manipulation=='TGI' ,], 
        aes(condition, rating, group = ID, colour = VAS)) +
-  geom_point(size = 1, position = position_dodge(.3)) +
+  geom_point(size = 2, position = position_dodge(.3)) +
   geom_errorbar(aes(ymin=rating-SD, ymax=rating+SD), width=.2,
                 position=position_dodge(.3)) +
   facet_wrap(~VAS) +
   scale_color_manual(values = c(blues[4],reds[4],purps[5])) +
-  labs(title = 'TGI') +
+  labs(title = 'TGI', x = 'Condition', y = 'VAS Rating') +
+  lims(y = c(-5,75)) +
   theme_classic() + 
   theme(legend.position = 'none')
-
-add_summary(H1TGI, 'mean',
-            color = 'grey',
-            shape = 21,
-            size = .5)
 
 
 # non TGI
 H1NTGI <- ggplot(VAS_H1[VAS_H1$manipulation=='CNT' ,], 
        aes(condition, rating, group = ID, colour = VAS)) +
-  geom_point(size = 1, position = position_dodge(.3)) +
+  geom_point(size = 2, position = position_dodge(.3)) +
   facet_wrap(~VAS) +
   geom_errorbar(aes(ymin=rating-SD, ymax=rating+SD), width=.2,
                   position=position_dodge(.3)) +
   scale_color_manual(values = c(blues[4],reds[4],purps[5])) +
-  labs(title = 'Non TGI') +
+  labs(title = 'Non TGI', x = '', y = 'VAS Rating') +
+  lims(y = c(-5,75)) +
   theme_classic() + 
   theme(legend.position = 'none')
 
-add_summary(H1NTGI, 'mean',
-            color = 'grey',
-            shape = 21,
-            size = .5)
+H1 <- ggarrange(H1NTGI, H1TGI,
+                ncol = 1, nrow = 2)
+
+ggsave('H1plot.png', H1, device = NULL, path = datPath, width = 5, height = 8)
    
 # H2: across dermatome
 VASSD <- aggregate(rating~ID*VAS*manipulation*condition*cold_probe*dermatome, 
                          sd, data = df_plot)
[…]

### 2022-04-12 analysis/tgispine_analysis.R
finalising individual trial plots

@@ -78,112 +78,123 @@ df_cold$VAS <- 'cold'
 names(df_cold)[12] <- 'rating'
 # combine
 df_plot <- rbind(df_burn, df_warm, df_cold)
+# recode levels for plotting
 df_plot$VAS <- factor(df_plot$VAS, 
                              levels = c("cold", "warm", "burn"))
 df_plot$condition <- factor(df_plot$condition, 
                       labels = c("ACR", "WIN"))
+df_plot$ID <- factor(df_plot$ID, 
+                            labels = c("P1", "P2", "P3"))
 
 # Define colors
-reds <- brewer.pal(6, "Reds")
-blues <- brewer.pal(6, "Blues")
-purps <- brewer.pal(6, "Purples")
-green <- brewer.pal(6, "Greens")
+reds <- brewer.pal(8, "Reds")
+redpu <- brewer.pal(8, "RdPu")
+orans <- brewer.pal(8, "Oranges")
+blues <- brewer.pal(8, "Blues")
+purps <- brewer.pal(8, "Purples")
+green <- brewer.pal(8, "YlGn")
+blgrn <- brewer.pal(8, "BuGn")
 
-caudal <- blues[6]
-rostral <- blues[3]
-distal <- green[6]
-proximal <- green[3]
-colours <- c(caudal, rostral, distal, proximal)
+# caudal, rostral, distal, proximal colours
+col_burn <- c(purps[4], purps[7], redpu[3], redpu[6])
+col_warm <- c(reds[3], reds[6], orans[3], orans[6])
+col_cold <- c(blues[3], blues[6], blgrn[4], blgrn[7])
 
 ## plot individual participants
 # isolate just my data (for now)
-AGM <- df_plot[df_plot$ID == '0001' ,]
-CEA <- df_plot[df_plot$ID == 'C001' ,]
-DE <- df_plot[df_plot$ID == 'D001' ,]
+P1 <- df_plot[df_plot$ID == 'P1' ,]
+P2 <- df_plot[df_plot$ID == 'P2' ,]
+P3 <- df_plot[df_plot$ID == 'P3' ,]
 
-# AGM - TGI
-P1TGI <- ggplot(AGM[AGM$manipulation=='TGI' ,], aes(group = trial_n, colour = cold_probe)) +
-  geom_point(aes(condition, rating), size = 1.5, position = position_dodge(.2)) +
-  facet_wrap(~VAS) +
[…]

### 2022-04-12 analysis/tgispine_analysis.R
getting pilot summary stats

@@ -7,6 +7,7 @@ library(dplyr)
 library(ggplot2)
 library(RColorBrewer)
 library(ggpubr)
+library(Rmisc)
 
 # paths
 datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
@@ -114,7 +115,7 @@ BTGI <- ggplot(df_plot[df_plot$VAS=='burn' & df_plot$manipulation == 'TGI' ,],
   scale_colour_manual(values = col_burn) +
   lims(y = c(0, 100)) +
   theme_classic() +
-  labs(title = 'TGI', x = 'Condition', y = 'VAS Rating') +
+  labs(title = 'TGI', x = 'Condition', y = '') +
   theme(legend.position = 'none',
         legend.title = element_blank())
 
@@ -126,15 +127,15 @@ BNTGI <- ggplot(df_plot[df_plot$VAS=='burn' & df_plot$manipulation == 'CNT' ,],
   scale_colour_manual(values = col_burn) +
   theme_classic() +
   lims(y = c(0, 100)) +
-  labs(title = 'Non TGI', x = '', y = 'VAS Rating') +
+  labs(title = 'Non TGI', x = 'Condition', y = 'VAS Rating') +
   theme(legend.position = 'bottom',
         legend.title = element_blank())
 
 BURN <- ggarrange(BNTGI, BTGI,
-                ncol = 1, nrow = 2,
+                ncol = 2, nrow = 1,
                 common.legend = TRUE,
                 legend = 'bottom')
-ggsave('BURNplot.png', BURN, device = NULL, path = datPath, width = 5, height = 8)
+ggsave('BURNplot.png', BURN, device = NULL, path = datPath, width = 8, height = 5)
 
 # WARM - TGI
 WTGI <- ggplot(df_plot[df_plot$VAS=='warm' & df_plot$manipulation == 'TGI' ,], 
@@ -144,7 +145,7 @@ WTGI <- ggplot(df_plot[df_plot$VAS=='warm' & df_plot$manipulation == 'TGI' ,],
   scale_colour_manual(values = col_warm) +
   lims(y = c(0, 100)) +
   theme_classic() +
-  labs(title = 'TGI', x = 'Condition', y = 'VAS Rating') +
+  labs(title = 'TGI', x = 'Condition', y = '') +
   theme(legend.position = 'none',
         legend.title = element_blank())
 
[…]

### 2022-04-12 analysis/tgispine_hypotheses.Rmd
using pilot to inform simulation, creating pilot plots

@@
 ```
+
 ## Simulate results for one participant
@@
 # Cold ratigs: simulation
-w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
-w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
-a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
-a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
-w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
-w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
+w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=5)
+w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=5)
+a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:50,1), sd=5)
+a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=5)
+w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:60,1), sd=15)
+w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:60,1), sd=15)
 a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
@@
 # Warm ratigs: simulation
-w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
-w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
+w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:65,1), sd=15)
+w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:70,1), sd=15)
 a_dr_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
-a_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
+a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
 w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
@@
 # Burning ratings: simulation
- w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
- w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
- a_dr_tgi_burn <- rnorm(trialN, mean=sample(5:40,1), sd=15)
- a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:50,1), sd=15)
-# 
+ w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:65,1), sd=15)
+ w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:60,1), sd=15)
+ a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:70,1), sd=15)
+ a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:60,1), sd=15)
  w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
@@
 df30 <- data.frame()
-for (i in 1:50) {
+for (i in 1:60) {
   df <- simulate_subj(i)
@@
 
-# running ANOVA on simulated data - to gain idea of effect size
+# running inferential stats on simulated data - to gain idea of effect size
 
-```{r, echo=FALSE}
+```{r}
 library(ez)
@@
 )
+
+## t-test
+# create seperate data-frames to allow for comparison
+within <- df_subj[df_subj$dermatome=='within' ,]
+across <- df_subj[df_subj$dermatome=='across' ,]
+proxc <- within[within$cold_location== 'prox_caud' ,]
+distc <- within[within$cold_location=='dist_rostr' ,]
+caudc <- across[across$cold_location=='prox_caud' ,]
+rostc <- across[across$cold_location=='dist_rostr' ,]
+
+## H1
+names(within)[7] <- 'within'
+names(across)[7] <- 'across'
+# merge
+H1_df <- merge(within, across, by = c('id','cold_location','stimuli','quality'))
+# difference
+H1_df$diff <- H1_df$within - H1_df$across
+
+H1test <- t.test(H1_df$within, H1_df$across, alternative = 'two.sided', paired = TRUE)
+
+```

### 2022-04-12 analysis/tgispine_analysis.R

@@ -202,6 +202,21 @@ ggsave('COLDplot.png', COLD, device = NULL, path = datPath, width = 8, height = 
 # get mean VAS responses for each condition
 VASresponse <- aggregate(rating~ID*VAS*manipulation*condition*cold_probe, 
                          median, data = df_plot)
+VASIQR <- aggregate(rating~ID*VAS*manipulation*condition*cold_probe, 
+                   IQR, data = df_plot)
+names(VASIQR)[6] <- 'iqr'
+
+VASresponse <- merge(VASresponse,VASIQR)
+
+# identifying labelling conditions
+VASresponse$conditionN[VASresponse$condition == "WIN" & 
+                         VASresponse$cold_probe == "distal"] <- 1
+VASresponse$conditionN[VASresponse$condition == "WIN" & 
+                         VASresponse$cold_probe == "proximal"] <- 2
+VASresponse$conditionN[VASresponse$condition == "ACR" & 
+                         VASresponse$cold_probe == "caudal"] <- 3
+VASresponse$conditionN[VASresponse$condition == "ACR" & 
+                         VASresponse$cold_probe == "rostral"] <- 4
 
 # H1: the effect of dermatome
 VAS_H1 <- aggregate(rating~ID*VAS*manipulation*condition, 
@@ -213,10 +228,10 @@ VAS_H1 <- merge(VAS_H1, VAS_H1_SD)
 # summary stats for participants
 # this is the data we will use to inform the simulation - save
 SUMstats <- summarySEwithin(data = VASresponse, measurevar = 'rating', 
-                            withinvars = c('manipulation','condition','cold_probe'), 
+                            withinvars = c('manipulation','VAS','condition','cold_probe'), 
                             na.rm = TRUE, conf.interval = .95)
 # get min and max median values
-range <- aggregate(rating~manipulation*condition*cold_probe, range, data = VASresponse)
+range <- aggregate(rating~manipulation*VAS*condition*cold_probe, range, data = VASresponse)
 # rename
 names(range)[4] <- 'min'
 names(range)[5] <- 'max'
@@ -224,37 +239,51 @@ names(range)[5] <- 'max'
 SUMstats <- merge(SUMstats, range)
 write.csv(SUMstats, 'pilotSummary.csv', row.names = FALSE)
 
[…]

### 2022-04-19 analysis/tgispine_hypotheses.Rmd
normalising the VAS data by maximum values, then using these data toinform the simulation

@@
 library(dplyr)
+library(truncnorm)
 
@@
 ```{r}
-simulate_subj <- function(subid) {
-trialN = 9
+simulate_subj <- function(subid, llim, ulim) {
+trialN = 10
 conditionN = 8
@@
 # The following intervals and mean can be changed to reflect hypotheses
-# Cold ratigs: simulation
-w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=5)
-w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=5)
-a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:50,1), sd=5)
-a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=5)
-w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:60,1), sd=15)
-w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:60,1), sd=15)
-a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
-a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
+# using normalised data here, so 0-1
+# Cold ratings: simulation
+w_dr_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.05:.40,1), sd=.05)
+w_pc_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.05:.30,1), sd=.05)
+a_dr_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.1:.60,1), sd=.05)
+a_pc_tgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.05:.75,1), sd=.05)
+w_dr_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.95,1), sd=.1)
+w_pc_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.80,1), sd=.1)
+a_dr_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.80,1), sd=.1)
+a_pc_nontgi_cold <- rtruncnorm(trialN, llim, ulim, mean=sample(.25:.95,1), sd=.1)
 
 # Warm ratigs: simulation
-w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:65,1), sd=15)
-w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:70,1), sd=15)
-a_dr_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
-a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
-w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
-w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
-a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
-a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
+w_dr_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.70,1), sd=.20)
+w_pc_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.70,1), sd=.20)
+a_dr_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.95,1), sd=.15)
+a_pc_tgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.10:.60,1), sd=.15)
+w_dr_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
+w_pc_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
+a_dr_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
+a_pc_nontgi_warm <- rtruncnorm(trialN, llim, ulim, mean=sample(.01:.25,1), sd=.05)
 
 # Burning ratings: simulation
- w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:65,1), sd=15)
- w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:60,1), sd=15)
- a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:70,1), sd=15)
- a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:60,1), sd=15)
- w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
- w_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
- a_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
- a_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
+ w_dr_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.80,1), sd=.10)
+ w_pc_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.70,1), sd=.15)
+ a_dr_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.25:.95,1), sd=.10)
+ a_pc_tgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(.20:.80,1), sd=.10)
+ w_dr_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
+ w_pc_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
+ a_dr_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
+ a_pc_nontgi_burn <- rtruncnorm(trialN, llim, ulim, mean=sample(0:.2,1), sd=.05)
 
@@
 for (i in 1:60) {
-  df <- simulate_subj(i)
+  df <- simulate_subj(i, 0, 1)
   df30 <- rbind(df30,df)}
@@
 H1_df$diff <- H1_df$within - H1_df$across
-
+# ttest
 H1test <- t.test(H1_df$within, H1_df$across, alternative = 'two.sided', paired = TRUE)
+# effect size
+H1es <- (mean(H1_df$diff))/(sd(H1_df$diff))
+H1test
+H1es
 

### 2022-04-19 analysis/tgispine_analysis.R

@@ -56,36 +56,56 @@ df_res <- df_res %>%
   mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
          cold_probe = recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
                              'dist' = 'distal', 'prox' = 'proximal'))
-
-##### Individual participant plots ######
-# just include valid trials < 33
-df_res <- df_res[df_res$trial_n < 33 ,]
-# change levels for plotting
+# change levels 
 df_res$cold_probe <- factor(df_res$cold_probe, 
                             levels = c("caudal", "rostral", "distal", "proximal"))
+df_res$ID <- factor(df_res$ID, 
+                    labels = c("1", "2", "3"))
 
-# isolate specific VAS types, then bind by column
+## normalise VAS ratings for each participant
+# just include valid trials < 33
+df_res <- df_res[df_res$trial_n < 33 ,]
+# create frame for new dataframe
+df_norm <- data.frame(matrix(ncol = 20, nrow = 0))
+for (id_idx in 1:3) {
+  tmp <- df_res[df_res$ID == id_idx ,]
+  # find the max value for each VAS ratings
+  max_burn <- max(tmp$VASburning, na.rm = TRUE)
+  max_warm <- max(tmp$VASwarm, na.rm = TRUE)
+  max_cold <- max(tmp$VAScold, na.rm = TRUE)
+  # then normalise all
+  tmp$norm_VASburn <- tmp$VASburning/max_burn
+  tmp$norm_VASwarm <- tmp$VASwarm/max_warm
+  tmp$norm_VAScold <- tmp$VAScold/max_cold
+    
+  # compile all into one data-frame
+  df_norm <- rbind(df_norm, tmp)
+}
+
+##### Individual participant plots ######
+# first need to make app data frame, isolate specific VAS types then bind by column
 # burning
-df_burn <- df_res[, 1:12]
+df_burn <- df_norm[, c(1:12,18)]
 df_burn$VAS <- 'burn'
 names(df_burn)[12] <- 'rating'
+names(df_burn)[13] <- 'norm_rating'
 # warm
-df_warm <- df_res[, c(1:11,13)]
+df_warm <- df_norm[, c(1:11,13,19)]
 df_warm$VAS <- 'warm'
 names(df_warm)[12] <- 'rating'
+names(df_warm)[13] <- 'norm_rating'
 #cold
-df_cold <- df_res[, c(1:11,14)]
[…]

### 2022-04-22 analysis/tgispine_og-plots-exp1.Rmd
adding tgispine analysis code for old data - to use for power calculation

---
title: "TGI plots"
output: html_notebook
---

# Libraries
```{r warning = FALSE}
library(readr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(dplyr)
```

# Import data 
```{r}
path <- '/Users/au706616/Documents/Experiments/SPINALTGI/PreviousData/'
filename <- 'tgi-spine2-data-exp1.csv'
df <- read_delim(file.path(path,filename), ",", col_names = TRUE)
df$dermatome <- factor(df$dermatome, levels = c('within','across'))
df$location_arm <- factor(df$location_arm, levels = c('forearm','upperarm'))
df$location_cold <- factor(df$location_cold, levels = c('dist_caud','prox_rost'))
df$id <- factor(df$id)
df
```

# Summary
```{r}
n_stim <- df %>% count(id = df$id, dermatome = df$dermatome, location_cold = df$location_cold, stim = df$stim) # number of stimuli per condition
df_median <- aggregate(list(cold = df$cold, warm = df$warm, pain = df$pain), by = list(id = df$id, dermatome = df$dermatome, location_cold = df$location_cold), FUN = median)
df_median
```
# Analysis and effect sizes
```{r}
# cold ratings anova

# cold ratings linear mixed model
# warm ratings anova
# warm ratings linear mixed model
```

# Theme for plots 
```{r warning = FALSE}
variance_theme = theme( 
    text = element_text(size = 14),
    #axis.line = element_line(size = 0.7, color = "black"),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title=element_text(size=12), 
    legend.text=element_text(size=12),
    plot.title = element_text(lineheight=.8, face="bold", size = 12),
    panel.border = element_rect(size=1),
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(),
    axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
    legend.key = element_blank(),
    axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
    # axis.text.x = element_text()

# set a figure directory
#figdir<-"~/Dropbox/!Projects/2017_TGI_ginty/figure/"
# dpi resolution
resolution = 600
```
# Figure 1: cold ratings
```{r}
p1 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = cold, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,100))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Blues", direction = 1) +
   theme(legend.position="none")+
   ylab("Cold Ratings")+
   xlab("")
p1

# ggsave(file=paste(figdir, "EXP1_tgi_boxplot_cold.pdf"), width=7, height=7, dpi = resolution, units = "cm")

```

# Figure 2: warm ratings
```{r}
p2 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = warm, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,100))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Reds", direction = -1) +
   theme(legend.position="none")+
   ylab("Warm Ratings")+
   xlab("")
p2

#ggsave(file=paste(figdir, "EXP1_tgi_boxplot_warm.pdf"), width=7, height=7, dpi = resolution, units = "cm")

```
# Figure 3: pain ratings
```{r}
p3 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = pain, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,100))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Purples", direction = -1) +
   theme(legend.position="none")+
   ylab("Pain Ratings")+
   xlab("")
p3

#ggsave(file=paste(figdir, "EXP1_tgi_boxplot_pain.pdf"), width=7, height=7, dpi = resolution, units = "cm")
```

### 2022-04-22 analysis/tgispine_og-plots-exp1.Rmd
running anova to extract information about relative effect size, now to do with lme

@@
 library(dplyr)
+library(ez)
 ```
@@
 df_median
+
+# normalise the vas ratings, then summarise - does this change effect size?
+# create frame for new dataframe
+df_norm <- data.frame(matrix(ncol = 12, nrow = 0))
+# index through each participant
+for (id_idx in 1:nrow(count(df, id))) {
+  id_idx = id_idx+1 # there is no id=1
+  tmp <- df[df$id == id_idx ,]
+
+  # find the max value for each VAS ratings
+  max_cold <- max(tmp$cold, na.rm = TRUE)
+  max_warm <- max(tmp$warm, na.rm = TRUE)
+  max_pain <- max(tmp$pain, na.rm = TRUE)
+  # then normalise all
+  tmp$ncold <- tmp$cold/max_cold
+  tmp$nwarm <- tmp$warm/max_warm
+  tmp$npain <- tmp$pain/max_pain
+
+  # compile all into one data-frame
+  df_norm <- rbind(df_norm, tmp)
+}
+
+# summary
+df_nmedian <- aggregate(list(cold = df_norm$ncold, warm = df_norm$nwarm, pain = df_norm$npain), 
+                        by = list(id = df_norm$id, dermatome = df_norm$dermatome, 
+                                  location_cold = df_norm$location_cold), FUN = median)
 ```
@@
 # cold ratings anova
+cold_anova <- ezANOVA(
+  data = df_nmedian
+  , dv = .(cold)
+  , wid = .(id)
+  , within = .(dermatome, location_cold),
+  return_aov = TRUE,
+  detailed = TRUE
+)
 
@@
 # warm ratings anova
+warm_anova <- ezANOVA(
+  data = df_nmedian
+  , dv = .(warm)
+  , wid = .(id)
+  , within = .(dermatome, location_cold),
+  return_aov = TRUE,
+  detailed = TRUE
+)
+
 # warm ratings linear mixed model
@@
 ```{r}
-p1 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = cold, fill = dermatome))+
+p1 <-ggplot(df_nmedian, aes(x = interaction(location_cold,dermatome), y = cold, fill = dermatome))+
    theme_bw()+
@@
    scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
-   scale_y_continuous(limits = c(0,100))+
+   scale_y_continuous(limits = c(0,1))+
    guides(fill = FALSE)+
@@
 ```{r}
-p2 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = warm, fill = dermatome))+
+p2 <-ggplot(df_nmedian, aes(x = interaction(location_cold,dermatome), y = warm, fill = dermatome))+
    theme_bw()+
@@
 ```{r}
-p3 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = pain, fill = dermatome))+
+p3 <-ggplot(df_nmedian, aes(x = interaction(location_cold,dermatome), y = pain, fill = dermatome))+
    theme_bw()+

### 2022-04-22 VAS_run.m
adding features to VAS, creating audio function (incompl)

@@ -2,7 +2,7 @@
 %% A.G. Mitchell - 25.02.2022
 % Developed from code by Camila Deolindo & Francesca Fardo
 
-% Last edit - 28.03.22
+% Last edit - 22.04.22
 
 % Helpers required: 
 % VAS_loadParams.m; getVasRatings.m; SetupRand.m; ptbConfig.m; 
@@ -103,6 +103,15 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
             % to control when each trial starts - can remove this if VAS questions
             % need to be continuous  
 
+            %% TO DO:
+            % need to change instructions to fit with the different types
+            % of vas ratings - one during peak sensation, one during
+            % sustained TGI (make this clear in instructions, too)
+            % e.g. 'first you will be asked to rate how strong the most
+            % extreme burning sensation is within the first few seconds of
+            % stimulation. Next, you will be asked to rate how cold, warm
+            % or burning the stimulus feels at the specific moment'
+
             DrawFormattedText(scr.win, vars.instructions.StartVas, 'center', 'center', scr.TextColour);
             [~, ~] = Screen('Flip', scr.win);
             KbStrokeWait;
@@ -133,6 +142,12 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
                 results.QuestionType(trial_idx, question_type_idx) = vars.instructions.Question(question_type_idx); 
     
             end 
+
+            %% TO D0
+            % add an audio tone to indicate end of rating for the
+            % experimenter
+            % create psychport audio function
+
             % adding pseudorandomised info from the trial - extracted from
             % counterbalance csv file
             results.trialInfo(trial_idx, 1:6) = procedure(pseudo_idx, 1:6);

### 2022-04-22 helperFunctions/audioPlay.m

@@ -1,0 +1,33 @@
+%function [] = audioPlay(scr, vars)
+%% PsychPortAudio function
+% Plays a simple tone for 200ms through psychotoolbox
+% will need ptgConfig and a paramater script to run as well
+% AG. Mitchell: 22.04.22
+
+% BEEP DETAILS NEED CHANGING FROM THE TUTORIAL CODE - also add to params
+% script?
+% Initialize Sounddriver
+InitializePsychSound(1);
+% Number of channels and Frequency of the sound
+nrchannels = 2;
+freq = 48000;
+% How many times to we wish to play the sound
+repetitions = 1;
+% Length of the beep
+beepLengthSecs = 1;
+% Length of the pause between beeps
+beepPauseTime = 1;
+% Start immediately (0 = immediately)
+startCue = 0;
+
+% Should we wait for the device to really start (1 = yes)
+% INFO: See help PsychPortAudio
+waitForDeviceStart = 1;
+
+pa = PsychPortAudio('Open');
+
+
+
+
+
+%end

### 2022-04-28 analysis/tgispine_lme_power.Rmd
adding new power analysis code for lme

---
title: "TGI-spinal-power"
author: "A.G. Mitchell"
date: '2022-04-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
```

### 2022-04-28 analysis/tgispine_analysis.R

@@ -82,6 +82,9 @@ for (id_idx in 1:3) {
   df_norm <- rbind(df_norm, tmp)
 }
 
+# save new data-frame
+write.csv(df_norm, 'STGI_compiled-data.csv', row.names = FALSE)
+
 ##### Individual participant plots ######
 # first need to make app data frame, isolate specific VAS types then bind by column
 # burning

### 2022-04-28 analysis/tgispine_lme_power.Rmd
starting with simple model

@@
 ```
+
+# Getting data frame and paths
+```{r}
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/'
+setwd(datPath)
+
+df_phs <- read.csv(file.choose())
+```
+
+Create the first model. There is one model for each rating (instead of using rating as a parameter in the model).
+First, going to try this on a very simple model where effect of manipulation (TGI vs. control) will be tested on rating of cold thermode, with subject as random effect
+```{r}
+# Summarise data per rating, per participant
+# although summary not needed!
+sum_pain <- aggregate(VASburning~ID*manipulation*condition*cold_probe, median, data = df_phs)
+sum_warm <- aggregate(VASwarm~ID*manipulation*condition*cold_probe, median, data = df_phs)
+sum_cold <- aggregate(VAScold~ID*manipulation*condition*cold_probe, median, data = df_phs)
+
+# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
+model.cold <- glmer(VAScold ~ manipulation + (1|ID), family = 'poisson', data = df_phs)
+
+```

### 2022-04-28 analysis/tgispine_lme_power.Rmd
creating more complex models for analysis

@@
 df_phs <- read.csv(file.choose())
+
+# need to recode levels for cold_probe to reduce number of levels from 4 to 2
+df_phs$cold_location[df_phs$cold_probe == 'distal'] <- 'dist_rostr' 
+df_phs$cold_location[df_phs$cold_probe == 'rostral'] <- 'dist_rostr'
+df_phs$cold_location[df_phs$cold_probe == 'proximal'] <- 'prox_caud'
+df_phs$cold_location[df_phs$cold_probe == 'caudal'] <- 'prox_caud'
+df_phs$cold_location <- as.factor(df_phs$cold_location)
 ```
@@
 # first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
-model.cold <- glmer(VAScold ~ manipulation + (1|ID), family = 'poisson', data = df_phs)
+model.cold <- lmer(VAScold ~ manipulation + (1+manipulation|ID), data = df_phs)
+summary(model.cold)
+```
+# View the coefficients for each person (should vary, due to random slope model)
+```{r}
+coef(model.cold)
+```
 
+Now make a second, more complicated model where cold ratings are regressed by both manipulation and dermatome position (condition)
+```{r}
+model.cold2 <- lmer(VAScold ~ manipulation + condition + (1+manipulation|ID), 
+                    data = df_phs)
+summary(model.cold2)
 ```
+
+Finally a third model where all predictors are added - manipulation, condition and cold location
+Still just on cold ratings
+```{r}
+model.cold3 <- lmer(VAScold ~ manipulation + condition + cold_location +
+                      (1+manipulation|ID), 
+                    data = df_phs)
+summary(model.cold3)
+```

### 2022-04-28 analysis/tgispine_lme_power.Rmd
pushing all to git

@@
 
+# Running power analysis on simple model
+```{r}
+# extract fixed effects from the model
+tgi_effect <- fixef(model.cold)["manipulationTGI"]
+# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
+# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
+# change the effect size to effect size of interest
+fixef(model.cold)["manipulationTGI"] <- -17
+
+# then run power analysis
+powerSim(model.cold)
+```
+
 Now make a second, more complicated model where cold ratings are regressed by both manipulation and dermatome position (condition)

### 2022-05-03 analysis/tgispine_lme_power.Rmd
running lmm power calculation

--- 2022-04-28 analysis/tgispine_lme_power.Rmd
@@
 
+# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
+df_phs$cold <- df_phs$VAScold/100
+df_phs$warm <- df_phs$VASwarm/100
+df_phs$burn <- df_phs$VASburning/100
+df_phs$ID <- factor(df_phs$ID)
+
 # first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
-model.cold <- lmer(VAScold ~ manipulation + (1+manipulation|ID), data = df_phs)
+model.cold <- lmer(cold ~ manipulation + (1|ID), data = df_phs)
 summary(model.cold)
@@
 coef(model.cold)
+```
+
+# Running power analysis on simple model
+```{r, include = FALSE}
+# add more participants to the model, for simulation
+model.coldN <- extend(model.cold, along ='manipulationTGI', n=10)
+summary(model.coldN)
+# extract fixed effects from the model
+tgi_effect <- fixef(model.coldN)["manipulationTGI"]
+# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
+# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
+# change the effect size to effect size of interest
+fixef(model.coldN)["manipulationTGI"] <- 10
+
+# then run power analysis
+powerSim(model.coldN)
 ```
@@
 ```{r}
-model.cold3 <- lmer(VAScold ~ manipulation + condition + cold_location +
-                      (1+manipulation|ID), 
+model.cold3 <- lmer(cold ~ manipulation + condition + cold_location +
+                      (1|ID), 
                     data = df_phs)

### 2022-05-03 analysis/tgispine_lme_power.Rmd
adding model of interest for cold location, and running power analysis

--- 2022-04-28 analysis/tgispine_lme_power.Rmd
@@
 ```{r}
+# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
+df_phs$cold <- df_phs$VAScold/100
+df_phs$warm <- df_phs$VASwarm/100
+df_phs$burn <- df_phs$VASburning/100
+df_phs$ID <- factor(df_phs$ID)
+
 # Summarise data per rating, per participant
-# although summary not needed!
-sum_pain <- aggregate(VASburning~ID*manipulation*condition*cold_probe, median, data = df_phs)
-sum_warm <- aggregate(VASwarm~ID*manipulation*condition*cold_probe, median, data = df_phs)
-sum_cold <- aggregate(VAScold~ID*manipulation*condition*cold_probe, median, data = df_phs)
+sum_burn <- aggregate(burn~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
+sum_warm <- aggregate(warm~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
+sum_cold <- aggregate(cold~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
+# then compile all data again
+sum_burn$VAS = 'burn'
+names(sum_burn)[6] <- 'rating'
+sum_warm$VAS = 'warm'
+names(sum_warm)[6] <- 'rating'
+sum_cold$VAS = 'cold'
+names(sum_cold)[6] <- 'rating'
+df_sum <- rbind(sum_cold, sum_warm)
+df_sum <- rbind(df_sum, sum_burn)
 
 # first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
-model.cold <- lmer(VAScold ~ manipulation + (1+manipulation|ID), data = df_phs)
+model.cold <- lmer(rating ~ manipulation + condition + cold_location +
+                     (1|ID) + (1|procedure), 
+                   data = df_sum[df_sum$VAS == 'cold' ,])
 summary(model.cold)
@@
 coef(model.cold)
+```
+
+Create a model with more data points per variable, to extract more power
+# First, let's try N = 100
+```{r, include = FALSE}
+# add more participants to the model, for simulation
+model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=100)
+summary(model.coldN)
+# check that number of data points per variable does = 30
+dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.coldN))
+print(dat_model)
+```
+
+# Run power analysis!
+````{r}
+# extract fixed effects from the model - take the lowest effect size from the model
+tgi_effect <- fixef(model.coldN)["cold_locationprox_caud"]
+# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
+# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
+# change the effect size to effect size of interest
+fixef(model.cold)["manipulationTGI"] <- tgi_effect
+
+# then run power analysis
+powerSim(model.cold)
+```
+
+Now to run a power curve on the data to find out the optimal number of participants needed for the effect of interest
+```{r}
+# let's see if this works because it hasn't before
+pc.cold <- powerCurve(model.coldN)
+print(pc.cold)
 ```

### 2022-05-03 analysis/tgispine_lme_power.Rmd
formalising power analysis to determine how many observations per variable combination is requried

@@
 Create a model with more data points per variable, to extract more power
-# First, let's try N = 100
-```{r, include = FALSE}
-# add more participants to the model, for simulation
-model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=100)
+```{r}
+# First, let's try to add 30 observations per variable combination, which would mean N = 30
+model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
 summary(model.coldN)
@@
 # Run power analysis!
-````{r}
+````{r, results = 'hide'}
 # extract fixed effects from the model - take the lowest effect size from the model
-tgi_effect <- fixef(model.coldN)["cold_locationprox_caud"]
+tgi_effect <- fixef(model.coldN)["manipulationTGI"]
+cond_effect <- fixef(model.coldN)["conditionwithin"]
+cold_loc_effect <- fixef(model.coldN)["cold_locationprox_caud"]
 # need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
@@
 # change the effect size to effect size of interest
-fixef(model.cold)["manipulationTGI"] <- tgi_effect
+fixef(model.coldN)["cold_locationprox_caud"] <- cold_loc_effect
 
 # then run power analysis
-powerSim(model.cold)
+pwr.cold <- powerSim(model.coldN)
+print(pwr.cold)
 ```
@@
 ```{r}
-# let's see if this works because it hasn't before
-pc.cold <- powerCurve(model.coldN)
+# can run a power curve to determine the point of trade off between N observations and power
+pc.cold <- powerCurve(model.coldN, within='manipulation+condition+cold_location', 
+                      breaks= seq(0, 30, by = 3))
 print(pc.cold)
@@
 
-Now make a second, more complicated model where cold ratings are regressed by both manipulation and dermatome position (condition)
+# Plot power curve!
 ```{r}
-model.cold2 <- lmer(VAScold ~ manipulation + condition + (1+manipulation|ID), 
-                    data = df_phs)
-summary(model.cold2)
+
 ```
-
-Finally a third model where all predictors are added - manipulation, condition and cold location
-Still just on cold ratings
-```{r}
-model.cold3 <- lmer(cold ~ manipulation + condition + cold_location +
-                      (1|ID), 
-                    data = df_phs)
-summary(model.cold3)
-```

### 2022-05-03 analysis/tgispine_lme_power.Rmd
pushing to git
doing the same for warm - model, power & power curve

@@
 pc.cold <- powerCurve(model.coldN, within='manipulation+condition+cold_location', 
-                      breaks= seq(0, 30, by = 3))
+                      breaks= seq(1, 30, by = 3))
 print(pc.cold)
@@
 ```{r}
+plot(pc.cold) # a good visualisation :)
+```
 
+Now let's do the same for warm!
+# Warm model
+```{r}
+model.warm <- lmer(rating ~ manipulation + condition + cold_location +
+                     (1|ID),
+                   data = df_sum[df_sum$VAS == 'warm' ,])
+summary(model.warm)
 ```
+
+# Extend the model observations to n = 50, and extract smallest effect size of interest
+```{r}
+# using n050 here as expecting smaller effect sizes
+model.warmN <- extend(model.warm, within = 'manipulation+condition+cold_location', n=50)
+# extracting effect sizes from the extended model
+tgi_effect <- fixef(model.warmN)["manipulationTGI"]
+cond_effect <- fixef(model.warmN)["conditionwithin"]
+cold_loc_effect <- fixef(model.warmN)["cold_locationprox_caud"]
+# add smallest effect size - same as cold model
+fixef(model.coldN)["cold_locationprox_caud"] <- cold_loc_effect
+
+# then run power analysis
+pwr.warm <- powerSim(model.warmN)
+print(pwr.warm)
+```
+# Run a power curve on these data with n = 50
+```{r}
+# can run a power curve to determine the point of trade off between N observations and power
+pc.warm <- powerCurve(model.warmN, within='manipulation+condition+cold_location', 
+                      breaks= seq(1, 50, by = 5))
+print(pc.warm)
+```

### 2022-05-09 analysis/tgispine_lme_power.Rmd
adding model summary to code

@@
 library(simr)
+library(broom)
+library(brms)
+library(modelsummary)
+library(tibble)
+
+set.seed(1234)  # Make everything reproducible
+
+# Define the goodness-of-fit stats to include in modelsummary()
+gof_stuff <- tribble(
+  ~raw, ~clean, ~fmt,
+  "nobs", "N", 0,
+  "r.squared", "R²", 3
+)
 ```
@@
 # first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
+# first the simplest model
 model.cold <- lmer(rating ~ manipulation + condition + cold_location +
+                     (1|ID), 
+                   data = df_sum[df_sum$VAS == 'cold' ,])
+# then adding procedure as a fiexed effect
+model.cold2 <- lmer(rating ~ manipulation + condition + cold_location +
                      (1|ID) + (1|procedure), 
                    data = df_sum[df_sum$VAS == 'cold' ,])
-summary(model.cold)
+# then modelling slope of the subjects
+model.cold3 <- lmer(rating ~ manipulation + condition + cold_location +
+                     (1+manipulation|ID) + (1|procedure), 
+                   data = df_sum[df_sum$VAS == 'cold' ,])
+
+# summarise all 3 models
+modelsummary(list(model.cold, model.cold2, model.cold3),
+             gof_map = gof_stuff)
 ```
 # View the coefficients for each person (should vary, due to random slope model)
-```{r}
-coef(model.cold)
-```
 
-Create a model with more data points per variable, to extract more power
+# Run power analysis - to do this use the simplest model (model.cold)
+# First, Create a model with more data points per variable, to extract more power
 ```{r}

### 2022-05-09 analysis/tgispine_lme_power.Rmd
zero inflated beta regression models for cold and warm

@@
 library(tibble)
+library(DHARMa)
+library(glmmTMB)
 
@@
 ```
+Need to change this and create two cold models - one with zero inflated and one without
+Also need to check Bayesian
+- Check out Jesper's code
 
@@
 df_sum <- rbind(df_sum, sum_burn)
+```
 
-# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
-# first the simplest model
-model.cold <- lmer(rating ~ manipulation + condition + cold_location +
-                     (1|ID), 
-                   data = df_sum[df_sum$VAS == 'cold' ,])
-# then adding procedure as a fiexed effect
-model.cold2 <- lmer(rating ~ manipulation + condition + cold_location +
-                     (1|ID) + (1|procedure), 
-                   data = df_sum[df_sum$VAS == 'cold' ,])
-# then modelling slope of the subjects
-model.cold3 <- lmer(rating ~ manipulation + condition + cold_location +
-                     (1+manipulation|ID) + (1|procedure), 
-                   data = df_sum[df_sum$VAS == 'cold' ,])
+# Now to model effects! Try a zero inflated regression model
+```{r}
+# First model cold VAS
+model.cold = glmmTMB::glmmTMB(rating ~ manipulation + condition + cold_location + (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = df_phs$warm)
+# then model warm VAS
+```
+# Look at model assumptions
+```{r}
+model.cold.assmup <- simulateResiduals(model.cold)
+plot(model.cold.assmup)
+```
 
-# summarise all 3 models
-modelsummary(list(model.cold, model.cold2, model.cold3),
-             gof_map = gof_stuff)
-```
 # View the coefficients for each person (should vary, due to random slope model)
@@
 ```{r}
-model.warm <- lmer(rating ~ manipulation + condition + cold_location +
+model.warm <- lmerTest::lmer(rating ~ manipulation + condition + cold_location +
                      (1|ID),

### 2022-05-09 analysis/tgispine_lme_power.Rmd
preparing data for beta regression

@@
 library(glmmTMB)
+library(reshape2)
 
@@
 )
+
+# setting working directory
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
+knitr::opts_knit$set(root.dir = datPath)
 ```
-Need to change this and create two cold models - one with zero inflated and one without
-Also need to check Bayesian
-- Check out Jesper's code
 
-# Getting data frame and paths
+# Getting data and reformatting to fit model
 ```{r}
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/'
-setwd(datPath)
-
-df_phs <- read.csv(file.choose())
+df <- read.csv('STGI_compiled-data.csv')
 
 # need to recode levels for cold_probe to reduce number of levels from 4 to 2
-df_phs$cold_location[df_phs$cold_probe == 'distal'] <- 'dist_rostr' 
-df_phs$cold_location[df_phs$cold_probe == 'rostral'] <- 'dist_rostr'
-df_phs$cold_location[df_phs$cold_probe == 'proximal'] <- 'prox_caud'
-df_phs$cold_location[df_phs$cold_probe == 'caudal'] <- 'prox_caud'
-df_phs$cold_location <- as.factor(df_phs$cold_location)
-```
+df$cold_location[df$cold_probe == 'distal'] <- 'dist_rostr' 
+df$cold_location[df$cold_probe == 'rostral'] <- 'dist_rostr'
+df$cold_location[df$cold_probe == 'proximal'] <- 'prox_caud'
+df$cold_location[df$cold_probe == 'caudal'] <- 'prox_caud'
+df$cold_location <- as.factor(df$cold_location)
 
-Create the first model. There is one model for each rating (instead of using rating as a parameter in the model).
-First, going to try this on a very simple model where effect of manipulation (TGI vs. control) will be tested on rating of cold thermode, with subject as random effect
-```{r}
+# reshape data so that there is one rating column per participant, with a VAS column = type of rating
+df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburning"), 
+                        id.vars=c("ID","trial_n","manipulation","procedure",
+                                  "trial_type","arm","condition","cold_location"),
+             variable.name = 'VAS', value.name = 'rating')
+# rename the VAS ratings
+df_VAS <- df_VAS %>% 
+  mutate(VAS = revalue(VAS, c("VAScold" = "cold",
+                                    "VASwarm" = "warm",
+                                    "VASburning" = "burning")))
+
+# to run zero inflated regressions need to make sure no values = 100, as cannot model them, so simply minus a very small fraction from those values
+df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$beta-0.0001, df_VAS$beta <- df_VAS$rating)
+
 # transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
-df_phs$cold <- df_phs$VAScold/100
-df_phs$warm <- df_phs$VASwarm/100
-df_phs$burn <- df_phs$VASburning/100
-df_phs$ID <- factor(df_phs$ID)
+df_VAS$beta <- df_VAS$beta/100
+df_VAS$ID <- factor(df_VAS$ID)
 
 # Summarise data per rating, per participant
-sum_burn <- aggregate(burn~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
-sum_warm <- aggregate(warm~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
-sum_cold <- aggregate(cold~ID*manipulation*condition*cold_location*procedure, median, data = df_phs)
-# then compile all data again
-sum_burn$VAS = 'burn'
-names(sum_burn)[6] <- 'rating'
-sum_warm$VAS = 'warm'
-names(sum_warm)[6] <- 'rating'
-sum_cold$VAS = 'cold'
-names(sum_cold)[6] <- 'rating'
-df_sum <- rbind(sum_cold, sum_warm)
-df_sum <- rbind(df_sum, sum_burn)
+df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
+                    median, data = df)
 ```
@@
 # First model cold VAS
-model.cold = glmmTMB::glmmTMB(rating ~ manipulation + condition + cold_location + (1|ID),
+model.cold = glmmTMB::glmmTMB(cold ~ manipulation + condition + cold_location + (1|ID),
                       family = glmmTMB::beta_family(),
                       ziformula = ~1+manipulation,
-                      data = df_phs$warm)
+                      data = df)
+summary(model.cold)
 # then model warm VAS

### 2022-05-09 analysis/tgispine_lme_power.Rmd
creating warm and cold zero inflated models

@@
 ```{r}
+# import compiled data
 df <- read.csv('STGI_compiled-data.csv')
@@
 # First model cold VAS
-model.cold = glmmTMB::glmmTMB(cold ~ manipulation + condition + cold_location + (1|ID),
+model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
+                                (1|ID),
                       family = glmmTMB::beta_family(),
                       ziformula = ~1+manipulation,
-                      data = df)
+                      data = df_VAS[df_VAS$VAS == 'cold' ,])
+# then model warm VAS
+model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = df_VAS[df_VAS$VAS == 'warm' ,])
+# model summaries
 summary(model.cold)
-# then model warm VAS
+summary(model.warm)
 ```
@@
 ```{r}
+# cold assumption
 model.cold.assmup <- simulateResiduals(model.cold)
@@
 
-# View the coefficients for each person (should vary, due to random slope model)
+```{r}
+# warm assumption
+model.warm.assump <- simulateResiduals(model.warm)
+plot(model.warm.assump)
+```
 

### 2022-05-09 analysis/tgispine_lme_power.Rmd
trying and failing to run power analysis, time to rest

@@
 
-# Run power analysis - to do this use the simplest model (model.cold)
-# First, Create a model with more data points per variable, to extract more power
+Cold model power analysis
+# Run power analyses!!
+# Cold first, then warm
+# Create a model with more data points per variable, to extract more power
 ```{r}
 # First, let's try to add 30 observations per variable combination, which would mean N = 30
-model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
-summary(model.coldN)
+model.cold.ex <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
+summary(model.cold.ex)
 # check that number of data points per variable does = 30
-dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.coldN))
+dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.cold.ex))
 print(dat_model)
-```
 
-# Run power analysis!
-````{r, results = 'hide'}
-# extract fixed effects from the model - take the lowest effect size from the model
-tgi_effect <- fixef(model.coldN)["manipulationTGI"]
-cond_effect <- fixef(model.coldN)["conditionwithin"]
-cold_loc_effect <- fixef(model.coldN)["cold_locationprox_caud"]
-# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
-# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
-# change the effect size to effect size of interest
-fixef(model.coldN)["cold_locationprox_caud"] <- cold_loc_effect
+# extract relevant effect sizes
+tgi_effect <- fixef(model.cold.ex)["manipulationTGI"]
+cond_effect <- fixef(model.cold.ex)["conditionwithin"]
+cold_loc_effect <- fixef(model.cold.ex)["cold_locationprox_caud"]
 
-# then run power analysis
-pwr.cold <- powerSim(model.coldN)
-print(pwr.cold)
-```
+# power analysis - using smallest effect size
+fixef(model.cold.ex)["manipulationTGI"] <- cold_loc_effect
+pwr.warm <- powerSim(model.warmN)
+print(pwr.warm)
 
-Now to run a power curve on the data to find out the optimal number of participants needed for the effect of interest
-```{r}
+# power curve
 # can run a power curve to determine the point of trade off between N observations and power
-pc.cold <- powerCurve(model.coldN, within='manipulation+condition+cold_location', 
+pc.cold <- powerCurve(model.cold.ex, within='manipulation+condition+cold_location', 
                       breaks= seq(1, 30, by = 3))

### 2022-05-10 analysis/tgispine_lme_power.Rmd
creating density plots

@@
 library(reshape2)
+library(tidyverse)
+library(plyr)
 
@@
 df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
-                    median, data = df)
+                    median, data = df_VAS)
+```
+
+# Plotting data distributions to see what kind of model family is required
+```{r}
+ggplot(data = df_VAS) +
+  geom_density(aes(beta, fill = manipulation), alpha = .5) +
+  facet_wrap(~VAS)
 ```
@@
                                 (1|ID),
-                      family = glmmTMB::beta_family(),
+                      family = glmmTMB::betabinomial(),
                       ziformula = ~1+manipulation,
@@
 # cold assumption
-model.cold.assmup <- simulateResiduals(model.cold)
+model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
 plot(model.cold.assmup)
@@
 # warm assumption
-model.warm.assump <- simulateResiduals(model.warm)
+model.warm.assump <- simulateResiduals(model.warm, n = 1000)
 plot(model.warm.assump)

### 2022-05-10 analysis/tgispine_lme_power.Rmd
trying (& failing) to get the simr to work with glmm

@@
                       ziformula = ~1+manipulation,
-                      data = df_VAS[df_VAS$VAS == 'cold' ,])
+                      data = df_VAS[df_VAS$VAS == 'cold' ,],
+                      na.action = na.omit)
 # then model warm VAS
@@
                                 (1|ID),
-                      family = glmmTMB::betabinomial(),
+                      family = glmmTMB::beta_family(),
                       ziformula = ~1+manipulation,
@@
 # extract relevant effect sizes
-tgi_effect <- fixef(model.cold.ex)["manipulationTGI"]
-cond_effect <- fixef(model.cold.ex)["conditionwithin"]
-cold_loc_effect <- fixef(model.cold.ex)["cold_locationprox_caud"]
+tgi_effect <- fixef(model.cold.ex)[['cond']][['manipulationTGI']]
+cond_effect <- fixef(model.cold.ex)[['cond']][['conditionwithin']]
+cold_loc_effect <- fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']]
 
 # power analysis - using smallest effect size
-fixef(model.cold.ex)["manipulationTGI"] <- cold_loc_effect
-pwr.warm <- powerSim(model.warmN)
-print(pwr.warm)
+fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- .2
+pwr.cold <- powerSim(model.cold.ex)
+print(pwr.cold)
 

### 2022-05-11 VAS_calibration.m
adding calibration code to extract TGI temperatures

@@ -1,0 +1,151 @@
+%% VAS rating main script
+%% A.G. Mitchell - 25.02.2022
+% Developed from code by Camila Deolindo & Francesca Fardo
+
+% Last edit - 22.04.22
+
+% Helpers required: 
+% VAS_loadParams.m; getVasRatings.m; SetupRand.m; ptbConfig.m; 
+% openScreen.m; StimCount.m; slideScale.m; drawFixation.m;
+% angle2pix.m
+% probably more...            
+        
+
+%% Load parameters
+clear all % clearing all old data
+
+% Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
+vars.control.devFlag  = 1; 
+
+VAS_loadParams;
+addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
+% path to save data to - should be changed depending on laptop (VAS_loadParams.m)
+datPath = vars.filename.path;
+runPath = pwd;
+
+% Reseed the random-number generator
+SetupRand;
+
+%% Psychtoolbox settings
+PsychDefaultSetup(2);
+ListenChar(2); %disable keypress
+Screen('Preference', 'SkipSyncTests', 2);
+scr.ViewDist = vars.ViewDist; % viewing distance
+[scr, keys] = ptbConfig(scr, vars);
+
+%% Prepare to start
+%  try
+% Set text size, dependent on screen resolution
+if any(logical(scr.winRect(:)>3000))       % 4K resolution
+    scr.TextSize = 65;
+else
+    scr.TextSize = vars.instructions.textSize;
+end
+% Check if window is already open (if not, open screen window) 
+[scr]=openScreen(scr);
+
+% Dummy calls to prevent delays
+vars.control.RunSuccessfull = 0;
+vars.control.Aborted = 0;
+vars.control.Error = 0;
+vars.control.thisTrial = 1;
+vars.control.abortFlag = 0;
+[~, ~, keys.KeyCode] = KbCheck;
+
+%% Start screen
+Screen('TextSize', scr.win, scr.TextSize);
+DrawFormattedText(scr.win, vars.instructions.StartScreen, 'center', 'center', scr.TextColour);
+[~, ~] = Screen('Flip', scr.win);
+KbStrokeWait;
+
+%% Preparing to present VAS
+    
+trial_idx = 0 ; %create a seperate index for individual trials
+
+for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
[…]

### 2022-05-11 VAS_loadParams.m
creating basic code framework

@@ -22,6 +22,7 @@ vars.ViewDist = 56;
 vars.task.NTrialReps         = 3; %number of repeat trials per condition (i.e. thermode in right place)
 vars.task.NBlocksTotal       = 1; %Total number of blocks per pseudorandom procedure (n x 16 trials)
 vars.task.NTrialsChange      = 3; % The frequency of thermode change per trial (if thermode is changed every trial, set to 1)
+vars.task.CalibReps          = 15; % set to the max number of trials required to calibrate temperature for TGI, atm this is a guess
 
 %Times
 %vars.task.jitter             = randInRange(1,3,[1,vars.task.NTrialsTotal]); % time between the beginning of the trial and the beginning of the stimulation

### 2022-05-11 VAS_calibration.m
got loop to break if burning rating is above 15

@@ -73,12 +73,6 @@ vars.control.thisTrial = 1;
 vars.control.abortFlag = 0;
 [~, ~, keys.KeyCode] = KbCheck;
 
-%% Start screen
-Screen('TextSize', scr.win, scr.TextSize);
-DrawFormattedText(scr.win, vars.instructions.StartScreen, 'center', 'center', scr.TextColour);
-[~, ~] = Screen('Flip', scr.win);
-KbStrokeWait;
-
 %% Preparing to present VAS  
 trial_idx = 0 ; %create a seperate index for individual trials
 for rep_idx = 1:vars.task.CalibReps %loop through trial repeats, 3 trials per thermode location
@@ -105,22 +99,22 @@ for rep_idx = 1:vars.task.CalibReps %loop through trial repeats, 3 trials per th
             getVasRatings(keys, scr, vars, initial_question);  
     results.QuestionType(trial_idx, initial_question) = vars.instructions.Question(initial_question); 
 
-    % A mouse click if participants feel burning - breaks the loop
-    [x, y, buttons] = GetMouse(scr.win);
-    if any(buttons)
-        sca;
-        break
-    end
-
     % Wait a small amount of time (1s) after the first vas rating, to
     % divide up time
-    WaitSecs(1)
+    WaitSecs(.5)
 
     results.trialInfo(trial_idx, 1) = trial_idx;
     if vars.control.devFlag == 0
         results.trialInfo.coolTemp(trial_idx) = vars.filename.ID(4);
         results.trialInfo.warmTemp(trial_idx) = vars.filename.ID(5);
-    end            
+    end    
+
+    % break the loop if VAS rating is above 15
+    if results.vasResponse(trial_idx, initial_question) > 15
+        sca;
+        break
+    end
+        
 end
 
 sca; % close VAS

### 2022-05-11 VAS_loadParams.m

@@ -53,6 +53,9 @@ vars.instructions.StartScreen = ['For each trial, you will experience thermal st
 
 vars.instructions.StartVas = 'When instructed by the experimenter, press a key to start rating';
 
+vas.instructions.Calib = ['At this stage, you simply need to rate how the stimulus is BURNING.\n\n' ...
+    'Please be honest, and provide any feedback about your experience to the experimenter.'];
+
 vars.instructions.Question = {'At the moment, what is the strongest BURNING sensation you are feeling?',...
                                'At the moment, how much is the stimulus BURNING?',...
                                'At the moment, how WARM is the stimulus?',...

### 2022-05-11 VAS_calibration.m
changing so procedures 5-8 can also be coded

@@ -109,8 +109,9 @@ for rep_idx = 1:vars.task.CalibReps %loop through trial repeats, 3 trials per th
         results.trialInfo.warmTemp(trial_idx) = vars.filename.ID(5);
     end    
 
-    % break the loop if VAS rating is above 15
-    if results.vasResponse(trial_idx, initial_question) > 15
+    % break the loop if VAS rating is above 10, then participant is
+    % experiencing TGI
+    if results.vasResponse(trial_idx, initial_question) > 10
         sca;
         break
     end

### 2022-05-12 VAS_calibration.m
piloting changes

@@ -15,7 +15,7 @@
 clear all % clearing all old data
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
-vars.control.devFlag  = 1; 
+vars.control.devFlag  = 0; 
 
 VAS_loadParams;
 addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
@@ -32,7 +32,7 @@ if vars.control.devFlag == 0 %only run if not debugging
     % task is either TGI or control, participant number is a string of 4 digits
     % (e.g. 0001), counterbalance procedure is index 1,2,3 or 4
     vars.filename.calib = string(inputdlg({'Participant number:', 'Task:'},...
-        'Participant information', [1 30], [1 10]));
+        'Participant information', [1 30; 1 10]));
     
     % make participant folder in correct path
     ppPath = fullfile(datPath, vars.filename.calib(1));
@@ -43,8 +43,8 @@ if vars.control.devFlag == 0 %only run if not debugging
     vars.filename.date = datestr(now, formatout);
     
     % saving file name with participantID_pseudorandomProcedure_Date
-    matName = sprintf('%s_%s_%s_CALIB_spinalTGI.mat', vars.filename.calib(1,2), vars.filename.date);
-    csv_ratName = sprintf('%s_%s_%s_CALIB_spinalTGI.csv', vars.filename.calib(1,2), vars.filename.date);
+    matName = sprintf('%s_%s_%s_CALIB_spinalTGI.mat', vars.filename.calib(1,:), vars.filename.date);
+    csv_ratName = sprintf('%s_%s_%s_CALIB_spinalTGI.csv', vars.filename.calib(1,:), vars.filename.date);
 end
 
 %% Psychtoolbox settings
@@ -103,11 +103,7 @@ for rep_idx = 1:vars.task.CalibReps %loop through trial repeats, 3 trials per th
     % divide up time
     WaitSecs(.5)
 
-    results.trialInfo(trial_idx, 1) = trial_idx;
-    if vars.control.devFlag == 0
-        results.trialInfo.coolTemp(trial_idx) = vars.filename.ID(4);
-        results.trialInfo.warmTemp(trial_idx) = vars.filename.ID(5);
-    end    
+    results.trialInfo(trial_idx, 1) = trial_idx;  
 
     % break the loop if VAS rating is above 10, then participant is
     % experiencing TGI

### 2022-05-12 VAS_loadParams.m

@@ -20,7 +20,7 @@ vars.ViewDist = 56;
 
 %Trials
 vars.task.NTrialReps         = 3; %number of repeat trials per condition (i.e. thermode in right place)
-vars.task.NBlocksTotal       = 1; %Total number of blocks per pseudorandom procedure (n x 16 trials)
+vars.task.NBlocksTotal       = 2; %Total number of blocks per pseudorandom procedure (n x 16 trials)
 vars.task.NTrialsChange      = 3; % The frequency of thermode change per trial (if thermode is changed every trial, set to 1)
 vars.task.CalibReps          = 15; % set to the max number of trials required to calibrate temperature for TGI, atm this is a guess
 
@@ -38,7 +38,7 @@ vars.task.device = 'keyboard';
 vars.task.randomise = readtable('counterbalancing.csv'); 
 
 %% Instructions
-vars.instructions.textSize = 32;
+vars.instructions.textSize = 28;
 
 vars.instructions.StartScreen = ['For each trial, you will experience thermal stimulation on your skin.\n\n' ...
     'At the beginning of the trial, please rate the most intense burning sensation you are experiencing from\n' ...

### 2022-05-12 analysis/tgispine_analysis.R
adapting analysis for new data formats and analysing new pilot

@@ -16,9 +16,9 @@ setwd(datPath)
 filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
 # empty dataframes for data
 ## with new data trials file will have changed to include temperature coding!
-df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
-df_VAS <- read.csv(text='VASburning,VASwarm,VAScold,trial_n,ID,manipulation')
-df_RT <- read.csv(text='RTburning,RTwarm,RTcold,trial_n,ID,manipulation')
+df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
+df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
+df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')
 
 ##### Data compiling #####
 # trial files
@@ -33,7 +33,7 @@ for (file in filenames){
   # VAS response files
   if (isTRUE(substr(basename(file), 22, 29)=="Response")){
     tmp <- read.csv(file, header = FALSE)
-    colnames(tmp) <- c('VASburning','VASwarm','VAScold','trial_n')
+    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
     tmp$ID <- substr(basename(file), 1, 4)
     tmp$manipulation <- substr(basename(file), 8, 10)
     df_VAS <- rbind(df_VAS, tmp)
@@ -41,7 +41,7 @@ for (file in filenames){
   # VAS RT files
   if (isTRUE(substr(basename(file), 22, 26)=="RespT")){
     tmp <- read.csv(file, header = FALSE)
-    colnames(tmp) <- c('RTburning','RTwarm','RTcold','trial_n')
+    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
     tmp$ID <- substr(basename(file), 1, 4)
     tmp$manipulation <- substr(basename(file), 8, 10)
     df_RT <- rbind(df_RT, tmp)
@@ -60,23 +60,25 @@ df_res <- df_res %>%
 df_res$cold_probe <- factor(df_res$cold_probe, 
[…]

### 2022-05-12 analysis/tgispine_hypotheses.Rmd
simulating models with new data

@@
 simulate_subj <- function(subid, llim, ulim) {
-trialN = 10
+trialN = 12
 conditionN = 8
@@
 
-# running inferential stats on simulated data - to gain idea of effect size
+# run ZOIB regression on the simulated data - and extract power from chosen effect sizes
 
 ```{r}
-library(ez)
-library(psychReport)
-# isolate just TGI for purposes of determining effect size
-df_tgi <- df_subj[df_subj$stimuli == 'tgi' ,]
+# cold ratings
+model.cold = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
+                                (1|id),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+stimuli,
+                      data = df30[df30$quality == 'cold' ,],
+                      na.action = na.omit)
+# warm ratings
+model.warm = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
+                                (1|id),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+stimuli,
+                      data = df30[df30$quality == 'warm' ,],
+                      na.action = na.omit)
 
-# burning VAS
-burn_anova <- ezANOVA(
-  data = df_tgi[df_tgi$quality == 'burn' ,]
-  , dv = .(x)
-  , wid = .(id)
-  , within = .(dermatome, cold_location),
-  return_aov = TRUE,
-  detailed = TRUE
-)
-
-# warm VAS
-warm_anova <- ezANOVA(
-  data = df_tgi[df_tgi$quality == 'warm' ,]
-  , dv = .(x)
-  , wid = .(id)
-  , within = .(dermatome, cold_location),
-  return_aov = TRUE,
-  detailed = TRUE
-)
-
-# cold VAS
-cold_anova <- ezANOVA(
-  data = df_tgi[df_tgi$quality == 'cold' ,]
-  , dv = .(x)
-  , wid = .(id)
-  , within = .(dermatome, cold_location),
-  return_aov = TRUE,
-  detailed = TRUE
-)
-
-## t-test
-# create seperate data-frames to allow for comparison
-within <- df_subj[df_subj$dermatome=='within' ,]
-across <- df_subj[df_subj$dermatome=='across' ,]
-proxc <- within[within$cold_location== 'prox_caud' ,]
-distc <- within[within$cold_location=='dist_rostr' ,]
-caudc <- across[across$cold_location=='prox_caud' ,]
-rostc <- across[across$cold_location=='dist_rostr' ,]
-
-## H1
-names(within)[7] <- 'within'
-names(across)[7] <- 'across'
-# merge
-H1_df <- merge(within, across, by = c('id','cold_location','stimuli','quality'))
-# difference
-H1_df$diff <- H1_df$within - H1_df$across
-# ttest
-H1test <- t.test(H1_df$within, H1_df$across, alternative = 'two.sided', paired = TRUE)
-# effect size
-H1es <- (mean(H1_df$diff))/(sd(H1_df$diff))
-H1test
-H1es
+# model summaries
+summary(model.cold)
+summary(model.warm)
 

### 2022-05-12 analysis/tgispine_lme_power.Rmd
simulating models with new data

@@
 # reshape data so that there is one rating column per participant, with a VAS column = type of rating
-df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburning"), 
-                        id.vars=c("ID","trial_n","manipulation","procedure",
+df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburn"), 
+                        id.vars=c("ID","trial_n","manipulation","order",
                                   "trial_type","arm","condition","cold_location"),
@@
                                     "VASwarm" = "warm",
-                                    "VASburning" = "burning")))
+                                    "VASburn" = "burn")))
 
@@
 # Summarise data per rating, per participant
-df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
+df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*order*VAS, 
                     median, data = df_VAS)
@@
 # power analysis - using smallest effect size
-fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- .2
+fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
 pwr.cold <- powerSim(model.cold.ex)

### 2022-05-12 analysis/tgispine_analysis.R

@@ -351,46 +351,48 @@ ggsave('H1plot.png', H1, device = NULL, path = datPath, width = 9, height = 4.5)
    
 ##### Hypothesis 2 plotting #####
 # isolating across
-VAS_H2 <- VASresponse[VASresponse$condition == 'across' ,]
+VAS_H2 <- VASresponse[VASresponse$condition == 'within' ,]
 
 # plotting - TGI
-ggplot(VAS_H2[VAS_H2$manipulation=='TGI' ,], 
-       aes(cold_probe, norm_rating, group = ID, colour = VAS)) +
-  geom_point(position = position_dodge(.3)) +
-  geom_errorbar(aes(ymin=norm_rating-std, ymax=norm_rating+std), width=.2,
-                position=position_dodge(.3)) +
+H2 <- ggplot(VAS_H2, aes(cold_probe, norm_rating, group = ID, colour = VAS)) +
+  geom_point(data = VAS_H2 %>% 
+               filter(manipulation == 'TGI'), size = 2.5, position = position_dodge(.3)) +
+  geom_line(data = VAS_H2 %>% 
+              filter(manipulation == 'TGI'), aes(group = ID), position = position_dodge(.3)) +
+  geom_point(data = VAS_H2 %>% 
+               filter(manipulation == 'CNT'), size = 2.5, position = position_dodge(.3),
+             alpha = .5) +
+  geom_line(data = VAS_H2 %>% 
+              filter(manipulation == 'CNT'), aes(group = ID), position = position_dodge(.3),
+            alpha = .5) +
   facet_wrap(~VAS) +
   scale_color_manual(values = c(blues[4],reds[4],purps[5])) +
-  labs(title = 'TGI', x = '', y = 'VAS Rating') +
+  labs(title = 'Within Dermatome', x = '', y = 'VAS Rating') +
   #lims(y = c(-20,100)) +
   theme_classic() +
   theme(legend.position = 'none')
 
-# non TGI
-ggplot(VAS_H2[VAS_H2$manipulation=='CNT' ,], 
-       aes(cold_probe, rating, group = ID, colour = VAS)) +
-  geom_point(position = position_dodge(.3)) +
+##### Hypothesis 3 plotting #####
+# isolating across
+VAS_H3 <- VASresponse[VASresponse$condition == 'across' ,]
+
+# plotting - TGI
[…]

### 2022-05-16 analysis/tgispine_lme_power.Rmd
adding beta power code template to simulate power

@@
   geom_density(aes(beta, fill = manipulation), alpha = .5) +
-  facet_wrap(~VAS)
+  facet_wrap(~VAS) +
+  theme_classic()
 ```

### 2022-05-16 analysis/beta_power.R

@@ -1,0 +1,95 @@
+## Beta Regression Power Analysis
+## Simulations to assess statistical power given alpha, n, effect size
+## Tyson S. Barrett
+
+library(tidyverse)
+library(betareg)
+
+set.seed(84322)
+
+## Population Model
+pop <- 100000              ## provides the population size (arbitrary) - just want it big
+n <- 400                   ## change this to what sample size we want to test
+vars <- paste0("x", 1:10)
+preds <- map(vars, ~data.frame(rnorm(pop, sd = 1)) %>% set_names(.x)) %>% 
+  do.call("cbind", .)
+data <- preds %>% 
+  mutate(outcome = .04*preds$x1 + .04*preds$x2 + .04*preds$x1*preds$x2 + rbeta(pop, 2.1, 3.5)) %>% 
+  mutate(outcome = case_when(outcome < 0 ~ 0,
+                             TRUE ~ outcome)) %>% 
+  mutate(outcome = outcome/max(outcome)) %>% 
+  mutate(outcome = (outcome * (pop - 1) + .5) / pop) %>% 
+  mutate(x1 = scale(x1),
+         x2 = scale(x2))
+
+## rough estimate of partial correlation for x1
+lm(scale(outcome) ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9 + x10,
+   data = data)
+
+## Odds ratio effect size here
+betareg::betareg(outcome ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9 + x10,
+                 data = data) %>% 
+  coef() %>% 
+  exp()
+
+## Start plot of the distribution of the outcome
+plot(density(data$outcome), lwd = 2, col = "chartreuse3",
+     main = "Distribution of Outcome",
+     xlab = "Value of Outcome",
+     ylim=c(0, 2.5))
+
+## Replications
+replicates <- replicate(1000, {
+  
+  d1 <- data[sample(1:pop, n), ]
+  lines(density(d1$outcome), col = alpha("dodgerblue3", .1))
+  
+  ## Population Effect Size
+  betareg::betareg(outcome ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9 + x10,
+                   data = d1) %>% 
+    summary() %>% 
+    coef() %>% 
+    .$mean                
+},
+simplify = FALSE)
+
+## Finish Plot
[…]

### 2022-05-16 analysis/tgispine_lmebeta_power.Rmd
saving old lmer power code, jic

--- 2022-05-16 analysis/tgispine_lme_power.Rmd
@@
 # Create a model with more data points per variable, to extract more power
-```{r}
-# First, let's try to add 30 observations per variable combination, which would mean N = 30
-model.cold.ex <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
-summary(model.cold.ex)
-# check that number of data points per variable does = 30
-dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.cold.ex))
-print(dat_model)
-
-# extract relevant effect sizes
-tgi_effect <- fixef(model.cold.ex)[['cond']][['manipulationTGI']]
-cond_effect <- fixef(model.cold.ex)[['cond']][['conditionwithin']]
-cold_loc_effect <- fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']]
-
-# power analysis - using smallest effect size
-fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
-pwr.cold <- powerSim(model.cold.ex)
-print(pwr.cold)
-
-# power curve
-# can run a power curve to determine the point of trade off between N observations and power
-pc.cold <- powerCurve(model.cold.ex, within='manipulation+condition+cold_location', 
-                      breaks= seq(1, 30, by = 3))
-print(pc.cold)
-```
-
-# Plot power curve!
-```{r}
-plot(pc.cold) # a good visualisation :)
-```
-
-Now let's do the same for warm!
-# Warm model
-```{r}
-model.warm <- lmerTest::lmer(rating ~ manipulation + condition + cold_location +
-                     (1|ID),
-                   data = df_sum[df_sum$VAS == 'warm' ,])
-summary(model.warm)
-```
-
-# Extend the model observations to n = 50, and extract smallest effect size of interest
-```{r}
-# using n050 here as expecting smaller effect sizes
-model.warmN <- extend(model.warm, within = 'manipulation+condition+cold_location', n=50)
-# extracting effect sizes from the extended model
-tgi_effect <- fixef(model.warmN)["manipulationTGI"]
-cond_effect <- fixef(model.warmN)["conditionwithin"]
-cold_loc_effect <- fixef(model.warmN)["cold_locationprox_caud"]
-# add smallest effect size - same as cold model
-fixef(model.coldN)["cold_locationprox_caud"] <- cold_loc_effect
-
-# then run power analysis
-pwr.warm <- powerSim(model.warmN)
-print(pwr.warm)
-```
-# Run a power curve on these data with n = 50
-```{r}
-# can run a power curve to determine the point of trade off between N observations and power
-pc.warm <- powerCurve(model.warmN, within='manipulation+condition+cold_location', 
-                      breaks= seq(1, 50, by = 5))
-print(pc.warm)
-```

### 2022-05-16 analysis/beta_power.R

@@ -9,15 +9,18 @@ set.seed(84322)
 
 ## Population Model
 pop <- 100000              ## provides the population size (arbitrary) - just want it big
-n <- 400                   ## change this to what sample size we want to test
-vars <- paste0("x", 1:10)
+n <- 50                    ## change this to what sample size we want to test
+
+vars <- paste0("x", 1:10)  # variables of interest
 preds <- map(vars, ~data.frame(rnorm(pop, sd = 1)) %>% set_names(.x)) %>% 
-  do.call("cbind", .)
+  do.call("cbind", .) # creating data frame based on x with 'pop' number of observations & 10 variables
+
+# creating outcome variable to be partially based on the predictor variables
 data <- preds %>% 
   mutate(outcome = .04*preds$x1 + .04*preds$x2 + .04*preds$x1*preds$x2 + rbeta(pop, 2.1, 3.5)) %>% 
   mutate(outcome = case_when(outcome < 0 ~ 0,
                              TRUE ~ outcome)) %>% 
-  mutate(outcome = outcome/max(outcome)) %>% 
+  mutate(outcome = outcome/max(outcome)) %>% # normalising outcome variable
   mutate(outcome = (outcome * (pop - 1) + .5) / pop) %>% 
   mutate(x1 = scale(x1),
          x2 = scale(x2))

### 2022-05-16 analysis/tgispine_lme_power.Rmd
trying to create power calculation with glmmTMB but cannot find an aappropriate package. will simulate own tomorrow

@@
                       ziformula = ~1+manipulation,
-                      data = df_VAS[df_VAS$VAS == 'warm' ,])
 # model summaries
@@
 
+# Extract coefficients (effect sizes) of interest from pilot data model
+modelc.coefs <- model.cold.ex %>% summary() %>% 
+  coef()
+
 # extract relevant effect sizes
@@
 # power analysis - using smallest effect size
-fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
+(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
 pwr.cold <- powerSim(model.cold.ex)

### 2022-05-16 analysis/tgispine_lmebeta_power.Rmd
trying to create power calculation with glmmTMB but cannot find an aappropriate package. will simulate own tomorrow

@@
 library(plyr)
+library(betareg)
 
@@
 
-Cold model power analysis
 # Run power analyses!!
+This code is extracted from [TBD]
 # Cold first, then warm
-# Create a model with more data points per variable, to extract more power
+
+```{r}
+# Extract coefficient sizes
+modelc.coefs
+
+GetHyperparam<-function(x,b=NULL){
+  ## Get the hyperparameters from the mixed effect model
+  fe <- fixef(x)
+
+  if(is.null(b))
+    b<-fe[2] # use the data effect size if not supplied
+  mu.a <- fe[1] 
+  vc <- VarCorr(x)
+  sigma.y <- as.numeric(vc[5, 2]) # Residual StdDev
+  sigma.a <- as.numeric(vc[2, 2]) # Cobblebar StdDev
+  sigma.g <- as.numeric(vc[4, 2]) # Cobblebar:transect StdDev
+  hp<-c(b, mu.a, sigma.y, sigma.a, sigma.g)
+  names(hp)<-c("b", "mu.a", "sigma.y", "sigma.a", "sigma.g")
+  return(hp)
+}
+```

### 2022-05-17 analysis/tgispine_zoib_power-sim.Rmd
informing simulations with pilot data

---
title: "TGI-spinal-power"
author: "A.G. Mitchell"
date: '2022-04-28'
output: html_document
---

Calculating the N required for the TGI spinal experiment, by simulating data frame based on pilot data from N = 4 -- this will change!
Pre-registration link:

# Last edited: 17.05.2022

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
library(reshape2)
library(truncnorm)
library(tidyverse)
library(plyr)
library(data.table)

set.seed(1234)  # Make everything reproducible

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)

# setting working directory
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
knitr::opts_knit$set(root.dir = datPath)
```

```{r}
# import compiled data
df <- read.csv('STGI_compiled-data.csv')
```

# Reformatting data frame to extract key information
```{r}
# need to recode levels for cold_probe to reduce number of levels from 4 to 2
df$cold_location[df$cold_probe == 'distal'] <- 'dist_rostr' 
df$cold_location[df$cold_probe == 'rostral'] <- 'dist_rostr'
df$cold_location[df$cold_probe == 'proximal'] <- 'prox_caud'
df$cold_location[df$cold_probe == 'caudal'] <- 'prox_caud'
df$cold_location <- as.factor(df$cold_location)

# reshape data so that there is one rating column per participant, with a VAS column = type of rating
df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburn"), 
                        id.vars=c("ID","trial_n","manipulation","order",
                                  "trial_type","arm","condition","cold_location"),
             variable.name = 'VAS', value.name = 'rating')
# rename the VAS ratings
df_VAS <- df_VAS %>% 
  mutate(VAS = revalue(VAS, c("VAScold" = "cold",
                                    "VASwarm" = "warm",
                                    "VASburn" = "burn")))

# to run zero inflated regressions need to make sure no values = 100, as cannot model them, so simply minus a very small fraction from those values
df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$beta-0.0001, df_VAS$beta <- df_VAS$rating)

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_VAS$beta <- df_VAS$beta/100
df_VAS$ID <- factor(df_VAS$ID)

# Summarise beta per rating, per condition for all participants (for simulations)
# mean
df_sum <- aggregate(beta~manipulation*condition*cold_location*VAS, 
                    mean, data = df_VAS)
setnames(df_sum, "beta", "mean")
# standard deviation
df_sd <- aggregate(beta~manipulation*condition*cold_location*VAS, 
                    SD, data = df_VAS)
setnames(df_sd, "beta", "std")
# merge
df_sum <- merge(df_sum, df_sd)

# creating individual data-frames for specific conditions (to make simulation easier)
cnt_cold <- df_sum[df_sum$manipulation == 'CNT' & df_sum$VAS == 'cold' ,]
cnt_warm <- df_sum[df_sum$manipulation == 'CNT' & df_sum$VAS == 'warm' ,]
cnt_burn <- df_sum[df_sum$manipulation == 'CNT' & df_sum$VAS == 'burn' ,]
tgi_cold <- df_sum[df_sum$manipulation == 'TGI' & df_sum$VAS == 'cold' ,]
tgi_warm <- df_sum[df_sum$manipulation == 'TGI' & df_sum$VAS == 'warm' ,]
tgi_burn <- df_sum[df_sum$manipulation == 'TGI' & df_sum$VAS == 'burn' ,]
```

# Simulating data function
```{r}
simulate_subj <- function(subid, llim, ulim) {
# trial info
trialN = 12
conditionN = 8
ratingN = 3
# creating simulation data-frame
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

# Simulate data here based on means and standard deviations of the above pilot sample
# Cold ratings: simulation
# tgi
w_dr_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_tgi_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 6])
# control
w_dr_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_cnt_cold <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 6])

# Warm ratings: simulation
# tgi
w_dr_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_tgi_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 6])
# control
w_dr_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_cnt_warm <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 6])

# Burning ratings: simulation
# tgi
w_dr_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_tgi_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 6])
# control
w_dr_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 6])
w_pc_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 6])
a_dr_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
    sd=filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 6])
a_pc_cnt_burn <- 
  truncnorm::rtruncnorm(
    trialN, llim, ulim, 
    mean=filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 5], 
    sd=filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 6])

df$rating <- c(w_dr_tgi_cold, w_pc_tgi_cold, a_dr_tgi_cold, a_pc_tgi_cold, w_dr_nontgi_cold, w_pc_nontgi_cold, a_dr_nontgi_cold, a_pc_nontgi_cold,
               w_dr_tgi_warm, w_pc_tgi_warm, a_dr_tgi_warm, a_pc_tgi_warm, w_dr_nontgi_warm, w_pc_nontgi_warm, a_dr_nontgi_warm, a_pc_nontgi_warm,
               w_dr_tgi_burn, w_pc_tgi_burn, a_dr_tgi_burn, a_pc_tgi_burn, w_dr_nontgi_burn, w_pc_nontgi_burn, a_dr_nontgi_burn, a_pc_nontgi_burn)
return(df)}
```

# Simulate data for different N (n = 20; n = 30; n = 40)
```{r}
```

# Plotting data distributions to see what kind of model family is required
```{r}
ggplot(data = df_VAS) +
  geom_density(aes(beta, fill = manipulation), alpha = .5) +
  facet_wrap(~VAS) +
  theme_classic()
```

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,],
                      na.action = na.omit) 
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```

```{r}
# warm assumption
model.warm.assump <- simulateResiduals(model.warm, n = 1000)
plot(model.warm.assump)
```

# Run power analyses!!
This code is extracted from [TBD]
# Cold first, then warm

```{r}
# Extract coefficient sizes
modelc.coefs

GetHyperparam<-function(x,b=NULL){
  ## Get the hyperparameters from the mixed effect model
  fe <- fixef(x)

  if(is.null(b))
    b<-fe[2] # use the data effect size if not supplied
  mu.a <- fe[1] 
  vc <- VarCorr(x)
  sigma.y <- as.numeric(vc[5, 2]) # Residual StdDev
  sigma.a <- as.numeric(vc[2, 2]) # Cobblebar StdDev
  sigma.g <- as.numeric(vc[4, 2]) # Cobblebar:transect StdDev
  hp<-c(b, mu.a, sigma.y, sigma.a, sigma.g)
  names(hp)<-c("b", "mu.a", "sigma.y", "sigma.a", "sigma.g")
  return(hp)
}
```

### 2022-05-17 VAS_run.m

@@ -15,7 +15,7 @@
 clear all % clearing all old data
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
-vars.control.devFlag  = 0; 
+vars.control.devFlag  = 1; 
 
 VAS_loadParams;
 addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
@@ -142,7 +142,7 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
                 question_type_idx = randQuestion(rand_idx);
                 [results.vasResponse(trial_idx, question_type_idx), ...
                     results.vasReactionTime(trial_idx, question_type_idx)] = ...
-                    getVasRatings(keys, scr, vars, question_type_idx);  
+                    getVasRatings(keys, scr, vars, question_type_idx)  
                 % adding trial numbers to data-frame for later merging
                 results.vasResponse(trial_idx, 5) = trial_idx;
                 results.vasReactionTime(trial_idx, 5) = trial_idx;

### 2022-05-17 analysis/tgispine_zoib_power-sim.Rmd
pre lunch commit

@@
 
-df$rating <- c(w_dr_tgi_cold, w_pc_tgi_cold, a_dr_tgi_cold, a_pc_tgi_cold, w_dr_nontgi_cold, w_pc_nontgi_cold, a_dr_nontgi_cold, a_pc_nontgi_cold,
-               w_dr_tgi_warm, w_pc_tgi_warm, a_dr_tgi_warm, a_pc_tgi_warm, w_dr_nontgi_warm, w_pc_nontgi_warm, a_dr_nontgi_warm, a_pc_nontgi_warm,
-               w_dr_tgi_burn, w_pc_tgi_burn, a_dr_tgi_burn, a_pc_tgi_burn, w_dr_nontgi_burn, w_pc_nontgi_burn, a_dr_nontgi_burn, a_pc_nontgi_burn)
+# creating rating variable
+df$rating <- c(w_dr_tgi_cold, w_pc_tgi_cold, a_dr_tgi_cold, a_pc_tgi_cold, 
+               w_dr_cnt_cold, w_pc_cnt_cold, a_dr_cnt_cold, a_pc_cnt_cold,
+               w_dr_tgi_warm, w_pc_tgi_warm, a_dr_tgi_warm, a_pc_tgi_warm, 
+               w_dr_cnt_warm, w_pc_cnt_warm, a_dr_cnt_warm, a_pc_cnt_warm,
+               w_dr_tgi_burn, w_pc_tgi_burn, a_dr_tgi_burn, a_pc_tgi_burn, 
+               w_dr_cnt_burn, w_pc_cnt_burn, a_dr_cnt_burn, a_pc_cnt_burn)
 return(df)}
@@
 ```{r}
+# creating individual data-frames from simulated data
+n = 20
+df20 <- data.frame()
+for (i in 1:n) {
+  df <- simulate_subj(i, 0, 1)
+  df20 <- rbind(df20,df)}
+
+n = 30
+df30 <- data.frame()
+for (i in 1:n) {
+  df <- simulate_subj(i, 0, 1)
+  df30 <- rbind(df30,df)}
+
+n = 40
+df40 <- data.frame()
+for (i in 1:n) {
+  df <- simulate_subj(i, 0, 1)
+  df40 <- rbind(df40,df)}
+df20 #just show a sample, to check
 ```
@@
 ```{r}
-ggplot(data = df_VAS) +
-  geom_density(aes(beta, fill = manipulation), alpha = .5) +
-  facet_wrap(~VAS) +
+# do this for the largest simulated dataset
+ggplot2::ggplot(data = df40) +
+  geom_density(aes(rating, fill = stimuli), alpha = .5) +
+  facet_wrap(~quality) +
   theme_classic()
 ```
+# Plot effects in largest data set (n = 40)
 
@@
 # First model cold VAS
-model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
-                                (1|ID),
+model.cold40 = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
+                                (1|id),
                       family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_VAS[df_VAS$VAS == 'cold' ,],
+                      ziformula = ~1+stimuli,
+                      data = filter(df40, quality == 'cold'),
                       na.action = na.omit) 
 # then model warm VAS
-model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
+model.warm40 = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                 (1|ID),

### 2022-05-17 analysis/tgispine_zoib_power-sim.Rmd
running models

@@
 # do this for the largest simulated dataset
+df40$quality <- factor(df40$quality, 
+                             levels = c("cold", "warm", "burn"))
 ggplot2::ggplot(data = df40) +
@@
 ```
-# Plot effects in largest data set (n = 40)
+# Summary statistics for the largest data set - for plotting
+```{r}
+# define each condition
+df40$conditionN[df40$dermatome == "within" & df40$cold_location == "dist_rostr"] <- 1
+df40$conditionN[df40$dermatome == "within" & df40$cold_location == "prox_caud"] <- 2
+df40$conditionN[df40$dermatome == "across" & df40$cold_location == "dist_rostr"] <- 3
+df40$conditionN[df40$dermatome == "across" & df40$cold_location == "prox_caud"] <- 4
+
+# Subject-level summary statistics
+df <- df40
+df_subj <- aggregate(df$rating, by = list(id = df$id, conditionN = df$conditionN, dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = mean)
+#df_subj$dermatome <- factor(df_subj$dermatome, levels = c('within','across')) # re-order conditions
+df_subj
+
+# Group-level stats
+df <- df_subj
+group_mean   <- aggregate(df$x, by = list(conditionN = df$conditionN, dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = mean)
+group_median <- aggregate(df$x, by = list(conditionN = df$conditionN,dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = median)
+group_sd     <- aggregate(df$x, by = list(conditionN = df$conditionN,dermatome = df$dermatome, cold_location = df$cold_location, stimuli = df$stimuli, quality = df$quality), FUN = sd)
+group_se     <- group_sd$x/sqrt(length(unique(df$id)))
+
+df_group <- data.frame(group_mean, mean = group_mean$x, median = group_median$x, sd = group_sd$x, se = group_se)
+df_group
+
+# isolating specific data sets for plotting
+df_subj_cold <- df_subj %>% filter(quality == 'cold')
+df_group_cold <- df_group %>% filter(quality == 'cold')
+df_subj_warm <- df_subj %>% filter(quality == 'warm')
+df_group_warm <- df_group %>% filter(quality == 'warm')
+df_subj_burn <- df_subj %>% filter(quality == 'burn')
+df_group_burn <- df_group %>% filter(quality == 'burn')
+
+```
+
+## Settings for plots
+```{r, echo = FALSE}
+# Load libraries
+library("ggplot2")
+library("gghalves")
+library("RColorBrewer")
+
+# Define colors
+reds <- brewer.pal(6, "Reds")
+blues <- brewer.pal(6, "Blues")
+purps <- brewer.pal(6, "Purples")
+
+col_cold_n <- blues[5]
+col_cold_w <- blues[3]
+col_warm_n <- reds[3]
+col_warm_w <- reds[5]
+col_burn_n <- purps[3]
+col_burn_w <- purps[5]
+
+# Parameters for plots
+tgi_theme = theme( 
+    text = element_text(size = 14),
+    axis.title.x = element_text(size = 12),
+    axis.title.y = element_text(size = 12),
+    legend.title=element_text(size=12), 
+    legend.text=element_text(size=12),
+    plot.title = element_text(lineheight=.8, face="bold", size = 12),
+    panel.border = element_rect(size=1),
+    panel.grid.minor = element_blank(), 
+    panel.grid.major = element_blank(),
+    axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
+    legend.key = element_blank(),
+    axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
+
+# Other parameters
+nudge1 = .2
+nudge2 = .3
+nudge3 = .4
+
+# Define how to plot half violins
+tgi_half_violin <- function(
+    df_subj, tgi_dermatome, tgi_cold_location, tgi_stimuli, nudge, color) 
+  {v1 <- geom_half_violin(
+    data = df_subj %>% filter(
+      dermatome == tgi_dermatome & cold_location == tgi_cold_location & stimuli == tgi_stimuli), 
+    aes(x = conditionN, y = x), position = position_nudge(x = nudge), 
+    side = "r", fill = color, alpha = .8)
+return(v1)}
+
+# Define how to plot group means and error bars
+tgi_group_mean <- function(df_group, tgi_dermatome, tgi_cold_location, tgi_stimuli, nudge, color, shape) {
+m1 <- geom_point(
+  data = df_group %>% filter(dermatome == tgi_dermatome & cold_location == tgi_cold_location & stimuli == tgi_stimuli), 
+  aes(x = conditionN, y = mean), position = position_nudge(x = nudge + .05), size = 3, shape = shape)
+return(m1)}
+
+# Define how to plot error bars
+tgi_group_error <- function(df_group, tgi_dermatome, tgi_cold_location, tgi_stimuli, tgi_nudge, tgi_color) {
+e1 <- geom_errorbar(
+  data = df_group %>% filter(dermatome == tgi_dermatome & cold_location == tgi_cold_location & stimuli == tgi_stimuli), 
+  aes(x = conditionN, y = mean, ymin = mean - se, ymax = mean + se), position = position_nudge(tgi_nudge + .05), width = 0)
+return(e1)}
+
+```
+
+# Plotting cold
+```{r}
+set.seed(321)
+df_subj_cold$xj <- jitter(df_subj_cold$conditionN, amount=.1)
+
+# cold plot
+c1 <- ggplot(data = df_subj_cold, 
+             mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +
+
+  # Add theme
+   theme_bw() +
+   tgi_theme +
+   geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
+
+   # Add points (for each subject and condition)
+   geom_point(aes(x = xj), size = 2, alpha = .8) +
+
+  # Add half violin plots
+   tgi_half_violin(df_subj_cold, "within", "dist_rostr", "non-tgi", nudge2, col_cold_n) +
+   tgi_half_violin(df_subj_cold, "within", "prox_caud", "non-tgi", nudge2, col_cold_n) +
+   tgi_half_violin(df_subj_cold, "across", "dist_rostr", "non-tgi", nudge2, col_cold_n) +
+   tgi_half_violin(df_subj_cold, "across", "prox_caud", "non-tgi", nudge2, col_cold_n) +
+   tgi_half_violin(df_subj_cold, "within", "dist_rostr", "tgi", nudge1, col_cold_w) +
+   tgi_half_violin(df_subj_cold, "within", "prox_caud", "tgi", nudge1, col_cold_w) +
+   tgi_half_violin(df_subj_cold, "across", "dist_rostr", "tgi", nudge1, col_cold_w) +
+   tgi_half_violin(df_subj_cold, "across", "prox_caud", "tgi", nudge1, col_cold_w) +
+
+   # Add group summary stats (between-condition lines, errors bars, and means)
+   geom_line(data = df_group_cold %>% filter(stimuli == "non-tgi"), 
+             aes(x = conditionN + .45, y = mean)) +
+   geom_line(data = df_group_cold %>% filter(stimuli == "tgi"), 
+             aes(x = conditionN + .35, y = mean)) +
+
+   tgi_group_error(df_group_cold, "within", "dist_rostr", "non-tgi", nudge3, col_cold_n) +
+   tgi_group_error(df_group_cold, "within", "prox_caud", "non-tgi", nudge3, col_cold_n) +
+   tgi_group_error(df_group_cold, "across", "dist_rostr", "non-tgi", nudge3, col_cold_n) +
+   tgi_group_error(df_group_cold, "across", "prox_caud", "non-tgi", nudge3, col_cold_n) +
+   tgi_group_error(df_group_cold, "within", "dist_rostr", "tgi", nudge2, col_cold_w) +
+   tgi_group_error(df_group_cold, "within", "prox_caud", "tgi", nudge2, col_cold_w) +
+   tgi_group_error(df_group_cold, "across", "dist_rostr", "tgi", nudge2, col_cold_w) +
+   tgi_group_error(df_group_cold, "across", "prox_caud", "tgi", nudge2, col_cold_w) +
+
+   tgi_group_mean(df_group_cold, "within", "dist_rostr", "non-tgi", nudge3, col_cold_n, 22) +
+   tgi_group_mean(df_group_cold, "within", "prox_caud", "non-tgi", nudge3, col_cold_n, 22) +
+   tgi_group_mean(df_group_cold, "across", "dist_rostr", "non-tgi", nudge3, col_cold_n, 22) +
+   tgi_group_mean(df_group_cold, "across", "prox_caud", "non-tgi", nudge3, col_cold_n, 22) +
+   tgi_group_mean(df_group_cold, "within", "dist_rostr", "tgi", nudge2, col_cold_w, 21) +
+   tgi_group_mean(df_group_cold, "within", "prox_caud", "tgi", nudge2, col_cold_w, 21) +
+   tgi_group_mean(df_group_cold, "across", "dist_rostr", "tgi", nudge2, col_cold_w, 21) +
+   tgi_group_mean(df_group_cold, "across", "prox_caud", "tgi", nudge2, col_cold_w, 21) +
+
+   # Define additional settings
+   scale_shape_manual(values = c(22, 21)) +
+   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), 
+                      labels=c("distal", "proximal", "rostral","caudal"), limits=c(0.6, 5)) +
+   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(blues[6],blues[3])) +
+   scale_color_manual(labels = c("non-TGI", "TGI"), values=c(blues[6], "gray25")) +
+   guides(shape = FALSE) +
+   labs(title = "", x = "", y = "Cold ratings", fill = "Stimuli", color = "Stimuli") +
+   ggtitle('Figure 1: Cold perception')
+
+c1
+```
+
+# Plotting warm
+```{r}
+set.seed(321)
+df_subj_warm$xj <- jitter(df_subj_warm$conditionN, amount=.1)
+
+# cold plot
+w1 <- ggplot(data = df_subj_warm, 
+             mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +
+
+  # Add theme
+   theme_bw() +
+   tgi_theme +
+   geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
+
+   # Add points (for each subject and condition)
+   geom_point(aes(x = xj), size = 2, alpha = .8) +
+
+  # Add half violin plots
+   tgi_half_violin(df_subj_warm, "within", "dist_rostr", "non-tgi", nudge2, col_warm_n) +
+   tgi_half_violin(df_subj_warm, "within", "prox_caud", "non-tgi", nudge2, col_warm_n) +
+   tgi_half_violin(df_subj_warm, "across", "dist_rostr", "non-tgi", nudge2, col_warm_n) +
+   tgi_half_violin(df_subj_warm, "across", "prox_caud", "non-tgi", nudge2, col_warm_n) +
+   tgi_half_violin(df_subj_warm, "within", "dist_rostr", "tgi", nudge1, col_warm_w) +
+   tgi_half_violin(df_subj_warm, "within", "prox_caud", "tgi", nudge1, col_warm_w) +
+   tgi_half_violin(df_subj_warm, "across", "dist_rostr", "tgi", nudge1, col_warm_w) +
+   tgi_half_violin(df_subj_warm, "across", "prox_caud", "tgi", nudge1, col_warm_w) +
+
+   # Add group summary stats (between-condition lines, errors bars, and means)
+   geom_line(data = df_group_warm %>% filter(stimuli == "non-tgi"), 
+             aes(x = conditionN + .45, y = mean)) +
+   geom_line(data = df_group_warm %>% filter(stimuli == "tgi"), 
+             aes(x = conditionN + .35, y = mean)) +
+
+   tgi_group_error(df_group_warm, "within", "dist_rostr", "non-tgi", nudge3, col_warm_n) +
+   tgi_group_error(df_group_warm, "within", "prox_caud", "non-tgi", nudge3, col_warm_n) +
+   tgi_group_error(df_group_warm, "across", "dist_rostr", "non-tgi", nudge3, col_warm_n) +
+   tgi_group_error(df_group_warm, "across", "prox_caud", "non-tgi", nudge3, col_warm_n) +
+   tgi_group_error(df_group_warm, "within", "dist_rostr", "tgi", nudge2, col_warm_w) +
+   tgi_group_error(df_group_warm, "within", "prox_caud", "tgi", nudge2, col_warm_w) +
+   tgi_group_error(df_group_warm, "across", "dist_rostr", "tgi", nudge2, col_warm_w) +
+   tgi_group_error(df_group_warm, "across", "prox_caud", "tgi", nudge2, col_warm_w) +
+
+   tgi_group_mean(df_group_warm, "within", "dist_rostr", "non-tgi", nudge3, col_warm_n, 22) +
+   tgi_group_mean(df_group_warm, "within", "prox_caud", "non-tgi", nudge3, col_warm_n, 22) +
+   tgi_group_mean(df_group_warm, "across", "dist_rostr", "non-tgi", nudge3, col_warm_n, 22) +
+   tgi_group_mean(df_group_warm, "across", "prox_caud", "non-tgi", nudge3, col_warm_n, 22) +
+   tgi_group_mean(df_group_warm, "within", "dist_rostr", "tgi", nudge2, col_warm_w, 21) +
+   tgi_group_mean(df_group_warm, "within", "prox_caud", "tgi", nudge2, col_warm_w, 21) +
+   tgi_group_mean(df_group_warm, "across", "dist_rostr", "tgi", nudge2, col_warm_w, 21) +
+   tgi_group_mean(df_group_warm, "across", "prox_caud", "tgi", nudge2, col_warm_w, 21) +
+
+   # Define additional settings
+   scale_shape_manual(values = c(22, 21)) +
+   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), 
+                      labels=c("distal", "proximal", "rostral","caudal"), limits=c(0.6, 5)) +
+   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_warm_n, col_warm_w)) +
+   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", reds[6])) +
+   guides(shape = FALSE) +
+   labs(title = "", x = "", y = "Warm ratings", fill = "Stimuli", color = "Stimuli") +
+   ggtitle('Figure 2: Warm perception')
+
+w1
+```
+# Plotting burn
+```{r}
+set.seed(321)
+df_subj_burn$xj <- jitter(df_subj_burn$conditionN, amount=.1)
+
+# cold plot
+b1 <- ggplot(data = df_subj_burn, 
+             mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +
+
+  # Add theme
+   theme_bw() +
+   tgi_theme +
+   geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
+
+   # Add points (for each subject and condition)
+   geom_point(aes(x = xj), size = 2, alpha = .8) +
+
+  # Add half violin plots
+   tgi_half_violin(df_subj_burn, "within", "dist_rostr", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "within", "prox_caud", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "across", "dist_rostr", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "across", "prox_caud", "non-tgi", nudge2, col_burn_n) +
+   tgi_half_violin(df_subj_burn, "within", "dist_rostr", "tgi", nudge1, col_burn_w) +
+   tgi_half_violin(df_subj_burn, "within", "prox_caud", "tgi", nudge1, col_burn_w) +
+   tgi_half_violin(df_subj_burn, "across", "dist_rostr", "tgi", nudge1, col_burn_w) +
+   tgi_half_violin(df_subj_burn, "across", "prox_caud", "tgi", nudge1, col_burn_w) +
+
+   # Add group summary stats (between-condition lines, errors bars, and means)
+   geom_line(data = df_group_burn %>% filter(stimuli == "non-tgi"), 
+             aes(x = conditionN + .45, y = mean)) +
+   geom_line(data = df_group_burn %>% filter(stimuli == "tgi"), 
+             aes(x = conditionN + .35, y = mean)) +
+
+   tgi_group_error(df_group_burn, "within", "dist_rostr", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "within", "prox_caud", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "across", "dist_rostr", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "across", "prox_caud", "non-tgi", nudge3, col_burn_n) +
+   tgi_group_error(df_group_burn, "within", "dist_rostr", "tgi", nudge2, col_burn_w) +
+   tgi_group_error(df_group_burn, "within", "prox_caud", "tgi", nudge2, col_burn_w) +
+   tgi_group_error(df_group_burn, "across", "dist_rostr", "tgi", nudge2, col_burn_w) +
+   tgi_group_error(df_group_burn, "across", "prox_caud", "tgi", nudge2, col_burn_w) +
+
+   tgi_group_mean(df_group_burn, "within", "dist_rostr", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "within", "prox_caud", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "across", "dist_rostr", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "across", "prox_caud", "non-tgi", nudge3, col_burn_n, 22) +
+   tgi_group_mean(df_group_burn, "within", "dist_rostr", "tgi", nudge2, col_burn_w, 21) +
+   tgi_group_mean(df_group_burn, "within", "prox_caud", "tgi", nudge2, col_burn_w, 21) +
+   tgi_group_mean(df_group_burn, "across", "dist_rostr", "tgi", nudge2, col_burn_w, 21) +
+   tgi_group_mean(df_group_burn, "across", "prox_caud", "tgi", nudge2, col_burn_w, 21) +
+
+   # Define additional settings
+   scale_shape_manual(values = c(22, 21)) +
+   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), 
+                      labels=c("distal", "proximal", "rostral","caudal"), limits=c(0.6, 5)) +
+   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_burn_n, col_burn_w)) +
+   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", purps[6])) +
+   guides(shape = FALSE) +
+   labs(title = "", x = "", y = "Burn ratings", fill = "Stimuli", color = "Stimuli") +
+   ggtitle('Figure 2: Burn perception')
+
+b1
+```
 
@@
 # then model warm VAS
-model.warm40 = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
-                                (1|ID),
+model.warm40 = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
+                                (1|id),
                       family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_VAS[df_VAS$VAS == 'warm' ,])
+                      ziformula = ~1+stimuli,
+                      data = filter(df40, quality == 'warm'),
+                      na.action = na.omit) 
 # model summaries
-summary(model.cold)
-summary(model.warm)
+summary(model.cold40)
+summary(model.warm40)
 ```
@@
 ```{r}
-# cold assumption
-model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
+# cold assumption - on n = 20
+model.cold.assmup <- simulateResiduals(model.cold40, n = 1000)
 plot(model.cold.assmup)
@@
 ```{r}
-# warm assumption
-model.warm.assump <- simulateResiduals(model.warm, n = 1000)
+# warm assumption - on n = 20
+model.warm.assump <- simulateResiduals(model.warm40, n = 1000)
 plot(model.warm.assump)
@@
 
-# Run power analyses!!
-This code is extracted from [TBD]
-# Cold first, then warm
+# Extract the power from each model
+```{r}
 
-```{r}
-# Extract coefficient sizes
-modelc.coefs
-
-GetHyperparam<-function(x,b=NULL){
-  ## Get the hyperparameters from the mixed effect model
-  fe <- fixef(x)
-
-  if(is.null(b))
-    b<-fe[2] # use the data effect size if not supplied
-  mu.a <- fe[1] 
-  vc <- VarCorr(x)
-  sigma.y <- as.numeric(vc[5, 2]) # Residual StdDev
-  sigma.a <- as.numeric(vc[2, 2]) # Cobblebar StdDev
-  sigma.g <- as.numeric(vc[4, 2]) # Cobblebar:transect StdDev
-  hp<-c(b, mu.a, sigma.y, sigma.a, sigma.g)
-  names(hp)<-c("b", "mu.a", "sigma.y", "sigma.a", "sigma.g")
-  return(hp)
-}
 ```

### 2022-05-17 analysis/tgispine_zoib_power-sim.Rmd
creating model and simulation functions

@@
 
-# Simulate data for different N (n = 20; n = 30; n = 40)
-```{r}
-# creating individual data-frames from simulated data
-n = 20
-df20 <- data.frame()
-for (i in 1:n) {
-  df <- simulate_subj(i, 0, 1)
-  df20 <- rbind(df20,df)}
-
-n = 30
-df30 <- data.frame()
-for (i in 1:n) {
-  df <- simulate_subj(i, 0, 1)
-  df30 <- rbind(df30,df)}
-
-n = 40
-df40 <- data.frame()
-for (i in 1:n) {
-  df <- simulate_subj(i, 0, 1)
-  df40 <- rbind(df40,df)}
-df20 #just show a sample, to check
-```
-
 # Plotting data distributions to see what kind of model family is required
@@
 ```
+# Model function - Using zero inflated regression model
+```{r}
+# First model cold VAS
+model <- function(x, vas = c('cold','warm','burn')) {
+  if (vas[1] == 'cold'){
+    x1 <- x %>%  filter(quality == 'cold')
+  } else if (vas[1] == 'warm'){
+
+  } else if (vas[1] == 'burn') {
+    x1 <- x %>%  filter(quality == 'burn')
+  }
+
+  mod = glmmTMB::glmmTMB(
+    rating ~ stimuli + dermatome + cold_location + trialn + (1|id),
+    family = glmmTMB::beta_family(),
+    ziformula = ~1+stimuli,
+    data = x1,
+    na.action = na.omit)
+
+return(summary(mod))}
+```
+
+# Extract the power from each model
+```{r}
+# the warm model has the smallest effect size, so should extract power calculation for this model only
+# do this for 40 participants, for 1000 simulations
+nSims <- 1000
+po <- data.frame()
+for (i in 1:nSims){
+  # creating individual data-frames from simulated data
+  n = 40
+  df40 <- data.frame()
+  for (i in 1:n) {
+    df <- simulate_subj(i, 0, 1)
+    df40 <- rbind(df40,df)}
+  # then run the model based on simulated data
+  m <- model(df40, 'warm')
+  # extracting the p-value and effect size
+  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
+  po <- rbind(po,tmp)
+}
+
+# rename columns
+names(po)[1] <- 'pval'
+names(po)[2] <- 'eff'
+po$sig <- as.numeric(po$pval < .05) #is significant
+po$sig[is.na(po$sig)] <- 0 #removing any NAs (code as unsig)
+
+power <- sum(po$sig)/nSims
+power
+```
+
+# Now plot most recently simulated data
 # Summary statistics for the largest data set - for plotting
@@
 
-# Now to model effects! Try a zero inflated regression model
-```{r}
-# First model cold VAS
-model.cold40 = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
-                                (1|id),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+stimuli,
-                      data = filter(df40, quality == 'cold'),
-                      na.action = na.omit) 
-# then model warm VAS
-model.warm40 = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
-                                (1|id),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+stimuli,
-                      data = filter(df40, quality == 'warm'),
-                      na.action = na.omit) 
-# model summaries
-summary(model.cold40)
-summary(model.warm40)
-```
 # Look at model assumptions
@@
 ```
-
-```{r}
-# warm assumption - on n = 20
-model.warm.assump <- simulateResiduals(model.warm40, n = 1000)
-plot(model.warm.assump)
-```
-
-# Extract the power from each model
-```{r}
-
-```

### 2022-05-18 analysis/tgispine_zoib_power-sim.Rmd
creating two power simulations - one for warm, one for cold

@@
 
-# Last edited: 17.05.2022
+# Last edited: 18.05.2022
 
@@
 # reshape data so that there is one rating column per participant, with a VAS column = type of rating
-df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburn"), 
+df_VAS <- reshape2::melt(df, measure.vars= c("VAScold", "VASwarm","VASburn"), 
                         id.vars=c("ID","trial_n","manipulation","order",
@@
 
-# Plotting data distributions to see what kind of model family is required
-```{r}
-# do this for the largest simulated dataset
-df40$quality <- factor(df40$quality, 
-                             levels = c("cold", "warm", "burn"))
-ggplot2::ggplot(data = df40) +
-  geom_density(aes(rating, fill = stimuli), alpha = .5) +
-  facet_wrap(~quality) +
-  theme_classic()
-```
 # Model function - Using zero inflated regression model
@@
 
-# Extract the power from each model
+# Extract the power from each model - first cold
 ```{r}
@@
 nSims <- 1000
+n <- 32 # number of participants to simulate
 po <- data.frame()
@@
   # creating individual data-frames from simulated data
-  n = 40
-  df40 <- data.frame()
+  df_sim <- data.frame()
   for (i in 1:n) {
     df <- simulate_subj(i, 0, 1)
-    df40 <- rbind(df40,df)}
+    df_sim <- rbind(df_sim,df)}
   # then run the model based on simulated data
-  m <- model(df40, 'warm')
+  m <- model(df_csim, 'cold')
+  # extracting the p-value and effect size
+  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
+  po <- rbind(po,tmp)
+}
+
+# rename columns
+names(po)[1] <- 'pval'
+names(po)[2] <- 'eff'
+po$sig <- as.numeric(po$pval < .05) #is significant
+po$sig[is.na(po$sig)] <- 0 #removing any NAs (code as unsig)
+
+power <- sum(po$sig)/nSims # calculating power
+
+# some renaming
+po_c <- po
+power_c <- power
+
+power c
+```
+
+# Then warm
+```{r}
+# the warm model has the smallest effect size, so should extract power calculation for this model only
+# do this for 40 participants, for 1000 simulations
+nSims <- 1000
+n <- 32 # number of participants to simulate
+po <- data.frame()
+for (i in 1:nSims){
+  # creating individual data-frames from simulated data
+  df_sim <- data.frame()
+  for (i in 1:n) {
+    df <- simulate_subj(i, 0, 1)
+    df_sim <- rbind(df_sim,df)}
+  # then run the model based on simulated data
+  m <- model(df_sim, 'warm')
   # extracting the p-value and effect size
@@
 power <- sum(po$sig)/nSims
-power
+# some renaming
+po_w <- po
+power_w <- power
+
+power_w
+```
+
+# Plotting data distributions to see what kind of model family is required
+```{r}
+# do this for the largest simulated dataset
+df40$quality <- factor(df40$quality, 
+                             levels = c("cold", "warm", "burn"))
+ggplot2::ggplot(data = df40) +
+  geom_density(aes(rating, fill = stimuli), alpha = .5) +
+  facet_wrap(~quality) +
+  theme_classic()
 ```

### 2022-05-18 analysis/tgispine_zoib_power-sim.Rmd
fixing data so standard deviations are across particpants, not trials

@@
 
-# Summarise beta per rating, per condition for all participants (for simulations)
-# mean
+# Summarise beta per rating, per condition, per participant
+# median
+df_sum_pp <- aggregate(beta~ID*manipulation*condition*cold_location*VAS, 
+                    median, data = df_VAS)
+
+# now summarise across participants
 df_sum <- aggregate(beta~manipulation*condition*cold_location*VAS, 
-                    mean, data = df_VAS)
+                    mean, data = df_sum_pp)
 setnames(df_sum, "beta", "mean")
@@
 df_sd <- aggregate(beta~manipulation*condition*cold_location*VAS, 
-                    SD, data = df_VAS)
+                    SD, data = df_sum_pp)
 setnames(df_sd, "beta", "std")
@@
     df <- simulate_subj(i, 0, 1)
-    df_sim <- rbind(df_sim,df)}
+    df_sim <- rbind(df_sim,df)
+    }
   # then run the model based on simulated data
-  m <- model(df_csim, 'cold')
+  m <- model(df_sim, 'cold')
   # extracting the p-value and effect size
@@
     df <- simulate_subj(i, 0, 1)
-    df_sim <- rbind(df_sim,df)}
+    df_sim <- rbind(df_sim,df)
+    }
   # then run the model based on simulated data

### 2022-05-18 analysis/tgispine_zoib_power-sim.Rmd
updating VAS calibration and run

@@
   } else if (vas[1] == 'warm'){
-
+    x1 <- x %>%  filter(quality == 'warm')
   } else if (vas[1] == 'burn') {
@@
 
-power c
+power_c
 ```

### 2022-05-18 VAS_calibration.m

@@ -15,7 +15,7 @@
 clear all % clearing all old data
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
-vars.control.devFlag  = 0; 
+vars.control.devFlag  = 1; 
 
 VAS_loadParams;
 addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
@@ -75,43 +75,43 @@ vars.control.abortFlag = 0;
 
 %% Preparing to present VAS  
 trial_idx = 0 ; %create a seperate index for individual trials
-for rep_idx = 1:vars.task.CalibReps %loop through trial repeats, 3 trials per thermode location
-    % record number of total trials per participant
-    trial_idx = trial_idx+1;
-    %% Open VAS screen
-    % to control when each trial starts - can remove this if VAS questions
-    % need to be continuous  
-    
-    DrawFormattedText(scr.win, vars.instructions.StartVas, 'center', 'center', scr.TextColour);
-    [~, ~] = Screen('Flip', scr.win);
-    KbStrokeWait;
-
-    % run countdown during TGI stimulation - number of seconds defined in
-    % VAS_loadParams.m
-    StimCount(scr, vars); 
-
-    %% Run VAS
-    % run one VAS to rate burning experience
-    Screen('TextSize', scr.win, scr.TextSize); % resetting text size
-    initial_question = 1; %indexing the initial question for the VAS rating
-    [results.vasResponse(trial_idx, initial_question),...
-        results.vasReactionTime(trial_idx, initial_question)] = ...
-            getVasRatings(keys, scr, vars, initial_question);  
-    results.QuestionType(trial_idx, initial_question) = vars.instructions.Question(initial_question); 
-
-    % Wait a small amount of time (1s) after the first vas rating, to
-    % divide up time
-    WaitSecs(.5)
-
-    results.trialInfo(trial_idx, 1) = trial_idx;  
-
-    % break the loop if VAS rating is above 10, then participant is
-    % experiencing TGI
-    if results.vasResponse(trial_idx, initial_question) > 10
-        sca;
-        break
-    end
+for test_idx = 1:4 % loop thorugh the number of calib 'tests' you do (atm, 2 on each arm)
+    for rep_idx = 1:vars.task.CalibReps %loop through trial repeats, 3 trials per thermode location
+        % record number of total trials per participant
+        trial_idx = trial_idx+1;
+        %% Open VAS screen
[…]

### 2022-05-18 VAS_loadParams.m

@@ -72,7 +72,7 @@ vars.instructions.Thermode = 'Please wait whilst we change the location of the t
 vars.instructions.ConfEndPoints = {'Not at all', 'Extreme'};    
 %% Waiting during stimulation
 vars.waitStim.text = 'When the countdown ends, please rate your experience. Press SPACE when done.';
-vars.waitStim.secs = 5; %the number of seconds you want to stimulate TGI for
+vars.waitStim.secs = 10; %the number of seconds you want to stimulate TGI for
 vars.waitStim.textSize = 65;
 
 %% Audio parameters - for ptb audio

### 2022-05-18 VAS_run.m

@@ -117,7 +117,7 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
             % run countdown during TGI stimulation - number of seconds defined in
             % VAS_loadParams.m
             % StimCount(scr, vars); 
-
+            vars.initq.start = GetSecs;
             % run one VAS to rate burning experience
             Screen('TextSize', scr.win, scr.TextSize); % resetting text size
             initial_question = 1; %indexing the initial question for the VAS rating
@@ -126,9 +126,12 @@ for block_idx=1:vars.task.NBlocksTotal %loop through blocks (usually 2)
                     getVasRatings(keys, scr, vars, initial_question);  
             results.QuestionType(trial_idx, initial_question) = vars.instructions.Question(initial_question); 
 
-            % Wait a small amount of time (1s) after the first vas rating, to
-            % divide up time
-            WaitSecs(1)
+            % Wait some time to make sure that TGI experience is a full 10s
+            % before starting main task
+            vars.initq.end = GetSecs;
+            vars.initq.length = vars.initq.end - vars.initq.start;
+            WaitSecs(vars.waitStim.secs-vars.initq.length)
+
         
             %% Run VAS
             % Will loop through the number of VAS questions

### 2022-05-18 analysis/tgispine_zoib_power-sim.Rmd
simulation, push to git

@@
 # do this for 40 participants, for 1000 simulations
-nSims <- 1000
+nSims <- 500
 n <- 32 # number of participants to simulate
@@
 po$sig <- as.numeric(po$pval < .05) #is significant
-po$sig[is.na(po$sig)] <- 0 #removing any NAs (code as unsig)
+po <- po[!is.na(po$sig) ,] #removing any NAs (models that did not converge) from the data frame
 
-power <- sum(po$sig)/nSims # calculating power
+power <- sum(po$sig)/length(po$sig) # calculating power
 

### 2022-05-19 VAS_calibration.m
moving unused files

@@ -15,7 +15,7 @@
 clear all % clearing all old data
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
-vars.control.devFlag  = 1; 
+vars.control.devFlag  = 0; 
 
 VAS_loadParams;
 addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)

### 2022-05-20 analysis/tgispine_analysis.R
pushing to git

@@ -59,12 +59,13 @@ df_res <- df_res %>%
 # change levels 
 df_res$cold_probe <- factor(df_res$cold_probe, 
                             levels = c("caudal", "rostral", "distal", "proximal"))
-df_res$ID <- factor(df_res$ID, 
-                    labels = c("1", "2", "3", "4"))
+# recode ID
+df_res$ID <- factor(df_res$ID, labels = c(
+  '1','2','3','4','5','6'))
 
 ## normalise VAS ratings for each participant
 # just include valid trials, trials for ID = 1 are not valid above 32
-test <- df_res[!(df_res$ID == 'P1' & df_res$trial_n > 32) ,]
+test <- df_res[!(df_res$ID == '1' & df_res$trial_n > 32) ,]
 
 ## normalising the data
 # create frame for new dataframe
@@ -224,9 +225,13 @@ ggsave('COLDplot.png', COLD, device = NULL, path = datPath, width = 8, height = 
 
 
 ##### Summary stats #####
+# first, plot density to get distribution
+ggplot(df_plot) +
+  geom_density(aes(norm_rating, fill = manipulation)) +
+  facet_wrap(~VAS)
 # get mean VAS responses for each condition
 VASresponse <- aggregate(norm_rating~ID*VAS*manipulation*condition*cold_probe, 
-                         mean, data = df_plot)
+                         median, data = df_plot)
 VASSD <- aggregate(norm_rating~ID*VAS*manipulation*condition*cold_probe, 
                    sd, data = df_plot)
 names(VASSD)[6] <- 'std'

### 2022-05-20 analysis/tgispine_zoib_power-sim.Rmd
tidying up sim file, more logical order

@@
 # setting working directory
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
+datPath <- '/home/alexm/sTGI/'
 knitr::opts_knit$set(root.dir = datPath)
@@
 
-return(summary(mod))}
+return(mod)}
 ```
 
+# First, simulate one data-set and run models (warm, cold and burn perception) to take a look at data
+```{r}
+df_sim <- data.frame()
+n = 50 #an example number of participants
+for (i in 1:n) {
+  df <- simulate_subj(i, 0, 1)
+  df_sim <- rbind(df_sim,df)
+}
+df50 <- df_sim
+
+# Plotting data distributions to see what kind of model family is required
+df50$quality <- factor(df50$quality, 
+                             levels = c("cold", "warm", "burn"))
+ggplot2::ggplot(data = df50) +
+  geom_density(aes(rating, fill = stimuli), alpha = .5) +
+  facet_wrap(~quality) +
+  theme_classic()
+```
+
+# running models based on simmed data
+```{r}
+# models for each VAS
+mc <- model(df_sim, 'cold')
+mw <- model(df_sim, 'warm')
+mb <- model(df_sim, 'burn')
+
+# show models
+summary(mc)
+summary(mw)
+summary(mb)
+```
+
+# Look at model assumptions
+```{r}
+# cold assumption - on n = 50
+mc.assump <- simulateResiduals(mc, n = 1000)
+plot(mc.assump)
+```
+
+## SIMULATIONS ##
+# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
 # Extract the power from each model - first cold
@@
 # do this for 40 participants, for 1000 simulations
-nSims <- 500
-n <- 32 # number of participants to simulate
+nSims <- 1000
+n <- 40 # number of participants to simulate
 po <- data.frame()
@@
   m <- model(df_sim, 'cold')
+  m1 <- summary(m)
   # extracting the p-value and effect size
-  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
+  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
   po <- rbind(po,tmp)
@@
   m <- model(df_sim, 'warm')
+  m1 <- summary(m)
   # extracting the p-value and effect size
-  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
+  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
   po <- rbind(po,tmp)
@@
 
-# Plotting data distributions to see what kind of model family is required
-```{r}
-# do this for the largest simulated dataset
-df40$quality <- factor(df40$quality, 
-                             levels = c("cold", "warm", "burn"))
-ggplot2::ggplot(data = df40) +
-  geom_density(aes(rating, fill = stimuli), alpha = .5) +
-  facet_wrap(~quality) +
-  theme_classic()
-```
-
-# Now plot most recently simulated data
+## PLOTTING - plot simulated data (d50 from earlier)
 # Summary statistics for the largest data set - for plotting
@@
 # define each condition
-df40$conditionN[df40$dermatome == "within" & df40$cold_location == "dist_rostr"] <- 1
-df40$conditionN[df40$dermatome == "within" & df40$cold_location == "prox_caud"] <- 2
-df40$conditionN[df40$dermatome == "across" & df40$cold_location == "dist_rostr"] <- 3
-df40$conditionN[df40$dermatome == "across" & df40$cold_location == "prox_caud"] <- 4
+df50$conditionN[df50$dermatome == "within" & df50$cold_location == "dist_rostr"] <- 1
+df50$conditionN[df50$dermatome == "within" & df50$cold_location == "prox_caud"] <- 2
+df50$conditionN[df50$dermatome == "across" & df50$cold_location == "dist_rostr"] <- 3
+df50$conditionN[df50$dermatome == "across" & df50$cold_location == "prox_caud"] <- 4
 
@@
 ```
-
-# Look at model assumptions
-```{r}
-# cold assumption - on n = 20
-model.cold.assmup <- simulateResiduals(model.cold40, n = 1000)
-plot(model.cold.assmup)
-```

### 2022-05-30 analysis/tgispine_zoib_power-sim.Rmd
updating power calc simulation script, changing to beta distrib

@@
 library(data.table)
+library(extraDistr)
 
@@
 df_VAS$ID <- factor(df_VAS$ID)
+```
 
+# Summary statistics
+```{r}
 # Summarise beta per rating, per condition, per participant
@@
 
-# creating individual data-frames for specific conditions (to make simulation easier)
-cnt_cold <- df_sum[df_sum$manipulation == 'CNT' & df_sum$VAS == 'cold' ,]
-cnt_warm <- df_sum[df_sum$manipulation == 'CNT' & df_sum$VAS == 'warm' ,]
-cnt_burn <- df_sum[df_sum$manipulation == 'CNT' & df_sum$VAS == 'burn' ,]
-tgi_cold <- df_sum[df_sum$manipulation == 'TGI' & df_sum$VAS == 'cold' ,]
-tgi_warm <- df_sum[df_sum$manipulation == 'TGI' & df_sum$VAS == 'warm' ,]
-tgi_burn <- df_sum[df_sum$manipulation == 'TGI' & df_sum$VAS == 'burn' ,]
+# creating relevant data-frames for simulation
+tgi_cold <- df_sum %>% 
+  filter(manipulation == 'TGI', VAS == 'cold')
+tgi_warm <- df_sum %>% 
+  filter(manipulation == 'TGI', VAS == 'warm')
+tgi_burn <- df_sum %>% 
+  filter(manipulation == 'TGI', VAS == 'burn')
+cnt_cold <- df_sum %>% 
+  filter(manipulation == 'CNT', VAS == 'cold')
+cnt_warm <- df_sum %>% 
+  filter(manipulation == 'CNT', VAS == 'warm')
+cnt_burn <- df_sum %>% 
+  filter(manipulation == 'CNT', VAS == 'burn')
+
+# finally, count how many zeros there are in the data
+# this is to model zero inflated regression
+# cold cnt
+CNTc_zero <- df_VAS %>% 
+    filter(VAS == 'cold' & manipulation == 'CNT') %>% 
+    dplyr::count(beta == 0) %>% 
+    mutate(prop = n / sum(n))
+# cold tgi
+TGIc_zero <- df_VAS %>% 
+    filter(VAS == 'cold', manipulation == 'TGI') %>% 
+    dplyr::count(beta == 0) %>% 
+    mutate(prop = n / sum(n))
+# warm cnt
+CNTw_zero <- df_VAS %>% 
+    filter(VAS == 'warm', manipulation == 'CNT') %>% 
+    dplyr::count(beta == 0) %>% 
+    mutate(prop = n / sum(n))
+# warm tgi
+TGIw_zero <- df_VAS %>% 
+    filter(VAS == 'warm', manipulation == 'TGI') %>% 
+    dplyr::count(beta == 0) %>% 
+    mutate(prop = n / sum(n))
+
 ```
 
-# Simulating data function
+# First, run a model on the pilot data, one for each VAS, to use for simulation
+```{r}
+# COLD
+mc.og = glmmTMB::glmmTMB(
+    beta ~ manipulation + condition + cold_location + trial_n + (1|ID),
+    family = glmmTMB::beta_family(),
+    ziformula = ~1+manipulation,
+    data = filter(df_VAS, VAS == 'cold'),
+    na.action = na.omit) 
+# WARM
+mw.og = glmmTMB::glmmTMB(
+    beta ~ manipulation + condition + cold_location + trial_n + (1|ID),
+    family = glmmTMB::beta_family(),
+    ziformula = ~1+manipulation,
+    data = filter(df_VAS, VAS == 'warm'),
+    na.action = na.omit) 
+# BURN
+mb.og = glmmTMB::glmmTMB(
+    beta ~ manipulation + condition + cold_location + trial_n + (1|ID),
+    family = glmmTMB::beta_family(),
+    ziformula = ~1+manipulation,
+    data = filter(df_VAS, VAS == 'burn'),
+    na.action = na.omit)
+
+summary(mc.og)
+summary(mw.og)
+summary(mb.og)
+```
+
+# Data to use in simulation
+```{r}
+
+```
+
+# Simulating data function - simulate model estimates (mean & sd) into beta distribution
 ```{r}
@@
 power_c
+write.csv(po_c, 'simulation_model_cold.csv', row.names = FALSE)
 ```
@@
 nSims <- 1000
-n <- 32 # number of participants to simulate
+n <- 40 # number of participants to simulate
 po <- data.frame()
@@
 po$sig <- as.numeric(po$pval < .05) #is significant
-po$sig[is.na(po$sig)] <- 0 #removing any NAs (code as unsig)
+po <- po[!is.na(po$sig) ,] #removing any NAs (models that did not converge) from the data frame
 
@@
 po_w <- po
+write.csv(po_w, 'simulation_model_warm.csv', row.names = FALSE)
 power_w <- power

### 2022-05-30 analysis/tgispine_zoib_power-sim.Rmd
modelling using beta distribution instead of truncated normal

@@
 )
+
+# function to estimate beta parameters from mean and variance
+estBetaParams <- function(mu, var) {
+     a <- ((1 - mu) / var - 1 / mu) * mu ^ 2
+     b <- a * (1 / mu - 1)
+     params = c(a,b)
+     return(params)
+}
 
@@
 df_sum <- merge(df_sum, df_sd)
+
+# get estimated beta parameters (shape 1 and shape 2) from means and SD
+for (c_idx in 1:length(df_sum$manipulation)){
+  p <- estBetaParams(df_sum$mean[c_idx], (df_sum$std[c_idx]*df_sum$std[c_idx]))
+  df_sum$alpha[c_idx] <- p[1]
+  df_sum$beta[c_idx] <- p[2]
+}
 
@@
 
-# Data to use in simulation
-```{r}
-
-```
-
-# Simulating data function - simulate model estimates (mean & sd) into beta distribution
 ```{r}
@@
 w_dr_tgi_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 7],
+    filter(tgi_cold, condition == 'within' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 w_pc_tgi_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 7],
+    filter(tgi_cold, condition == 'within' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 a_dr_tgi_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 7],
+    filter(tgi_cold, condition == 'across' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 a_pc_tgi_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 7],
+    filter(tgi_cold, condition == 'across' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 # control
 w_dr_cnt_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 7],
+    filter(cnt_cold, condition == 'within' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 w_pc_cnt_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 7],
+    filter(cnt_cold, condition == 'within' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 a_dr_cnt_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 7],
+    filter(cnt_cold, condition == 'across' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 a_pc_cnt_cold <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 6])
-
+  rbeta(
+    trialN,
+    filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 7],
+    filter(cnt_cold, condition == 'across' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 # Warm ratings: simulation
@@
 w_dr_tgi_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 7],
+    filter(tgi_warm, condition == 'within' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 w_pc_tgi_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 7],
+    filter(tgi_warm, condition == 'within' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 a_dr_tgi_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 7],
+    filter(tgi_warm, condition == 'across' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 a_pc_tgi_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 7],
+    filter(tgi_warm, condition == 'across' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 # control
 w_dr_cnt_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 7],
+    filter(cnt_warm, condition == 'within' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 w_pc_cnt_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 7],
+    filter(cnt_warm, condition == 'within' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 a_dr_cnt_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 7],
+    filter(cnt_warm, condition == 'across' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 a_pc_cnt_warm <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 6])
-
-# Burning ratings: simulation
-# tgi
+  rbeta(
+    trialN,
+    filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 7],
+    filter(cnt_warm, condition == 'across' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
+# burn
 w_dr_tgi_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 7],
+    filter(tgi_burn, condition == 'within' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 w_pc_tgi_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 7],
+    filter(tgi_burn, condition == 'within' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 a_dr_tgi_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 7],
+    filter(tgi_burn, condition == 'across' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 a_pc_tgi_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 7],
+    filter(tgi_burn, condition == 'across' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 # control
 w_dr_cnt_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 7],
+    filter(cnt_burn, condition == 'within' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 w_pc_cnt_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 7],
+    filter(cnt_burn, condition == 'within' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 a_dr_cnt_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 5], 
-    sd=filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 7],
+    filter(cnt_burn, condition == 'across' & cold_location == 'dist_rostr')[, 8],
+    ncp = 0)
 a_pc_cnt_burn <- 
-  truncnorm::rtruncnorm(
-    trialN, llim, ulim, 
-    mean=filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 5], 
-    sd=filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 6])
+  rbeta(
+    trialN,
+    filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 7],
+    filter(cnt_burn, condition == 'across' & cold_location == 'prox_caud')[, 8],
+    ncp = 0)
 
@@
                w_dr_cnt_burn, w_pc_cnt_burn, a_dr_cnt_burn, a_pc_cnt_burn)
+
 return(df)}

### 2022-06-01 analysis/tgispine_zoib_power-sim.Rmd
adding zeros to simulated data set and correcting some bugs in the function

@@
     mutate(prop = n / sum(n))
+# burn cnt
+CNTb_zero <- df_VAS %>% 
+    filter(VAS == 'burn', manipulation == 'CNT') %>% 
+    dplyr::count(beta == 0) %>% 
+    mutate(prop = n / sum(n))
+# burn tgi
+TGIb_zero <- df_VAS %>% 
+    filter(VAS == 'burn', manipulation == 'TGI') %>% 
+    dplyr::count(beta == 0) %>% 
+    mutate(prop = n / sum(n))
 
+```
+
+# Proportion zero function
+Replaces proportion of data with zero, based on proportions for each condition calculated from pilot data - used in the simulation
+```{r}
+set.seed(1)
+prop_zero <- function(x, vas = c('cold','warm','burn')) {
+  x2 <- data.frame()
+  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .03
+  r <- rnorm(2, mean=0, sd=.05)
+  if (vas[1] == 'cold'){
+    x1 <- x %>%  filter(quality == 'cold')
+    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
+    zp_cnt <- CNTc_zero$prop[2] + r[1] 
+    zp_tgi <- TGIc_zero$prop[2] + r[2]
+    # adding if loop to make sure zp does not reach 0
+    if (isTRUE(zp_cnt < 0)){
+      zp_cnt = 0
+    }
+    if (isTRUE(zp_tgi < 0)){
+      zp_tgi = 0
+    }
+    # turn zp into the proportion of total columns
+    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
+    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
+
+    # isolate TGI and non-TGI
+    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
+    x_tgi <- x1 %>% filter(stimuli == 'tgi')
+    # finally, replace a proportion of the data with zeros! 
+    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
+    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0
+
+    #compile both data-sets again
+    x2 <- rbind(x_cnt, x_tgi)
+
+  } else if (vas[1] == 'warm'){
+    x1 <- x %>%  filter(quality == 'warm')
+    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each       participant
+    zp_cnt <- CNTw_zero$prop[2] + r[1] 
+    zp_tgi <- TGIw_zero$prop[2] + r[2]
+    # adding if loop to make sure zp does not reach 0
+    if (isTRUE(zp_cnt < 0)){
+      zp_cnt = 0
+    }
+    if (isTRUE(zp_tgi < 0)){
+      zp_tgi = 0
+    }
+    # turn zp into the proportion of total columns
+    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
+    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
+    # isolate TGI and non-TGI
+    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
+    x_tgi <- x1 %>% filter(stimuli == 'tgi')
+    # finally, replace a proportion of the data with zeros! 
+    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
+    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0
+
+    #compile both data-sets again
+    x2 <- rbind(x_cnt, x_tgi)
+
+  } else if (vas[1] == 'burn') {
+    x1 <- x %>%  filter(quality == 'burn')
+    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
+    zp_cnt <- CNTb_zero$prop[2] + r[1] 
+    zp_tgi <- TGIb_zero$prop[2] + r[2]
+    # adding if loop to make sure zp does not reach 0
+    if (isTRUE(zp_cnt < 0)){
+      zp_cnt = 0
+    }
+    if (isTRUE(zp_tgi < 0)){
+      zp_tgi = 0
+    }
+    # turn zp into the proportion of total columns
+    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
+    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
+
+    # isolate TGI and non-TGI
+    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
+    x_tgi <- x1 %>% filter(stimuli == 'tgi')
+    # finally, replace a proportion of the data with zeros! 
+    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
+    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0
+
+    #compile both data-sets again
+    x2 <- rbind(x_cnt, x_tgi)
+  }
+  return(x2)
+}
 ```
@@
 ```
-
+# Simulation of data function
 ```{r}
-simulate_subj <- function(subid, llim, ulim) {
+simulate_subj <- function(subid) {
 # trial info
@@
   mod = glmmTMB::glmmTMB(
-    rating ~ stimuli + dermatome + cold_location + trialn + (1|id),
+    rating ~ stimuli + dermatome + cold_location +
+      trialn + (1|id),
     family = glmmTMB::beta_family(),
@@
 for (i in 1:n) {
-  df <- simulate_subj(i, 0, 1)
-  df_sim <- rbind(df_sim,df)
+  df <- simulate_subj(i)
+  # simulating proportion of zero responses into the data using prop_zero (defined above)
+  # this is a bit raw, but works!
+  df_c <- prop_zero(df, 'cold')
+  df_w <- prop_zero(df, 'warm')
+  df_b <- prop_zero(df, 'burn')
+  # bind all
+  df_z <- rbind(df_c, df_w)
+  df_z <- rbind(df_z, df_b)
+
+  df_sim <- rbind(df_sim, df_z)
+
+  #rm(df_c, df_w, df_b, df_z, df) #making sure these data-frames don't overlap
 }
 df50 <- df_sim
+# sanity check that all simulations are different
+sc <- aggregate(rating~id*stimuli, mean, data = df50)
 
@@
 ggplot2::ggplot(data = df50) +
-  geom_density(aes(rating, fill = stimuli), alpha = .5) +
+  geom_histogram(aes(rating, fill = stimuli), alpha = .5, binwidth = .05) +
   facet_wrap(~quality) +
@@
 plot(mc.assump)
+# warm assumption - on n = 50
+mw.assump <- simulateResiduals(mw, n = 1000)
+plot(mw.assump)
+# warm assumption - on n = 50
+mb.assump <- simulateResiduals(mb, n = 1000)
+plot(mb.assump)
 ```
@@
 ```{r}
-# the warm model has the smallest effect size, so should extract power calculation for this model only
+# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
 # do this for 40 participants, for 1000 simulations
 nSims <- 1000
-n <- 40 # number of participants to simulate
-po <- data.frame()
+n <- 32 # number of participants to simulate
+po_c <- data.frame()
+po_w <- data.frame()
 for (i in 1:nSims){
@@
   for (i in 1:n) {
-    df <- simulate_subj(i, 0, 1)
-    df_sim <- rbind(df_sim,df)
+    df <- simulate_subj(i)
+    # simulating proportion of zero responses into the data using prop_zero (defined above)
+    # this is a bit raw, but works!
+    df_c <- prop_zero(df, 'cold')
+    df_w <- prop_zero(df, 'warm')
+    df_b <- prop_zero(df, 'burn')
+    # bind all
+    df_z <- rbind(df_c, df_w)
+    df_z <- rbind(df_z, df_b)
+
+    df_sim <- rbind(df_sim, df_z)
   }
-  # then run the model based on simulated data
+  # then run the cold model based on simulated data
   m <- model(df_sim, 'cold')
   m1 <- summary(m)
+  # extracting the p-value and effect size of cold location (our effect of interest)
+  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
+  po_c <- rbind(po_c,tmp)
+
+  # and the warm model based on simulated data
+  m <- model(df_sim, 'warm')
+  m2 <- summary(m)
   # extracting the p-value and effect size
-  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
-  po <- rbind(po,tmp)
+  tmp1 <- c(m2$coefficients$cond[4,4], m2$coefficients$cond[4,1])
+  po_w <- rbind(po_w,tmp1)
 }
 
+# first get cold power
 # rename columns
-names(po)[1] <- 'pval'
-names(po)[2] <- 'eff'
-po$sig <- as.numeric(po$pval < .05) #is significant
-po <- po[!is.na(po$sig) ,] #removing any NAs (models that did not converge) from the data frame
+names(po_c)[1] <- 'pval'
+names(po_c)[2] <- 'eff'
+po_c$sig <- as.numeric(po_c$pval < .05) #is significant
+po_c <- po_c[!is.na(po_c$sig) ,] #removing any NAs (models that did not converge) from the data frame
 
-power <- sum(po$sig)/length(po$sig) # calculating power
+power_c <- sum(po_c$sig)/length(po_c$sig) # calculating power
 
+write.csv(po_c, 'simulation_model_cold.csv', row.names = FALSE)
+print(paste0('Cold power: ', round(power_c,2)))
+
+# then for warm
 # some renaming
-po_c <- po
-power_c <- power
+names(po_w)[1] <- 'pval'
+names(po_w)[2] <- 'eff'
+po_w$sig <- as.numeric(po_w$pval < .05) #is significant
+po_w <- po_w[!is.na(po_w$sig) ,] #removing any NAs (models that did not converge) from the data frame
 
-power_c
-write.csv(po_c, 'simulation_model_cold.csv', row.names = FALSE)
-```
+power_w <- sum(po_w$sig)/length(po_w$sig) # calculating power
 
-# Then warm
-```{r}
-# the warm model has the smallest effect size, so should extract power calculation for this model only
-# do this for 40 participants, for 1000 simulations
-nSims <- 1000
-n <- 40 # number of participants to simulate
-po <- data.frame()
-for (i in 1:nSims){
-  # creating individual data-frames from simulated data
-  df_sim <- data.frame()
-  for (i in 1:n) {
-    df <- simulate_subj(i, 0, 1)
-    df_sim <- rbind(df_sim,df)
-    }
-  # then run the model based on simulated data
-  m <- model(df_sim, 'warm')
-  m1 <- summary(m)
-  # extracting the p-value and effect size
-  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
-  po <- rbind(po,tmp)
-}
-
-# rename columns
-names(po)[1] <- 'pval'
-names(po)[2] <- 'eff'
-po$sig <- as.numeric(po$pval < .05) #is significant
-po <- po[!is.na(po$sig) ,] #removing any NAs (models that did not converge) from the data frame
-
-power <- sum(po$sig)/nSims
-# some renaming
-po_w <- po
 write.csv(po_w, 'simulation_model_warm.csv', row.names = FALSE)
-power_w <- power
-
-power_w
+print(paste0('Warm power: ', round(power_w,2)))
 ```

### 2022-06-01 VAS_loadParams.m
clarifyiing instructions

@@ -51,7 +51,8 @@ vars.instructions.StartScreen = ['For each trial, you will experience thermal st
     'as instructed by the experimenter.\n\n' ...
     'When you are ready, press and key to begin.'];
 
-vars.instructions.StartVas = 'When instructed by the experimenter, press a key to start rating';
+vars.instructions.StartVas = ['When instructed by the experimenter, press a key to start rating.\n\n' ...
+    'Once done, press SPACE to move to the next scale.'];
 
 vas.instructions.Calib = ['At this stage, you simply need to rate how the stimulus is BURNING.\n\n' ...
     'Please be honest, and provide any feedback about your experience to the experimenter.'];

### 2022-06-21 analysis/tgispine_zoib_power-sim.Rmd
Gosia changes

@@
 # setting working directory
-datPath <- '/home/alexm/sTGI/'
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw'
 knitr::opts_knit$set(root.dir = datPath)
@@
 # to run zero inflated regressions need to make sure no values = 100, as cannot model them, so simply minus a very small fraction from those values
-df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$beta-0.0001, df_VAS$beta <- df_VAS$rating)
+df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$rating-0.0001, df_VAS$rating)
 
@@
 ```{r}
-set.seed(1)
+set.seed(326) #is this needed?
 prop_zero <- function(x, vas = c('cold','warm','burn')) {
   x2 <- data.frame()
-  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .03
+  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .05
   r <- rnorm(2, mean=0, sd=.05)

### 2022-06-23 VAS_loadParams.m
adding language files

@@ -5,13 +5,13 @@
 % Last edit: 17/03/2022
 
 %% Key flags
-                                                 
+
 vars.control.inputDevice =  2;   % Response method for button presses 1 - mouse, 2 - keyboard 
 vars.control.fixedTiming = 0; %add if timing of all trials should be same length, regardless of resp
 vars.control.audio = 1; %is audio input required? 1 - yes, 0 - no
 
 %% Paths
-vars.filename.path = "/Users/au706616/Documents/Experiments/SPINALTGI/"; % this should change depending on computer used
+vars.filename.path = "C:\Users\Jespe\OneDrive\Skrivebord\spinalTGI\SpinalTGI-main"; % this should change depending on computer used
 
 %% Task parameters
 
@@ -39,42 +39,11 @@ vars.task.randomise = readtable('counterbalancing.csv');
 
 %% Instructions
 vars.instructions.textSize = 28;
-
-vars.instructions.StartScreen = ['For each trial, you will experience thermal stimulation on your skin.\n\n' ...
-    'At the beginning of the trial, please rate the most intense burning sensation you are experiencing from\n' ...
-    'either probe A or B at the beginning of stimulation on a scale of 0 - 100.\n\n' ...
-    'After this you will then be asked how much probe A or B\n' ...
-    'is BURNING, feels WARM or feels COLD on a scale of 0 - 100.\n\n' ...
-    '0 represents no burning/warm/cold sensation, and 100 an extreme burning/warm/cold sensation.\n'...
-    'Please use the entire length of the scale and rate 0 if you experience none of the associated sensation.\n\n'...
-    'It is important that you rate the sensation you are experiencing AT THE MOMENT coming from ONE probe\n'...
-    'as instructed by the experimenter.\n\n' ...
-    'When you are ready, press and key to begin.'];
-
-vars.instructions.StartVas = ['When instructed by the experimenter, press a key to start rating.\n\n' ...
-    'Once done, press SPACE to move to the next scale.'];
-
-vas.instructions.Calib = ['At this stage, you simply need to rate how the stimulus is BURNING.\n\n' ...
-    'Please be honest, and provide any feedback about your experience to the experimenter.'];
-
-vars.instructions.Question = {'At the moment, what is the strongest BURNING sensation you are feeling?',...
-                               'At the moment, how much is the stimulus BURNING?',...
-                               'At the moment, how WARM is the stimulus?',...
[…]

### 2022-06-23 VAS_practice.m

@@ -74,14 +74,14 @@ vars.control.abortFlag = 0;
 [~, ~, keys.KeyCode] = KbCheck;
 
 %% Params
-vars.task.practiceReps = 6 % to be determined
+vars.task.practiceReps = 6; % to be determined
 vars.instructions.PracticeStart = ['During the experiment you will use a scale of 0 - 100\n' ...
     'to rate sensations that you experience.\n\n' ...
     'Please use the following trials to practice how to use the scale.\n\n' ...
     'Use the left and right arrow keys to put the marker at the desired postion.\n' ...
     'Once done, press SPACE to move to the next scale.\n\n' ...
     'Time to answer is limited.\n\n' ...
-    'Press any key to continue.']
+    'Press any key to continue.'];
 vars.instructions.PracticeQuestions = {'Please place the marker near the left end of the scale.',...
                                'Please place the marker near the right end of the scale.',...
                                'Please place the marker in the middle of the scale.' }; 

### 2022-06-23 VAS_run.m

@@ -2,7 +2,7 @@
 %% A.G. Mitchell - 25.02.2022
 % Developed from code by Camila Deolindo & Francesca Fardo
 
-% Last edit - 22.04.22
+% Last edit - 23.06.22
 
 % Helpers required: 
 % VAS_loadParams.m; getVasRatings.m; SetupRand.m; ptbConfig.m; 
@@ -16,6 +16,7 @@ clear all % clearing all old data
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
 vars.control.devFlag  = 1; 
+vars.control.language = 2;  %1 for English 2 for Danish
 
 VAS_loadParams;
 addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)

### 2022-06-23 helperFunctions/Danish_instructions.m

@@ -1,0 +1,39 @@
+%% Instructions for VAS_run.m in Danish
+% JF Ehmsen, DE Christensen
+% 23.06.22
+%% Variables
+vars.instructions.StartScreen = ['For hver runde vil du mærke termisk stimulation.\n\n' ...
+    'I starten af hver stimulation og runde, bedes du vurdere den mest intense brændende følelese du\n' ...
+    'mærker fra enten holder A eller B på en skala fra 0 - 100.\n\n' ...
+    'Efter dette, skal du vurdere hvor brændende, varm og kold som holder A eller B er,\n' ...
+    'på en skala fra 0 - 100.\n\n' ...
+    '0 betyder at det ikke føles brændende/varmt/koldt, og 100 betyder at det føles ekstremt brændende/varmt/koldt.\n'...
+    'Venligst brug hele skalaen, og svar 0, hvis du ikke føler noget af det ovenstående.\n\n'...
+    'Det er vigtigt at du vurderer den følelse du føler i det sekund du svarer, fra den holder\n'...
+    'som du specifikt er blevet instrueret i at skulle have fokus på af forskningsassistenten.\n\n' ...
+    'Når du er klar, tryk på en vilkårlig tast for at gå i gang.'];
+
+vars.instructions.StartVas = ['Efter instruks af forskningsassistenten, tryk på en tast, for at starte med at vurdere.\n\n' ...
+    'Når du er færdig, tryk på MELLEMRUM, for at fortsætte til næste vurdering.'];
+
+vas.instructions.Calib = ['Du skal nu, vurdere hvor meget stimulationen føles BRÆNDENDE.\n\n' ...
+    'Du bedes svare ærligt og giv enhver tilbagemelding vedrørende din oplevelse/følelse til assistenten.'];
+
+vars.instructions.Question = {'På nuværende tidpsunkt, hvor stærk er den stærkeste BRÆNDENDE følelse?',...
+                               'På nuværende tidpsunkt, hvor BRÆNDENDE føles stimulutionen?',...
+                               'På nuværende tidpsunkt, hvor VARM føles stimulutionen?',...
+                               'På nuværende tidpsunkt, hvor KOLD føles stimulutionen?' }; 
+                           
+vars.instructions.QuestionCode = [1 2 3 4]; % 1 - initial burn, 2 - burning, 3 - warm, 4 - cold
[…]

### 2022-06-23 helperFunctions/English_instructions.m

@@ -1,0 +1,39 @@
+%% Instructions for VAS_run.m in English
+% AG Mitchell, JF Ehmsen, DE Christensen
+% 23.06.22
+%% Variables
+vars.instructions.StartScreen = ['For each trial, you will experience thermal stimulation on your skin.\n\n' ...
+    'At the beginning of the trial, please rate the most intense burning sensation you are experiencing from\n' ...
+    'either probe A or B at the beginning of stimulation on a scale of 0 - 100.\n\n' ...
+    'After this you will then be asked how much probe A or B\n' ...
+    'is BURNING, feels WARM or feels COLD on a scale of 0 - 100.\n\n' ...
+    '0 represents no burning/warm/cold sensation, and 100 an extreme burning/warm/cold sensation.\n'...
+    'Please use the entire length of the scale and rate 0 if you experience none of the associated sensation.\n\n'...
+    'It is important that you rate the sensation you are experiencing AT THE MOMENT coming from ONE probe\n'...
+    'as instructed by the experimenter.\n\n' ...
+    'When you are ready, press and key to begin.'];
+
+vars.instructions.StartVas = ['When instructed by the experimenter, press a key to start rating.\n\n' ...
+    'Once done, press SPACE to move to the next scale.'];
+
+vas.instructions.Calib = ['At this stage, you simply need to rate how the stimulus is BURNING.\n\n' ...
+    'Please be honest, and provide any feedback about your experience to the experimenter.'];
+
+vars.instructions.Question = {'At the moment, what is the strongest BURNING sensation you are feeling?',...
+                               'At the moment, how much is the stimulus BURNING?',...
+                               'At the moment, how WARM is the stimulus?',...
+                               'At the moment, how COLD is the stimulus?' }; 
+                           
+vars.instructions.QuestionCode = [1 2 3 4]; % 1 - initial burn, 2 - burning, 3 - warm, 4 - cold
+vars.instructions.whichQuestion = [1 1 1 1]; %Enable or disable question (1 = enabled) %% not sure this works, needs fixing!
+
+vars.instructions.whichKey = {'LR','UD'}; % Left/Right. Up/Down. If you are using the mouse as an input device let this entirely as LR
+      
+vars.instructions.ThermodeSwitch = 2:vars.task.NTrialsChange:(vars.task.NBlocksTotal*16); %When to ask participant to change thermode position (starting from 2)
[…]

### 2022-06-23 VAS_loadParams.m
fixing small bugs

@@ -11,7 +11,7 @@ vars.control.fixedTiming = 0; %add if timing of all trials should be same length
 vars.control.audio = 1; %is audio input required? 1 - yes, 0 - no
 
 %% Paths
-vars.filename.path = "C:\Users\Jespe\OneDrive\Skrivebord\spinalTGI\SpinalTGI-main"; % this should change depending on computer used
+vars.filename.path = "/Users/au706616/Documents/Experiments/SPINALTGI/"; % this should change depending on computer used
 
 %% Task parameters
 
@@ -39,6 +39,8 @@ vars.task.randomise = readtable('counterbalancing.csv');
 
 %% Instructions
 vars.instructions.textSize = 28;
+vars.waitStim.secs = 10;
+
 if vars.control.language == 1
     English_instructions;
 elseif vars.control.language == 2

### 2022-06-23 VAS_run.m

@@ -13,13 +13,14 @@
 
 %% Load parameters
 clear all % clearing all old data
+addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
 vars.control.devFlag  = 1; 
 vars.control.language = 2;  %1 for English 2 for Danish
-
+% load other relevant parameters
 VAS_loadParams;
-addpath helperFunctions % getting helper functions to path, just incase they are not already added (make sure they are in the same folder)
+
 % path to save data to - should be changed depending on laptop (VAS_loadParams.m)
 datPath = vars.filename.path;
 runPath = pwd;

### 2022-06-23 helperFunctions/Danish_instructions.m

@@ -18,11 +18,15 @@ vars.instructions.StartVas = ['Efter instruks af forskningsassistenten, tryk på 
 
 vas.instructions.Calib = ['Du skal nu, vurdere hvor meget stimulationen føles BRÆNDENDE.\n\n' ...
     'Du bedes svare ærligt og giv enhver tilbagemelding vedrørende din oplevelse/følelse til assistenten.'];
-
-vars.instructions.Question = {'På nuværende tidpsunkt, hvor stærk er den stærkeste BRÆNDENDE følelse?',...
-                               'På nuværende tidpsunkt, hvor BRÆNDENDE føles stimulutionen?',...
-                               'På nuværende tidpsunkt, hvor VARM føles stimulutionen?',...
-                               'På nuværende tidpsunkt, hvor KOLD føles stimulutionen?' }; 
+% 
+% vars.instructions.Question = {'På nuværende tidpsunkt, hvor stærk er den stærkeste BRÆNDENDE følelse?',...
+%                                'På nuværende tidpsunkt, hvor BRÆNDENDE føles stimulutionen?',...
+%                                'På nuværende tidpsunkt, hvor VARM føles stimulutionen?',...
+%                                'På nuværende tidpsunkt, hvor KOLD føles stimulutionen?' }; 
+ vars.instructions.Question = {'Paa nuvaerende tidpsunkt, hvor staerk er den staerkeste BRAENDENDE foelelse?',...
+                                'Paa nuvaerende tidpsunkt, hvor BRAENDENDE foeles stimulutionen?',...
+                                'Paa nuvaerende tidpsunkt, hvor VARM foeles stimulutionen?',...
+                                'Paa nuvaerende tidpsunkt, hvor KOLD foeles stimulutionen?' }; 
                            
 vars.instructions.QuestionCode = [1 2 3 4]; % 1 - initial burn, 2 - burning, 3 - warm, 4 - cold
 vars.instructions.whichQuestion = [1 1 1 1]; %Enable or disable question (1 = enabled) %% not sure this works, needs fixing!
@@ -33,7 +37,5 @@ vars.instructions.ThermodeSwitch = 2:vars.task.NTrialsChange:(vars.task.NBlocksT
 vars.instructions.Thermode = 'Vent venligst, imens vi rykker rundt på apparatet. Tryk på en tast, når det er gjort.';
 
[…]

### 2022-06-23 helperFunctions/English_instructions.m

@@ -33,7 +33,6 @@ vars.instructions.ThermodeSwitch = 2:vars.task.NTrialsChange:(vars.task.NBlocksT
 vars.instructions.Thermode = 'Please wait whilst we change the location of the thermode. Press a key when done.';
 
 vars.instructions.ConfEndPoints = {'Not at all', 'Extreme'};    
-%% Waiting during stimulation
+
 vars.waitStim.text = 'When the countdown ends, please rate your experience. Press SPACE when done.';
-vars.waitStim.secs = 10; %the number of seconds you want to stimulate TGI for
-vars.waitStim.textSize = 65;
+

### 2022-06-23 analysis/tgispine_zoib_power-sim.Rmd

@@
 ggplot2::ggplot(data = df50) +
-  geom_histogram(aes(rating, fill = stimuli), alpha = .5, binwidth = .05) +
+  geom_histogram(aes(rating, fill = stimuli), alpha = .5, binwidth = .05, position = "identity") +
   facet_wrap(~quality) +
@@
 
-## SIMULATIONS ##
+## SIMULATIONS
 # Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model

### 2022-06-24 VAS_loadParams.m
update Language settings, no special characters

@@ -6,6 +6,7 @@
 
 %% Key flags
 
+vars.control.language = 2;  %1 for English 2 for Danish
 vars.control.inputDevice =  2;   % Response method for button presses 1 - mouse, 2 - keyboard 
 vars.control.fixedTiming = 0; %add if timing of all trials should be same length, regardless of resp
 vars.control.audio = 1; %is audio input required? 1 - yes, 0 - no

### 2022-06-24 VAS_run.m

@@ -17,7 +17,6 @@ addpath helperFunctions % getting helper functions to path, just incase they are
 
 % Development flag 1. Set to 1 when developing the task, will optimize stim size for laptop, not hide cursor
 vars.control.devFlag  = 1; 
-vars.control.language = 2;  %1 for English 2 for Danish
 % load other relevant parameters
 VAS_loadParams;
 

### 2022-06-24 helperFunctions/Danish_instructions.m

@@ -2,22 +2,22 @@
 % JF Ehmsen, DE Christensen
 % 23.06.22
 %% Variables
-vars.instructions.StartScreen = ['For hver runde vil du mærke termisk stimulation.\n\n' ...
-    'I starten af hver stimulation og runde, bedes du vurdere den mest intense brændende følelese du\n' ...
-    'mærker fra enten holder A eller B på en skala fra 0 - 100.\n\n' ...
-    'Efter dette, skal du vurdere hvor brændende, varm og kold som holder A eller B er,\n' ...
-    'på en skala fra 0 - 100.\n\n' ...
-    '0 betyder at det ikke føles brændende/varmt/koldt, og 100 betyder at det føles ekstremt brændende/varmt/koldt.\n'...
-    'Venligst brug hele skalaen, og svar 0, hvis du ikke føler noget af det ovenstående.\n\n'...
-    'Det er vigtigt at du vurderer den følelse du føler i det sekund du svarer, fra den holder\n'...
-    'som du specifikt er blevet instrueret i at skulle have fokus på af forskningsassistenten.\n\n' ...
-    'Når du er klar, tryk på en vilkårlig tast for at gå i gang.'];
+vars.instructions.StartScreen = ['For hver runde vil du maerke termisk stimulation.\n\n' ...
+    'I starten af hver stimulation og runde, bedes du vurdere den mest intense braendende foelelese du\n' ...
+    'maerker fra enten holder A eller B paa en skala fra 0 - 100.\n\n' ...
+    'Efter dette, skal du vurdere hvor braendende, varm og kold som holder A eller B er,\n' ...
+    'paa en skala fra 0 - 100.\n\n' ...
+    '0 betyder at det ikke foeles braendende/varmt/koldt, og 100 betyder at det foeles ekstremt braendende/varmt/koldt.\n'...
+    'Venligst brug hele skalaen, og svar 0, hvis du ikke foeler noget af det ovenstaaende.\n\n'...
+    'Det er vigtigt at du vurderer den foelelse du foeler i det sekund du svarer, fra den holder\n'...
+    'som du specifikt er blevet instrueret i at skulle have fokus paa af forskningsassistenten.\n\n' ...
+    'Naar du er klar, tryk paa en vilkaarlig tast for at gaa i gang.'];
 
[…]

### 2022-06-24 analysis/tgispine_zoib_power-sim.Rmd
add burn to power calculation

--- 2022-06-21 analysis/tgispine_zoib_power-sim.Rmd
@@
 po_w <- data.frame()
+po_b <- data.frame()
 for (i in 1:nSims){
@@
   po_w <- rbind(po_w,tmp1)
+
+  # then run the burn model based on simulated data
+  m <- model(df_sim, 'burn')
+  m1 <- summary(m)
+  # extracting the p-value and effect size of cold location (our effect of interest)
+  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
+  po_b <- rbind(po_b,tmp)
 }
@@
 print(paste0('Warm power: ', round(power_w,2)))
+
+# then for burn
+# some renaming
+names(po_b)[1] <- 'pval'
+names(po_b)[2] <- 'eff'
+po_b$sig <- as.numeric(po_b$pval < .05) #is significant
+po_b <- po_b[!is.na(po_b$sig) ,] #removing any NAs (models that did not converge) from the data frame
+
+power_b <- sum(po_b$sig)/length(po_b$sig) # calculating power
+
+write.csv(po_b, 'simulation_model_warm.csv', row.names = FALSE)
+print(paste0('Burn power: ', round(power_b,2)))
 ```

### 2022-11-06 analysis/tgispine_lme_power.Rmd
creating plot from pilot data for presentation

@@
 knitr::opts_chunk$set(echo = TRUE)
-library(lme4)
+#library(lme4)
 library(simr)
@@
                       family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
+                      ziformula = ~1+manipulation)
 # model summaries

### 2022-11-06 analysis/tgispine_analysis.R

@@ -51,6 +51,11 @@ for (file in filenames){
 # merge all files
 df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
 df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))
+
+# remove participant 019, stopped testing halfway
+df_res <- df_res[df_res$ID != '019' ,]
+
+
 # recode conditions
 df_res <- df_res %>%
   mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
@@ -71,10 +76,12 @@ df_med <- aggregate(VASburn~ID*manipulation*cold_probe*trial_type, median, data 
 df_id <- aggregate(VASburn~ID, median, data = df_res)
 tgi <-  df_med %>% 
   filter(manipulation == 'TGI')
+cnt <-  df_med %>% 
+  filter(manipulation == 'CNT')
 
 # identify test results where pvalue is < .05
 i = 0
-test = data.frame(matrix(nrow = 10, ncol = 3))
+test = data.frame(matrix(nrow = 31, ncol = 3))
 colnames(test) <- c('ID','pval','responder')
 for (id in df_id$ID){
   i = i+1

### 2022-11-06 analysis/tgispine_analysis_pilot.R

@@ -1,0 +1,137 @@
+## SPINAL TGI ANALYSIS SCRIPT ##
+## Created by A.G. Mitchell on 06.04.2022 ##
+# Last edited: 08.04.22
+
+##### Loading libraries & data #####
+library(dplyr)
+library(ggplot2)
+library(RColorBrewer)
+library(ggpubr)
+library(Rmisc)
+library(ggpol)
+
+# paths
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/TestData/pilot'
+# load in relevant csv from pilot data 
+filenames <- 'sTGI_compiled-data.csv'
+pilot_dat <- read.csv(file.path(datPath,filenames)) 
+
+# summary data - one for each VAS
+burn <- aggregate(VASburn~ID*manipulation*cold_probe*condition, median, data = pilot_dat)
+cold <- aggregate(VAScold~ID*manipulation*cold_probe*condition, median, data = pilot_dat)
+warm <- aggregate(VASwarm~ID*manipulation*cold_probe*condition, median, data = pilot_dat)
+# reshape these data-frames
+burn$quality <- 'BURN'
+burn <- dplyr::rename(burn, VAS = VASburn)
+cold$quality <- 'COLD'
+cold <- dplyr::rename(cold, VAS = VAScold)
+warm$quality <- 'WARM'
+warm <- dplyr::rename(warm, VAS = VASwarm)
+
+# then bind!
+all_dat <- rbind(burn, warm, cold)
+# recode levels for plotting
+all_dat$quality <- factor(all_dat$quality)
+all_dat$condition <- factor(all_dat$condition)
+all_dat$manipulation <- factor(all_dat$manipulation)
+all_dat$cold_probe <- factor(all_dat$cold_probe)
+
+# extract medians for all
+pilot_sum <- summarySEwithin(data = all_dat, measurevar = 'VAS', 
+                             withinvars = c('quality', 'cold_probe', 'condition', 'manipulation'),
+                             na.rm = TRUE)
+
+##### PLOTTING ######
+
+# Define colors
+reds <- brewer.pal(8, "Reds")
+redpu <- brewer.pal(8, "RdPu")
+orans <- brewer.pal(8, "Oranges")
+blues <- brewer.pal(8, "Blues")
+purps <- brewer.pal(8, "Purples")
+green <- brewer.pal(8, "YlGn")
+blgrn <- brewer.pal(8, "BuGn")
+
+##### Hypothesis 1: median values #####
[…]

### 2022-11-06 analysis/tgispine_analysis_pilot.R
finalising it

@@ -64,12 +64,16 @@ ggplot(all_dat) +
   geom_boxplot(data = all_dat %>% filter(manipulation == 'CNT'),
     aes(cold_probe, VAS, colour = quality, fill = quality)) +
   facet_wrap(~quality) +
-  scale_color_manual(values = c(blues[4],reds[4],purps[4])) +
+  scale_color_manual(values = c(blues[5],reds[5],purps[5])) +
   scale_fill_manual(values = c(blues[1],reds[1],purps[1])) +
   ylim(0,100) +
   labs(title = 'No TGI', y = 'VAS Rating', x= '') +
   theme_classic() +
-  theme(legend.position = 'none') -> nTGIplot 
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 11),
+        title = element_text(size = 12)) -> nTGIplot 
 
 ggplot(all_dat) +
   geom_boxplot(data = all_dat %>% filter(manipulation == 'TGI'),
@@ -80,13 +84,18 @@ ggplot(all_dat) +
   ylim(0,100) +
   labs(title = 'TGI', y = 'VAS Rating', x= 'Location of Cold Probe') +
   theme_classic() +
-  theme(legend.position = 'none') -> TGIplot 
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 11),
+        title = element_text(size = 12)) -> TGIplot 
 
 H1plot <- ggarrange(nTGIplot, TGIplot,
                     ncol = 1, nrow = 2)
 
 ggsave('PILOT_plot.png', H1plot, device = NULL, path = datPath,
-       width = 6, height = 10, dpi = 699)
+       width = 8, height = 8, dpi = 600)
+
    
 ##### Hypothesis 2 plotting #####
 # isolating across

### 2022-12-02 analysis/tgi-spinal_analysis.Rmd
adding analysis code

---
title: "TGI Spinal Analysis Code"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
```

# Loading data
```{r}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
setwd(datPath)
```

# Extract all .csv files and compile
```{r}
# load in all csv files
filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
# empty dataframes for data
## with new data trials file will have changed to include temperature coding!
df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')

```

### 2022-12-02 analysis/tgispine_analysis.R

@@ -81,7 +81,7 @@ cnt <-  df_med %>%
 
 # identify test results where pvalue is < .05
 i = 0
-test = data.frame(matrix(nrow = 31, ncol = 3))
+test = data.frame(matrix(nrow = 40, ncol = 3))
 colnames(test) <- c('ID','pval','responder')
 for (id in df_id$ID){
   i = i+1

### 2022-12-02 analysis/tgi-spinal_analysis.Rmd
compiling

@@
 datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
-setwd(datPath)
-```
+anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
 
 # Extract all .csv files and compile
-```{r}
-# load in all csv files
 filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
@@
 
+## Data compiling
+# trial files
+setwd(datPath)
+for (file in filenames){
+  # trial files
+  if (isTRUE(substr(basename(file), 24, 24)=="t")){
+    tmp <- read.csv(file)
+    tmp$ID <- substr(basename(file), 4, 6)
+    tmp$manipulation <- substr(basename(file), 17, 19)
+    df_trials <- rbind(df_trials, tmp)
+  }
+  # VAS response files
+  if (isTRUE(substr(basename(file), 24, 29)=="rating")){
+    tmp <- read.csv(file, header = FALSE)
+    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
+    tmp$ID <- substr(basename(file), 4, 6)
+    tmp$manipulation <- substr(basename(file), 17, 19)
+    df_VAS <- rbind(df_VAS, tmp)
+  }
+  # VAS RT files
+  if (isTRUE(substr(basename(file), 24, 29)=="respti")){
+    tmp <- read.csv(file, header = FALSE)
+    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
+    tmp$ID <- substr(basename(file), 4, 6)
+    tmp$manipulation <- substr(basename(file), 17, 19)
+    df_RT <- rbind(df_RT, tmp)
+  }
+}
+
+# merge all files
+df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
+df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))
+
+# remove participant 019, stopped testing halfway
+df_res <- df_res[df_res$ID != '019' ,]
 ```
+
+# Data organisation
+```{r}
+# recode conditions
+df_res <- df_res %>%
+  mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
+         cold_probe = recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
+                             'dist' = 'distal', 'prox' = 'proximal'))
+# change levels 
+df_res$cold_probe <- factor(df_res$cold_probe, 
+                            levels = c("caudal", "rostral", "distal", "proximal"))
+
+# save new data-frame
+fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
+write.csv(df_res, fileName, row.names = FALSE)
+
+# check we have 40 participants with 96 trials
+id_check <- count(df_res, 'ID')
+id_check
+```
+
+# Responder check
+Check whether participants median burning ratings for TGI is significantly above 0
+If not, flag them as a 'non-responder'
+```{r}
+# Calculate median burning rating for all participants
+# TGI trials only
+# Then flag how many are not sig > 0
+df_med <- aggregate(VASburn~ID*manipulation*cold_probe*trial_type, median, data = df_res)
+tgi <-  df_med %>% 
+  filter(manipulation == 'TGI')
+cnt <-  df_med %>% 
+  filter(manipulation == 'CNT')
+
+# identify test results where pvalue is < .05
+i = 0
+test = data.frame(matrix(nrow = 40, ncol = 3))
+colnames(test) <- c('ID','pval','responder')
+for (id in df_id$ID){
+  i = i+1
+  tmp1 <- tgi[tgi$ID == id ,]
+  test$ID[i] <- id
+  test$pval[i] <- (t.test(tmp1$VASburn, mu = 0, alternative = 'greater'))$p.value
+  test$responder[i] <- isTRUE(test$pval[i] < .05)
+}
+
+# combine responder logic with main data-frame
+test$responder <- ifelse(test$responder == TRUE, 1, 0)
+test <- test[, c(1,3)]
+df_res <- merge(df_res, test, by = 'ID')
+
+# count the number of false responses
+nNONRESP <- sum(test$responder == FALSE)
+# print
+print(paste0('Non responders: ', nNONRESP, '/', length(test$ID)))
+```
+
+# Let's look at the data!
+```{r}
+# Reorganise data-frame 
+# pivot longer the VAS response by each quality of sensation
+# do this for both RT and VAS
+df_long <-
+
+# then remove NaNs for burning
+
+# then plot :D
+```

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
all data plot

@@
 # do this for both RT and VAS
-df_long <-
+df_long <- df_res %>% 
+  pivot_longer(cols = c(VASinit, VASburn, VASwarm, VAScold),
+               names_to = 'quality',
+               values_to = 'VAS')
+df_long2 <- df_res %>% 
+  pivot_longer(cols = c(RTinit, RTburn, RTwarm, RTcold),
+               names_to = 'quality',
+               values_to = 'RT')
+# remove the VAS & RT from quality column
+df_long$quality <- substr(df_long$quality, 4, 7)
+df_long2$quality <- substr(df_long2$quality, 3, 6)
+# remove columns from both then merge
+df_long <- df_long[, c(1:12,17:19)]
+df_long2 <- df_long2[, c(1:12,17:19)]
+df_long <- merge(df_long, df_long2)
 
-# then remove NaNs for burning
+# then remove NaNs
+df_long <- df_long %>% filter(!is.na(VAS))
+# remove the initial trials - not important for now
+init_burn <- filter(df_long, quality == 'init')
+all_vas <- filter(df_long, quality != 'init')
 
+# calculate means
+vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
 # then plot :D
+blue <- brewer.pal(6, "Blues")
+grey <- brewer.pal(6, "Greys")
+
+ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
+  geom_point(position = position_dodge(.2)) +
+  facet_wrap(~quality) +
+  scale_colour_manual(values = c(grey[3], blue[4])) +
+  theme_bw()
 ```

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
adding density plots for VAS ratings

@@
 all_vas <- filter(df_long, quality != 'init')
+# order the labelling of quality so it is cold, warm, burn
 
+# plot distribution of data
+ggplot(all_vas) +
+  geom_density(aes(VAS, colour = manipulation)) +
+  facet_wrap(~quality, scales = "free") +
+  theme_bw()
+```
+# MAIN HYPOTHESES
+# Plot descriptives for each hypotheses
+Hypothesis 1: within vs. across dermatomes
+
+```{r}
 # calculate means
 vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
+vas_h1 <- aggregate(VAS)
 # then plot :D
@@
   geom_point(position = position_dodge(.2)) +
-  facet_wrap(~quality) +
+  facet_grid(~quality*manipulation) +
   scale_colour_manual(values = c(grey[3], blue[4])) +
@@
 ```
+
+Hypothesis 2 a & b: relative location of warm and cold

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
merging dmographics

--- 2022-12-05 analysis/tgi-spinal_analysis.Rmd
@@
 ```{r}
+# transform the ID of participants to remove 0
+
 # recode conditions
@@
                             levels = c("caudal", "rostral", "distal", "proximal"))
+
+# incorporate demographics
+# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
+# have saved these in the demo .csv as well, so will add these in
+demoFile <- 'STGI_participant-demographics.csv'
+fileName = paste(datPath, demoFile, sep = '')
+df_demo <- read.csv(fileName)
+# merge
+test <- merge(df_res, df_demo)
 
@@
 
+# plot distribution of data
+ggplot(df_long) +
+  geom_density(aes(VAS, colour = manipulation)) +
+  facet_wrap(~quality, scales = "free_y") +
+  theme_bw()
+```
+# MAIN HYPOTHESES
+# Plot descriptives for each hypotheses
+Hypothesis 1: within vs. across dermatomes
+
+```{r}
 # calculate means
-vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
+vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
+                      median, data = all_vas)
+vas_h1 <- aggregate(VAS)
 # then plot :D

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
small edits

@@
 # Loading data
-```{r}
+```{r paths, echo = FALSE}
 # paths

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
id vals

--- 2022-12-05 analysis/tgi-spinal_analysis.Rmd
@@
 # transform the ID of participants to remove 0
-
+df_res$ID <- as.numeric(df_res$ID)
 # recode conditions
@@
 colnames(test) <- c('ID','pval','responder')
-for (id in df_id$ID){
+for (id in tgi$ID){
   i = i+1

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
test

@@
 # identify test results where pvalue is < .05
+tgi$ID <- as.factor(tgi$ID)
 i = 0

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
still plotting

@@
 ## Loading libraries
-library(dplyr)
-library(ggplot2)
 library(RColorBrewer)
@@
 library(Rmisc)
+library(tidyverse)
+library(gghalves)
+library(ggpol)
 ```
@@
                       median, data = all_vas)
-vas_h1 <- aggregate(VAS)
+vas_h1 <- aggregate(VAS ~ quality*manipulation*condition*ID, mean, data = vas_meds)
+
+# summary means for h1
+
 # then plot :D
+# first colours
 blue <- brewer.pal(6, "Blues")
 grey <- brewer.pal(6, "Greys")
+purp <- brewer.pal(6, "Purples")
+oran <- brewer.pal(6, "Oranges")
+gren <- brewer.pal(6, "Greens")
 
-ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
-  geom_point(position = position_dodge(.2)) +
-  facet_grid(~quality*manipulation) +
-  scale_colour_manual(values = c(grey[3], blue[4])) +
-  theme_bw()
+# nudge and jitter
+nudge1 = -0.1
+nudge2 = 0.1
+vas_h1$dermatome <- ifelse(vas_h1$condition == 'within', 1, 2)  # recode within and across
+vas_h1$condition <- factor(vas_h1$condition, labels = c('within', 'across'),
+                           levels = c('within', 'across'))
+# recode quality for this plot
+vas_h1$quality1[vas_h1$quality == 'cold'] <- 1
+vas_h1$quality1[vas_h1$quality == 'warm'] <- 2
+vas_h1$quality1[vas_h1$quality == 'burn'] <- 3
+
+vas_h1$xj <- jitter(vas_h1$quality1, 0.2)
+
+ggplot(data = vas_h1, aes(colour = condition, group = ID)) +
+  geom_point(data = vas_h1 %>% 
+               filter(manipulation == 'CNT', condition == 'within'),
+               aes(xj, VAS), position = position_nudge(-.1)) +
+  geom_point(data = vas_h1 %>% 
+               filter(manipulation == 'CNT', condition == 'across'),
+               aes(xj, VAS), position = position_nudge(.1)) +
+  scale_colour_manual(values = c(purp[6], purp[3])) +
+  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
+  theme_classic() -> h1_cnt_plot
+
+ggplot(data = vas_h1, aes(colour = condition)) +
+  geom_point(data = vas_h1 %>% 
+               filter(manipulation == 'TGI', condition == 'within'),
+               aes(xj, VAS), position = position_nudge(-.1)) +
+  geom_point(data = vas_h1 %>% 
+               filter(manipulation == 'TGI', condition == 'across'),
+               aes(xj, VAS), position = position_nudge(.1)) +
+  scale_colour_manual(values = c(purp[6], purp[3])) +
+  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
+  theme_classic() -> h1_tgi_plot
+
+h1_plot <- ggarrange(h1_cnt_plot, h1_tgi_plot,
+                     ncol = 2, nrow = 1,
+                     common.legend = TRUE)
+h1_plot
 ```
@@
 Hypothesis 2 a & b: relative location of warm and cold
+
+# ZOIB regression
+Running main analysis of a zero inflated beta regression
+Outcome: VAS
+Predictors: manipulation (CNT, TGI), cold probe location ()
+Run a seperate regression for each quality
+# Cold
+# Warm
+# Burn
+
+# Run one regression including quality as a predictor

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
calculating difference across cnt and tgi for h1

@@
                aes(xj, VAS), position = position_nudge(.1)) +
-  scale_colour_manual(values = c(purp[6], purp[3])) +
+  scale_colour_manual(values = c(blue[6], blue[3])) +
   scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
+  labs(title = 'Non TGI', y = 'Visual Analogue Scale 0 - 100', 
+       x = 'Sensation') +
   theme_classic() -> h1_cnt_plot
@@
   scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
+  labs(title = 'TGI', y = NULL, 
+       x = 'Sensation') +
   theme_classic() -> h1_tgi_plot
@@
 h1_plot
+
+# difference between across and within 
+# first remove jitter
+vas_h1 <- vas_h1[, c(1:7)]
+# then pivot wider and calculate difference
+vas_h1_diff <- vas_h1 %>% 
+  pivot_wider(names_from = manipulation, values_from = VAS) %>% 
+  mutate(difference = TGI - CNT)
+
+# now plot the difference
 ```

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
plotting the difference

--- 2022-12-05 analysis/tgi-spinal_analysis.Rmd
@@
                       median, data = all_vas)
-vas_h1 <- aggregate(VAS)
-# then plot :D
+vas_h1 <- aggregate(VAS ~ quality*manipulation*condition*ID, mean, data = vas_meds)
+# change name of manipulation
+vas_h1$manipulation <- factor(vas_h1$manipulation,
+                           labels = c('Non-TGI', 'TGI'))
+# summary means for h1
+h1_sum <- summarySEwithin(data = vas_h1, measurevar = 'VAS',
+                               withinvars = c('manipulation', 'quality', 'condition'))
+
+# plot the summary statistics
+# first colours
 blue <- brewer.pal(6, "Blues")
 grey <- brewer.pal(6, "Greys")
+purp <- brewer.pal(6, "Purples")
+oran <- brewer.pal(6, "Oranges")
+gren <- brewer.pal(6, "Greens")
 
-ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
-  geom_point(position = position_dodge(.2)) +
-  facet_grid(~quality*manipulation) +
-  scale_colour_manual(values = c(grey[3], blue[4])) +
-  theme_bw()
+# then pivot wider and calculate difference
+vas_h1_diff <- vas_h1 %>% 
+  pivot_wider(names_from = condition, values_from = VAS) %>% 
+  mutate(difference = within - across)
+# recode quality
+vas_h1_diff$quality <- factor(vas_h1_diff$quality,
+                           levels = c('cold', 'warm', 'burn'))
+
+# summary statistics
+h1_diff_sum <- summarySEwithin(data = vas_h1_diff, measurevar = 'difference',
+                               withinvars = c('manipulation', 'quality'))
+
+# now plot the difference
+ggplot(data = vas_h1_diff, aes(colour = quality)) +
+  geom_hline(yintercept = 0, colour = 'grey50') +
+  geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
+             alpha = .5) +
+  geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
+             fill = 'grey15',
+             shape = 21, size = 3) +
+  geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
+                                        ymax = difference+ci), 
+                width = .1, size = .7, colour = 'grey15') +
+  facet_wrap(~quality) +
+  scale_colour_manual(values = c(blue[4], oran[4], purp[4])) +
+  labs(title = 'Hypothesis 1: Segmental Distance',
+       y = 'Within - Across VAS Ratings', x = NULL) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h1_diff_plot
+
+h1_diff_plot
 ```

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
small final edits

@@
 
-```{r}
+```{r h1}
 # calculate means
@@
 
+```
+
+# Hypothesis 1: plot difference across conditions of interest
+```{r h1diff}
 # then pivot wider and calculate difference
@@
 h1_diff_plot
+ggsave('h1_difference.png', h1_diff_plot, path = anaPath, device = NULL, 
+       width = 7, height = 4.5, dpi = 1000)
 ```

### 2022-12-06 analysis/tgi-spinal_analysis.Rmd
h1 summary stats plot

@@
 # check we have 40 participants with 96 trials
-id_check <- count(df_res, 'ID')
+id_check <- count(df_res, ID)
 id_check
@@
 colnames(test) <- c('ID','pval','responder')
+
 for (id in tgi$ID){
@@
 
+# order conditions
+h1_sum$condition <- factor(h1_sum$condition, levels = c('within', 'across'))
+h1_sum$quality <- factor(h1_sum$quality, levels = c('cold', 'warm', 'burn'))
+
+# plot
+ggplot(h1_sum, aes(colour = quality, group = manipulation, alpha = manipulation)) + 
+  geom_point(aes(condition, VAS), size = 2, position = position_dodge(-.3)) +
+  geom_errorbar(aes(condition, ymin = VAS-ci, ymax = VAS+ci), width = .1, size = .7,
+                position = position_dodge(-.3)) +
+  geom_line(aes(condition, VAS), size = .7, position = position_dodge(-.3)) +
+  facet_wrap(~quality) +
+  scale_colour_manual(values = c(blue[4], oran[4], purp[4])) +
+  scale_alpha_discrete(range = c(0.6, 1)) +
+  ylim(0,50) +
+  theme_bw() 
 ```
@@
 Hypothesis 2 a & b: relative location of warm and cold
+```{r h2}
+# Summary statistics
+h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
+                          withinvars = c('quality','manipulation','cold_probe'))
+
+# organise data for plotting
+
+# plot all data - half-violins
+
+```
 

### 2022-12-06 analysis/tgi-spinal_analysis.Rmd
plotting h2  - all the data

@@
 # first colours
-blue <- brewer.pal(6, "Blues")
-grey <- brewer.pal(6, "Greys")
-purp <- brewer.pal(6, "Purples")
-oran <- brewer.pal(6, "Oranges")
-gren <- brewer.pal(6, "Greens")
+blue <- brewer.pal(8, "Blues")
+grey <- brewer.pal(8, "Greys")
+purp <- brewer.pal(8, "Purples")
+oran <- brewer.pal(8, "Oranges")
+gren <- brewer.pal(8, "Greens")
 
@@
   facet_wrap(~quality) +
-  scale_colour_manual(values = c(blue[4], oran[4], purp[4])) +
+  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
   scale_alpha_discrete(range = c(0.6, 1)) +
@@
   facet_wrap(~quality) +
-  scale_colour_manual(values = c(blue[4], oran[4], purp[4])) +
+  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
   labs(title = 'Hypothesis 1: Segmental Distance',
@@
 # Summary statistics
+# First, change name of manipulation
+vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
 h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
@@
 # organise data for plotting
+vas_meds$cold_probe <- factor(vas_meds$cold_probe, levels = 
+                                c('proximal', 'distal', 'rostral', 'caudal'))
+h2_sum$cold_probe <- factor(h2_sum$cold_probe, levels = 
+                                c('proximal', 'distal', 'rostral', 'caudal'))
+# recoding cold probe location so can jitter
+vas_meds$cold_code <- factor(vas_meds$cold_probe, labels = 
+                                c(1,2,3,4))
+h2_sum$cold_code <- factor(h2_sum$cold_probe, labels = 
+                                c(1,2,3,4))
+# creating jitter
+vas_meds$xj <- jitter(as.numeric(vas_meds$cold_code), amount = .05)
+
+nudge1 = -.1
+nudge2 = .1
 
 # plot all data - half-violins
+# COLD
+ggplot(data = vas_meds %>% 
+         filter(quality == 'cold'),
+       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  # summary stats
+  geom_point(data = h2_sum %>% 
+               filter(quality == 'cold'), 
+             aes(x = as.numeric(cold_code), y = VAS),
+             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
+             position = position_nudge(nudge1)) +
+  geom_errorbar(data = h2_sum %>% 
+               filter(quality == 'cold'), 
+               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
+               colour = 'grey20', width = .05, size = .7,
+               position = position_nudge(nudge1)) +
+  geom_line(data = h2_sum %>% 
+              filter(quality == 'cold'), 
+              aes(x = as.numeric(cold_code), y = VAS), 
+              colour = 'grey20', size = .7, alpha = .6,
+              position = position_nudge(nudge1)) +
+  facet_wrap(~manipulation) +
+  scale_colour_manual(values = c(blue[4], blue[6])) +
+  scale_fill_manual(values = c(blue[4], blue[6])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  labs(title = 'Cold ratings', x = NULL, 
+         y = 'VAS Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_cold_plot
 
+# WARM
+ggplot(data = vas_meds %>% 
+         filter(quality == 'warm'),
+       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  # summary stats
+  geom_point(data = h2_sum %>% 
+               filter(quality == 'warm'), 
+             aes(x = as.numeric(cold_code), y = VAS),
+             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
+             position = position_nudge(nudge1)) +
+  geom_errorbar(data = h2_sum %>% 
+               filter(quality == 'warm'), 
+               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
+               colour = 'grey20', width = .05, size = .7,
+               position = position_nudge(nudge1)) +
+  geom_line(data = h2_sum %>% 
+              filter(quality == 'warm'), 
+              aes(x = as.numeric(cold_code), y = VAS), 
+              colour = 'grey20', size = .7, alpha = .6,
+              position = position_nudge(nudge1)) +
+  facet_wrap(~manipulation) +
+  scale_colour_manual(values = c(oran[4], oran[6])) +
+  scale_fill_manual(values = c(oran[4], oran[6])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  labs(title = 'Warm ratings', x = 'Location of cold probe', 
+         y = NULL) +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_warm_plot
+
+# BURN
+ggplot(data = vas_meds %>% 
+         filter(quality == 'burn'),
+       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  # summary stats
+  geom_point(data = h2_sum %>% 
+               filter(quality == 'burn'), 
+             aes(x = as.numeric(cold_code), y = VAS),
+             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
+             position = position_nudge(nudge1)) +
+  geom_errorbar(data = h2_sum %>% 
+               filter(quality == 'burn'), 
+               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
+               colour = 'grey20', width = .05, size = .7,
+               position = position_nudge(nudge1)) +
+  geom_line(data = h2_sum %>% 
+              filter(quality == 'burn'), 
+              aes(x = as.numeric(cold_code), y = VAS), 
+              colour = 'grey20', size = .7, alpha = .6,
+              position = position_nudge(nudge1)) +
+  facet_wrap(~manipulation) +
+  scale_colour_manual(values = c(purp[4], purp[6])) +
+  scale_fill_manual(values = c(purp[4], purp[6])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  labs(title = 'Burn ratings', x = 'Location of cold probe', 
+         y = 'VAS Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_burn_plot
+
+# arrange entire plot
+h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
+                     nrow = 2, ncol = 2)
+h2_plot
+
+ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
+       width = 10, height = 6.5, dpi = 600)
 ```

### 2022-12-06 analysis/tgi-spinal_analysis.Rmd
beginning to regress...

@@
 library(ggpol)
+library(simr)
+library(broom)
+library(brms)
+library(modelsummary)
+library(tibble)
+library(DHARMa)
+library(glmmTMB)
 ```
@@
 Run a seperate regression for each quality
+
+```{r model_prep}
+set.seed(1234)  # Make everything reproducible
+
+# Define the goodness-of-fit stats to include in modelsummary()
+gof_stuff <- tribble(
+  ~raw, ~clean, ~fmt,
+  "nobs", "N", 0,
+  "r.squared", "R²", 3
+)
+
+# recode cold_location and condition to reduce levels in regression
+df_long$cold_cond[df_long$cold_probe == 'distal'] <- 'dist_rostr' 
+df_long$cold_cond[df_long$cold_probe == 'rostral'] <- 'dist_rostr' 
+df_long$cold_cond[df_long$cold_probe == 'proximal'] <- 'prox_caud' 
+df_long$cold_cond[df_long$cold_probe == 'caudal'] <- 'prox_caud'
+
+# to run zero inflated regressions need to make sure no values = 100, 
+# as cannot model them, so simply minus a very small fraction from those values
+df_long$beta <- ifelse(df_long$VAS==100, df_long$beta-0.0001, df_long$beta <- df_long$VAS)
+
+# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
+df_long$beta <- df_long$beta/100
+df_long$ID <- factor(df_long$ID)
+```
 # Cold
@@
 # Run one regression including quality as a predictor
+```{r}
+# Try and model all with ratings
+model.all = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + quality + trial_n +
+                                quality*manipulation*condition + (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = df_long,
+                      na.action = na.omit) 
+summary(model.all)
+```

### 2022-12-07 analysis/tgi-spinal_analysis.Rmd
small changes

@@
 ```
+
 # Cold
+```{r coldmod}
+# Try and model all with ratings
+model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + trial_n +
+                                manipulation*condition*cold_cond + (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation + (1|ID),
+                      data = df_long %>% filter(quality == 'cold'),
+                      na.action = na.omit) 
+summary(model.cold)
+```
 # Warm
+```{r coldmod}
+# Try and model all with ratings
+model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + trial_n +
+                                manipulation*condition*cold_cond + (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation + (1|ID),
+                      data = df_long %>% filter(quality == 'warm'),
+                      na.action = na.omit) 
+summary(model.warm)
+```
+
 # Burn
@@
 # Run one regression including quality as a predictor
-```{r}
-# Try and model all with ratings
-model.all = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + quality + trial_n +
-                                quality*manipulation*condition + (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_long,
-                      na.action = na.omit) 
-summary(model.all)
-```

### 2022-12-13 analysis/tgi-spinal_analysis.Rmd
running analyses as preÃ-registered

--- 2022-12-06 analysis/tgi-spinal_analysis.Rmd
@@
 ## Loading libraries
-library(RColorBrewer)
-library(ggpubr)
-library(Rmisc)
-library(tidyverse)
-library(gghalves)
-library(ggpol)
-library(simr)
-library(broom)
-library(brms)
-library(modelsummary)
-library(tibble)
-library(DHARMa)
-library(glmmTMB)
+# check for pacman package and install if not found
+if (!require("pacman")) install.packages("pacman")
+  pacman::p_load(boot, broom, broom.mixed, brms, caret, DHARMa, 
+                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmertest, 
+                 modelsummary, RColorBrewer, rcompanion, reshape2, Rmisc,
+                 rsample, simr, tibble, tidyverse, wesanderson
+                 )
+```
+
+```{r paths}
+# paths
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
+anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
 ```
@@
 # Loading data
-```{r paths, echo = FALSE}
-# paths
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
-anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
-
+```{r data, echo = FALSE}
 # Extract all .csv files and compile
@@
 
-# remove participant 019, stopped testing halfway
+# remove participant 019, stopped testing halfway due to broken thermal probe
 df_res <- df_res[df_res$ID != '019' ,]
@@
 # check we have 40 participants with 96 trials
-id_check <- count(df_res, ID)
+id_check <- count(df_res, 'ID')
 id_check
@@
 
-for (id in tgi$ID){
+for (id in levels(tgi$ID)){
   i = i+1
@@
 nudge2 = .1
+
+# TRY THESE PLOTS WITH BOX JITTER? gghalves may be too messy
 
@@
 df_long$ID <- factor(df_long$ID)
+
+# normalised VAS ratings - just incase?
 ```
+
+Running models as pre-registered: 
 # Cold
-# Warm
-# Burn
-
-# Run one regression including quality as a predictor
-```{r}
+```{r coldmod}
 # Try and model all with ratings
-model.all = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + quality + trial_n +
-                                quality*manipulation*condition + (1|ID),
+model.cold = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure + trial_n +
+                                (1|ID),
                       family = glmmTMB::beta_family(),
                       ziformula = ~1+manipulation,
-                      data = df_long,
+                      data = df_long %>% filter(quality == 'cold'),
                       na.action = na.omit) 
-summary(model.all)
+mc <- summary(model.cold)
+mc
 ```
+# Warm
+```{r warmmod}
+# Try and model all with ratings
+model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure +
+                                trial_n + (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = df_long %>% filter(quality == 'warm'),
+                      na.action = na.omit) 
+mw <- summary(model.warm)
+mw
+```
+
+# Burn
+The burning hypothesis is only for participants that experience burning TGI 
+(aka are responders)
+```{r burnmod}
+# First, remove non-responders
+df_resp <- df_long %>% 
+  filter(responder == 1)
+# check n
+n <- count(df_resp, 'ID')
+length(n$ID)
+# Try and model all with ratings
+model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure +
+                                trial_n +(1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation + (1|ID),
+                      data = df_resp %>% filter(quality == 'burn'),
+                      na.action = na.omit) 
+mb <- summary(model.burn)
+mb
+```
+
+# Run model checks on all
+```{r checks}
+# cold assumption - on n = 50
+mc.assump <- simulateResiduals(model.cold, n = 1000)
+plot(mc.assump)
+# warm assumption - on n = 50
+mw.assump <- simulateResiduals(model.warm, n = 1000)
+plot(mw.assump)
+# warm assumption - on n = 50
+mb.assump <- simulateResiduals(model.burn, n = 1000)
+plot(mb.assump)
+```
+# Plot 32 burn responders seperately
+```{r burn32}
+```
+# Run one regression including quality as a predictor

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
adding other exploratory analyses - regression by dermatome

@@
   pacman::p_load(boot, broom, broom.mixed, brms, caret, DHARMa, 
-                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmertest, 
+                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                  modelsummary, RColorBrewer, rcompanion, reshape2, Rmisc,
@@
 ```
+# Plot 32 burn responders seperately
+```{r burn32}
+```
 
@@
 df_long$ID <- factor(df_long$ID)
-
-# normalised VAS ratings - just incase?
 ```
@@
 # Run model checks on all
-```{r checks}
+```{r checks, warning=FALSE}
 # cold assumption - on n = 50
@@
 ```
-# Plot 32 burn responders seperately
-```{r burn32}
+# Run individual models on within and across dermatomes for H2
+Directly compare proximal-distal and rostral-caudal results for each quality
+
+# Cold - within and across
+```{r cold_indiv}
+# seperate data-frames
+within <- df_long %>% 
+  filter(condition == 'within')
+across <-  df_long %>% 
+  filter(condition == 'across')
+
+# within
+model.wcold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = within %>% filter(quality == 'cold'),
+                      na.action = na.omit) 
+mwc <- summary(model.wcold)
+mwc
+
+# across
+model.acold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = across %>% filter(quality == 'cold'),
+                      na.action = na.omit) 
+mac <- summary(model.acold)
+mac
 ```
-# Run one regression including quality as a predictor
+
+# Warm - within and across
+```{r warm_indiv}
+# within
+model.wwarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = within %>% filter(quality == 'warm'),
+                      na.action = na.omit) 
+mww <- summary(model.wwarm)
+mww
+
+# across
+model.awarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = across %>% filter(quality == 'warm'),
+                      na.action = na.omit) 
+maw <- summary(model.awarm)
+maw
+```
+
+# Burn - within and across
+```{r burn_indiv}
+# isolate responders only
+within <- df_long %>% 
+  filter(condition == 'within' & responder == 1)
+across <-  df_long %>% 
+  filter(condition == 'across' & responder == 1)
+
+# within
+model.wburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = within %>% filter(quality == 'burn'),
+                      na.action = na.omit) 
+mwb <- summary(model.wburn)
+mwb
+
+# across
+model.aburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = across %>% filter(quality == 'burn'),
+                      na.action = na.omit) 
+mab <- summary(model.aburn)
+mab
+```

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
running planned correlation

@@
 if (!require("pacman")) install.packages("pacman")
-  pacman::p_load(boot, broom, broom.mixed, brms, caret, DHARMa, 
+  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, 
                  gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
-                 modelsummary, RColorBrewer, rcompanion, reshape2, Rmisc,
+                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                  rsample, simr, tibble, tidyverse, wesanderson
@@
 ```
+
+# EXPLORATORY HYPOTHESES
+# Correlation between quality (cold/warm/burn)
+
+```{r corr}
+# remove columns
+df_corr <- df_res[, c(1:9,14:16,21)]
+df_corr <- df_corr %>% 
+  pivot_wider(names_from = 'manipulation', values_from = c('VAScold','VASwarm','VASburn')) %>% 
+  select(c(ID,VAScold_CNT,VAScold_TGI,VASwarm_CNT,VASwarm_TGI,VASburn_CNT,VASburn_TGI)) %>% 
+  rename(NonTGI_cold = VAScold_CNT,
+         TGI_cold = VAScold_TGI,
+         NonTGI_warm = VASwarm_CNT,
+         TGI_warm = VASwarm_TGI,
+         NonTGI_burn = VASburn_CNT,
+         TGI_burn = VASburn_TGI)
+
+# average values within participants
+df_corr <- aggregate(. ~ID, mean, data = df_corr)
+# remove ID
+df_corr <- select(df_corr, -ID)
+
+# correlate
+cormat <- hetcor(df_corr, type = 'pearson')$correlations
+cormat
+
+# significance values
+
+# correlation matrix
+# plotting correlations between variables
+corrplot(cormat, method="circle", addrect = 0,
+         title = "VAS rating correlation matrix", mar = c(0,0,1,0), 
+         tl.cex=0.9) 
+```

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
creating scatter plotsø

--- 2022-12-14 analysis/tgi-spinal_analysis.Rmd
@@
 if (!require("pacman")) install.packages("pacman")
-  pacman::p_load(boot, broom, broom.mixed, brms, caret, DHARMa, 
+  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, 
                  gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
-                 modelsummary, RColorBrewer, rcompanion, reshape2, Rmisc,
-                 rsample, simr, tibble, tidyverse, wesanderson
+                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
+                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                  )
@@
 ```
+
+# EXPLORATORY HYPOTHESES
+# Correlation between quality (cold/warm/burn)
+
+```{r corr}
+# remove columns
+df_corr <- df_res[, c(1:9,14:16,21)]
+df_corr <- df_corr %>% 
+  pivot_wider(names_from = 'manipulation', values_from = c('VAScold','VASwarm','VASburn')) %>% 
+  select(c(ID,VAScold_CNT,VAScold_TGI,VASwarm_CNT,VASwarm_TGI,VASburn_CNT,VASburn_TGI)) %>% 
+  rename(CNTcold = VAScold_CNT,
+         TGIcold = VAScold_TGI,
+         CNTwarm = VASwarm_CNT,
+         TGIwarm = VASwarm_TGI,
+         CNTburn = VASburn_CNT,
+         TGIburn = VASburn_TGI)
+
+# average values within participants
+df_corr <- aggregate(. ~ID, mean, data = df_corr)
+# remove ID
+df_corr <- select(df_corr, -ID)
+
+# correlate
+qual_cor <- hetcor(df_corr, type = 'spearman')
+cormat <- qual_cor$correlations
+
+# significance values
+p <- cor.mtest(df_corr, type ='spearman')$p
+
+# correlation matrix
+# plotting correlations between variables
+corrplot(cormat, type = 'lower',
+         p.mat = p, insig = "p-value", sig.level = -1,
+         title = "VAS rating correlation matrix", 
+         mar = c(0,0,1,0), 
+         tl.cex=0.9) 
+```
+# Scatter plots
+```{r scatter}
+# Non TGI plots
+ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  theme_bw() -> CNT_cw_plot
+
+ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  theme_bw() -> CNT_cb_plot
+
+ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  theme_bw() -> CNT_wb_plot
+
+# combine non TGI
+
+# TGI plots
+ggplot(df_corr, aes(x = TGIcold, y = TGIwarm)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  theme_bw() -> TGI_cw_plot
+
+ggplot(df_corr, aes(x = TGIcold, y = TGIburn)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  theme_bw() -> TGI_cb_plot
+
+ggplot(df_corr, aes(x = TGIwarm, y = TGIburn)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  theme_bw() -> TGI_wb_plot
+
+# combine TGI
+```
+
+# Initial burn
+Are there any observed differences in dermatome and warm and cold afferents
+for the first initial burning rating, before trial begins?

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
updating scatters

@@
 ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> CNT_cw_plot
@@
 ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> CNT_cb_plot
@@
 ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> CNT_wb_plot
@@
 # combine non TGI
+CNT_corr_plot <- ggarrange(CNT_cw_plot, CNT_cb_plot, CNT_wb_plot,
+                           nrow = 1, ncol = 3,
+                           labels = c('A.','B.','C.'))
+CNT_corr_plot <- annotate_figure(CNT_corr_plot, 
+                                 top = text_grob("Non-TGI", 
+                                                 size = 12))
+CNT_corr_plot
 

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
saving plot

--- 2022-12-14 analysis/tgi-spinal_analysis.Rmd
@@
   theme_bw()
+
+# summary statistics
 ```
@@
 
+# check distribution of data
+df_means <- aggregate(VAS ~ ID*quality*manipulation, mean, data = vas_meds)
+ggplot(df_means, aes(colour = quality)) +
+  geom_density(aes(VAS)) +
+  theme_bw()
+
 # correlate
@@
 ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  geom_text(aes(label = paste0("R = ",
+                               round(cormat[1,3], 2))),
+            x=8, y=90, size = 5) +
+  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> CNT_cw_plot
@@
 ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  geom_text(aes(label = paste0("R = ",
+                               round(cormat[1,5], 2))),
+            x=8, y=90, size = 5) +
+  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> CNT_cb_plot
@@
 ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  geom_text(aes(label = paste0("R = ",
+                               round(cormat[3,5], 2))),
+            x=8, y=90, size = 5) +
+  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> CNT_wb_plot
@@
 # combine non TGI
+CNT_corr_plot <- ggarrange(CNT_cw_plot, CNT_cb_plot, CNT_wb_plot,
+                           nrow = 1, ncol = 3,
+                           labels = c('A','B','C'))
+CNT_corr_plot <- annotate_figure(CNT_corr_plot, 
+                                 top = text_grob("Non-TGI", 
+                                                 size = 12))
 
@@
 ggplot(df_corr, aes(x = TGIcold, y = TGIwarm)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  geom_text(aes(label = paste0("R = ",
+                               round(cormat[2,4], 2))),
+            x=8, y=90, size = 5) +
+  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> TGI_cw_plot
@@
 ggplot(df_corr, aes(x = TGIcold, y = TGIburn)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  geom_text(aes(label = paste0("R = ",
+                               round(cormat[2,6], 2))),
+            x=8, y=90, size = 5) +
+  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> TGI_cb_plot
@@
 ggplot(df_corr, aes(x = TGIwarm, y = TGIburn)) +
-  geom_point() +
-  geom_smooth(method='lm') +
+  geom_smooth(method='lm', colour = 'black', alpha = .5) +
+  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
+  geom_text(aes(label = paste0("R = ",
+                               round(cormat[4,6], 2))),
+            x=8, y=90, size = 5) +
+  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
+  xlim(0,100) + ylim(-15,100) +
   theme_bw() -> TGI_wb_plot
@@
 # combine TGI
+TGI_corr_plot <- ggarrange(TGI_cw_plot, TGI_cb_plot, TGI_wb_plot,
+                           nrow = 1, ncol = 3,
+                           labels = c('D','E','F'))
+TGI_corr_plot <- annotate_figure(TGI_corr_plot, 
+                                 top = text_grob("TGI", 
+                                                 size = 12))
+
+# put two together
+corr_plot <- ggarrange(CNT_corr_plot, TGI_corr_plot,
+                       nrow = 2, ncol = 1)
+corr_plot
+
+ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
+       width = 14, height = 9, dpi = 1000)
 ```

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
trying to model zero and one inflated

@@
 if (!require("pacman")) install.packages("pacman")
-  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, 
+  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, gamlss,
                  gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
@@
 df_long$beta <- ifelse(df_long$VAS==100, df_long$beta-0.0001, df_long$beta <- df_long$VAS)
+df_long$beta <- df_long$beta/100
 
 # transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
-df_long$beta <- df_long$beta/100
+df_long$VAS <- df_long$VAS/100
 df_long$ID <- factor(df_long$ID)
@@
 # Try and model all with ratings
-model.cold = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure + trial_n +
-                                (1|ID),
+model.cold = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
+                                (1|ID) + (1|order),
                       family = glmmTMB::beta_family(),
@@
 mc
+
+model.cold1 = gamlss(VAS ~ manipulation * condition * cold_cond + procedure + trial_n +
+                                random(ID),
+                    nu.formula = ~ 1+manipulation,
+                    tau.formula = ~ 1+manipulation,
+                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
+                                   tau.link = 'logit'),
+                    data = test %>% filter(quality == 'cold'),
+                    trace = F) 
+mc1 <- summary(model.cold1)
+mc1
 ```
@@
 # Try and model all with ratings
-model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure +
-                                trial_n + (1|ID),
+model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
+                                trial_n + (1|ID) + (1|order),
                       family = glmmTMB::beta_family(),
@@
 # Try and model all with ratings
-model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure +
-                                trial_n +(1|ID),
+model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
+                                trial_n + (1|ID) + (1|order),
                       family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation + (1|ID),
+                      ziformula = ~1+manipulation,
                       data = df_resp %>% filter(quality == 'burn'),
@@
 mb
+
+model.burn1 = gamlss(VAS ~ manipulation * condition * cold_cond + trial_n +
+                                random(ID) + random(as.factor(procedure)),
+                    nu.formula = ~ 1+manipulation,
+                    tau.formula = ~ 1+manipulation,
+                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
+                                   tau.link = 'logit'),
+                    data = df_resp %>% filter(quality == 'burn'),
+                    trace = F) 
+mc1 <- summary(model.burn1)
+mc1
 ```
@@
 # correlate
-qual_cor <- hetcor(df_corr, type = 'spearman')
+qual_cor <- hetcor(df_corr, type = 'pearson')
 cormat <- qual_cor$correlations
@@
 # significance values
-p <- cor.mtest(df_corr, type ='spearman')$p
+p <- cor.mtest(df_corr, type ='pearson')$p
 
@@
 for the first initial burning rating, before trial begins?
+
+```{r initmod}
+# Try and model all with ratings
+model.init = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
+                                trial_n + (1|ID) + (1|order),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = df_long %>% filter(quality == 'init'),
+                      na.action = na.omit) 
+mi <- summary(model.init)
+mi
+
+model.burn1 = gamlss(VAS ~ manipulation * condition * cold_cond + trial_n +
+                                random(ID) + random(as.factor(procedure)),
+                    nu.formula = ~ 1+manipulation,
+                    tau.formula = ~ 1+manipulation,
+                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
+                                   tau.link = 'logit'),
+                    data = df_resp %>% filter(quality == 'burn'),
+                    trace = F) 
+mc1 <- summary(model.burn1)
+mc1
+```

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
adding non zero plots and finalising analysis

@@
 if (!require("pacman")) install.packages("pacman")
-  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, gamlss,
+  pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
                  gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
@@
 ```{r h2}
-# Summary statistics
-# First, change name of manipulation
+# Change name of manipulation
 vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal')) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal')) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal')) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral')) +
+  facet_wrap(~manipulation)
+
   geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
@@
 ```
+
+# Same plot, no zeros
+```{r h2nozero}
+# First, remove zeros from trials to better represent analysis
+vas_nozero <- all_vas %>% 
+  filter(VAS > 0)
+
+vas_meds1 <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
+                      median, data = vas_nozero)
+
+# Change name of manipulation
+vas_meds1$manipulation <- factor(vas_meds1$manipulation, labels = c('Non-TGI', 'TGI'))
+h2_sum1 <- summarySEwithin(data = vas_meds1, measurevar = 'VAS', 
+                          withinvars = c('quality','manipulation','cold_probe'))
+
+# organise data for plotting
+vas_meds1$cold_probe <- factor(vas_meds1$cold_probe, levels = 
+                                c('proximal', 'distal', 'rostral', 'caudal'))
+h2_sum1$cold_probe <- factor(h2_sum1$cold_probe, levels = 
+                                c('proximal', 'distal', 'rostral', 'caudal'))
+# recoding cold probe location so can jitter
+vas_meds1$cold_code <- factor(vas_meds1$cold_probe, labels = 
+                                c(1,2,3,4))
+h2_sum1$cold_code <- factor(h2_sum1$cold_probe, labels = 
+                                c(1,2,3,4))
+# creating jitter
+vas_meds1$xj <- jitter(as.numeric(vas_meds1$cold_code), amount = .05)
+
+nudge1 = -.1
+nudge2 = .1
+
+# TRY THESE PLOTS WITH BOX JITTER? gghalves may be too messy
+
+# plot all data - half-violins
+# COLD
+ggplot(data = vas_meds1 %>% 
+         filter(quality == 'cold'),
+       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'proximal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'distal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'rostral'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'caudal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  # summary stats
+  geom_point(data = h2_sum1 %>% 
+               filter(quality == 'cold'), 
+             aes(x = as.numeric(cold_code), y = VAS),
+             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
+             position = position_nudge(nudge1)) +
+  geom_errorbar(data = h2_sum1 %>% 
+               filter(quality == 'cold'), 
+               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
+               colour = 'grey20', width = .05, size = .7,
+               position = position_nudge(nudge1)) +
+  geom_line(data = h2_sum1 %>% 
+              filter(quality == 'cold'), 
+              aes(x = as.numeric(cold_code), y = VAS), 
+              colour = 'grey20', size = .7, alpha = .6,
+              position = position_nudge(nudge1)) +
+  facet_wrap(~manipulation) +
+  scale_colour_manual(values = c(blue[4], blue[6])) +
+  scale_fill_manual(values = c(blue[4], blue[6])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  labs(title = 'Cold ratings', x = NULL, 
+         y = 'VAS Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_cold_plot
+
+# WARM
+ggplot(data = vas_meds1 %>% 
+         filter(quality == 'warm'),
+       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'proximal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'distal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'rostral'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'caudal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  # summary stats
+  geom_point(data = h2_sum1 %>% 
+               filter(quality == 'warm'), 
+             aes(x = as.numeric(cold_code), y = VAS),
+             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
+             position = position_nudge(nudge1)) +
+  geom_errorbar(data = h2_sum1 %>% 
+               filter(quality == 'warm'), 
+               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
+               colour = 'grey20', width = .05, size = .7,
+               position = position_nudge(nudge1)) +
+  geom_line(data = h2_sum1 %>% 
+              filter(quality == 'warm'), 
+              aes(x = as.numeric(cold_code), y = VAS), 
+              colour = 'grey20', size = .7, alpha = .6,
+              position = position_nudge(nudge1)) +
+  facet_wrap(~manipulation) +
+  scale_colour_manual(values = c(oran[4], oran[6])) +
+  scale_fill_manual(values = c(oran[4], oran[6])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  labs(title = 'Warm ratings', x = 'Location of cold probe', 
+         y = NULL) +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_warm_plot
+
+# BURN
+ggplot(data = vas_meds1 %>% 
+         filter(quality == 'burn'),
+       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
+  geom_half_violin(
+    data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'distal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'rostral'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  geom_half_violin(
+    data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'caudal'),
+    aes(x = xj, y = VAS), 
+    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
+  # summary stats
+  geom_point(data = h2_sum1 %>% 
+               filter(quality == 'burn'), 
+             aes(x = as.numeric(cold_code), y = VAS),
+             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
+             position = position_nudge(nudge1)) +
+  geom_errorbar(data = h2_sum1 %>% 
+               filter(quality == 'burn'), 
+               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
+               colour = 'grey20', width = .05, size = .7,
+               position = position_nudge(nudge1)) +
+  geom_line(data = h2_sum1 %>% 
+              filter(quality == 'burn'), 
+              aes(x = as.numeric(cold_code), y = VAS), 
+              colour = 'grey20', size = .7, alpha = .6,
+              position = position_nudge(nudge1)) +
+  facet_wrap(~manipulation) +
+  scale_colour_manual(values = c(purp[4], purp[6])) +
+  scale_fill_manual(values = c(purp[4], purp[6])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  labs(title = 'Burn ratings', x = 'Location of cold probe', 
+         y = 'VAS Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_burn_plot
+
+# arrange entire plot
+h21_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
+                     nrow = 2, ncol = 2)
+h21_plot
+
+ggsave('h2_nozero_plot.png', h21_plot, device = NULL, path = anaPath,
+       width = 10, height = 6.5, dpi = 600)
+```
+
+# Differences
+```{r h2diff}
+# recode cold_location and condition to reduce levels in regression
+vas_meds$cold_cond[vas_meds$cold_probe == 'distal'] <- 'dist_rost' 
+vas_meds$cold_cond[vas_meds$cold_probe == 'rostral'] <- 'dist_rost' 
+vas_meds$cold_cond[vas_meds$cold_probe == 'proximal'] <- 'prox_caud' 
+vas_meds$cold_cond[vas_meds$cold_probe == 'caudal'] <- 'prox_caud'
+
+# then pivot wider and calculate difference
+vas_h2_diff <- vas_meds %>% 
+  select(-c(cold_code, xj, cold_probe)) %>% 
+  pivot_wider(id_cols = c(ID, quality, manipulation, condition), 
+              names_from = cold_cond, values_from = VAS) %>% 
+  mutate(difference = prox_caud - dist_rost)
+# recode quality
+vas_h2_diff$quality <- factor(vas_h2_diff$quality,
+                           levels = c('cold', 'warm', 'burn'))
+# summary statistics
+h2_diff_sum <- summarySEwithin(data = vas_h2_diff, measurevar = 'difference',
+                               withinvars = c('manipulation', 'quality', 'condition'))
+
+# plot the differences - within
+ggplot(data = vas_h2_diff %>% 
+         filter(condition == 'within'), 
+       aes(manipulation, difference, colour = quality)) +
+  geom_hline(yintercept = 0) +
+  geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5) +
+  geom_point(data = h2_diff_sum %>% 
+               filter(condition == 'within'), 
+             aes(manipulation, difference), colour = 'grey15',
+             fill = 'grey15',
+             shape = 21, size = 3) +
+  geom_errorbar(data = h2_diff_sum %>% 
+               filter(condition == 'within'), 
+               aes(manipulation, ymin = difference-ci, ymax = difference+ci),
+               width = .1, size = .7, colour = 'grey15') +
+  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
+  labs(title = 'Hypothesis 2 Cold & Warm Afferents: Within',
+       y = 'Proximal - Distal VAS Ratings', x = NULL) +
+  facet_wrap(~quality) +
+  theme_classic()
+
+# plot the differences - across
+ggplot(data = vas_h2_diff %>% 
+         filter(condition == 'across'), 
+       aes(manipulation, difference, colour = quality)) +
+  geom_hline(yintercept = 0) +
+  geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5) +
+  geom_point(data = h2_diff_sum %>% 
+               filter(condition == 'across'), 
+             aes(manipulation, difference), colour = 'grey15',
+             fill = 'grey15',
+             shape = 21, size = 3) +
+  geom_errorbar(data = h2_diff_sum %>% 
+               filter(condition == 'across'), 
+               aes(manipulation, ymin = difference-ci, ymax = difference+ci),
+               width = .1, size = .7, colour = 'grey15') +
+  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
+  labs(title = 'Hypothesis 2 Cold & Warm Afferents: Across',
+       y = 'Caudal - Rostral VAS Ratings', x = NULL) +
+  facet_wrap(~quality) +
+  theme_classic()
+```
+
 # Plot 32 burn responders seperately
@@
 # transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
-df_long$VAS <- df_long$VAS/100
+#df_long$VAS <- df_long$VAS/100
 df_long$ID <- factor(df_long$ID)
@@
 mc
+
+Anova(model.cold)
 
@@
 mw
+
+Anova(model.warm)
 ```
@@
 mb
+
+Anova(model.burn)
 
@@
 ```
-# Run individual models on within and across dermatomes for H2
-Directly compare proximal-distal and rostral-caudal results for each quality
-
-# Cold - within and across
-```{r cold_indiv}
-# seperate data-frames
-within <- df_long %>% 
-  filter(condition == 'within')
-across <-  df_long %>% 
-  filter(condition == 'across')
-
-# within
-model.wcold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'cold'),
-                      na.action = na.omit) 
-mwc <- summary(model.wcold)
-mwc
-
-# across
-model.acold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'cold'),
-                      na.action = na.omit) 
-mac <- summary(model.acold)
-mac
-```
-
-# Warm - within and across
-```{r warm_indiv}
-# within
-model.wwarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'warm'),
-                      na.action = na.omit) 
-mww <- summary(model.wwarm)
-mww
-
-# across
-model.awarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'warm'),
-                      na.action = na.omit) 
-maw <- summary(model.awarm)
-maw
-```
-
-# Burn - within and across
-```{r burn_indiv}
-# isolate responders only
-within <- df_long %>% 
-  filter(condition == 'within' & responder == 1)
-across <-  df_long %>% 
-  filter(condition == 'across' & responder == 1)
-
-# within
-model.wburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'burn'),
-                      na.action = na.omit) 
-mwb <- summary(model.wburn)
-mwb
-
-# across
-model.aburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'burn'),
-                      na.action = na.omit) 
-mab <- summary(model.aburn)
-mab
-```
-
 # EXPLORATORY HYPOTHESES
@@
 ```
+
 # Scatter plots
@@
 ```
+
+# Run individual models on within and across dermatomes for H2
+Directly compare proximal-distal and rostral-caudal results for each quality
+
+# Cold - within and across
+```{r cold_indiv}
+# seperate data-frames
+within <- df_long %>% 
+  filter(condition == 'within')
+across <-  df_long %>% 
+  filter(condition == 'across')
+
+# within
+model.wcold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = within %>% filter(quality == 'cold'),
+                      na.action = na.omit) 
+mwc <- summary(model.wcold)
+mwc
+
+# across
+model.acold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = across %>% filter(quality == 'cold'),
+                      na.action = na.omit) 
+mac <- summary(model.acold)
+mac
+```
+
+# Warm - within and across
+```{r warm_indiv}
+# within
+model.wwarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = within %>% filter(quality == 'warm'),
+                      na.action = na.omit) 
+mww <- summary(model.wwarm)
+mww
+
+# across
+model.awarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = across %>% filter(quality == 'warm'),
+                      na.action = na.omit) 
+maw <- summary(model.awarm)
+maw
+```
+
+# Burn - within and across
+```{r burn_indiv}
+# isolate responders only
+within <- df_long %>% 
+  filter(condition == 'within' & responder == 1)
+across <-  df_long %>% 
+  filter(condition == 'across' & responder == 1)
+
+# within
+model.wburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = within %>% filter(quality == 'burn'),
+                      na.action = na.omit) 
+mwb <- summary(model.wburn)
+mwb
+
+# across
+model.aburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                (1|ID),
+                      family = glmmTMB::beta_family(),
+                      ziformula = ~1+manipulation,
+                      data = across %>% filter(quality == 'burn'),
+                      na.action = na.omit) 
+mab <- summary(model.aburn)
+mab
+```

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
recreating as box plots

@@
 
-# TRY THESE PLOTS WITH BOX JITTER? gghalves may be too messy
-
-# plot all data - half-violins
+# plot all data
 # COLD
@@
   geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'proximal')) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'distal')) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'caudal')) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'rostral')) +
-  facet_wrap(~manipulation)
-
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum %>% 
-               filter(quality == 'cold'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum %>% 
-               filter(quality == 'cold'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
-               position = position_nudge(nudge1)) +
-  geom_line(data = h2_sum %>% 
-              filter(quality == 'cold'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(blue[4], blue[6])) +
-  scale_fill_manual(values = c(blue[4], blue[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  scale_colour_manual(values = c(blue[5], blue[7])) +
+  scale_fill_manual(values = c(blue[2], blue[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
   labs(title = 'Cold ratings', x = NULL, 
@@
   theme(legend.position = 'none') -> h2_cold_plot
+h2_cold_plot
 
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum %>% 
-               filter(quality == 'warm'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum %>% 
-               filter(quality == 'warm'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
-               position = position_nudge(nudge1)) +
-  geom_line(data = h2_sum %>% 
-              filter(quality == 'warm'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(oran[4], oran[6])) +
-  scale_fill_manual(values = c(oran[4], oran[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Warm ratings', x = 'Location of cold probe', 
-         y = NULL) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  scale_colour_manual(values = c(oran[5], oran[7])) +
+  scale_fill_manual(values = c(oran[2], oran[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Warm ratings', x = NULL, 
+         y = 'VAS Rating (0-100)') +
   ylim(-0.5,100) +
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum %>% 
-               filter(quality == 'burn'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum %>% 
-               filter(quality == 'burn'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
-               position = position_nudge(nudge1)) +
-  geom_line(data = h2_sum %>% 
-              filter(quality == 'burn'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(purp[4], purp[6])) +
-  scale_fill_manual(values = c(purp[4], purp[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Burn ratings', x = 'Location of cold probe', 
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  scale_colour_manual(values = c(purp[5], purp[7])) +
+  scale_fill_manual(values = c(purp[2], purp[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Burn ratings', x = NULL, 
          y = 'VAS Rating (0-100)') +
@@
 h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
-                     nrow = 2, ncol = 2)
+                     nrow = 2, ncol = 2,
+                     common.legend = TRUE)
 h2_plot
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum1 %>% 
-               filter(quality == 'cold'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum1 %>% 
-               filter(quality == 'cold'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
-               position = position_nudge(nudge1)) +
-  geom_line(data = h2_sum1 %>% 
-              filter(quality == 'cold'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(blue[4], blue[6])) +
-  scale_fill_manual(values = c(blue[4], blue[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  scale_colour_manual(values = c(blue[5], blue[7])) +
+  scale_fill_manual(values = c(blue[2], blue[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
   labs(title = 'Cold ratings', x = NULL, 
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum1 %>% 
-               filter(quality == 'warm'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum1 %>% 
-               filter(quality == 'warm'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
-               position = position_nudge(nudge1)) +
-  geom_line(data = h2_sum1 %>% 
-              filter(quality == 'warm'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(oran[4], oran[6])) +
-  scale_fill_manual(values = c(oran[4], oran[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Warm ratings', x = 'Location of cold probe', 
-         y = NULL) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  scale_colour_manual(values = c(oran[5], oran[7])) +
+  scale_fill_manual(values = c(oran[2], oran[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Warm ratings', x = NULL, 
+         y = 'VAS Rating (0-100)') +
   ylim(-0.5,100) +
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum1 %>% 
-               filter(quality == 'burn'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum1 %>% 
-               filter(quality == 'burn'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
-               position = position_nudge(nudge1)) +
-  geom_line(data = h2_sum1 %>% 
-              filter(quality == 'burn'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(purp[4], purp[6])) +
-  scale_fill_manual(values = c(purp[4], purp[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Burn ratings', x = 'Location of cold probe', 
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  scale_colour_manual(values = c(purp[5], purp[7])) +
+  scale_fill_manual(values = c(purp[2], purp[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Burn ratings', x = NULL, 
          y = 'VAS Rating (0-100)') +

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
Ãcompleting plots for h2

--- 2022-12-15 analysis/tgi-spinal_analysis.Rmd
@@
   geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'proximal')) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'distal')) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'caudal')) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'rostral')) +
-  facet_wrap(~manipulation)
-
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum %>% 
-               filter(quality == 'cold'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum %>% 
-               filter(quality == 'cold'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
     position = position_nudge(nudge1)) + 
   geom_line(data = h2_sum %>% 
-              filter(quality == 'cold'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(blue[4], blue[6])) +
-  scale_fill_manual(values = c(blue[4], blue[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+    filter(quality == 'cold', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
+  scale_colour_manual(values = c(blue[5], blue[7])) +
+  scale_fill_manual(values = c(blue[2], blue[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
   labs(title = 'Cold ratings', x = NULL, 
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum %>% 
-               filter(quality == 'warm'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum %>% 
-               filter(quality == 'warm'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
     position = position_nudge(nudge1)) + 
   geom_line(data = h2_sum %>% 
-              filter(quality == 'warm'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(oran[4], oran[6])) +
-  scale_fill_manual(values = c(oran[4], oran[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Warm ratings', x = 'Location of cold probe', 
-         y = NULL) +
+    filter(quality == 'warm', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
+  scale_colour_manual(values = c(oran[5], oran[7])) +
+  scale_fill_manual(values = c(oran[2], oran[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Warm ratings', x = NULL, 
+         y = 'VAS Rating (0-100)') +
   ylim(-0.5,100) +
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum %>% 
-               filter(quality == 'burn'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum %>% 
-               filter(quality == 'burn'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
     position = position_nudge(nudge1)) + 
   geom_line(data = h2_sum %>% 
-              filter(quality == 'burn'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(purp[4], purp[6])) +
-  scale_fill_manual(values = c(purp[4], purp[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Burn ratings', x = 'Location of cold probe', 
+    filter(quality == 'burn', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
+  scale_colour_manual(values = c(purp[5], purp[7])) +
+  scale_fill_manual(values = c(purp[2], purp[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Burn ratings', x = NULL, 
          y = 'VAS Rating (0-100)') +
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum1 %>% 
-               filter(quality == 'cold'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum1 %>% 
-               filter(quality == 'cold'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum1 %>% 
+    filter(quality == 'cold', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
     position = position_nudge(nudge1)) + 
   geom_line(data = h2_sum1 %>% 
-              filter(quality == 'cold'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(blue[4], blue[6])) +
-  scale_fill_manual(values = c(blue[4], blue[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
+    filter(quality == 'cold', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
+  scale_colour_manual(values = c(blue[5], blue[7])) +
+  scale_fill_manual(values = c(blue[2], blue[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
   labs(title = 'Cold ratings', x = NULL, 
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum1 %>% 
-               filter(quality == 'warm'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum1 %>% 
-               filter(quality == 'warm'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum1 %>% 
+    filter(quality == 'warm', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
     position = position_nudge(nudge1)) + 
   geom_line(data = h2_sum1 %>% 
-              filter(quality == 'warm'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(oran[4], oran[6])) +
-  scale_fill_manual(values = c(oran[4], oran[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Warm ratings', x = 'Location of cold probe', 
-         y = NULL) +
+    filter(quality == 'warm', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
+  scale_colour_manual(values = c(oran[5], oran[7])) +
+  scale_fill_manual(values = c(oran[2], oran[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Warm ratings', x = NULL, 
+         y = 'VAS Rating (0-100)') +
   ylim(-0.5,100) +
@@
        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
-  geom_half_violin(
-    data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'proximal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'distal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'rostral'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  geom_half_violin(
-    data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'caudal'),
-    aes(x = xj, y = VAS), 
-    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
-  # summary stats
-  geom_point(data = h2_sum1 %>% 
-               filter(quality == 'burn'), 
-             aes(x = as.numeric(cold_code), y = VAS),
-             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
-             position = position_nudge(nudge1)) +
-  geom_errorbar(data = h2_sum1 %>% 
-               filter(quality == 'burn'), 
-               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
-               colour = 'grey20', width = .05, size = .7,
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_boxjitter(data = vas_meds1 %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), width = .2,
+      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum1 %>% 
+    filter(quality == 'burn', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
     position = position_nudge(nudge1)) + 
   geom_line(data = h2_sum1 %>% 
-              filter(quality == 'burn'), 
-              aes(x = as.numeric(cold_code), y = VAS), 
-              colour = 'grey20', size = .7, alpha = .6,
-              position = position_nudge(nudge1)) +
-  facet_wrap(~manipulation) +
-  scale_colour_manual(values = c(purp[4], purp[6])) +
-  scale_fill_manual(values = c(purp[4], purp[6])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
-  labs(title = 'Burn ratings', x = 'Location of cold probe', 
+    filter(quality == 'burn', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
+  scale_colour_manual(values = c(purp[5], purp[7])) +
+  scale_fill_manual(values = c(purp[2], purp[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(title = 'Burn ratings', x = NULL, 
          y = 'VAS Rating (0-100)') +

### 2022-12-16 analysis/tgi-spinal_analysis.Rmd
modelling marginal effects

@@
   pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
-                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
+                 ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                  modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
@@
 
-model.cold1 = gamlss(VAS ~ manipulation * condition * cold_cond + procedure + trial_n +
-                                random(ID),
-                    nu.formula = ~ 1+manipulation,
-                    tau.formula = ~ 1+manipulation,
-                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
-                                   tau.link = 'logit'),
-                    data = test %>% filter(quality == 'cold'),
-                    trace = F) 
-mc1 <- summary(model.cold1)
-mc1
+df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
+
+cold.eff <- glm(bin~1+manipulation, 
+                  family = binomial(link = 'logit'),
+                  data = df_long %>% filter(quality == 'cold'))
+summary(cold.eff)
+
+# marginal effects from glm
+eff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
+plot(eff)
+
+eff <- ggeffects::ggeffect(model.cold, terms = c('condition', 'manipulation', 'cold_cond'),
+                           type = 'random', ci.lvl = .95)
+plot(eff)
 ```
@@
 
-model.burn1 = gamlss(VAS ~ manipulation * condition * cold_cond + trial_n +
-                                random(ID) + random(as.factor(procedure)),
-                    nu.formula = ~ 1+manipulation,
-                    tau.formula = ~ 1+manipulation,
-                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
-                                   tau.link = 'logit'),
-                    data = df_resp %>% filter(quality == 'burn'),
-                    trace = F) 
-mc1 <- summary(model.burn1)
-mc1
 ```

### 2022-12-16 analysis/tgi-spinal_analysis.Rmd
additions required for writing up - e.g. R2

--- 2022-12-15 analysis/tgi-spinal_analysis.Rmd
@@
   pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
-                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
-                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
+                 ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
+                 modelsummary, mumin, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                  rsample, rstatix, simr, tibble, tidyverse, wesanderson
@@
 vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
-h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
-                          withinvars = c('quality','manipulation','cold_probe'))
+h2_sum <- aggregate(VAS~quality*manipulation*cold_probe, median, data = vas_meds)
 
@@
 nudge2 = .1
+```
 
+# All dat plot
+
+```{r}
 # plot all data
@@
       outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1)) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
   scale_colour_manual(values = c(blue[5], blue[7])) +
@@
   theme_classic() +
-  theme(legend.position = 'none') -> h2_cold_plot
-h2_cold_plot
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 11),
+        axis.title = element_text(size = 12),
+        title = element_text(size = 12)) -> h2_cold_plot
 
@@
       outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1)) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
   scale_colour_manual(values = c(oran[5], oran[7])) +
@@
   theme_classic() +
-  theme(legend.position = 'none') -> h2_warm_plot
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 11),
+        axis.title = element_text(size = 12),
+        title = element_text(size = 12)) -> h2_warm_plot
 
@@
       outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1)) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2)) +
   scale_colour_manual(values = c(purp[5], purp[7])) +
@@
   theme_classic() +
-  theme(legend.position = 'none')  -> h2_burn_plot
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 11),
+        axis.title = element_text(size = 12),
+        title = element_text(size = 12))  -> h2_burn_plot
 
@@
 h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
-                     nrow = 2, ncol = 2,
-                     common.legend = TRUE)
+                     nrow = 2, ncol = 2)
 h2_plot
@@
 ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
-       width = 10, height = 6.5, dpi = 600)
-```
-
-# Same plot, no zeros
-```{r h2nozero}
-# First, remove zeros from trials to better represent analysis
-vas_nozero <- all_vas %>% 
-  filter(VAS > 0)
-
-vas_meds1 <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
-                      median, data = vas_nozero)
-
-# Change name of manipulation
-vas_meds1$manipulation <- factor(vas_meds1$manipulation, labels = c('Non-TGI', 'TGI'))
-h2_sum1 <- summarySEwithin(data = vas_meds1, measurevar = 'VAS', 
-                          withinvars = c('quality','manipulation','cold_probe'))
-
-# organise data for plotting
-vas_meds1$cold_probe <- factor(vas_meds1$cold_probe, levels = 
-                                c('proximal', 'distal', 'rostral', 'caudal'))
-h2_sum1$cold_probe <- factor(h2_sum1$cold_probe, levels = 
-                                c('proximal', 'distal', 'rostral', 'caudal'))
-# recoding cold probe location so can jitter
-vas_meds1$cold_code <- factor(vas_meds1$cold_probe, labels = 
-                                c(1,2,3,4))
-h2_sum1$cold_code <- factor(h2_sum1$cold_probe, labels = 
-                                c(1,2,3,4))
-# creating jitter
-vas_meds1$xj <- jitter(as.numeric(vas_meds1$cold_code), amount = .05)
-
-nudge1 = -.1
-nudge2 = .1
-
-# plot all data
-# COLD
-ggplot(data = vas_meds1 %>% 
-         filter(quality == 'cold'),
-       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  scale_colour_manual(values = c(blue[5], blue[7])) +
-  scale_fill_manual(values = c(blue[2], blue[4])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Cold ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
-  ylim(-0.5,100) +
-  theme_classic() +
-  theme(legend.position = 'none') -> h2_cold_plot
-h2_cold_plot
-
-# WARM
-ggplot(data = vas_meds1 %>% 
-         filter(quality == 'warm'),
-       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  scale_colour_manual(values = c(oran[5], oran[7])) +
-  scale_fill_manual(values = c(oran[2], oran[4])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Warm ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
-  ylim(-0.5,100) +
-  theme_classic() +
-  theme(legend.position = 'none') -> h2_warm_plot
-
-# BURN
-ggplot(data = vas_meds1 %>% 
-         filter(quality == 'burn'),
-       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds1 %>% 
-    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  scale_colour_manual(values = c(purp[5], purp[7])) +
-  scale_fill_manual(values = c(purp[2], purp[4])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Burn ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
-  ylim(-0.5,100) +
-  theme_classic() +
-  theme(legend.position = 'none')  -> h2_burn_plot
-
-# arrange entire plot
-h21_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
-                     nrow = 2, ncol = 2)
-h21_plot
-
-ggsave('h2_nozero_plot.png', h21_plot, device = NULL, path = anaPath,
-       width = 10, height = 6.5, dpi = 600)
+       width = 10, height = 7, dpi = 600)
 ```
@@
   scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-  labs(title = 'Hypothesis 2 Cold & Warm Afferents: Within',
+  labs(title = 'Within: Proximal vs. Distal',
        y = 'Proximal - Distal VAS Ratings', x = NULL) +
   facet_wrap(~quality) +
-  theme_classic()
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_diff_within
 
@@
   scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-  labs(title = 'Hypothesis 2 Cold & Warm Afferents: Across',
+  labs(title = 'Across: Rostral vs. Caudal',
        y = 'Caudal - Rostral VAS Ratings', x = NULL) +
   facet_wrap(~quality) +
-  theme_classic()
+  theme_classic() +
+  theme(legend.position = 'none') -> h2_diff_across
+
+# arrange entire plot
+h2diff_plot <- ggarrange(h2_diff_within, h2_diff_across,
+                     nrow = 2, ncol = 1)
+h2diff_plot
+
+ggsave('h2_diff_plot.png', h2diff_plot, device = NULL, path = anaPath,
+       width = 6, height = 9, dpi = 600)
 ```
@@
 Anova(model.cold)
+# get Rsq with the mumin package
 
-model.cold1 = gamlss(VAS ~ manipulation * condition * cold_cond + procedure + trial_n +
-                                random(ID),
-                    nu.formula = ~ 1+manipulation,
-                    tau.formula = ~ 1+manipulation,
-                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
-                                   tau.link = 'logit'),
-                    data = test %>% filter(quality == 'cold'),
-                    trace = F) 
-mc1 <- summary(model.cold1)
-mc1
+# Getting the marginal effects for plotting
+# First the zeros - create new lm mo
+df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
+
+cold.eff <- glm(bin~1+manipulation, 
+                  family = binomial(link = 'logit'),
+                  data = df_long %>% filter(quality == 'cold'))
+summary(cold.eff)
+
+eff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
+plot(eff)
+
+eff <- ggeffects::ggeffect(model.cold, terms = c('condition', 'manipulation', 'cold_cond'),
+                           type = 'random', ci.lvl = .95)
+plot(eff)
 ```

### 2023-01-04 analysis/tgi-spinal_analysis.Rmd
pushing to git
marginal effects plotting

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, message = FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
                  ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
-                 modelsummary, mumin, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
+                 modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                  rsample, rstatix, simr, tibble, tidyverse, wesanderson
@@
 df_res <- df_res %>%
-  mutate(condition = recode(condition, '1' = 'within', '2' = 'across'),
-         cold_probe = recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
+  mutate(condition = dplyr::recode(condition, '1' = 'within', '2' = 'across'),
+         cold_probe = dplyr::recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
                              'dist' = 'distal', 'prox' = 'proximal'))
@@
 # get Rsq with the mumin package
+```
+# Marginal effect plots of full model - cold
+```{r}
+cold_eff <- ggeffects::ggpredict(model.cold, terms = c('cold_cond', 'manipulation', 'condition'),
+                           ci.lvl = .95)
+# changing labels for plotting
+cold_eff$group <- factor(cold_eff$group, labels = c('Non-TGI', 'TGI'))
+cold_eff <- cold_eff %>% 
+  mutate(label = 
+           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
+                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
+                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
+                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
+         )
 
-# Getting the marginal effects for plotting
-# First the zeros - create new lm mo
-df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
+cold_eff$label = factor(cold_eff$label, levels = c('proximal','distal','caudal','rostral'))
 
-cold.eff <- glm(bin~1+manipulation, 
-                  family = binomial(link = 'logit'),
-                  data = df_long %>% filter(quality == 'cold'))
-summary(cold.eff)
+# plotting - within
+ggplot(data = cold_eff %>% 
+         filter(facet == 'within'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3)) +
+  geom_line(position = position_dodge(.3)) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1) +
+  ylim(0.1, 0.5) +
+  theme_bw()
+# plotting - across
+ggplot(data = cold_eff %>% 
+         filter(facet == 'across'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3)) +
+  geom_line(position = position_dodge(.3)) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1) +
+  ylim(0.1, 0.5) +
+  theme_bw() +
+  theme(legend.title = element_blank())
+```
 
-eff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
-plot(eff)
-
-eff <- ggeffects::ggeffect(model.cold, terms = c('condition', 'manipulation', 'cold_cond'),
-                           type = 'random', ci.lvl = .95)
-plot(eff)
-```
 # Warm
@@
 Anova(model.warm)
+
+eff <- ggeffects::ggeffect(model.warm, terms = c('cold_cond','condition'),
+                           type = 'random', ci.lvl = .95)
+plot(eff)
 ```
@@
 Anova(model.burn)
+
+```
+
+# Zero inflation marginal effects plot of all models
+```{r zero_plots}
+# Getting the marginal effects for plotting
+# First the zeros - create new lm mo
+df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
+
+# model for each VAS
+cold.eff <- glm(bin~1+manipulation, 
+                  family = binomial(link = 'logit'),
+                  data = df_long %>% filter(quality == 'cold'))
+summary(cold.eff)
+
+# Data-frames
+cold_zeff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
+# changing labels for plotting
+cold_zeff$x <- factor(cold_zeff$x, labels = c('Non-TGI', 'TGI'))
+
+# plotting
+ggplot(cold_zeff, aes(x, predicted)) +
+  geom_point() +
+  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
+                width = .1) +
+  theme_bw()
 

### 2023-01-04 analysis/tgi-spinal_analysis.Rmd
marginal effects - warm

@@
        aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3)) +
-  geom_line(position = position_dodge(.3)) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
   geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1) +
+                position = position_dodge(.3), width = .1, size = .8) +
   ylim(0.1, 0.5) +
-  theme_bw()
+  labs(x = NULL, y = 'Predicted Cold Rating (0 - 1)') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(blue[4], blue[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_coldw_eff
 # plotting - across
@@
        aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3)) +
-  geom_line(position = position_dodge(.3)) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
   geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1) +
+                position = position_dodge(.3), width = .1, size = .8) +
   ylim(0.1, 0.5) +
-  theme_bw() +
-  theme(legend.title = element_blank())
+  labs(x = NULL, y = '') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(blue[4], blue[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_colda_eff
+
+# combine
+plot_cold_eff <- ggarrange(plot_coldw_eff, plot_colda_eff,
+                           ncol = 2, nrow = 1,
+                           common.legend = TRUE,
+                           legend = 'bottom')
+plot_cold_eff
 ```
@@
 Anova(model.warm)
+```
+# Marginal effect plots of full model - warm
+```{r}
+warm_eff <- ggeffects::ggpredict(model.warm, terms = c('cold_cond', 'manipulation', 'condition'),
+                            ci.lvl = .95)
+# changing labels for plotting
+warm_eff$group <- factor(warm_eff$group, labels = c('Non-TGI', 'TGI'))
+warm_eff <- warm_eff %>% 
+  mutate(label = 
+           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
+                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
+                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
+                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
+         )
 
-eff <- ggeffects::ggeffect(model.warm, terms = c('cold_cond','condition'),
-                           type = 'random', ci.lvl = .95)
-plot(eff)
+warm_eff$label = factor(warm_eff$label, levels = c('proximal','distal','caudal','rostral'))
+
+# plotting - within
+ggplot(data = warm_eff %>% 
+         filter(facet == 'within'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.4) +
+  labs(x = NULL, y = 'Predicted Warm Rating (0 - 1)') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(oran[4], oran[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_warmw_eff
+# plotting - across
+ggplot(data = warm_eff %>% 
+         filter(facet == 'across'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.4) +
+  labs(x = NULL, y = '') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(oran[4], oran[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_warma_eff
+
+# combine
+plot_warm_eff <- ggarrange(plot_warmw_eff, plot_warma_eff,
+                           ncol = 2, nrow = 1,
+                           common.legend = TRUE,
+                           legend = 'bottom')
+plot_warm_eff
 ```

### 2023-01-04 analysis/tgi-spinal_analysis.Rmd
completed marginal effect plots

--- 2023-01-04 analysis/tgi-spinal_analysis.Rmd
@@
        aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3)) +
-  geom_line(position = position_dodge(.3)) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
   geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1) +
-  ylim(0.1, 0.5) +
-  theme_bw()
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.5) +
+  labs(x = NULL, y = 'Predicted Cold Rating (0 - 1)') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(blue[4], blue[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_coldw_eff
 # plotting - across
@@
        aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3)) +
-  geom_line(position = position_dodge(.3)) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
   geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1) +
-  ylim(0.1, 0.5) +
-  theme_bw() +
-  theme(legend.title = element_blank())
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.5) +
+  labs(x = NULL, y = '') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(blue[4], blue[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 10)) -> plot_colda_eff
+
+# combine
+plot_cold_eff1 <- ggarrange(plot_coldw_eff, plot_colda_eff,
+                           ncol = 2, nrow = 1,
+                           common.legend = TRUE,
+                           legend = 'right')
+plot_cold_eff1
 ```
@@
 Anova(model.warm)
-
-eff <- ggeffects::ggeffect(model.warm, terms = c('cold_cond','condition'),
-                           type = 'random', ci.lvl = .95)
-plot(eff)
-```
-
+```
+# Marginal effect plots of full model - warm
+```{r}
+warm_eff <- ggeffects::ggpredict(model.warm, terms = c('cold_cond', 'manipulation', 'condition'),
+                            ci.lvl = .95)
+# changing labels for plotting
+warm_eff$group <- factor(warm_eff$group, labels = c('Non-TGI', 'TGI'))
+warm_eff <- warm_eff %>% 
+  mutate(label = 
+           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
+                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
+                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
+                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
+         )
+
+warm_eff$label = factor(warm_eff$label, levels = c('proximal','distal','caudal','rostral'))
+
+# plotting - within
+ggplot(data = warm_eff %>% 
+         filter(facet == 'within'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.5) +
+  labs(x = NULL, y = 'Predicted Warm Rating (0 - 1)') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(oran[4], oran[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_warmw_eff
+# plotting - across
+ggplot(data = warm_eff %>% 
+         filter(facet == 'across'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.5) +
+  labs(x = NULL, y = '') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(oran[4], oran[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 10)) -> plot_warma_eff
+
+# combine
+plot_warm_eff1 <- ggarrange(plot_warmw_eff, plot_warma_eff,
+                           ncol = 2, nrow = 1,
+                           common.legend = TRUE,
+                           legend = 'right')
+plot_warm_eff1
+```
 # Burn
@@
 Anova(model.burn)
-
+```
+
+# Marginal effect plots of full model - burn
+```{r}
+burn_eff <- ggeffects::ggpredict(model.burn, terms = c('cold_cond', 'manipulation', 'condition'),
+                            ci.lvl = .95)
+# changing labels for plotting
+burn_eff$group <- factor(burn_eff$group, labels = c('Non-TGI', 'TGI'))
+burn_eff <- burn_eff %>% 
+  mutate(label = 
+           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
+                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
+                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
+                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
+         )
+
+burn_eff$label = factor(burn_eff$label, levels = c('proximal','distal','caudal','rostral'))
+
+# plotting - within
+ggplot(data = burn_eff %>% 
+         filter(facet == 'within'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.5) +
+  labs(x = NULL, y = 'Predicted Burn Rating (0 - 1)') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(purp[4], purp[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 11)) -> plot_burnw_eff
+# plotting - across
+ggplot(data = burn_eff %>% 
+         filter(facet == 'across'), 
+       aes(label, predicted, group = group, colour = group),) +
+  geom_point(position = position_dodge(.3), size = 2.5) +
+  geom_line(position = position_dodge(.3), size = 1) +
+  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
+                position = position_dodge(.3), width = .1, size = .8) +
+  ylim(0, 0.5) +
+  labs(x = NULL, y = '') +
+  facet_wrap(~facet) +
+  scale_colour_manual(values = c(purp[4], purp[7])) +
+  theme_classic() +
+  theme(legend.title = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12),
+        strip.text = element_text(size = 12),
+        legend.text = element_text(size = 10)) -> plot_burna_eff
+
+# combine
+plot_burn_eff1 <- ggarrange(plot_burnw_eff, plot_burna_eff,
+                           ncol = 2, nrow = 1,
+                           common.legend = TRUE,
+                           legend = 'right')
+plot_burn_eff1
 ```
@@
 df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
+df_resp$bin <- ifelse(df_resp$VAS == 0, 1, 0)
 
 # model for each VAS
-cold.eff <- glm(bin~1+manipulation, 
+# cold
+cold.zeff <- glm(bin~1+manipulation, 
                   family = binomial(link = 'logit'),
                   data = df_long %>% filter(quality == 'cold'))
-summary(cold.eff)
+summary(cold.zeff)
+# warm
+warm.zeff <- glm(bin~1+manipulation, 
+                  family = binomial(link = 'logit'),
+                  data = df_long %>% filter(quality == 'warm'))
+summary(warm.zeff)
+# burn
+burn.zeff <- glm(bin~1+manipulation, 
+                  family = binomial(link = 'logit'),
+                  data = df_resp %>% filter(quality == 'burn'))
+summary(burn.zeff)
 
 # Data-frames
-cold_zeff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
+cold_zeff <- ggeffects::ggeffect(cold.zeff, terms = c('manipulation'))
+warm_zeff <- ggeffects::ggeffect(warm.zeff, terms = c('manipulation'))
+burn_zeff <- ggeffects::ggeffect(burn.zeff, terms = c('manipulation'))
 # changing labels for plotting
 cold_zeff$x <- factor(cold_zeff$x, labels = c('Non-TGI', 'TGI'))
-
-# plotting
-ggplot(cold_zeff, aes(x, predicted)) +
-  geom_point() +
+warm_zeff$x <- factor(warm_zeff$x, labels = c('Non-TGI', 'TGI'))
+burn_zeff$x <- factor(burn_zeff$x, labels = c('Non-TGI', 'TGI'))
+
+# plotting - cold
+ggplot(cold_zeff, aes(x, predicted, colour = x)) +
+  geom_point(size = 2.5) +
   geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
-                width = .1) +
-  theme_bw()
-
-```
-
+                width = .05, size = .8) +
+  labs(y = 'Predicted proportion of zeros', x = NULL) +
+  ylim(0,.25) +
+  scale_colour_manual(values = c(blue[4], blue[7])) +
+  theme_classic() + 
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12)) -> plot_zcold
+
+# warm
+ggplot(warm_zeff, aes(x, predicted, colour = x)) +
+  geom_point(size = 2.5) +
+  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
+                width = .05, size = .8) +
+  labs(y = 'Predicted proportion of zeros', x = NULL) +
+  ylim(.45,.7) +
+  scale_colour_manual(values = c(oran[4], oran[7])) +
+  theme_classic() + 
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12)) -> plot_zwarm
+
+# burn
+ggplot(burn_zeff, aes(x, predicted, colour = x)) +
+  geom_point(size = 2.5) +
+  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
+                width = .05, size = .8) +
+  labs(y = 'Predicted proportion of zeros', x = NULL) +
+  ylim(.05,.3) +
+  scale_colour_manual(values = c(purp[4], purp[7])) +
+  theme_classic() + 
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12)) -> plot_zburn
+```
+
+# Compile all marginal effect plots
+```{r}
+# Cold
+plot_cold_eff <- ggarrange(plot_zcold, plot_cold_eff1,
+                   ncol = 2, nrow = 1,
+                   widths = c(.35,1))
+# add title
+plot_cold_eff <- annotate_figure(plot_cold_eff, top = text_grob("Cold Ratings", 
+                                                size = 12, hjust = 4.05))
+plot_cold_eff
+
+# Warm
+plot_warm_eff <- ggarrange(plot_zwarm, plot_warm_eff1,
+                   ncol = 2, nrow = 1,
+                   widths = c(.35,1))
+# add title
+plot_warm_eff <- annotate_figure(plot_warm_eff, top = text_grob("Warm Ratings", 
+                                                size = 12, hjust = 3.69))
+plot_warm_eff
+
+# Burn
+plot_burn_eff <- ggarrange(plot_zburn, plot_burn_eff1,
+                   ncol = 2, nrow = 1,
+                   widths = c(.35,1))
+# add title
+plot_burn_eff <- annotate_figure(plot_burn_eff, top = text_grob("Burn Ratings", 
+                                                size = 12, hjust = 4.1))
+plot_burn_eff
+
+# Compile all!
+plot_eff <- ggarrange(plot_cold_eff, plot_warm_eff, plot_burn_eff,
+                      ncol = 1, nrow = 3)
+plot_eff
+
+ggsave('h2_effects_plot.png', plot_eff, device = NULL, path = anaPath,
+       width = 9, height = 8, dpi = 600)
+```
 # Run model checks on all

### 2023-02-07 analysis/bayesVAS.Rmd
bayesian VAS analysis - start

---
title: "Bayes VAS"
author: "A.G. Mitchell"
date: "2023-02-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)        # ggplot, dplyr, %>%, and friends
library(brms)             # Bayesian modeling through Stan
library(tidybayes)        # Manipulate Stan objects in a tidy way
library(broom)            # Convert model objects to data frames
library(broom.mixed)      # Convert brms model objects to data frames
library(vdemdata)         # Use data from the Varieties of Democracy (V-Dem) project
library(betareg)          # Run beta regression models
library(extraDistr)       # Use extra distributions like dprop()
library(ggdist)           # Special geoms for posterior distributions
library(gghalves)         # Special half geoms
library(ggbeeswarm)       # Special distribution-shaped point jittering
library(ggrepel)          # Automatically position labels
library(patchwork)        # Combine ggplot objects
library(marginaleffects)  # Calculate marginal effects for frequentist models
library(emmeans)          # Calculate marginal effects in even fancier ways
library(modelsummary)     # Create side-by-side regression tables

set.seed(1234)  # Make everything reproducible

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)

# Custom ggplot theme to make pretty plots
# Get the font at https://fonts.google.com/specimen/Barlow+Semi+Condensed
theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA))
}

# Make labels use Barlow by default
update_geom_defaults("label_repel", list(family = "Barlow Semi Condensed"))
```

### 2023-04-14 analysis/tgi-spinal_analysis-exp1.Rmd
small changes based on pp number- checking responder rate

--- 2023-01-04 analysis/tgi-spinal_analysis.Rmd
@@
 ---
-title: "TGI Spinal Analysis Code"
+title: "TGI Spinal Analysis Code Experiment 1"
 author: "A.G. Mitchell"
@@
 # paths
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
-anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Raw/'
+anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Analysis/'
 ```

### 2023-04-14 analysis/tgi-spinal_analysis-exp2.Rmd
small changes based on pp number- checking responder rate

--- 2023-01-04 analysis/tgi-spinal_analysis.Rmd
@@
 ---
-title: "TGI Spinal Analysis Code"
+title: "TGI Spinal Analysis Code Experiment 2"
 author: "A.G. Mitchell"
-date: "2022-12-02"
+date: "2023-04-14"
 output: html_document
@@
 # paths
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
-anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
+datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Raw/'
+anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Analysis/'
 ```
@@
 
-# remove participant 019, stopped testing halfway due to broken thermal probe
-df_res <- df_res[df_res$ID != '019' ,]
+# remove participants 047 and 048
+# one had ongoing pain, the other missed 6 trials
+df_res <- df_res[df_res$ID != '047' ,]
+df_res <- df_res[df_res$ID != '048' ,]
 ```
@@
 i = 0
-test = data.frame(matrix(nrow = 40, ncol = 3))
+test = data.frame(matrix(nrow = 27, ncol = 3))
 colnames(test) <- c('ID','pval','responder')

### 2023-05-01 analysis/tgi-spinal_analysis-exp2.Rmd
checking responder rate for exp 2

@@
 i = 0
-test = data.frame(matrix(nrow = 27, ncol = 3))
+test = data.frame(matrix(nrow = 35, ncol = 3))
 colnames(test) <- c('ID','pval','responder')
@@
   scale_alpha_discrete(range = c(0.6, 1)) +
-  ylim(0,50) +
+  ylim(0,70) +
   theme_bw() 

### 2023-05-23 analysis/tgi-spinal_analysis-exp2.Rmd
results of experiment 2

@@
 }
-
+```
+
+# merging
+```{r data, echo = FALSE}
 # merge all files
@@
 # have saved these in the demo .csv as well, so will add these in
-demoFile <- 'STGI_participant-demographics.csv'
+demoFile <- 'STGI_exp2_participant-demographics.csv'
 fileName = paste(datPath, demoFile, sep = '')
@@
 i = 0
-test = data.frame(matrix(nrow = 35, ncol = 3))
+test = data.frame(matrix(nrow = 40, ncol = 3))
 colnames(test) <- c('ID','pval','responder')
@@
   labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(0,.25) +
+  ylim(.20,.60) +
   scale_colour_manual(values = c(blue[4], blue[7])) +
@@
   labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(.45,.7) +
+  ylim(0,.25) +
   scale_colour_manual(values = c(oran[4], oran[7])) +

### 2023-06-15 Examples/parameters_lidocaine.py
changing file structure and making private(again)

@@ -1,200 +1,0 @@
-# Authors: Francesca Fardo <francesca@cfin.au.dk>, Thea Rolskov Sloth, Signe Kirk Brødbæk
-import os
-import pandas as pd
-import numpy as np
-from psychopy import data, visual, core, event
-import platform
-
-def getParameters(subject_n,tasks,qst_selection,lidocaine_timepoint,arm,warm,cold,comPort):
-    """Create parameters for all tasks
-    Many parameters, aesthetics, and options are controlled by the 
-    parameters/dictonary defined here. 
-    These are intended to provide 
-    flexibility and modularity to the tasks. In many cases, unique versions of the 
-    task (e.g., different number of trials) can be created simply by changing these 
-    parameters, with no further interaction with the underlying task code.
-    """
-    ###################
-    # Define parameters
-    ###################
-    parameters = {} # initialize parameters
-    # Variable parameters
-    parameters['subject_n'] = subject_n
-    parameters['tasks'] = tasks
-    parameters['qst_selection'] = qst_selection
-    parameters['lidocaine_timepoint'] = lidocaine_timepoint
-    parameters['arm'] = arm
-    parameters['TGIwarm'] = warm
-    parameters['TGIcold'] = cold
-    parameters['comPort'] = comPort
-    
-    # Fixed Parameters
-    if platform.system() == 'Darwin': 
-        parameters['slash'] = '/' # mac paths
-    elif platform.system() == 'Windows': 
-        parameters['slash'] = '﻿\\' # win paths
-    parameters['allowedKeys'] = ['left', 'right',' up', 'down','q', 'space', 'p'] #redundant?
-    parameters['nextTask'] = ['space']
-    parameters['quit'] = ['q']
-    parameters['path'] = os.getcwd()
-    parameters['pathResults'] = parameters['path'] +  parameters['slash'] + 'results' +  parameters['slash'] + subject_n
-    #Saving data
-    # preparing df
-    parameters['trialInfo'] = tasks + '_' + lidocaine_timepoint + '_' + subject_n + '_' + arm + '_'
-    parameters['columnsVas'] = ['subject_n','arm','temps','trial_n','vas','rating','time'] 
-    parameters['lidocaine_df'] = pd.DataFrame(columns = parameters['columnsVas'])
-    
[…]

### 2023-06-15 Examples/run_lidocaine.py

@@ -1,36 +1,0 @@
-# Authors: Francesca Fardo <francesca@cfin.au.dk>, Thea Rolskov Sloth, Signe Kirk Brødbæk
-#import os
-from parameters_lidocaine import getParameters
-from task_functions import run
-from psychopy import gui
-
-#Create popup information box
-popup = gui.Dlg(title = "Participant Information")
-popup.addField("Subject number",'TLH15') # Example
-popup.addField("Task", choices=["Demo_QST","QST","Demo_TGI","TGI","Demo_TSL2","TSL2"]) # Dropdown menu
-popup.addField("Start QST from", choices = ["CDT","WDT","TSL1","CPT","HPT"])
-popup.addField("lidocaine_timepoint", choices=["00","45","90"]) # Dropdown menu
-popup.addField("arm", choices=["A","B"]) # Dropdown menu
-popup.addFixedField(" ", "--- For TGI only ---")
-popup.addField("TGI Warm","39.99") # Example
-popup.addField("TGI Cold","28.92") # Example
-popup.addField("comPort", choices=["/dev/tty.usbmodem14101","COM3"])#"COM3") # Example
-popup.show()
-if popup.OK: # To retrieve data from popup window
-    ID = popup.data 
-elif popup.Cancel: # To cancel the experiment if popup is closed
-    core.quit()
-
-#extract parameters from gui
-parameters = getParameters(
-    subject_n = ID[0],
-    tasks = ID[1],
-    qst_selection = ID[2],
-    lidocaine_timepoint = ID[3],
-    arm = ID[4],
-    warm = ID[6],
-    cold = ID[7],
-    comPort = ID[8])
-
-#run experiment
-run(parameters)

### 2023-06-15 Examples/task_functions.py

@@ -1,495 +1,0 @@
-# Authors: Francesca Fardo <francesca@cfin.au.dk>, Thea Rolskov Sloth, Signe Kirk Brødbæk
-import datetime as dt
-import pyglet #redundant?
-from psychopy import prefs
-prefs.general['audioLib'] = ['PTB']
-from psychopy import event, visual, core, gui, sound #gui redundant?
-import pandas as pd
-import random
-import numpy as np
-
-import tcs_functions as tcs
-
-#Define clock
-timer = core.Clock()
-
-#Quit experiment by pressing q
-def quit_exp(parameters):
-    """ Quit experiment by pressing the 'q' key """
-    #win = parameters['win1']  # redundant?
-    if event.getKeys(keyList=parameters['quit']):
-        print ("User exited")
-        core.quit()
-
-#Display messages
-def messageWait(parameters):
-    """ Continue to the next task by pressing the space bar
-    and display message to participant """
-    win0 = parameters['win0']
-    win1 = parameters['win1']
-    waitText0=visual.TextStim(win0, height=parameters['textSize'], text=parameters['texts']['textContinue'])
-    waitText1=visual.TextStim(win1, height=parameters['textSize'], text=parameters['texts']['textNext'])
-    waitText0.draw()
-    waitText1.draw()
-    win1.flip()
-    win0.flip()
-    quit_exp(parameters)
-    event.waitKeys(keyList = parameters['nextTask'])
-
-def messageInstruction(parameters, text):
-    win0 = parameters['win0']
-    win1 = parameters['win1']
-    textInstruction0 = visual.TextStim(win0, height=parameters['textSize'], text = (text + "\n \n Tryk SPACE for at begynde"))
-    textInstruction1 = visual.TextStim(win1, height=parameters['textSize'], text = text)
-    textInstruction0.draw()
-    textInstruction1.draw()
-    win0.flip()
-    win1.flip()
-    #quit_exp(parameters) #redundant?
-    event.waitKeys(keyList=parameters['nextTask'])
-
-def messageParticipantAndExperimenter(parameters, text0, text1):
-    win0 = parameters['win0']
-    win1 = parameters['win1']
-    text0 = visual.TextStim(win0, height=parameters['textSize'], text = text0)
-    text1 = visual.TextStim(win1, height=parameters['textSize'], text = text1)
-    text0.draw()
-    text1.draw()
-    win0.flip()
-    win1.flip()
-
[…]

### 2023-06-15 bayesVAS.Rmd
more shuffling

---
title: "Bayes VAS"
author: "A.G. Mitchell"
date: "2023-02-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)        # ggplot, dplyr, %>%, and friends
library(brms)             # Bayesian modeling through Stan
library(tidybayes)        # Manipulate Stan objects in a tidy way
library(broom)            # Convert model objects to data frames
library(broom.mixed)      # Convert brms model objects to data frames
library(betareg)          # Run beta regression models
library(extraDistr)       # Use extra distributions like dprop()
library(ggdist)           # Special geoms for posterior distributions
library(gghalves)         # Special half geoms
library(ggbeeswarm)       # Special distribution-shaped point jittering
library(ggrepel)          # Automatically position labels
library(patchwork)        # Combine ggplot objects
library(marginaleffects)  # Calculate marginal effects for frequentist models
library(emmeans)          # Calculate marginal effects in even fancier ways
library(modelsummary)     # Create side-by-side regression tables

set.seed(1234)  # Make everything reproducible

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)

# Custom ggplot theme to make pretty plots
# Get the font at https://fonts.google.com/specimen/Barlow+Semi+Condensed
theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA))
}

# Make labels use Barlow by default
update_geom_defaults("label_repel", list(family = "Barlow Semi Condensed"))

anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
```

# Load own data
```{r}
setwd(anaPath)
dat <- read.csv('STGI_compiled-data.csv')

# data wrangling
dat <- dat %>% 
  select(ID, trial_n, manipulation, arm, condition, dermatome, cold_probe, order, VASburn)
head(dat)
```

```{r}
# plot data
dat$manipulation <- as.factor(dat$manipulation)

quota_halves <- ggplot(dat, aes(x = manipulation, y = VASburn)) +
  geom_half_point(aes(color = manipulation), 
                  transformation = position_quasirandom(width = 0.1),
                  side = "l", size = 0.5, alpha = 0.5) +
  geom_half_boxplot(aes(fill = manipulation), side = "r") + 
  scale_fill_viridis_d(option = "plasma", end = 0.8) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = "none", fill = "none") +
  labs(x = "Manipulation", y = "Burning VAS") +
  theme_classic()

quota_densities <- ggplot(dat, aes(x = VASburn, fill = manipulation)) +
  geom_density(alpha = 0.6) +
  scale_fill_viridis_d(option = "plasma", end = 0.8) +
  labs(x = "Burning VAS", y = "Density", fill = "Quota") +
  theme_classic() +
  theme(legend.position = "bottom")

quota_halves | quota_densities
```
# Frequentist beta regression
```{r}
# transform VAS ratings into beta
dat1 <- dat %>% 
  mutate(VASburn = VASburn/100) %>% 
  mutate(beta = ifelse(VASburn == 0, 0.001, VASburn)) %>% 
  mutate(beta = ifelse(VASburn == 1, VASburn - 0.001, beta)) %>% 
  filter(!is.na(beta))

# run normal beta regression
model_beta <- betareg(beta ~ manipulation | manipulation, 
                      data = dat1, 
                      link = "logit")
tidy(model_beta)

# calculating model effect of manipulation
beta_mu_intercept <- model_beta %>% 
  tidy() %>% 
  filter(component == "mean", term == "(Intercept)") %>% 
  pull(estimate)

beta_mu_quota <- model_beta %>% 
  tidy() %>% 
  filter(component == "mean", term == "manipulationTGI") %>% 
  pull(estimate)

plogis(beta_mu_intercept + beta_mu_quota) - plogis(beta_mu_intercept)
```

TGI increases average burn rating by 5% - when zeros are included in the model

```{r}
beta_phi_intercept <- model_beta %>% 
  tidy() %>% 
  filter(component == "precision", term == "(Intercept)") %>% 
  pull(estimate)

beta_phi_quota <- model_beta %>% 
  tidy() %>% 
  filter(component == "precision", term == "manipulationTGI") %>% 
  pull(estimate)

no_tgi_title <- paste0("dprop(mean = plogis(", round(beta_mu_intercept, 2),
                         "), size = exp(", round(beta_phi_intercept, 2), "))")

tgi_title <- paste0("dprop(mean = plogis(", round(beta_mu_intercept, 2),
                      " + ", round(beta_mu_quota, 2), 
                      "), size = exp(", round(beta_phi_intercept, 2),
                      " + ", round(beta_phi_quota, 2), "))")

ggplot(data = tibble(x = 0:1), aes(x = x)) +
  geom_density(data = dat2, 
               aes(x = beta, fill = manipulation), alpha = 0.5, color = NA) +
  stat_function(fun = dprop, size = 1,
                args = list(size = exp(beta_phi_intercept), 
                            mean = plogis(beta_mu_intercept)),
                aes(color = no_tgi_title)) +
  stat_function(fun = dprop, size = 1,
                args = list(size = exp(beta_phi_intercept + beta_phi_quota), 
                            mean = plogis(beta_mu_intercept + beta_mu_quota)),
                aes(color = tgi_title)) +
  scale_fill_viridis_d(option = "plasma", end = 0.8, name = "Manipulation",
                       guide = guide_legend(ncol = 1, order = 1)) +
  scale_color_viridis_d(option = "plasma", end = 0.8, direction = -1, name = "",
                        guide = guide_legend(reverse = TRUE, ncol = 1, order = 2)) +
  labs(x = "Burning VAS") +
  theme_classic() +
  theme(legend.position = "bottom")
```

```{r}
# brms model
model_beta_bayes <- brm(
  bf(VASburn ~ manipulation,
     phi ~ quota), 
  data = dat1,
  family = (), #need to change family
  chains = 4, iter = 2000, warmup = 1000,
  cores = 4, seed = 1234, 
  # Use the cmdstanr backend for Stan because it's faster and more modern than
  # the default rstan You need to install the cmdstanr package first
  # (https://mc-stan.org/cmdstanr/) and then run cmdstanr::install_cmdstan() to
  # install cmdstan on your computer.
  backend = "cmdstanr"
)
```

### 2023-06-15 old/tgispine_hypotheses.Rmd
more shuffling

--- 2022-05-12 analysis/tgispine_hypotheses.Rmd
@@
 df30 <- data.frame()
-for (i in 1:60) {
+for (i in 1:30) {
   df <- simulate_subj(i, 0, 1)
@@
 summary(model.warm)
+```
 
+# next, run model checks
+
+```{r}
+# first check cold
+model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
+plot(model.cold.assmup)
 ```
+```{r}
+# then check warm
+model.warm.assmup <- simulateResiduals(model.warm, n = 1000)
+plot(model.warm.assmup)
+```

### 2023-06-15 old/tgispine_og-plots-exp1.Rmd
more shuffling

--- 2022-04-22 analysis/tgispine_og-plots-exp1.Rmd
@@
                         by = list(id = df_norm$id, dermatome = df_norm$dermatome, 
-                                  location_cold = df_norm$location_cold), FUN = median)
+                                  location_cold = df_norm$location_cold, arm = df_norm$location_arm),
+                        FUN = median)
+# divide by arm location
+df_upper <- df_nmedian[df_nmedian$arm == 'upperarm' ,]
+df_fore <- df_nmedian[df_nmedian$arm == 'forearm' ,]
 ```
@@
 # cold ratings anova
-cold_anova <- ezANOVA(
-  data = df_nmedian
+coldu_anova <- ezANOVA(
+  data = df_upper
+  , dv = .(cold)
+  , wid = .(id)
+  , within = .(dermatome, location_cold),
+  return_aov = TRUE,
+  detailed = TRUE
+)
+
+coldf_anova <- ezANOVA(
+  data = df_fore
   , dv = .(cold)
@@
 # warm ratings anova
-warm_anova <- ezANOVA(
-  data = df_nmedian
+warmu_anova <- ezANOVA(
+  data = df_upper
+  , dv = .(warm)
+  , wid = .(id)
+  , within = .(dermatome, location_cold),
+  return_aov = TRUE,
+  detailed = TRUE
+)
+
+warmf_anova <- ezANOVA(
+  data = df_fore
   , dv = .(warm)

### 2023-06-15 tgi-compiler.Rmd
more shuffling

--- 2023-04-14 analysis/tgi-spinal_analysis-exp1.Rmd
@@
 ---
-title: "TGI Spinal Analysis Code Experiment 1"
+title: "TGI Spinal Data Compiler"
 author: "A.G. Mitchell"
@@
 
+To compile all the raw data, need to access paths in directory
+This is done for experiment 1 first, then experiment 2
+
 ```{r paths}
@@
 
-# Loading data
+# EXPERIMENT 1 DATA
 ```{r data, echo = FALSE}
@@
 # have saved these in the demo .csv as well, so will add these in
-demoFile <- 'STGI_participant-demographics.csv'
+demoFile <- 'STGI_exp1_participant-demographics.csv'
 fileName = paste(datPath, demoFile, sep = '')
@@
 # merge
-test <- merge(df_res, df_demo)
+df_res <- merge(df_res, df_demo)
+df_res <- df_res %>% 
+  select(-c(warmT, coldT, Tested, Calibration, Notes))
 
 # save new data-frame
-fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
-write.csv(df_res, fileName, row.names = FALSE)
+write.csv(df_res, file.path("data", "STGI_exp1_compiled-data.csv"), row.names = FALSE)
 
@@
 # correlate
-qual_cor <- hetcor(df_corr, type = 'pearson')
+qual_cor <- hetcor(df_corr, type = 'spearman')
 cormat <- qual_cor$correlations
@@
 # significance values
-p <- cor.mtest(df_corr, type ='pearson')$p
+p <- cor.mtest(df_corr, type ='spearman')$p
 
@@
                                round(cormat[1,3], 2))),
-            x=8, y=90, size = 5) +
+            x=78, y=91, size = 5) +
   labs(x = 'Cold Ratings', y = 'Warm Ratings') +
-  xlim(0,100) + ylim(-15,100) +
-  theme_bw() -> CNT_cw_plot
+  xlim(0,100) + ylim(-10,100) +
+  theme_bw() +
+  theme(axis.title = element_text(size = 12)) -> CNT_cw_plot
 
@@
                                round(cormat[1,5], 2))),
-            x=8, y=90, size = 5) +
+            x=78, y=91, size = 5) +
   labs(x = 'Cold Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-15,100) +
-  theme_bw() -> CNT_cb_plot
+  xlim(0,100) + ylim(-10,100) +
+  theme_bw() +
+  theme(axis.title = element_text(size = 12)) -> CNT_cb_plot
 
@@
                                round(cormat[3,5], 2))),
-            x=8, y=90, size = 5) +
+            x=78, y=91, size = 5) +
   labs(x = 'Warm Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-15,100) +
-  theme_bw() -> CNT_wb_plot
+  xlim(0,100) + ylim(-10,100) +
+  theme_bw() +
+  theme(axis.title = element_text(size = 12)) -> CNT_wb_plot
 
@@
                                  top = text_grob("Non-TGI", 
-                                                 size = 12))
+                                                 size = 14))
 
@@
                                round(cormat[2,4], 2))),
-            x=8, y=90, size = 5) +
+            x=78, y=91, size = 5) +
   labs(x = 'Cold Ratings', y = 'Warm Ratings') +
-  xlim(0,100) + ylim(-15,100) +
-  theme_bw() -> TGI_cw_plot
+  xlim(0,100) + ylim(-10,100) +
+  theme_bw() +
+  theme(axis.title = element_text(size = 12)) -> TGI_cw_plot
 
@@
                                round(cormat[2,6], 2))),
-            x=8, y=90, size = 5) +
+            x=78, y=91, size = 5) +
   labs(x = 'Cold Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-15,100) +
-  theme_bw() -> TGI_cb_plot
+  xlim(0,100) + ylim(-10,100) +
+  theme_bw() +
+  theme(axis.title = element_text(size = 12)) -> TGI_cb_plot
 
@@
                                round(cormat[4,6], 2))),
-            x=8, y=90, size = 5) +
+            x=78, y=91, size = 5) +
   labs(x = 'Warm Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-15,100) +
-  theme_bw() -> TGI_wb_plot
+  xlim(0,100) + ylim(-10,100) +
+  theme_bw() +
+  theme(axis.title = element_text(size = 12)) -> TGI_wb_plot
 
@@
                                  top = text_grob("TGI", 
-                                                 size = 12))
+                                                 size = 14))
 
@@
 ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
-       width = 14, height = 9, dpi = 1000)
+       width = 10, height = 6.5, dpi = 1000)
 ```

### 2023-06-15 tgi-spinal_analysis-exp1.Rmd
more shuffling

--- 2023-06-15 tgi-compiler.Rmd
@@
 ---
-title: "TGI Spinal Data Compiler"
+title: "TGI Spinal Analysis Code Experiment 1"
 author: "A.G. Mitchell"
@@
 
-To compile all the raw data, need to access paths in directory
-This is done for experiment 1 first, then experiment 2
-
 ```{r paths}
@@
 
-# EXPERIMENT 1 DATA
+# Loading data
 ```{r data, echo = FALSE}
@@
 # merge
-df_res <- merge(df_res, df_demo)
-df_res <- df_res %>% 
-  select(-c(warmT, coldT, Tested, Calibration, Notes))
+test <- merge(df_res, df_demo)
 
 # save new data-frame
-write.csv(df_res, file.path("data", "STGI_exp1_compiled-data.csv"), row.names = FALSE)
+fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
+write.csv(df_res, fileName, row.names = FALSE)
 
 # check we have 40 participants with 96 trials
-id_check <- count(df_res, 'ID')
+id_check <- count(df_res, ID)
 id_check

### 2023-06-15 tgispine_zoib_power-sim.Rmd
more shuffling

--- 2022-06-24 analysis/tgispine_zoib_power-sim.Rmd
@@
 set.seed(326) #is this needed?
-prop_zero <- function(x, vas = c('cold','warm','burn')) {
-  x2 <- data.frame()
-  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .05
+prop_zero <- function(x, vas) {
+  # check if a correct vas parameter is provided
+  if (!vas %in% c("cold", "warm", "burn")) {
+    stop("Only cold / warm / burn parameters allowed", .call = TRUE)
+  }
+  if (length(vas) > 1) {
+    stop("VAS parameter should have length = 1", .call = TRUE)
+  }
+
+  # sellect subset of x
+  x1 <- x %>%  filter(quality == vas)
+
+  # sellect dfs with info about zero proportions
+  # switch function allows to select a value based on a condition
+  # a statement specified as the first parameter may be tested for many conditions # nolint
+  # conditions are specified as the next arguments
+  # returned value for a contition is given after = sign
+    df_CNT <- switch(vas,
+    cold = CNTc_zero,
+    warm = CNTw_zero,
+    burn = CNTb_zero)
+    df_TGI <- switch(vas,
+    cold = TGIc_zero,
+    warm = TGIw_zero,
+    burn = TGIb_zero)
+
+    # get info abut zero proportion and add some variablity
+    # first randomly generate two numbers around a normal distribution of 0,
+    # with a standard deviation of .05
     r <- rnorm(2, mean=0, sd=.05)
-  if (vas[1] == 'cold'){
-    x1 <- x %>%  filter(quality == 'cold')
-    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
-    zp_cnt <- CNTc_zero$prop[2] + r[1] 
-    zp_tgi <- TGIc_zero$prop[2] + r[2]
-    # adding if loop to make sure zp does not reach 0
-    if (isTRUE(zp_cnt < 0)){
+    # then retrieve the relevant data and add generated random number
+    zp_cnt <- df_CNT$prop[2] + r[1]
+    zp_tgi <- df_TGI$prop[2] + r[2]
+    # make sure that zp does not reach 0
+    if (isTRUE(zp_cnt < 0)) {
       zp_cnt = 0
     }
-    if (isTRUE(zp_tgi < 0)){
+    if (isTRUE(zp_tgi < 0)) {
       zp_tgi = 0
     }
-    # turn zp into the proportion of total columns
-    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
-    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
 
     # isolate TGI and non-TGI
-    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
-    x_tgi <- x1 %>% filter(stimuli == 'tgi')
+    x_cnt <- x1 %>% filter(stimuli == "non-tgi")
+    x_tgi <- x1 %>% filter(stimuli == "tgi")
+
+    # turn zp into the number of total columns
+    zp_cnt <- round(zp_cnt * nrow(x_cnt))
+    zp_tgi <- round(zp_tgi * nrow(x_tgi))
+
     # finally, replace a proportion of the data with zeros!
-    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
-    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0
+    x_cnt$rating[sample(nrow(x_cnt), zp_cnt)] <- 0
+    x_tgi$rating[sample(nrow(x_tgi), zp_tgi)] <- 0
 
@@
 
-  } else if (vas[1] == 'warm'){
-    x1 <- x %>%  filter(quality == 'warm')
-    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each       participant
-    zp_cnt <- CNTw_zero$prop[2] + r[1] 
-    zp_tgi <- TGIw_zero$prop[2] + r[2]
-    # adding if loop to make sure zp does not reach 0
-    if (isTRUE(zp_cnt < 0)){
-      zp_cnt = 0
-    }
-    if (isTRUE(zp_tgi < 0)){
-      zp_tgi = 0
-    }
-    # turn zp into the proportion of total columns
-    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
-    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
-    # isolate TGI and non-TGI
-    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
-    x_tgi <- x1 %>% filter(stimuli == 'tgi')
-    # finally, replace a proportion of the data with zeros! 
-    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
-    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0
-
-    #compile both data-sets again
-    x2 <- rbind(x_cnt, x_tgi)
-
-  } else if (vas[1] == 'burn') {
-    x1 <- x %>%  filter(quality == 'burn')
-    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
-    zp_cnt <- CNTb_zero$prop[2] + r[1] 
-    zp_tgi <- TGIb_zero$prop[2] + r[2]
-    # adding if loop to make sure zp does not reach 0
-    if (isTRUE(zp_cnt < 0)){
-      zp_cnt = 0
-    }
-    if (isTRUE(zp_tgi < 0)){
-      zp_tgi = 0
-    }
-    # turn zp into the proportion of total columns
-    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
-    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
-
-    # isolate TGI and non-TGI
-    x_cnt <- x1 %>% filter(stimuli == 'non-tgi')
-    x_tgi <- x1 %>% filter(stimuli == 'tgi')
-    # finally, replace a proportion of the data with zeros! 
-    x_cnt$rating[sample(nrow(x_cnt),zp_cnt)] <- 0
-    x_tgi$rating[sample(nrow(x_tgi),zp_tgi)] <- 0
-
-    #compile both data-sets again
-    x2 <- rbind(x_cnt, x_tgi)
-  }
     return(x2)

### 2023-06-15 old/VAStest.py

@@ -1,146 +1,0 @@
-import datetime as dt
-import random
-import pandas as pd
-import numpy as np
-import os
-import csv
-import pickle
-from parameters_spinal import getParameters
-
-from psychopy import prefs
-prefs.general['audioLib'] = ['PTB']
-from psychopy import event, visual, core, gui, sound #gui redundant?
-
-os.chdir('/Users/au706616/Documents/Git/SpinalTGI/') #set directory whilst debugging - to save results in useful place
-
-#Define clock
-timer = core.Clock()
-
-#Quit experiment by pressing q
-def quit_exp(parameters):
-    """ Quit experiment by pressing the 'q' key """
-    #win = parameters['win1']  # redundant?
-    if event.getKeys(keyList=parameters['quit']):
-        print ("User exited")
-        core.quit()
-
-parameters = getParameters(
-    subject_n = '1',
-    tasks = 'VAS',
-    arm = 'A')
-
-def vasRatingScale(parameters, vas, win=None):
-    """Rating scale, using keyboard inputs.
-    Parameters
-    ----------
-    parameters : dict
-        Parameters dictionary.
-    vas: 'pain', 'unpleasantness', 'cold', 'warm'
-    win1 : psychopy window instance for participant - the VAS is shown here
-        The window where to show the task.
-    win0 : experimenters screen
-    """
-    # Define window
-    if win is None:
-        win = parameters['win1']
-    else: 
-        win = visual.Window(screen=0, fullscr=False)
-
-    
-    #Setup pyglet keyboard for slider
-    #pyglet_key=pyglet.window.key #redundant?
-    #keyboard = pyglet_key.KeyStateHandler() #redundant?
-    #parameters['win1'].winHandle.push_handlers(keyboard) #redundant?
-     
-    # Define parameters for VAS scale
-    low = parameters['vasParameters']['low']
-    high = parameters['vasParameters']['high']
-    increment = parameters['vasParameters']['increment']
-
-    #setup four different ratingscales
-    labels = parameters['texts']['textVasAnchors'][vas]
-    text = parameters['texts']['textVasTitle'][vas]
-    #VAS scale
-    vasRatingScale = visual.RatingScale(win, 
-                    low = low,
-                    high = high ,
-                    marker = parameters['vasParameters']['marker'], 
-                    markerColor = parameters['vasParameters']['markerColor'], 
-                    markerStart = low,
-                    tickMarks = parameters['vasParameters']['tickMarks'], 
[…]

### 2023-06-15 old/parameters_spinal.py

@@ -1,143 +1,0 @@
-# Authors: Francesca Fardo <francesca@cfin.au.dk>, Thea Rolskov Sloth, Signe Kirk Brødbæk
-import os
-import pandas as pd
-import numpy as np
-from psychopy import data, visual, core, event
-import platform
-
-def getParameters(subject_n, tasks, arm):
-    """Create parameters for all tasks
-    Many parameters, aesthetics, and options are controlled by the 
-    parameters/dictonary defined here. 
-    These are intended to provide 
-    flexibility and modularity to the tasks. In many cases, unique versions of the 
-    task (e.g., different number of trials) can be created simply by changing these 
-    parameters, with no further interaction with the underlying task code.
-    """
-    ###################
-    # Define parameters
-    ###################
-    parameters = {} # initialize parameters
-    # Variable parameters
-    parameters['subject_n'] = subject_n
-    parameters['tasks'] = tasks
-    parameters['arm'] = arm
-    
-    # Fixed Parameters
-    if platform.system() == 'Darwin': 
-        parameters['slash'] = '/' # mac paths
-    elif platform.system() == 'Windows': 
-        parameters['slash'] = '﻿\\' # win paths
-    parameters['allowedKeys'] = ['left', 'right',' up', 'down','q', 'space', 'p'] #redundant?
-    parameters['nextTask'] = ['space']
-    parameters['quit'] = ['q']
-    parameters['path'] = os.getcwd()
-    parameters['pathResults'] = parameters['path'] +  parameters['slash'] + 'results' +  parameters['slash'] + subject_n
-    #Saving data
-    # preparing df
-    parameters['trialInfo'] = tasks + '_' + subject_n + '_' + arm + '_'
-    parameters['columnsVas'] = ['subject_n','arm','temps','trial_n','vas','rating','time'] 
-    parameters['lidocaine_df'] = pd.DataFrame(columns = parameters['columnsVas'])
-    
-    parameters['sumDfInfo'] = [subject_n, arm]
-    parameters['columnsSum'] = ['subject_n','timepoint','arm','task','threshold']
-    parameters['qst_filename'] = parameters['pathResults'] + parameters['slash'] + 'QST_summary' + '.csv'
-    if not os.path.isfile(parameters['qst_filename']):
-        parameters['qst_df'] = pd.DataFrame(columns = parameters['columnsSum'])
-    else:
-        parameters['qst_df'] = pd.read_csv(parameters['qst_filename'])
-    
-        
-    # Texts
[…]

### 2023-06-15 old/parameters_spinal_old.py

@@ -1,200 +1,0 @@
-# Authors: Francesca Fardo <francesca@cfin.au.dk>, Thea Rolskov Sloth, Signe Kirk Brødbæk
-import os
-import pandas as pd
-import numpy as np
-from psychopy import data, visual, core, event
-import platform
-
-def getParameters(subject_n):
-    """Create parameters for all tasks
-    Many parameters, aesthetics, and options are controlled by the 
-    parameters/dictonary defined here. 
-    These are intended to provide 
-    flexibility and modularity to the tasks. In many cases, unique versions of the 
-    task (e.g., different number of trials) can be created simply by changing these 
-    parameters, with no further interaction with the underlying task code.
-    """
-    ###################
-    # Define parameters
-    ###################
-    parameters = {} # initialize parameters
-    # Variable parameters
-    parameters['subject_n'] = subject_n
-    parameters['tasks'] = tasks
-    parameters['qst_selection'] = qst_selection
-    parameters['lidocaine_timepoint'] = lidocaine_timepoint
-    parameters['arm'] = arm
-    parameters['TGIwarm'] = warm
-    parameters['TGIcold'] = cold
-    parameters['comPort'] = comPort
-    
-    # Fixed Parameters
-    if platform.system() == 'Darwin': 
-        parameters['slash'] = '/' # mac paths
-    elif platform.system() == 'Windows': 
-        parameters['slash'] = '﻿\\' # win paths
-    parameters['allowedKeys'] = ['left', 'right',' up', 'down','q', 'space', 'p'] #redundant?
-    parameters['nextTask'] = ['space']
-    parameters['quit'] = ['q']
-    parameters['path'] = os.getcwd()
-    parameters['pathResults'] = parameters['path'] +  parameters['slash'] + 'results' +  parameters['slash'] + subject_n
-    #Saving data
-    # preparing df
-    parameters['trialInfo'] = tasks + '_' + lidocaine_timepoint + '_' + subject_n + '_' + arm + '_'
-    parameters['columnsVas'] = ['subject_n','arm','temps','trial_n','vas','rating','time'] 
-    parameters['lidocaine_df'] = pd.DataFrame(columns = parameters['columnsVas'])
-    
-    parameters['sumDfInfo'] = [subject_n, lidocaine_timepoint, arm]
[…]

### 2023-06-15 tgi-compiler.Rmd
making compiler code for exp1 and exp2

@@
 # paths
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Raw/'
-anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Analysis/'
+exp1Path <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Raw/'
+exp2Path <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Raw/'
 ```
@@
 # Extract all .csv files and compile
-filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
+filenames <- dir(exp1Path, recursive = TRUE, full.names = FALSE, pattern = '.csv')
 # empty dataframes for data
@@
 # trial files
-setwd(datPath)
+setwd(exp1Path)
 for (file in filenames){
@@
 df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))
-
+```
+# dData organisation
+```{r}
 # remove participant 019, stopped testing halfway due to broken thermal probe
 df_res <- df_res[df_res$ID != '019' ,]
-```
 
-# Data organisation
-```{r}
 # transform the ID of participants to remove 0
@@
 
+```
+
+# Merge with demographics
+```{r}
 # incorporate demographics
@@
 demoFile <- 'STGI_exp1_participant-demographics.csv'
-fileName = paste(datPath, demoFile, sep = '')
+fileName = paste(exp1Path, demoFile, sep = '')
 df_demo <- read.csv(fileName)
@@
 
-# Responder check
-Check whether participants median burning ratings for TGI is significantly above 0
-If not, flag them as a 'non-responder'
-```{r}
-# Calculate median burning rating for all participants
-# TGI trials only
-# Then flag how many are not sig > 0
-df_med <- aggregate(VASburn~ID*manipulation*cold_probe*trial_type, median, data = df_res)
-tgi <-  df_med %>% 
-  filter(manipulation == 'TGI')
-cnt <-  df_med %>% 
-  filter(manipulation == 'CNT')
+Do the same for experiment 2
+# EXPERIMENT 2 LOAD DATA
+```{r data, echo = FALSE}
+# Extract all .csv files and compile
+filenames <- dir(exp2Path, recursive = TRUE, full.names = FALSE, pattern = '.csv')
+# empty dataframes for data
+## with new data trials file will have changed to include temperature coding!
+df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
+df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
+df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')
 
-# identify test results where pvalue is < .05
-tgi$ID <- as.factor(tgi$ID)
-i = 0
-test = data.frame(matrix(nrow = 40, ncol = 3))
-colnames(test) <- c('ID','pval','responder')
-
-for (id in levels(tgi$ID)){
-  i = i+1
-  tmp1 <- tgi[tgi$ID == id ,]
-  test$ID[i] <- id
-  test$pval[i] <- (t.test(tmp1$VASburn, mu = 0, alternative = 'greater'))$p.value
-  test$responder[i] <- isTRUE(test$pval[i] < .05)
+## Data compiling
+# trial files
+setwd(exp2Path)
+for (file in filenames){
+  # trial files
+  if (isTRUE(substr(basename(file), 24, 24)=="t")){
+    tmp <- read.csv(file)
+    tmp$ID <- substr(basename(file), 4, 6)
+    tmp$manipulation <- substr(basename(file), 17, 19)
+    df_trials <- rbind(df_trials, tmp)
+  }
+  # VAS response files
+  if (isTRUE(substr(basename(file), 24, 29)=="rating")){
+    tmp <- read.csv(file, header = FALSE)
+    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
+    tmp$ID <- substr(basename(file), 4, 6)
+    tmp$manipulation <- substr(basename(file), 17, 19)
+    df_VAS <- rbind(df_VAS, tmp)
+  }
+  # VAS RT files
+  if (isTRUE(substr(basename(file), 24, 29)=="respti")){
+    tmp <- read.csv(file, header = FALSE)
+    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
+    tmp$ID <- substr(basename(file), 4, 6)
+    tmp$manipulation <- substr(basename(file), 17, 19)
+    df_RT <- rbind(df_RT, tmp)
+  }
 }
 
-# combine responder logic with main data-frame
-test$responder <- ifelse(test$responder == TRUE, 1, 0)
-test <- test[, c(1,3)]
-df_res <- merge(df_res, test, by = 'ID')
-
-# count the number of false responses
-nNONRESP <- sum(test$responder == FALSE)
-# print
-print(paste0('Non responders: ', nNONRESP, '/', length(test$ID)))
+# merge all files
+df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
+df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))
 ```
 
-# Let's look at the data!
+# Data organisation
 ```{r}
-# Reorganise data-frame 
-# pivot longer the VAS response by each quality of sensation
-# do this for both RT and VAS
-df_long <- df_res %>% 
-  pivot_longer(cols = c(VASinit, VASburn, VASwarm, VAScold),
-               names_to = 'quality',
-               values_to = 'VAS')
-df_long2 <- df_res %>% 
-  pivot_longer(cols = c(RTinit, RTburn, RTwarm, RTcold),
-               names_to = 'quality',
-               values_to = 'RT')
-# remove the VAS & RT from quality column
-df_long$quality <- substr(df_long$quality, 4, 7)
-df_long2$quality <- substr(df_long2$quality, 3, 6)
-# remove columns from both then merge
-df_long <- df_long[, c(1:12,17:19)]
-df_long2 <- df_long2[, c(1:12,17:19)]
-df_long <- merge(df_long, df_long2)
+# remove participants 047 and 048
+# one had ongoing pain, the other missed 6 trials
+df_res <- df_res[df_res$ID != '047' ,]
+df_res <- df_res[df_res$ID != '048' ,]
 
-# then remove NaNs
-df_long <- df_long %>% filter(!is.na(VAS))
-# remove the initial trials - not important for now
-init_burn <- filter(df_long, quality == 'init')
-all_vas <- filter(df_long, quality != 'init')
-
-# plot distribution of data
-ggplot(df_long) +
-  geom_density(aes(VAS, colour = manipulation)) +
-  facet_wrap(~quality, scales = "free_y") +
-  theme_bw()
-
-# summary statistics
-```
-# MAIN HYPOTHESES
-# Plot descriptives for each hypotheses
-Hypothesis 1: within vs. across dermatomes
-
-```{r h1}
-# calculate means
-vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
-                      median, data = all_vas)
-vas_h1 <- aggregate(VAS ~ quality*manipulation*condition*ID, mean, data = vas_meds)
-# change name of manipulation
-vas_h1$manipulation <- factor(vas_h1$manipulation,
-                           labels = c('Non-TGI', 'TGI'))
-# summary means for h1
-h1_sum <- summarySEwithin(data = vas_h1, measurevar = 'VAS',
-                               withinvars = c('manipulation', 'quality', 'condition'))
-
-# plot the summary statistics
-# first colours
-blue <- brewer.pal(8, "Blues")
-grey <- brewer.pal(8, "Greys")
-purp <- brewer.pal(8, "Purples")
-oran <- brewer.pal(8, "Oranges")
-gren <- brewer.pal(8, "Greens")
-
-# order conditions
-h1_sum$condition <- factor(h1_sum$condition, levels = c('within', 'across'))
-h1_sum$quality <- factor(h1_sum$quality, levels = c('cold', 'warm', 'burn'))
-
-# plot
-ggplot(h1_sum, aes(colour = quality, group = manipulation, alpha = manipulation)) + 
-  geom_point(aes(condition, VAS), size = 2, position = position_dodge(-.3)) +
-  geom_errorbar(aes(condition, ymin = VAS-ci, ymax = VAS+ci), width = .1, size = .7,
-                position = position_dodge(-.3)) +
-  geom_line(aes(condition, VAS), size = .7, position = position_dodge(-.3)) +
-  facet_wrap(~quality) +
-  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-  scale_alpha_discrete(range = c(0.6, 1)) +
-  ylim(0,50) +
-  theme_bw() 
+# transform the ID of participants to remove 0
+df_res$ID <- as.numeric(df_res$ID)
+# recode conditions
+df_res <- df_res %>%
+  mutate(condition = dplyr::recode(condition, '1' = 'within', '2' = 'across'),
+         cold_probe = dplyr::recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
+                             'dist' = 'distal', 'prox' = 'proximal'))
+# change levels 
+df_res$cold_probe <- factor(df_res$cold_probe, 
+                            levels = c("caudal", "rostral", "distal", "proximal"))
 ```
 
-# Hypothesis 1: plot difference across conditions of interest
-```{r h1diff}
-# then pivot wider and calculate difference
-vas_h1_diff <- vas_h1 %>% 
-  pivot_wider(names_from = condition, values_from = VAS) %>% 
-  mutate(difference = within - across)
-# recode quality
-vas_h1_diff$quality <- factor(vas_h1_diff$quality,
-                           levels = c('cold', 'warm', 'burn'))
+# Merge with demographics
+```{r}
+# incorporate demographics
+# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
+# have saved these in the demo .csv as well, so will add these in
+demoFile <- 'STGI_exp2_participant-demographics.csv'
+fileName = paste(exp2Path, demoFile, sep = '')
+df_demo <- read.csv(fileName)
+# merge
+df_res <- merge(df_res, df_demo)
+df_res <- df_res %>% 
+  select(-c(warmTGI, coldTGI, Tested, Calibration, Notes))
 
-# summary statistics
-h1_diff_sum <- summarySEwithin(data = vas_h1_diff, measurevar = 'difference',
-                               withinvars = c('manipulation', 'quality'))
+# save new data-frame
+write.csv(df_res, file.path("data", "STGI_exp1_compiled-data.csv"), row.names = FALSE)
 
-# now plot the difference
-ggplot(data = vas_h1_diff, aes(colour = quality)) +
-  geom_hline(yintercept = 0, colour = 'grey50') +
-  geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
-             alpha = .5) +
-  geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
-             fill = 'grey15',
-             shape = 21, size = 3) +
-  geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
-                                        ymax = difference+ci), 
-                width = .1, size = .7, colour = 'grey15') +
-  facet_wrap(~quality) +
-  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-  labs(title = 'Hypothesis 1: Segmental Distance',
-       y = 'Within - Across VAS Ratings', x = NULL) +
-  theme_classic() +
-  theme(legend.position = 'none') -> h1_diff_plot
-
-h1_diff_plot
-ggsave('h1_difference.png', h1_diff_plot, path = anaPath, device = NULL, 
-       width = 7, height = 4.5, dpi = 1000)
+# check we have 40 participants with 96 trials
+id_check <- count(df_res, ID)
+id_check
 ```
-
-Hypothesis 2 a & b: relative location of warm and cold
-```{r h2}
-# Change name of manipulation
-vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
-h2_sum <- aggregate(VAS~quality*manipulation*cold_probe, median, data = vas_meds)
-
-# organise data for plotting
-vas_meds$cold_probe <- factor(vas_meds$cold_probe, levels = 
-                                c('proximal', 'distal', 'rostral', 'caudal'))
-h2_sum$cold_probe <- factor(h2_sum$cold_probe, levels = 
-                                c('proximal', 'distal', 'rostral', 'caudal'))
-# recoding cold probe location so can jitter
-vas_meds$cold_code <- factor(vas_meds$cold_probe, labels = 
-                                c(1,2,3,4))
-h2_sum$cold_code <- factor(h2_sum$cold_probe, labels = 
-                                c(1,2,3,4))
-# creating jitter
-vas_meds$xj <- jitter(as.numeric(vas_meds$cold_code), amount = .05)
-
-nudge1 = -.1
-nudge2 = .1
-```
-
-# All dat plot
-
-```{r}
-# plot all data
-# COLD
-ggplot(data = vas_meds %>% 
-         filter(quality == 'cold'),
-       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_line(data = h2_sum %>% 
-    filter(quality == 'cold', manipulation == 'Non-TGI'),
-    aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge1)) + 
-  geom_line(data = h2_sum %>% 
-    filter(quality == 'cold', manipulation == 'TGI'),
-    aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge2)) +
-  scale_colour_manual(values = c(blue[5], blue[7])) +
-  scale_fill_manual(values = c(blue[2], blue[4])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Cold ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
-  ylim(-0.5,100) +
-  theme_classic() +
-  theme(legend.position = 'none',
-        axis.text = element_text(size = 11),
-        axis.title = element_text(size = 12),
-        title = element_text(size = 12)) -> h2_cold_plot
-
-# WARM
-ggplot(data = vas_meds %>% 
-         filter(quality == 'warm'),
-       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_line(data = h2_sum %>% 
-    filter(quality == 'warm', manipulation == 'Non-TGI'),
-    aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge1)) + 
-  geom_line(data = h2_sum %>% 
-    filter(quality == 'warm', manipulation == 'TGI'),
-    aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge2)) +
-  scale_colour_manual(values = c(oran[5], oran[7])) +
-  scale_fill_manual(values = c(oran[2], oran[4])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Warm ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
-  ylim(-0.5,100) +
-  theme_classic() +
-  theme(legend.position = 'none',
-        axis.text = element_text(size = 11),
-        axis.title = element_text(size = 12),
-        title = element_text(size = 12)) -> h2_warm_plot
-
-# BURN
-ggplot(data = vas_meds %>% 
-         filter(quality == 'burn'),
-       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_boxjitter(data = vas_meds %>% 
-    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-  geom_line(data = h2_sum %>% 
-    filter(quality == 'burn', manipulation == 'Non-TGI'),
-    aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge1)) + 
-  geom_line(data = h2_sum %>% 
-    filter(quality == 'burn', manipulation == 'TGI'),
-    aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge2)) +
-  scale_colour_manual(values = c(purp[5], purp[7])) +
-  scale_fill_manual(values = c(purp[2], purp[4])) +
-  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Burn ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
-  ylim(-0.5,100) +
-  theme_classic() +
-  theme(legend.position = 'none',
-        axis.text = element_text(size = 11),
-        axis.title = element_text(size = 12),
-        title = element_text(size = 12))  -> h2_burn_plot
-
-# arrange entire plot
-h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
-                     nrow = 2, ncol = 2)
-h2_plot
-
-ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
-       width = 10, height = 7, dpi = 600)
-```
-
-# Differences
-```{r h2diff}
-# recode cold_location and condition to reduce levels in regression
-vas_meds$cold_cond[vas_meds$cold_probe == 'distal'] <- 'dist_rost' 
-vas_meds$cold_cond[vas_meds$cold_probe == 'rostral'] <- 'dist_rost' 
-vas_meds$cold_cond[vas_meds$cold_probe == 'proximal'] <- 'prox_caud' 
-vas_meds$cold_cond[vas_meds$cold_probe == 'caudal'] <- 'prox_caud'
-
-# then pivot wider and calculate difference
-vas_h2_diff <- vas_meds %>% 
-  select(-c(cold_code, xj, cold_probe)) %>% 
-  pivot_wider(id_cols = c(ID, quality, manipulation, condition), 
-              names_from = cold_cond, values_from = VAS) %>% 
-  mutate(difference = prox_caud - dist_rost)
-# recode quality
-vas_h2_diff$quality <- factor(vas_h2_diff$quality,
-                           levels = c('cold', 'warm', 'burn'))
-# summary statistics
-h2_diff_sum <- summarySEwithin(data = vas_h2_diff, measurevar = 'difference',
-                               withinvars = c('manipulation', 'quality', 'condition'))
-
-# plot the differences - within
-ggplot(data = vas_h2_diff %>% 
-         filter(condition == 'within'), 
-       aes(manipulation, difference, colour = quality)) +
-  geom_hline(yintercept = 0) +
-  geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5) +
-  geom_point(data = h2_diff_sum %>% 
-               filter(condition == 'within'), 
-             aes(manipulation, difference), colour = 'grey15',
-             fill = 'grey15',
-             shape = 21, size = 3) +
-  geom_errorbar(data = h2_diff_sum %>% 
-               filter(condition == 'within'), 
-               aes(manipulation, ymin = difference-ci, ymax = difference+ci),
-               width = .1, size = .7, colour = 'grey15') +
-  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-  labs(title = 'Within: Proximal vs. Distal',
-       y = 'Proximal - Distal VAS Ratings', x = NULL) +
-  facet_wrap(~quality) +
-  theme_classic() +
-  theme(legend.position = 'none') -> h2_diff_within
-
-# plot the differences - across
-ggplot(data = vas_h2_diff %>% 
-         filter(condition == 'across'), 
-       aes(manipulation, difference, colour = quality)) +
-  geom_hline(yintercept = 0) +
-  geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5) +
-  geom_point(data = h2_diff_sum %>% 
-               filter(condition == 'across'), 
-             aes(manipulation, difference), colour = 'grey15',
-             fill = 'grey15',
-             shape = 21, size = 3) +
-  geom_errorbar(data = h2_diff_sum %>% 
-               filter(condition == 'across'), 
-               aes(manipulation, ymin = difference-ci, ymax = difference+ci),
-               width = .1, size = .7, colour = 'grey15') +
-  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-  labs(title = 'Across: Rostral vs. Caudal',
-       y = 'Caudal - Rostral VAS Ratings', x = NULL) +
-  facet_wrap(~quality) +
-  theme_classic() +
-  theme(legend.position = 'none') -> h2_diff_across
-
-# arrange entire plot
-h2diff_plot <- ggarrange(h2_diff_within, h2_diff_across,
-                     nrow = 2, ncol = 1)
-h2diff_plot
-
-ggsave('h2_diff_plot.png', h2diff_plot, device = NULL, path = anaPath,
-       width = 6, height = 9, dpi = 600)
-```
-
-# Plot 32 burn responders seperately
-```{r burn32}
-```
-
-# ZOIB regression
-Running main analysis of a zero inflated beta regression
-Outcome: VAS
-Predictors: manipulation (CNT, TGI), cold probe location ()
-Run a seperate regression for each quality
-
-```{r model_prep}
-set.seed(1234)  # Make everything reproducible
-
-# Define the goodness-of-fit stats to include in modelsummary()
-gof_stuff <- tribble(
-  ~raw, ~clean, ~fmt,
-  "nobs", "N", 0,
-  "r.squared", "R²", 3
-)
-
-# recode cold_location and condition to reduce levels in regression
-df_long$cold_cond[df_long$cold_probe == 'distal'] <- 'dist_rostr' 
-df_long$cold_cond[df_long$cold_probe == 'rostral'] <- 'dist_rostr' 
-df_long$cold_cond[df_long$cold_probe == 'proximal'] <- 'prox_caud' 
-df_long$cold_cond[df_long$cold_probe == 'caudal'] <- 'prox_caud'
-
-# to run zero inflated regressions need to make sure no values = 100, 
-# as cannot model them, so simply minus a very small fraction from those values
-df_long$beta <- ifelse(df_long$VAS==100, df_long$beta-0.0001, df_long$beta <- df_long$VAS)
-df_long$beta <- df_long$beta/100
-
-# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
-#df_long$VAS <- df_long$VAS/100
-df_long$ID <- factor(df_long$ID)
-```
-
-Running models as pre-registered: 
-# Cold
-```{r coldmod}
-# Try and model all with ratings
-model.cold = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
-                                (1|ID) + (1|order),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_long %>% filter(quality == 'cold'),
-                      na.action = na.omit) 
-mc <- summary(model.cold)
-mc
-
-Anova(model.cold)
-# get Rsq with the mumin package
-```
-# Marginal effect plots of full model - cold
-```{r}
-cold_eff <- ggeffects::ggpredict(model.cold, terms = c('cold_cond', 'manipulation', 'condition'),
-                           ci.lvl = .95)
-# changing labels for plotting
-cold_eff$group <- factor(cold_eff$group, labels = c('Non-TGI', 'TGI'))
-cold_eff <- cold_eff %>% 
-  mutate(label = 
-           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
-                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
-                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
-                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
-         )
-
-cold_eff$label = factor(cold_eff$label, levels = c('proximal','distal','caudal','rostral'))
-
-# plotting - within
-ggplot(data = cold_eff %>% 
-         filter(facet == 'within'), 
-       aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3), size = 2.5) +
-  geom_line(position = position_dodge(.3), size = 1) +
-  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1, size = .8) +
-  ylim(0, 0.5) +
-  labs(x = NULL, y = 'Predicted Cold Rating (0 - 1)') +
-  facet_wrap(~facet) +
-  scale_colour_manual(values = c(blue[4], blue[7])) +
-  theme_classic() +
-  theme(legend.title = element_blank(),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12),
-        strip.text = element_text(size = 12),
-        legend.text = element_text(size = 11)) -> plot_coldw_eff
-# plotting - across
-ggplot(data = cold_eff %>% 
-         filter(facet == 'across'), 
-       aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3), size = 2.5) +
-  geom_line(position = position_dodge(.3), size = 1) +
-  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1, size = .8) +
-  ylim(0, 0.5) +
-  labs(x = NULL, y = '') +
-  facet_wrap(~facet) +
-  scale_colour_manual(values = c(blue[4], blue[7])) +
-  theme_classic() +
-  theme(legend.title = element_blank(),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12),
-        strip.text = element_text(size = 12),
-        legend.text = element_text(size = 10)) -> plot_colda_eff
-
-# combine
-plot_cold_eff1 <- ggarrange(plot_coldw_eff, plot_colda_eff,
-                           ncol = 2, nrow = 1,
-                           common.legend = TRUE,
-                           legend = 'right')
-plot_cold_eff1
-```
-
-# Warm
-```{r warmmod}
-# Try and model all with ratings
-model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
-                                trial_n + (1|ID) + (1|order),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_long %>% filter(quality == 'warm'),
-                      na.action = na.omit) 
-mw <- summary(model.warm)
-mw
-
-Anova(model.warm)
-```
-# Marginal effect plots of full model - warm
-```{r}
-warm_eff <- ggeffects::ggpredict(model.warm, terms = c('cold_cond', 'manipulation', 'condition'),
-                            ci.lvl = .95)
-# changing labels for plotting
-warm_eff$group <- factor(warm_eff$group, labels = c('Non-TGI', 'TGI'))
-warm_eff <- warm_eff %>% 
-  mutate(label = 
-           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
-                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
-                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
-                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
-         )
-
-warm_eff$label = factor(warm_eff$label, levels = c('proximal','distal','caudal','rostral'))
-
-# plotting - within
-ggplot(data = warm_eff %>% 
-         filter(facet == 'within'), 
-       aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3), size = 2.5) +
-  geom_line(position = position_dodge(.3), size = 1) +
-  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1, size = .8) +
-  ylim(0, 0.5) +
-  labs(x = NULL, y = 'Predicted Warm Rating (0 - 1)') +
-  facet_wrap(~facet) +
-  scale_colour_manual(values = c(oran[4], oran[7])) +
-  theme_classic() +
-  theme(legend.title = element_blank(),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12),
-        strip.text = element_text(size = 12),
-        legend.text = element_text(size = 11)) -> plot_warmw_eff
-# plotting - across
-ggplot(data = warm_eff %>% 
-         filter(facet == 'across'), 
-       aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3), size = 2.5) +
-  geom_line(position = position_dodge(.3), size = 1) +
-  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1, size = .8) +
-  ylim(0, 0.5) +
-  labs(x = NULL, y = '') +
-  facet_wrap(~facet) +
-  scale_colour_manual(values = c(oran[4], oran[7])) +
-  theme_classic() +
-  theme(legend.title = element_blank(),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12),
-        strip.text = element_text(size = 12),
-        legend.text = element_text(size = 10)) -> plot_warma_eff
-
-# combine
-plot_warm_eff1 <- ggarrange(plot_warmw_eff, plot_warma_eff,
-                           ncol = 2, nrow = 1,
-                           common.legend = TRUE,
-                           legend = 'right')
-plot_warm_eff1
-```
-# Burn
-The burning hypothesis is only for participants that experience burning TGI 
-(aka are responders)
-```{r burnmod}
-# First, remove non-responders
-df_resp <- df_long %>% 
-  filter(responder == 1)
-# check n
-n <- count(df_resp, 'ID')
-length(n$ID)
-# Try and model all with ratings
-model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
-                                trial_n + (1|ID) + (1|order),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_resp %>% filter(quality == 'burn'),
-                      na.action = na.omit) 
-mb <- summary(model.burn)
-mb
-
-Anova(model.burn)
-```
-
-# Marginal effect plots of full model - burn
-```{r}
-burn_eff <- ggeffects::ggpredict(model.burn, terms = c('cold_cond', 'manipulation', 'condition'),
-                            ci.lvl = .95)
-# changing labels for plotting
-burn_eff$group <- factor(burn_eff$group, labels = c('Non-TGI', 'TGI'))
-burn_eff <- burn_eff %>% 
-  mutate(label = 
-           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
-                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
-                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
-                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
-         )
-
-burn_eff$label = factor(burn_eff$label, levels = c('proximal','distal','caudal','rostral'))
-
-# plotting - within
-ggplot(data = burn_eff %>% 
-         filter(facet == 'within'), 
-       aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3), size = 2.5) +
-  geom_line(position = position_dodge(.3), size = 1) +
-  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1, size = .8) +
-  ylim(0, 0.5) +
-  labs(x = NULL, y = 'Predicted Burn Rating (0 - 1)') +
-  facet_wrap(~facet) +
-  scale_colour_manual(values = c(purp[4], purp[7])) +
-  theme_classic() +
-  theme(legend.title = element_blank(),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12),
-        strip.text = element_text(size = 12),
-        legend.text = element_text(size = 11)) -> plot_burnw_eff
-# plotting - across
-ggplot(data = burn_eff %>% 
-         filter(facet == 'across'), 
-       aes(label, predicted, group = group, colour = group),) +
-  geom_point(position = position_dodge(.3), size = 2.5) +
-  geom_line(position = position_dodge(.3), size = 1) +
-  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
-                position = position_dodge(.3), width = .1, size = .8) +
-  ylim(0, 0.5) +
-  labs(x = NULL, y = '') +
-  facet_wrap(~facet) +
-  scale_colour_manual(values = c(purp[4], purp[7])) +
-  theme_classic() +
-  theme(legend.title = element_blank(),
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12),
-        strip.text = element_text(size = 12),
-        legend.text = element_text(size = 10)) -> plot_burna_eff
-
-# combine
-plot_burn_eff1 <- ggarrange(plot_burnw_eff, plot_burna_eff,
-                           ncol = 2, nrow = 1,
-                           common.legend = TRUE,
-                           legend = 'right')
-plot_burn_eff1
-```
-
-# Zero inflation marginal effects plot of all models
-```{r zero_plots}
-# Getting the marginal effects for plotting
-# First the zeros - create new lm mo
-df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
-df_resp$bin <- ifelse(df_resp$VAS == 0, 1, 0)
-
-# model for each VAS
-# cold
-cold.zeff <- glm(bin~1+manipulation, 
-                  family = binomial(link = 'logit'),
-                  data = df_long %>% filter(quality == 'cold'))
-summary(cold.zeff)
-# warm
-warm.zeff <- glm(bin~1+manipulation, 
-                  family = binomial(link = 'logit'),
-                  data = df_long %>% filter(quality == 'warm'))
-summary(warm.zeff)
-# burn
-burn.zeff <- glm(bin~1+manipulation, 
-                  family = binomial(link = 'logit'),
-                  data = df_resp %>% filter(quality == 'burn'))
-summary(burn.zeff)
-
-# Data-frames
-cold_zeff <- ggeffects::ggeffect(cold.zeff, terms = c('manipulation'))
-warm_zeff <- ggeffects::ggeffect(warm.zeff, terms = c('manipulation'))
-burn_zeff <- ggeffects::ggeffect(burn.zeff, terms = c('manipulation'))
-# changing labels for plotting
-cold_zeff$x <- factor(cold_zeff$x, labels = c('Non-TGI', 'TGI'))
-warm_zeff$x <- factor(warm_zeff$x, labels = c('Non-TGI', 'TGI'))
-burn_zeff$x <- factor(burn_zeff$x, labels = c('Non-TGI', 'TGI'))
-
-# plotting - cold
-ggplot(cold_zeff, aes(x, predicted, colour = x)) +
-  geom_point(size = 2.5) +
-  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
-                width = .05, size = .8) +
-  labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(0,.25) +
-  scale_colour_manual(values = c(blue[4], blue[7])) +
-  theme_classic() + 
-  theme(legend.position = 'none',
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12)) -> plot_zcold
-
-# warm
-ggplot(warm_zeff, aes(x, predicted, colour = x)) +
-  geom_point(size = 2.5) +
-  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
-                width = .05, size = .8) +
-  labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(.45,.7) +
-  scale_colour_manual(values = c(oran[4], oran[7])) +
-  theme_classic() + 
-  theme(legend.position = 'none',
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12)) -> plot_zwarm
-
-# burn
-ggplot(burn_zeff, aes(x, predicted, colour = x)) +
-  geom_point(size = 2.5) +
-  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
-                width = .05, size = .8) +
-  labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(.05,.3) +
-  scale_colour_manual(values = c(purp[4], purp[7])) +
-  theme_classic() + 
-  theme(legend.position = 'none',
-        axis.text = element_text(size = 10),
-        axis.title = element_text(size = 12)) -> plot_zburn
-```
-
-# Compile all marginal effect plots
-```{r}
-# Cold
-plot_cold_eff <- ggarrange(plot_zcold, plot_cold_eff1,
-                   ncol = 2, nrow = 1,
-                   widths = c(.35,1))
-# add title
-plot_cold_eff <- annotate_figure(plot_cold_eff, top = text_grob("Cold Ratings", 
-                                                size = 12, hjust = 4.05))
-plot_cold_eff
-
-# Warm
-plot_warm_eff <- ggarrange(plot_zwarm, plot_warm_eff1,
-                   ncol = 2, nrow = 1,
-                   widths = c(.35,1))
-# add title
-plot_warm_eff <- annotate_figure(plot_warm_eff, top = text_grob("Warm Ratings", 
-                                                size = 12, hjust = 3.69))
-plot_warm_eff
-
-# Burn
-plot_burn_eff <- ggarrange(plot_zburn, plot_burn_eff1,
-                   ncol = 2, nrow = 1,
-                   widths = c(.35,1))
-# add title
-plot_burn_eff <- annotate_figure(plot_burn_eff, top = text_grob("Burn Ratings", 
-                                                size = 12, hjust = 4.1))
-plot_burn_eff
-
-# Compile all!
-plot_eff <- ggarrange(plot_cold_eff, plot_warm_eff, plot_burn_eff,
-                      ncol = 1, nrow = 3)
-plot_eff
-
-ggsave('h2_effects_plot.png', plot_eff, device = NULL, path = anaPath,
-       width = 9, height = 8, dpi = 600)
-```
-# Run model checks on all
-```{r checks, warning=FALSE}
-# cold assumption - on n = 50
-mc.assump <- simulateResiduals(model.cold, n = 1000)
-plot(mc.assump)
-# warm assumption - on n = 50
-mw.assump <- simulateResiduals(model.warm, n = 1000)
-plot(mw.assump)
-# warm assumption - on n = 50
-mb.assump <- simulateResiduals(model.burn, n = 1000)
-plot(mb.assump)
-```
-# EXPLORATORY HYPOTHESES
-# Correlation between quality (cold/warm/burn)
-
-```{r corr}
-# remove columns
-df_corr <- df_res[, c(1:9,14:16,21)]
-df_corr <- df_corr %>% 
-  pivot_wider(names_from = 'manipulation', values_from = c('VAScold','VASwarm','VASburn')) %>% 
-  select(c(ID,VAScold_CNT,VAScold_TGI,VASwarm_CNT,VASwarm_TGI,VASburn_CNT,VASburn_TGI)) %>% 
-  rename(CNTcold = VAScold_CNT,
-         TGIcold = VAScold_TGI,
-         CNTwarm = VASwarm_CNT,
-         TGIwarm = VASwarm_TGI,
-         CNTburn = VASburn_CNT,
-         TGIburn = VASburn_TGI)
-
-# average values within participants
-df_corr <- aggregate(. ~ID, mean, data = df_corr)
-# remove ID
-df_corr <- select(df_corr, -ID)
-
-# check distribution of data
-df_means <- aggregate(VAS ~ ID*quality*manipulation, mean, data = vas_meds)
-ggplot(df_means, aes(colour = quality)) +
-  geom_density(aes(VAS)) +
-  theme_bw()
-
-# correlate
-qual_cor <- hetcor(df_corr, type = 'spearman')
-cormat <- qual_cor$correlations
-
-# significance values
-p <- cor.mtest(df_corr, type ='spearman')$p
-
-# correlation matrix
-# plotting correlations between variables
-corrplot(cormat, type = 'lower',
-         p.mat = p, insig = "p-value", sig.level = -1,
-         title = "VAS rating correlation matrix", 
-         mar = c(0,0,1,0), 
-         tl.cex=0.9) 
-```
-
-# Scatter plots
-```{r scatter}
-# Non TGI plots
-ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
-  geom_smooth(method='lm', colour = 'black', alpha = .5) +
-  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
-  geom_text(aes(label = paste0("R = ",
-                               round(cormat[1,3], 2))),
-            x=78, y=91, size = 5) +
-  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
-  xlim(0,100) + ylim(-10,100) +
-  theme_bw() +
-  theme(axis.title = element_text(size = 12)) -> CNT_cw_plot
-
-ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
-  geom_smooth(method='lm', colour = 'black', alpha = .5) +
-  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
-  geom_text(aes(label = paste0("R = ",
-                               round(cormat[1,5], 2))),
-            x=78, y=91, size = 5) +
-  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-10,100) +
-  theme_bw() +
-  theme(axis.title = element_text(size = 12)) -> CNT_cb_plot
-
-ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
-  geom_smooth(method='lm', colour = 'black', alpha = .5) +
-  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
-  geom_text(aes(label = paste0("R = ",
-                               round(cormat[3,5], 2))),
-            x=78, y=91, size = 5) +
-  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-10,100) +
-  theme_bw() +
-  theme(axis.title = element_text(size = 12)) -> CNT_wb_plot
-
-# combine non TGI
-CNT_corr_plot <- ggarrange(CNT_cw_plot, CNT_cb_plot, CNT_wb_plot,
-                           nrow = 1, ncol = 3,
-                           labels = c('A','B','C'))
-CNT_corr_plot <- annotate_figure(CNT_corr_plot, 
-                                 top = text_grob("Non-TGI", 
-                                                 size = 14))
-
-# TGI plots
-ggplot(df_corr, aes(x = TGIcold, y = TGIwarm)) +
-  geom_smooth(method='lm', colour = 'black', alpha = .5) +
-  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
-  geom_text(aes(label = paste0("R = ",
-                               round(cormat[2,4], 2))),
-            x=78, y=91, size = 5) +
-  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
-  xlim(0,100) + ylim(-10,100) +
-  theme_bw() +
-  theme(axis.title = element_text(size = 12)) -> TGI_cw_plot
-
-ggplot(df_corr, aes(x = TGIcold, y = TGIburn)) +
-  geom_smooth(method='lm', colour = 'black', alpha = .5) +
-  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
-  geom_text(aes(label = paste0("R = ",
-                               round(cormat[2,6], 2))),
-            x=78, y=91, size = 5) +
-  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-10,100) +
-  theme_bw() +
-  theme(axis.title = element_text(size = 12)) -> TGI_cb_plot
-
-ggplot(df_corr, aes(x = TGIwarm, y = TGIburn)) +
-  geom_smooth(method='lm', colour = 'black', alpha = .5) +
-  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
-  geom_text(aes(label = paste0("R = ",
-                               round(cormat[4,6], 2))),
-            x=78, y=91, size = 5) +
-  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
-  xlim(0,100) + ylim(-10,100) +
-  theme_bw() +
-  theme(axis.title = element_text(size = 12)) -> TGI_wb_plot
-
-# combine TGI
-TGI_corr_plot <- ggarrange(TGI_cw_plot, TGI_cb_plot, TGI_wb_plot,
-                           nrow = 1, ncol = 3,
-                           labels = c('D','E','F'))
-TGI_corr_plot <- annotate_figure(TGI_corr_plot, 
-                                 top = text_grob("TGI", 
-                                                 size = 14))
-
-# put two together
-corr_plot <- ggarrange(CNT_corr_plot, TGI_corr_plot,
-                       nrow = 2, ncol = 1)
-corr_plot
-
-ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
-       width = 10, height = 6.5, dpi = 1000)
-```
-
-# Initial burn
-Are there any observed differences in dermatome and warm and cold afferents
-for the first initial burning rating, before trial begins?
-
-```{r initmod}
-# Try and model all with ratings
-model.init = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
-                                trial_n + (1|ID) + (1|order),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = df_long %>% filter(quality == 'init'),
-                      na.action = na.omit) 
-mi <- summary(model.init)
-mi
-
-```
-
-# Run individual models on within and across dermatomes for H2
-Directly compare proximal-distal and rostral-caudal results for each quality
-
-# Cold - within and across
-```{r cold_indiv}
-# seperate data-frames
-within <- df_long %>% 
-  filter(condition == 'within')
-across <-  df_long %>% 
-  filter(condition == 'across')
-
-# within
-model.wcold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'cold'),
-                      na.action = na.omit) 
-mwc <- summary(model.wcold)
-mwc
-
-# across
-model.acold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'cold'),
-                      na.action = na.omit) 
-mac <- summary(model.acold)
-mac
-```
-
-# Warm - within and across
-```{r warm_indiv}
-# within
-model.wwarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'warm'),
-                      na.action = na.omit) 
-mww <- summary(model.wwarm)
-mww
-
-# across
-model.awarm = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'warm'),
-                      na.action = na.omit) 
-maw <- summary(model.awarm)
-maw
-```
-
-# Burn - within and across
-```{r burn_indiv}
-# isolate responders only
-within <- df_long %>% 
-  filter(condition == 'within' & responder == 1)
-across <-  df_long %>% 
-  filter(condition == 'across' & responder == 1)
-
-# within
-model.wburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'burn'),
-                      na.action = na.omit) 
-mwb <- summary(model.wburn)
-mwb
-
-# across
-model.aburn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
-                                (1|ID),
-                      family = glmmTMB::beta_family(),
-                      ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'burn'),
-                      na.action = na.omit) 
-mab <- summary(model.aburn)
-mab
-```

### 2023-06-15 tgi-spinal_analysis-exp1.Rmd
making compiler code for exp1 and exp2

@@
 
+# Load in data
 ```{r paths}
@@
 anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Analysis/'
-```
-
-# Loading data
-```{r data, echo = FALSE}
-# Extract all .csv files and compile
-filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
-# empty dataframes for data
-## with new data trials file will have changed to include temperature coding!
-df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
-df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
-df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')
-
-## Data compiling
-# trial files
-setwd(datPath)
-for (file in filenames){
-  # trial files
-  if (isTRUE(substr(basename(file), 24, 24)=="t")){
-    tmp <- read.csv(file)
-    tmp$ID <- substr(basename(file), 4, 6)
-    tmp$manipulation <- substr(basename(file), 17, 19)
-    df_trials <- rbind(df_trials, tmp)
-  }
-  # VAS response files
-  if (isTRUE(substr(basename(file), 24, 29)=="rating")){
-    tmp <- read.csv(file, header = FALSE)
-    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
-    tmp$ID <- substr(basename(file), 4, 6)
-    tmp$manipulation <- substr(basename(file), 17, 19)
-    df_VAS <- rbind(df_VAS, tmp)
-  }
-  # VAS RT files
-  if (isTRUE(substr(basename(file), 24, 29)=="respti")){
-    tmp <- read.csv(file, header = FALSE)
-    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
-    tmp$ID <- substr(basename(file), 4, 6)
-    tmp$manipulation <- substr(basename(file), 17, 19)
-    df_RT <- rbind(df_RT, tmp)
-  }
-}
-
-# merge all files
-df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
-df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))
-
-# remove participant 019, stopped testing halfway due to broken thermal probe
-df_res <- df_res[df_res$ID != '019' ,]
-```
-
-# Data organisation
-```{r}
-# transform the ID of participants to remove 0
-df_res$ID <- as.numeric(df_res$ID)
-# recode conditions
-df_res <- df_res %>%
-  mutate(condition = dplyr::recode(condition, '1' = 'within', '2' = 'across'),
-         cold_probe = dplyr::recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
-                             'dist' = 'distal', 'prox' = 'proximal'))
-# change levels 
-df_res$cold_probe <- factor(df_res$cold_probe, 
-                            levels = c("caudal", "rostral", "distal", "proximal"))
-
-# incorporate demographics
-# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
-# have saved these in the demo .csv as well, so will add these in
-demoFile <- 'STGI_exp1_participant-demographics.csv'
-fileName = paste(datPath, demoFile, sep = '')
-df_demo <- read.csv(fileName)
-# merge
-test <- merge(df_res, df_demo)
-
-# save new data-frame
-fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
-write.csv(df_res, fileName, row.names = FALSE)
-
-# check we have 40 participants with 96 trials
-id_check <- count(df_res, ID)
-id_check
 ```

### 2023-06-15 tgi-spinal_analysis-exp2.Rmd
making compiler code for exp1 and exp2

--- 2023-05-23 analysis/tgi-spinal_analysis-exp2.Rmd
@@
 anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Analysis/'
-```
-
-# Loading data
-```{r data, echo = FALSE}
-# Extract all .csv files and compile
-filenames <- dir(datPath, recursive = TRUE, full.names = FALSE, pattern = '.csv')
-# empty dataframes for data
-## with new data trials file will have changed to include temperature coding!
-df_trials <- read.csv(text='procedure,trial_type,arm,condition,dermatome,order,cold_probe,trial_n,coolTemp,warmTempID,manipulation')
-df_VAS <- read.csv(text='VASinit,VASburn,VASwarm,VAScold,trial_n,ID,manipulation')
-df_RT <- read.csv(text='RTinit,RTburn,RTwarm,RTcold,trial_n,ID,manipulation')
-
-## Data compiling
-# trial files
-setwd(datPath)
-for (file in filenames){
-  # trial files
-  if (isTRUE(substr(basename(file), 24, 24)=="t")){
-    tmp <- read.csv(file)
-    tmp$ID <- substr(basename(file), 4, 6)
-    tmp$manipulation <- substr(basename(file), 17, 19)
-    df_trials <- rbind(df_trials, tmp)
-  }
-  # VAS response files
-  if (isTRUE(substr(basename(file), 24, 29)=="rating")){
-    tmp <- read.csv(file, header = FALSE)
-    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
-    tmp$ID <- substr(basename(file), 4, 6)
-    tmp$manipulation <- substr(basename(file), 17, 19)
-    df_VAS <- rbind(df_VAS, tmp)
-  }
-  # VAS RT files
-  if (isTRUE(substr(basename(file), 24, 29)=="respti")){
-    tmp <- read.csv(file, header = FALSE)
-    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
-    tmp$ID <- substr(basename(file), 4, 6)
-    tmp$manipulation <- substr(basename(file), 17, 19)
-    df_RT <- rbind(df_RT, tmp)
-  }
-}
-```
-
-# merging
-```{r data, echo = FALSE}
-# merge all files
-df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
-df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))
-
-# remove participants 047 and 048
-# one had ongoing pain, the other missed 6 trials
-df_res <- df_res[df_res$ID != '047' ,]
-df_res <- df_res[df_res$ID != '048' ,]
-```
-
-# Data organisation
-```{r}
-# transform the ID of participants to remove 0
-df_res$ID <- as.numeric(df_res$ID)
-# recode conditions
-df_res <- df_res %>%
-  mutate(condition = dplyr::recode(condition, '1' = 'within', '2' = 'across'),
-         cold_probe = dplyr::recode(cold_probe, 'C6' = 'rostral', 'T1' = 'caudal',
-                             'dist' = 'distal', 'prox' = 'proximal'))
-# change levels 
-df_res$cold_probe <- factor(df_res$cold_probe, 
-                            levels = c("caudal", "rostral", "distal", "proximal"))
-
-# incorporate demographics
-# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
-# have saved these in the demo .csv as well, so will add these in
-demoFile <- 'STGI_exp2_participant-demographics.csv'
-fileName = paste(datPath, demoFile, sep = '')
-df_demo <- read.csv(fileName)
-# merge
-test <- merge(df_res, df_demo)
-
-# save new data-frame
-fileName = paste(anaPath, 'STGI_compiled-data.csv', sep = '')
-write.csv(df_res, fileName, row.names = FALSE)
-
-# check we have 40 participants with 96 trials
-id_check <- count(df_res, ID)
-id_check
 ```

### 2023-06-15 tgi-compiler.Rmd
making directory changes to analysis code

@@
 if (!require("pacman")) install.packages("pacman")
-  pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
-                 ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
-                 modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
-                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
-                 )
+  pacman::p_load(tidyverse)
 ```
@@
 # save new data-frame
-write.csv(df_res, file.path("data", "STGI_exp1_compiled-data.csv"), row.names = FALSE)
+write.csv(df_res, file.path("data", "STGI_exp2_compiled-data.csv"), row.names = FALSE)
 

### 2023-06-15 tgi-spinal_analysis-exp2.Rmd
making directory changes to analysis code

@@
 author: "A.G. Mitchell"
-date: "2023-04-14"
+date: "2022-12-02"
 output: html_document
 ---
+
+DATA ANALYSIS SCRIPT FOR TGI-SPINE EXPERIMENT 2
 
@@
 
+# Load in data
 ```{r paths}
-# paths
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Raw/'
-anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Analysis/'
+# experiment 1 file
+dat_file <- file.path("data", 'STGI_exp2_compiled-data.csv')
+# load all data file
+if (file.exists(dat_file)){
+  df_res <- read.csv(dat_file)
+  } else {
+    print('Data file does not exist, check data is in current directory. 
+          If not, run tgi-compiler.Rmd')
+  }
 ```
@@
                values_to = 'RT')
+
 # remove the VAS & RT from quality column
@@
 df_long2$quality <- substr(df_long2$quality, 3, 6)
+
 # remove columns from both then merge
-df_long <- df_long[, c(1:12,17:19)]
-df_long2 <- df_long2[, c(1:12,17:19)]
+df_long <- df_long %>% 
+  select(-c(coolTemp, warmTemp, Order, Manipulation.first))
+df_long2 <- df_long2 %>% 
+  select(-c(coolTemp, warmTemp, Order, Manipulation.first))
+
 df_long <- merge(df_long, df_long2)
@@
   scale_alpha_discrete(range = c(0.6, 1)) +
-  ylim(0,70) +
+  ylim(0,50) +
   theme_bw() 
@@
 h1_diff_plot
-ggsave('h1_difference.png', h1_diff_plot, path = anaPath, device = NULL, 
-       width = 7, height = 4.5, dpi = 1000)
+
+ggsave(here::here("figures", "E2_H1_difference.png"), plot = h1_diff_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 # All dat plot
-
 ```{r}
@@
 
-ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
-       width = 10, height = 7, dpi = 600)
+ggsave(here::here("figures", "E2_H2_allDat.png"), plot = h2_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 
-ggsave('h2_diff_plot.png', h2diff_plot, device = NULL, path = anaPath,
-       width = 6, height = 9, dpi = 600)
+ggsave(here::here("figures", "E2_H2_difference.png"), plot = h2diff_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 ```
+
 # Marginal effect plots of full model - cold
@@
 Anova(model.warm)
-```
+# save results
+```
+
 # Marginal effect plots of full model - warm
@@
   labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(.20,.60) +
+  ylim(0,.25) +
   scale_colour_manual(values = c(blue[4], blue[7])) +
@@
   labs(y = 'Predicted proportion of zeros', x = NULL) +
-  ylim(0,.25) +
+  ylim(.45,.7) +
   scale_colour_manual(values = c(oran[4], oran[7])) +
@@
 
-ggsave('h2_effects_plot.png', plot_eff, device = NULL, path = anaPath,
-       width = 9, height = 8, dpi = 600)
-```
+ggsave(here::here("figures", "E2_marginalEffects.png"), plot = plot_eff, 
+       device = NULL, width = 9, height = 5, dpi = 600)
+```
+
 # Run model checks on all
@@
 ```
+
 # EXPLORATORY HYPOTHESES
@@
 
-ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
-       width = 14, height = 9, dpi = 1000)
+ggsave(here::here("figures", "E2_correlations.png"), plot = corr_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```

### 2023-07-10 Manuscript.Rmd
manuscript_updates

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: 
  - name : "**Jesper Fischer Ehmsen**"
    affiliation: "1"
  - name : "Daniel Elmstrom Christensen"
    affliation : "2"
affliation:

  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
  word_document:
bibliography: knitting files/Citations.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
---

# Abstract

The Thermal Grill Illusion (TGI) is a phenomenon in which the juxtaposition of innocuous warm and cold temperatures elicits a burning sensation, offering a unique window to understand how pain can be perceived in response to harmless stimuli. Much debate has revolved around whether spinal mechanisms are involved in the generation of illusory pain, beyond supraspinal mechanisms. In this study, we investigated the role of the spinal cord in the generation of the TGI, in two independent experiments, involving a total of 80 healthy individuals. We applied heat and cold stimuli on dermatomes, namely areas of skin innervated by a single spinal nerve, mapped onto adjacent or nonadjacent spinal segments. Participants were asked to rate their perceptions of cold, warm, and burning sensations in response to TGI and control stimuli. Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the TGI that may illuminate processes underlying thermosensory integration in the spinal cord. Our findings revealed that both thermosensory and painful components of TGI perception were modulated similarly, with enhanced warm and burning ratings observed when cold and warm stimuli were confined within the same dermatome. Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but a notable enhancement of the TGI effect when the cold stimulus was associated with a more caudal segmental location along the spinal cord compared to the warm stimulus. These results provide insights into the organisation of the spinal cord in relation to the thermosensory integration and generation of the TGI.

\newpage

# Introduction

The thermal grill illusion (TGI) is a perceptual phenomenon that challenges conventional understanding of pain perception. It is a sensation of burning heat or pain when harmless cold and warm temperatures are applied to the skin simultaneously [@craig_thermal_1994; @craig_functional_1996]. 
Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors. The generation of this illusion is thus attributed to central nervous system mechanisms [@fardo_beyond_2020]. Recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017]. However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008, @fardo_beyond_2020]. The illusion of heat, also known as synthetic heat [@fruhstorfer_significance_2003; @green_localization_1977; -@green_synthetic_2002; -@green_temperature_2004], refers to non-painful sensations evoked by the thermal grill [@defrin_spatial_2008; @kern_pharmacological_2008; -@kern_effects_2008; @bouhassira_investigation_2005; @adam_relationships_2014]. The illusion of pain, which is the most recognised aspect of the TGI, is the distinctive burning sensation that accompanies the simultaneous presentation of cold and warm stimuli [@craig_thermal_1994; -@craig_functional_1996; @bach_thermal_2011]. The hallmark of both illusory components is a qualitative change in perception when the cold and warm stimuli are applied concurrently, compared to when they are presented individually. Historically, the thermosensory and painful components of the TGI were explained by distinct spinal and supraspinal mechanisms, respectively. The enhanced perception of heat in TGI was explained by a spinal inhibitory mechanism, drawing from observations in an animal model where simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone
[@craig_thermal_1994]. Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following a thalamic lesion [@craig_thermal_1994; -@bud_craig_new_1998]. Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion. Two studies posited that the illusory pain of the TGI depends uniquely on supraspinal mechanisms. This interpretation was based on the observed modulation of the illusion in accordance with a spatiotopic rather than somatotopic representation of the body [@marotta_transforming_2015]. Further, the illusion remained unaltered during concomitant tactile stimulation, suggesting ineffectiveness of tactile gating - a spinally-mediated process involving inhibition of nociceptive activity by concurrent somatosensory activity [@ferre_ineffectiveness_2018]. Counter to this perspective, other research endorsed a spinal contribution to the TGI. These studies demonstrated that the illusion varied depending on whether cold and warm stimuli were applied to dermatomes mapped either onto adjacent or non-adjacent spinal segments [@fardo_organization_2018]. Participants perceived the stimulation more veridically, consistently with a reduction in TGI perception, when warm or cold stimuli triggered more widespread activity along the spinal cord, corroborating the hypothesis that the spinal cord is an initial site of thermosensory integration underlying TGI. Further support for spinal mechanisms comes from research demonstrating that both noxious heat and the TGI were comparably reduced by conditioned pain modulation in humans. This suggests a similar influence of descending modulation, irrespective of whether the painful sensation was triggered by potentially harmful (noxious) or harmless (innocuous) stimuli [@harper_conditioned_2017]. These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain within the TGI.
In this paper our objective was twofold. Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes. Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and burning components. Here, to probe possible distinctions between the two qualitative components of the TGI, we measured subjective indices of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations. Secondly, we investigated spatial order effects associated with the integration of cold and warm sensory information at the dermatome (skin) and segmental (i.,e., spine) levels. At the dermatome level, we used body-related coordinates to define proximal (towards the elbow) and distal (towards the wrist) locations. At the spinal level, we used segment-related coordinates to define more rostral (towards the head) and more caudal (towards the lower back) locations. Given the organisation of the spinal cord along a rostral-caudal axis, where each dermatome is represented across multiple spinal segments through the Lissauer tract, this study aimed to glean indirect insights into the spinal mechanisms underpinning thermosensory integration and the generation of the TGI.

# Results and discussion
The Thermal Grill Illusion (TGI) is characterised by two key phenomena: thermosensory enhancement and illusory pain. Thermosensory enhancement refers to an amplified perception of heat or cold when cold and warm stimuli are simultaneously applied, as opposed to when each stimulus is presented individually or paired with a neutral temperature. Notably, the majority of individuals experience an intensification of heat rather than cold [@fardo_beyond_2020]. Illusory pain, on the other hand, denotes the perception of a burning sensation elicited by the pairing of warm and cold stimuli, an experience that is largely absent or significantly diminished when each stimulus is presented alone or combined with a neutral temperature. Thus, indicators of a stronger TGI are heightened warm and burning ratings, coupled with reduced cold ratings. 
To investigate thermosensory and burning components of the TGI, participants received pairs of temperatures on their forearms and were asked to quantify the levels of cold, warmth, and burning they experienced during each stimulation. These stimuli consisted of either cold-warm pairs (TGI stimuli), which potentially evoked an illusion of heat and pain, or control stimuli that involved pairing a cold or a warm stimulus of identical temperature as in the TGI condition with a baseline temperature of 30°C (non-TGI stimuli). All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments. In doing so, the stimuli elicited cold-related and warm-related neural activity that was either more focal or more widespread along the spinal cord. For each stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of a sensation, to 100, indicating an extreme sensation. For each instance of stimulation, participants were guided to focus their reporting on the sensations originating from a specific thermode. While the participants were unaware, this location corresponded to either the colder stimulus (Exp. 1) or the warmer stimulus (Exp. 2) of the paired temperatures. VAS ratings were analysed using zero-inflated beta regressions.

## Thermosensory and burning components of TGI perception are spinally mediated 
```{r, warning = F, message = F, echo = F,include=FALSE}
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
                 ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork
                 )
source(here::here("scripts","utility.R"))

#get models
source(here::here("scripts","models.R"))

stats = statistics(rerun = F)

list2env(stats, envir=environment())
```

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1"}
plot1()
```

In keeping with the unique heat and burning features of TGI, our results exhibited a more robust TGI when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments (Fig. 2). Participants reported a significantly reduced subjective experience of cold (Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[2]`, `r make_pvalue(stats_model_cold_exp1$p[2])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`), alongside a markedly enhanced subjective experience of warmth (Exp. 1: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`; Exp. 2: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`) for TGI compared to non-TGI stimuli. In addition, a heightened burning sensation was reported in our second experiment (Exp.1: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`; Exp. 2 $\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2])`) for TGI compared to non-TGI stimuli. These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level. These findings are consistent with previous results on the modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation  [@harper_conditioned_2017]. All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI.

## Undetected proximodistal bias in TGI
Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two warm stimuli presented on the forearm [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007]. In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3). Interestingly, we found no perceptual differences in TGI based on whether the cold stimulus was located proximally or distally (Exp. 1: xxx, xxx; Exp. 2: xxx, xxx). This result implies that the concept of distal inhibition may not apply when stimuli of different thermosensory qualities are presented. Alternatively, if it does apply, its effect size might be rather small, with limited impact on TGI perception.
<!-- Revision this but is proabably Run individual models on within and across dermatomes for H2 -->

```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Figure 2"}
plot2()
```

## Directional effects in inter-segmental sensory integration 
A main objective of this study was assessing spatial order effects along the rostrocaudal axis at the spinal level. We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli. The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord, as depicted in Figure 3. Our data revealed a substantial decrease in the subjective experience of cold (Exp. 1: estimate = xxx, p = xxx; Exp. 2: estimate: xxx, p = xxx), coupled with a significant increase in the subjective sensations of warmth (Exp. 1: estimate = xxx, p = xxx; Exp. 2: estimate: xxx, p = xxx) and burning sensations (Exp.1: estimate: xxx, p = xxx; Exp. 2 estimate: xxx, p = xxx) in response to TGI as compared to non-TGI stimuli. These findings were consistent across both experiments for thermosensory ratings, albeit with minor deviations that corresponded with the particular stimulation quality being assessed. The observed enhancement of warmth perception in Experiment 2 could be ascribed to the participants’ assessment of the warmer thermode as opposed to the colder one of Experiment 1. For burning ratings, significant results were seen in Experiment 2, but not in Experiment 1. One possible reason for this discrepancy could be the relatively low power in Experiment 1, as the power analysis was specifically focused on thermosensory ratings. Alternatively, assessing the warmer thermode might be a more accurate method for measuring TGI perception.

## Spinal organisation and TGI perception
The complexities of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) enhanced heat and burning sensations when cold-warm thermosensory integration takes place more focally within the spinal cord, and (2) discernible directional inter-segmental effects when distinct cold and warm stimuli elicited broader activity along the spinal cord. Small primary afferents, responsible for mediating temperature and pain sensations, split into ascending and descending branches that cover one to two segments before they enter the dorsal horn [@kerr_neuroanatomical_1975; @lamotte_distribution_1977). This pattern forms the Lissauer's tract, a structure hypothesised to regulate sensory transmission to the dorsal horn and influence spinal receptive field size [@wall_brief_1999].

Additionally, the endings of small primary afferents within the superficial laminae of the dorsal horn form synapses with both propriospinal neurons and projection neurons that target supraspinal structures known to significantly influence TGI perception [@craig_functional_1996; @lindstedt_evidence_2011; @leung_supraspinal_2014 + any other neuroimaging studies of the TGI].

Evidence from animal studies shows that propriospinal neurons, confined within the spinal cord, exhibit bidirectional collateral branches along the rostrocaudal plane [@saywell_electrophysiological_2011; @skinner_ascending_1989). These connections shape the network of interneurons that modulates sensory information delivered to the dorsal horn [@todd_neuronal_2010; @peirs_neural_2016].

Our finding of enhanced TGI perception with cold-warm stimuli applied within dermatomes might reflect the combined effects of the Lissauer's tract's short rostrocaudal span (comprising one to two segments, consistent with a single dermatome's boundary) and the characteristics of spinal circuits. These circuits, created by propriospinal neurons, may promote sensory integration within a spinal receptive field while simultaneously inhibiting activity in adjacent fields. This mechanism aligns with the concept of lateral inhibition, a ubiquitous process in sensory processing seen across both the peripheral and central nervous systems, and multiple sensory modalities, including thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021).
Further, our observation that spatial factors, such as the more caudal localisation of cold activity relative to warm activity in the spinal cord, influences TGI perception, suggests possible neuroanatomical and functional asymmetries. This could mean a greater number of ascending fibres than descending fibres carrying thermosensory information in the Lissauer's tract, an uneven distribution of ascending and descending collaterals of propriospinal neurons (Anatomical Hypotheses), or varying effects of inter-segmental inhibition along the rostrocaudal axis (Functional Hypothesis). Additional research is needed to illuminate the specific anatomical and functional features of the spinal cord that resulted in the observed effects of this study.

# Conclusion
Illusions in the thermo-nociceptive system can be leveraged to improve our understanding of mechanisms contributing to pain perception. Here, we presented results supporting the notion that the spinal cord plays a crucial role in the integration and processing of thermal information, contributing to the perception of both thermosensory enhancement and the illusory pain within the TGI. Additionally, we reported findings on directional inter-segmental effects in spinal integration underlying TGI. Further research is needed to elucidate the neuroanatomical and functional properties of the spinal cord, as well as the intricate interplay between supraspinal and spinal processes, that give rise to TGI perception.

# Methods

## Participants
The study entailed two separate experiments, collectively involving 80 healthy volunteers. The sample consisted of xx females and xx males, mean age = XX years old (SD = x.xx, range = xx - xx) in Experiment 1, and xx females and xx males, mean age = XX years old (SD = x.xx, range = xx - xx), in Experiment 2. The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark. Prior to commencing the study, all participants were fully informed about the procedures and provided their voluntary consent.

## Stimuli and procedure
All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3 software (version 5.4b). The procedure involved measurements of heat and cold pain thresholds, calibration of cold-warm temperature pairs eliciting TGI, and an experimental task where TGI and non-TGI stimuli were applied on dermatomes that mapped onto adjacent or non-adjacent spinal segments.
To measure cold and heat pain thresholds, we gradually adjusted the temperature of one thermode until the participant indicated an experience of pain by pressing a stop button or reached the maximum temperature cut-offs of 5ºC or 50ºC. We calibrated TGI stimuli by identifying a cold-warm temperature pair based on specific criteria: (1) consistently eliciting a burning sensation of at least 15 on a scale ranging from 0 to 100, (2) consistently avoiding a burning sensation (less than 15) when the cold-neutral (Exp. 1) or warm-neutral (Exp. 2) stimuli were presented, (3) both cold and warm temperatures falling within the innocuous range based on individual cold and heat pain thresholds. For pain threshold measurements and TGI calibration, we positioned the probes within a single dermatome. 
To address our experimental questions, we presented the calibrated TGI stimuli, as well as cold-neutral (Exp. 1) or warm-neutral (Exp. 2) non-TGI stimuli using two thermodes. In non-TGI stimuli the cold or warm temperatures were set to match the temperature used for TGI stimulation, but paired with a neutral temperature set at 30ºC. The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant’s forearm size. The positioning of the thermodes was either within the same dermatome (i.e., C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1). Further, we manipulated the spatial arrangement of the temperature pairs, by systematically presenting an equal number of trials where the cold thermode was applied on a proximal or distal location within a dermatome, or was applied on a dermatome that mapped onto a rostral or caudal segment along the spinal cord. We based the demarcation of the dermatome boundaries on the American Spinal Injury Association (ASIA) map (Fardo et al., 2018) and positioned the thermodes in relation to standard anatomical landmarks. Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head or the lower back. The possible spatial arrangements corresponded to the four conditions depicted in Figure 1. The order of the stimuli (TGI vs. non-TGI), the dermatome condition (within vs. across) and the relative placement of the colder temperature (proximal vs. distal or rostral vs. caudal) were pseudo-randomised and counterbalanced between participants.
During each trial, the experimenter positioned two thermodes, mounted on a stand using two independent clamps, on the participant’s skin for 10 seconds. An auditory cue (300Hz, 100ms) indicated the end of the stimulation period, after which the experimenter removed the thermodes from the participant’s skin. Participants then rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales. VAS scales were presented one at a time on a computer screen and appeared as a horizontal line, anchored at 0, representing no sensation (e.g., no burning), and 100, signifying an extreme sensation (e.g., extreme burning). The order of the three VAS scales was randomised across trials. For each scale,  participants provided their responses using the arrow keys on a keyboard and rated the intensity of their sensations from a specific location (labeled ‘A’ or ‘B’), based on the experimenter’s instruction. Unbeknown to the participant, this location systematically corresponded to either the colder temperature (Exp. 1) or the warmer temperature (Exp. 2). Participants had max 8 seconds to provide each rating, and if they did not complete a rating within the allowed timeframe, the trial was repeated. Following the completion of the last of the three VAS ratings, we presented a 200 ms fixation dot. Each thermode configuration was tested three consecutive times, on three different skin locations. An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter when to rearrange the thermode configuration to stimulate different dermatomes depending on a pseudo-randomisation order. Each of the four experimental conditions was repeated 12 times, with both the right and left forearms stimulated, and a minimum of five trials between the re-stimulation of the same skin location. This ensured that the same skin locations were not stimulated consecutively to minimise carry-over effects.
Experiments 1 and 2 were conducted in two independent groups of participants and followed exactly the same procedure except for two elements. In Experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs. In Experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs.

## Sample size
An initial pilot study informed the pre-registered calculation of the sample size. To test the directional TGI hypothesis with 95% power and detect an effect size of .12 or greater, we determined that we needed a minimum number of 32 TGI-responsive participants. We defined TGI-responders as those individuals for whom the median burning ratings for TGI stimuli significantly exceeded 0. Non-responders were individuals that did not meet this criterion when tested with the max cold-warm temperatures allowed in the experiment. The predefined cut-off for TGI stimulation was (xx-xx). In Experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants. We verified this criterion every 10 participants, resulting in a total sample size of 40 participants. In Experiment 2, we stopped recruitment once we collected data from 40 participants. This decision was based on meeting both required criteria: (1) matching the sample size of Exp. 1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.

## Data analyses
We re-scaled data from cold, warm and burning VAS ratings from their original values to a range of 0 to 1. Following re-scaling, we applied zero-inflated mixed-effects beta regression models separately for each set of VAS ratings. In these models, we incorporated three fixed effects. These included the type of stimulation (non-TGI vs. TGI), the dermatome condition (within the same dermatome vs. across different dermatomes) and the spatial positioning of the cold or neutral thermode (proximal vs. distal within dermatomes; rostral vs. caudal  across dermatomes). These choices allowed us to assess the individual and interactive effects of these three factors on VAS ratings. Further, we added random intercepts to our models to account for between-subject variability and the effects of repeated measures. The variables introduced as random intercepts included the participant ID, the counterbalancing order and the trial number. The choices of the zero-inflated approach and the use of beta regressions were necessitated by the specific distribution of VAS ratings. The beta distribution is suitable for modelling VAS rating data, as they are proportional in nature. Additionally, the zero-inflation was needed due to the presence of an excess number of zero values in specific ratings and conditions. Specifically, we anticipated an overrepresentation of zero values for thermosensory ratings that were counterfactual to the objective stimulation quality (i.e., cold ratings of warm stimuli and warm ratings of cold stimuli) and burning ratings of non-TGI stimuli. The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli. 
We carried out the statistical analyses using the 'glmmTMB' package in R (version x.xx), and statistical significance was set at p < .05. The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both Experiment 1 (add link) and Experiment 2 (add link). All data and code for the analysis are available in the github repository (xxx), ensuring the reproducibility of our findings.

# Authors contributions
Author contributions listed alphabetically according to CRediT taxonomy (https://credit.niso.org):
Conceptualization: DEC, JFE, FF, PH, AGM.
Data curation: JEF, AGM.
Formal analysis: JFE, FF, AGM.
Funding acquisition: FF.
Investigation: DEC, JFE, AGM.
Methodology: DEC, JFE, FF, AGM, AVS.
Project administration: FF, AGM.
Resources: FF, AGM.
Software: JFE, FF, AGM.
Supervision: FF, AGM.
Visualization: FF, AGM.
Writing – original draft: FF, AGM.
Writing – review & editing: FF, AGM. (+ others who will provide feedback)

# Acknowledgements
We would like to thank XXX for their help with participant recruitment and data collection. This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948788).

### 2023-07-10 tgi-spinal_analysis-exp1.Rmd
manuscript_updates

@@
 ```{r paths}
-# paths
-datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Raw/'
-anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Analysis/'
+# experiment 1 file
+dat_file <- file.path("data", 'STGI_exp1_compiled-data.csv')
+# load all data file
+if (file.exists(dat_file)){
+  df_res <- read.csv(dat_file)
+  } else {
+    print('Data file does not exist, check data is in current directory. 
+          If not, run tgi-compiler.Rmd')
+  }
 ```
@@
   theme_bw()
+
 ```
@@
 h1_diff_plot
-ggsave('h1_difference.png', h1_diff_plot, path = anaPath, device = NULL, 
-       width = 7, height = 4.5, dpi = 1000)
+
+ggsave(here::here("figures", "E1_H1_difference.png"), plot = h1_diff_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 
-ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
-       width = 10, height = 7, dpi = 600)
+ggsave(here::here("figures", "E1_H2_allDat.png"), plot = h2_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 
-ggsave('h2_diff_plot.png', h2diff_plot, device = NULL, path = anaPath,
-       width = 6, height = 9, dpi = 600)
+ggsave(here::here("figures", "E1_H2_difference.png"), plot = h2diff_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 df_long$ID <- factor(df_long$ID)
+
+df_long_exp1 = df_long
+
+source(here::here("scripts","utility.R"))
 ```
@@
 
+summary_stats(model.cold, 3,2)
 Anova(model.cold)
@@
 Anova(model.warm)
+# save results
 ```
@@
 
-ggsave('h2_effects_plot.png', plot_eff, device = NULL, path = anaPath,
-       width = 9, height = 8, dpi = 600)
-```
+ggsave(here::here("figures", "E1_marginalEffects.png"), plot = plot_eff, 
+       device = NULL, width = 9, height = 5, dpi = 600)
+```
+
 # Run model checks on all
@@
 
-ggsave('stgi_correlations.png', corr_plot, device = NULL, path = anaPath, 
-       width = 10, height = 6.5, dpi = 1000)
+ggsave(here::here("figures", "E1_correlations.png"), plot = corr_plot, 
+       device = NULL, width = 9, height = 5, dpi = 600)
 ```
@@
 # within
+
 model.wcold = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
@@
 mwc
+
+q = update(model.wcold, data = within %>% filter(quality == 'cold') %>% mutate(manipulation = as.factor(manipulation), manipulation = relevel(manipulation, ref ="TGI")))
+summary(q)
 
@@
 mac
+
+plot(ggeffect(model.wcold, terms = c("manipulation","cold_probe")))
+
+across %>% filter(quality == 'cold') %>% filter(beta != 0) %>% ggplot(aes(x = manipulation, y = beta, fill = cold_probe))+geom_boxplot(notch = T)
 ```
@@
 
+q = update(model.wwarm, data = within %>% filter(quality == 'warm') %>% mutate(manipulation = as.factor(manipulation), manipulation = relevel(manipulation, ref ="TGI")))
+summary(q)
+
 # across
@@
 
+q = update(model.wburn, data = within %>% filter(quality == 'burn') %>% mutate(manipulation = as.factor(manipulation), manipulation = relevel(manipulation, ref ="TGI")))
+summary(q)
+
 # across

### 2023-07-10 tgi-spinal_analysis-exp2.Rmd
manuscript_updates

@@
 df_long$ID <- factor(df_long$ID)
+
+df_long_exp2 = df_long
 ```
@@
                       ziformula = ~1+manipulation,
-                      data = df_long %>% filter(quality == 'cold'),
+                      data = df_long_exp2 %>% filter(quality == 'cold'),
                       na.action = na.omit) 
@@
                       ziformula = ~1+manipulation,
-                      data = df_long %>% filter(quality == 'warm'),
+                      data = df_long_exp2 %>% filter(quality == 'warm'),
                       na.action = na.omit) 
@@
 # First, remove non-responders
-df_resp <- df_long %>% 
+df_resp_exp2 <- df_long_exp2 %>% 
   filter(responder == 1)
 # check n
-n <- count(df_resp, 'ID')
+n <- count(df_resp_exp2, 'ID')
 length(n$ID)
@@
                       ziformula = ~1+manipulation,
-                      data = df_resp %>% filter(quality == 'burn'),
+                      data = df_resp_exp2 %>% filter(quality == 'burn'),
                       na.action = na.omit) 
@@
 # seperate data-frames
-within <- df_long %>% 
+within_exp2 <- df_long_exp2 %>% 
   filter(condition == 'within')
-across <-  df_long %>% 
+across_exp2 <-  df_long_exp2 %>% 
   filter(condition == 'across')
@@
                       ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'cold'),
+                      data = within_exp2 %>% filter(quality == 'cold'),
                       na.action = na.omit) 
@@
                       ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'cold'),
+                      data = across_exp2 %>% filter(quality == 'cold'),
                       na.action = na.omit) 
@@
                       ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'warm'),
+                      data = within_exp2 %>% filter(quality == 'warm'),
                       na.action = na.omit) 
@@
                       ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'warm'),
+                      data = across_exp2 %>% filter(quality == 'warm'),
                       na.action = na.omit) 
@@
 # isolate responders only
-within <- df_long %>% 
+within_exp2 <- df_long_exp2 %>% 
   filter(condition == 'within' & responder == 1)
-across <-  df_long %>% 
+across_exp2 <-  df_long_exp2 %>% 
   filter(condition == 'across' & responder == 1)
@@
                       ziformula = ~1+manipulation,
-                      data = within %>% filter(quality == 'burn'),
+                      data = within_exp2 %>% filter(quality == 'burn'),
                       na.action = na.omit) 
@@
                       ziformula = ~1+manipulation,
-                      data = across %>% filter(quality == 'burn'),
+                      data = across_exp2 %>% filter(quality == 'burn'),
                       na.action = na.omit) 

### 2023-07-10 scripts/models.R

@@ -1,0 +1,119 @@
+
+statistics = function(rerun){
+  
+if(rerun){
+  ######### Exp 1
+  
+  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
+  experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
+  
+  df_long_exp1 = experiment1$df_long
+  df_long_exp2 = experiment2$df_long
+  ## hypothsis 1
+  # Cold
+  model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
+                                  (1|ID) + (1|order),
+                                family = glmmTMB::beta_family(),
+                                ziformula = ~1+manipulation,
+                                data = df_long_exp1 %>% filter(quality == 'cold'),
+                                na.action = na.omit) 
+  
+  stats_model_cold_exp1 = summary_stat(model_cold_exp1, 2,2)
+  
+  # Warm
+  model_warm_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
+                                  trial_n + (1|ID) + (1|order),
+                                family = glmmTMB::beta_family(),
+                                ziformula = ~1+manipulation,
+                                data = df_long_exp1 %>% filter(quality == 'warm'),
+                                na.action = na.omit) 
+  
+  
+  stats_model_warm_exp1 = summary_stat(model_warm_exp1, 2,2)
+  
+  # Burn
+  #The burning hypothesis is only for participants that experience burning TGI 
+  #(aka are responders)
+  # First, remove non-responders
+  df_resp_exp1 <- df_long_exp1 %>% 
+    filter(responder == 1)
+  # check n
+  length(unique(df_resp_exp1$ID))
+  
+  model_burn_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
+                                  trial_n + (1|ID) + (1|order),
+                                family = glmmTMB::beta_family(),
+                                ziformula = ~1+manipulation,
+                                data = df_resp_exp1 %>% filter(quality == 'burn'),
+                                na.action = na.omit) 
+  
+  stats_model_burn_exp1 = summary_stat(model_burn_exp1, 2,2)
+  
+  
+  
+  
+  
+  ## hypothsis 2 (within)
+  ######### Exp 2
+
+  # Cold
+  model_cold_exp2 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
[…]

### 2023-07-10 scripts/utility.R

@@ -1,0 +1,348 @@
+#convinient function to make p-values to desired format
+make_pvalue = function(p_value){
+  if (p_value > 0.05){
+    p_value = round(p_value,2)
+    p = paste("p = ",p_value)
+  }
+  if (p_value < 0.05){
+    p = "p < .05 "
+  }
+  if(p_value < 0.01){
+    p = "p < .01"
+  }
+  if(p_value < 0.001){
+    p = "p < .001"
+  }
+  if(p_value < 0.0001){
+    p = "p < .0001"
+  }
+  return(p)
+}
+
+
+#get summary statistics from a generalized linear mixed effects model.
+#Arguments: model is the model to get statistics on. Coefficients is the index of the coefficients when using summary(model) (that is excluding the intercept and until the coefficients arguemnt),
+#round is the rounding of the statistics.
+summary_stat = function(model, coefficients, round){
+  a = summary(model)
+  coef = array(NA, coefficients)
+  std = array(NA, coefficients)
+  stat = array(NA, coefficients)
+  p = array(NA, coefficients)
+  
+  for (i in 1:coefficients){
+    coef[i] = a$coefficients$cond[1+i,1]
+    std[i] = a$coefficients$cond[1+i,2]
+    stat[i] = a$coefficients$cond[1+i,3]
+    p[i] = a$coefficients$cond[1+i,4]
+  }
+  return(list(beta = round(coef,round),std = round(std,round),stat = round(stat,round),p = p))
+  
+}
+
+
+
+
+
+
+
+
+
+
+
+# first colours
+blue <- brewer.pal(8, "Blues")
+grey <- brewer.pal(8, "Greys")
+purp <- brewer.pal(8, "Purples")
+oran <- brewer.pal(8, "Oranges")
+gren <- brewer.pal(8, "Greens")
+
+
+
+
+prep_data = function(file){
+  
+  if (file.exists(file)){
+    df_res <- read.csv(file)
+  } else {
+    print('Data file does not exist, check data is in current directory. 
+          If not, run tgi-compiler.Rmd')
+  }
+  # Calculate median burning rating for all participants
+  # TGI trials only
+  # Then flag how many are not sig > 0
+  df_med <- aggregate(VASburn~ID*manipulation*cold_probe*trial_type, median, data = df_res)
+  tgi <-  df_med %>% 
+    filter(manipulation == 'TGI')
+  cnt <-  df_med %>% 
+    filter(manipulation == 'CNT')
+  
[…]

### 2023-07-10 Manuscript.Rmd
pdf

@@
 output:
-  html_document: default
   pdf_document:
     latex_engine: xelatex
+  html_document: default
   word_document:

### 2023-07-10 scripts/utility.R

@@ -156,7 +156,7 @@ prep_data = function(file){
   
   
   #Hypothesis 2 a & b: relative location of warm and cold
-
+  
   # Change name of manipulation
   vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
   h2_sum <- aggregate(VAS~quality*manipulation*cold_probe, median, data = vas_meds)
@@ -220,10 +220,10 @@ prep_data = function(file){
 }
 
 
-make_plot1 = function(vas_h1_diff,h1_diff_sum){
+make_plot1 = function(vas_h1_diff,h1_diff_sum, exp){
   
   # now plot the difference
-  h1_diff_plot_exp1 = ggplot(data = vas_h1_diff, aes(colour = quality)) +
+  plot = ggplot(data = vas_h1_diff, aes(colour = quality)) +
     geom_hline(yintercept = 0, colour = 'grey50') +
     geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
                alpha = .5) +
@@ -231,18 +231,19 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum){
                fill = 'grey15',
                shape = 21, size = 3) +
     geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
-                                               ymax = difference+ci), 
+                                          ymax = difference+ci), 
                   width = .1, size = .7, colour = 'grey15') +
     facet_wrap(~quality) +
     scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-    labs(title = 'Experiment 1',
+    labs(title = paste0('Experiment ',exp),
          y = 'Within - Across VAS Ratings', x = NULL) +
     theme_classic() +
     theme(legend.position = 'none')+coord_cartesian(ylim = c(-30,30)) 
   
-  return(h1_diff_plot_exp1)
+  return(plot)
   
 }
+
 
 plot1 = function(){
   
@@ -253,18 +254,22 @@ plot1 = function(){
   h1_diff_sum_exp1 = experiment1$h1_diff_sum
   
   
-  h1_diff_plot_exp1 = make_plot1(vas_h1_diff_exp1,h1_diff_sum_exp1)
-
[…]

### 2023-07-12 Manuscript.Rmd
updates

--- 2023-07-10 Manuscript.Rmd
@@
                  modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
-                 rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork
+                 rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, cowplot
                  )
@@
 list2env(stats, envir=environment())
+
+#save.image("~/tgi-spinal/Workspace/stats.RData")
+
 ```
@@
 ```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1"}
+ggdraw() +
+    draw_image(magick::image_read(here::here("figures","figure1.PNG")), scale = 1)
+```
+
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2"}
 plot1()
@@
 3).
-Interestingly, we found no perceptual differences in TGI based on whether the cold stimulus was located proximally or distally (Exp.
-1: xxx, xxx; Exp.
-2: xxx, xxx).
-This result implies that the concept of distal inhibition may not apply when stimuli of different thermosensory qualities are presented.
-Alternatively, if it does apply, its effect size might be rather small, with limited impact on TGI perception.
-<!-- Revision this but is proabably Run individual models on within and across dermatomes for H2 -->
+Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp1_control$beta[2]`, `r make_pvalue(stats_within_cold_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_cold_exp1_control$beta[5]`, `r make_pvalue(stats_within_cold_exp1_control$p[5])`.
+No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp1_control$beta[2]`, `r make_pvalue(stats_within_warm_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_warm_exp1_control$beta[5]`, `r make_pvalue(stats_within_warm_exp1_control$p[5])`.
+significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
+(TGI: $\beta$ = `r stats_within_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp1_control$beta[2]`, `r make_pvalue(stats_within_burn_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_burn_exp1_control$beta[5]`, `r make_pvalue(stats_within_burn_exp1_control$p[5])`.
 
-```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Figure 2"}
+The second experiment showed similar results 
+Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp2_control$beta[2]`, `r make_pvalue(stats_within_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_cold_exp2_control$beta[5]`, `r make_pvalue(stats_within_cold_exp2_control$p[5])`.
+No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp2_control$beta[2]`, `r make_pvalue(stats_within_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_warm_exp2_control$beta[5]`, `r make_pvalue(stats_within_warm_exp2_control$p[5])`.
+significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
+(TGI: $\beta$ = `r stats_within_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp2_control$beta[2]`, `r make_pvalue(stats_within_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_burn_exp2_control$beta[5]`, `r make_pvalue(stats_within_burn_exp2_control$p[5])`.
+
+```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Figure 3"}
 plot2()
@@
 We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli.
+
+Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp1_control$beta[2]`, `r make_pvalue(stats_across_cold_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp1_control$beta[5]`, `r make_pvalue(stats_across_cold_exp1_control$p[5])`.
+No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_across_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp1_control$beta[2]`, `r make_pvalue(stats_across_warm_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp1_control$beta[5]`, `r make_pvalue(stats_across_warm_exp1_control$p[5])`.
+significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
+(TGI: $\beta$ = `r stats_across_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp1_control$beta[2]`, `r make_pvalue(stats_across_burn_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_burn_exp1_control$beta[5]`, `r make_pvalue(stats_across_burn_exp1_control$p[5])`.
+
+The second experiment showed similar results 
+Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp2_control$beta[2]`, `r make_pvalue(stats_across_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp2_control$beta[5]`, `r make_pvalue(stats_across_cold_exp2_control$p[5])`.
+No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_across_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp2_control$beta[2]`, `r make_pvalue(stats_across_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp2_control$beta[5]`, `r make_pvalue(stats_across_warm_exp2_control$p[5])`.
+significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
+(TGI: $\beta$ = `r stats_across_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp2_control$beta[2]`, `r make_pvalue(stats_across_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_burn_exp2_control$beta[5]`, `r make_pvalue(stats_across_burn_exp2_control$p[5])`.
+
 The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord, as depicted in Figure 3.
-Our data revealed a substantial decrease in the subjective experience of cold (Exp.
-1: estimate = xxx, p = xxx; Exp.
-2: estimate: xxx, p = xxx), coupled with a significant increase in the subjective sensations of warmth (Exp.
-1: estimate = xxx, p = xxx; Exp.
-2: estimate: xxx, p = xxx) and burning sensations (Exp.1: estimate: xxx, p = xxx; Exp.
-2 estimate: xxx, p = xxx) in response to TGI as compared to non-TGI stimuli.
 These findings were consistent across both experiments for thermosensory ratings, albeit with minor deviations that corresponded with the particular stimulation quality being assessed.
@@
 The study entailed two separate experiments, collectively involving 80 healthy volunteers.
-The sample consisted of xx females and xx males, mean age = XX years old (SD = x.xx, range = xx - xx) in Experiment 1, and xx females and xx males, mean age = XX years old (SD = x.xx, range = xx - xx), in Experiment 2.
+The sample consisted of `r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old (SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) in Experiment 1,
+
+and `r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary (Female at birth), mean age = `r descript_exp2_age$mean_age` years old (SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`), in Experiment 2.
 The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
@@
 The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.
-We carried out the statistical analyses using the 'glmmTMB' package in R (version x.xx), and statistical significance was set at p < .05.
-The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both Experiment 1 (add link) and Experiment 2 (add link).
-All data and code for the analysis are available in the github repository (xxx), ensuring the reproducibility of our findings.
+We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p < .05.
+The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [Experiment 1](https://osf.io/4xcn5/) and [Experiment 2](https://osf.io/dhg8u/).
+All data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript), ensuring the reproducibility of our findings.
 

### 2023-07-12 tgi-spinal_analysis-exp1.Rmd
updates

@@
 source(here::here("scripts","utility.R"))
+source(here::here("scripts","models.R"))
+
 ```
@@
 
-summary_stats(model.cold, 3,2)
+summary_stat(model.cold, 3,2)
 Anova(model.cold)

### 2023-07-12 scripts/models.R

@@ -1,14 +1,21 @@
 
 statistics = function(rerun){
+  #roudning
+  r = 2
+  
   
 if(rerun){
-  ######### Exp 1
+  
   
   experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
   experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
   
   df_long_exp1 = experiment1$df_long
   df_long_exp2 = experiment2$df_long
+  
+  
+  ######### Exp 1 (Hypothesis 1)
+  
   ## hypothsis 1
   # Cold
   model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
@@ -18,7 +25,7 @@ if(rerun){
                                 data = df_long_exp1 %>% filter(quality == 'cold'),
                                 na.action = na.omit) 
   
-  stats_model_cold_exp1 = summary_stat(model_cold_exp1, 2,2)
+  stats_model_cold_exp1 = summary_stat(model_cold_exp1, 2,r)
   
   # Warm
   model_warm_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
@@ -29,7 +36,7 @@ if(rerun){
                                 na.action = na.omit) 
   
   
-  stats_model_warm_exp1 = summary_stat(model_warm_exp1, 2,2)
+  stats_model_warm_exp1 = summary_stat(model_warm_exp1, 2,r)
   
   # Burn
   #The burning hypothesis is only for participants that experience burning TGI 
@@ -47,14 +54,143 @@ if(rerun){
                                 data = df_resp_exp1 %>% filter(quality == 'burn'),
                                 na.action = na.omit) 
   
-  stats_model_burn_exp1 = summary_stat(model_burn_exp1, 2,2)
+  stats_model_burn_exp1 = summary_stat(model_burn_exp1, 2,r)
   
+  
+  
+
+  ## hypothsis 2 (within)
+
+  within_exp1 <- df_long_exp1 %>% 
+    filter(condition == 'within')
+
+  
+  # within
+  
+  ### cold
+  
+  model_within_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + procedure + trial_n +
+                                   (1|ID),
+                                 family = glmmTMB::beta_family(),
+                                 ziformula = ~1+manipulation,
[…]

### 2023-07-12 scripts/utility.R

@@ -36,7 +36,7 @@ summary_stat = function(model, coefficients, round){
     stat[i] = a$coefficients$cond[1+i,3]
     p[i] = a$coefficients$cond[1+i,4]
   }
-  return(list(beta = round(coef,round),std = round(std,round),stat = round(stat,round),p = p))
+  return(list(beta = format(round(coef,round),nsmall = round),std = format(round(std,round),nsmall = round),stat = format(round(stat,round), nsmall = round),p = p))
   
 }
 

### 2023-07-12 Manuscript.Rmd
pdf_and_word

@@
 output:
-  html_document: default
+  word_document:
   pdf_document:
     latex_engine: xelatex
-  word_document:
+  html_document: default
 bibliography: knitting files/Citations.bib
@@
 
+\newpage
 # Results and discussion
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1"}
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Four experimental conditions depicting an exemplar cold and warm thermode placement within and across dermatomes.
+Within dermatomes, the relative location of the cold thermode was proximal or distal.
+Across dermatomes, the relative location of the corresponding spinal segments was rostral or caudal.
+"}
 ggdraw() +
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2"}
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = " Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
+Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
+Small dots are individual means, large dots are population means for each condition and error bars are 95% confidence intervals."}
 plot1()
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Figure 3"}
+```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the two dermatome conditions.
+The top panel shows the difference between proximal and distal cold afferent locations (within dermatomes) and the bottom panel shows the difference between rostral and caudal cold afferent locations, relative to warm, across stimulation type (Non-TGI, TGI) and VAS rating quality (cold, warm and burning).
+Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
 plot2()
@@
 
+\newpage
+
 # Methods
@@
 The study entailed two separate experiments, collectively involving 80 healthy volunteers.
-The sample consisted of `r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old (SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) in Experiment 1,
-
-and `r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary (Female at birth), mean age = `r descript_exp2_age$mean_age` years old (SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`), in Experiment 2.
+The sample consisted of `r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old (SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) in Experiment 1, and `r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary (Female at birth), mean age = `r descript_exp2_age$mean_age` years old (SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`), in Experiment 2.
 The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
@@
 
+\newpage
+
 # Authors contributions
@@
 We would like to thank XXX for their help with participant recruitment and data collection. This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948788).
+
+\newpage
+
+# References
+
+::: {#refs}
+:::

### 2023-07-12 Manuscript.Rmd
fix_refs

@@
   word_document:
+  html_document: default
   pdf_document:
     latex_engine: xelatex
-  html_document: default
 bibliography: knitting files/Citations.bib
@@
 The complexities of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) enhanced heat and burning sensations when cold-warm thermosensory integration takes place more focally within the spinal cord, and (2) discernible directional inter-segmental effects when distinct cold and warm stimuli elicited broader activity along the spinal cord.
-Small primary afferents, responsible for mediating temperature and pain sensations, split into ascending and descending branches that cover one to two segments before they enter the dorsal horn [@kerr_neuroanatomical_1975; @lamotte_distribution_1977).
+Small primary afferents, responsible for mediating temperature and pain sensations, split into ascending and descending branches that cover one to two segments before they enter the dorsal horn [@kerr_neuroanatomical_1975; @lamotte_distribution_1977].
 This pattern forms the Lissauer's tract, a structure hypothesised to regulate sensory transmission to the dorsal horn and influence spinal receptive field size [@wall_brief_1999].
@@
 
-Evidence from animal studies shows that propriospinal neurons, confined within the spinal cord, exhibit bidirectional collateral branches along the rostrocaudal plane [@saywell_electrophysiological_2011; @skinner_ascending_1989).
+Evidence from animal studies shows that propriospinal neurons, confined within the spinal cord, exhibit bidirectional collateral branches along the rostrocaudal plane [@saywell_electrophysiological_2011; @skinner_ascending_1989].
 These connections shape the network of interneurons that modulates sensory information delivered to the dorsal horn [@todd_neuronal_2010; @peirs_neural_2016].
@@
 These circuits, created by propriospinal neurons, may promote sensory integration within a spinal receptive field while simultaneously inhibiting activity in adjacent fields.
-This mechanism aligns with the concept of lateral inhibition, a ubiquitous process in sensory processing seen across both the peripheral and central nervous systems, and multiple sensory modalities, including thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021).
+This mechanism aligns with the concept of lateral inhibition, a ubiquitous process in sensory processing seen across both the peripheral and central nervous systems, and multiple sensory modalities, including thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021].
 Further, our observation that spatial factors, such as the more caudal localisation of cold activity relative to warm activity in the spinal cord, influences TGI perception, suggests possible neuroanatomical and functional asymmetries.
@@
 # Authors contributions
-Author contributions listed alphabetically according to CRediT taxonomy (https://credit.niso.org):
+Author contributions listed alphabetically according to [CRediT taxonomy](https://credit.niso.org):
 Conceptualization: DEC, JFE, FF, PH, AGM.

### 2023-07-12 Manuscript.Rmd
updates

@@
 
-The second experiment showed similar results 
-Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp2_control$beta[2]`, `r make_pvalue(stats_within_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_cold_exp2_control$beta[5]`, `r make_pvalue(stats_within_cold_exp2_control$p[5])`.
+The second experiment showed no difference that the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp2_control$beta[2]`, `r make_pvalue(stats_within_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_cold_exp2_control$beta[5]`, `r make_pvalue(stats_within_cold_exp2_control$p[5])`.
 No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp2_control$beta[2]`, `r make_pvalue(stats_within_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_warm_exp2_control$beta[5]`, `r make_pvalue(stats_within_warm_exp2_control$p[5])`.
-significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
+No significant differences was also found for the burning ratings for both TGI and control.
 (TGI: $\beta$ = `r stats_within_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp2_control$beta[2]`, `r make_pvalue(stats_within_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_burn_exp2_control$beta[5]`, `r make_pvalue(stats_within_burn_exp2_control$p[5])`.
@@
 
-Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp1_control$beta[2]`, `r make_pvalue(stats_across_cold_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp1_control$beta[5]`, `r make_pvalue(stats_across_cold_exp1_control$p[5])`.
-No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_across_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp1_control$beta[2]`, `r make_pvalue(stats_across_warm_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp1_control$beta[5]`, `r make_pvalue(stats_across_warm_exp1_control$p[5])`.
-significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
-(TGI: $\beta$ = `r stats_across_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp1_control$beta[2]`, `r make_pvalue(stats_across_burn_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_burn_exp1_control$beta[5]`, `r make_pvalue(stats_across_burn_exp1_control$p[5])`.
+Firstly the cold intensity was more when the cold probe was located more rostrally for both control and TGI trials  (TGI: $\beta$ = `r stats_across_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp1_control$beta[2]`, `r make_pvalue(stats_across_cold_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp1_control$beta[5]`, `r make_pvalue(stats_across_cold_exp1_control$p[5])`.
+A significant reduction in warm intensity was found for TGI trials, but not for the control trials (TGI: $\beta$ = `r stats_across_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp1_control$beta[2]`, `r make_pvalue(stats_across_warm_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp1_control$beta[5]`, `r make_pvalue(stats_across_warm_exp1_control$p[5])`.
+No significant differences was found for the burning ratings.(TGI: $\beta$ = `r stats_across_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp1_control$beta[2]`, `r make_pvalue(stats_across_burn_exp1_control$p[2])`) with no significant interaction between them  ($\beta$ = `r stats_across_burn_exp1_control$beta[5]`, `r make_pvalue(stats_across_burn_exp1_control$p[5])`).
 
-The second experiment showed similar results 
-Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp2_control$beta[2]`, `r make_pvalue(stats_across_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp2_control$beta[5]`, `r make_pvalue(stats_across_cold_exp2_control$p[5])`.
-No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_across_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp2_control$beta[2]`, `r make_pvalue(stats_across_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp2_control$beta[5]`, `r make_pvalue(stats_across_warm_exp2_control$p[5])`.
-significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
-(TGI: $\beta$ = `r stats_across_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp2_control$beta[2]`, `r make_pvalue(stats_across_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_burn_exp2_control$beta[5]`, `r make_pvalue(stats_across_burn_exp2_control$p[5])`.
+The second experiment showed that the cold intensity was more when the cold probe was located more rostrally for TGI trials, but not control trials.
+(TGI: $\beta$ = `r stats_across_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp2_control$beta[2]`, `r make_pvalue(stats_across_cold_exp2_control$p[2])`) with a significant interaction between them  $\beta$ = `r stats_across_cold_exp2_control$beta[5]`, `r make_pvalue(stats_across_cold_exp2_control$p[5])`.
+A significant difference in intensity was found for the warm ratings indicating that when the cold probe was located more rostrally the intensity was lower (TGI: $\beta$ = `r stats_across_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp2_control$beta[2]`, `r make_pvalue(stats_across_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp2_control$beta[5]`, `r make_pvalue(stats_across_warm_exp2_control$p[5])`.
+A significant differences was also found for the burning ratings in the control condition, but not in the TGI condition, indicating more distally located cold probe decreased ratings in the control condition.
+(TGI: $\beta$ = `r stats_across_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp2_control$beta[2]`, `r make_pvalue(stats_across_burn_exp2_control$p[2])`) with no significant interaction between them  ($\beta$ = `r stats_across_burn_exp2_control$beta[5]`, `r make_pvalue(stats_across_burn_exp2_control$p[5])`).
 
@@
 Author contributions listed alphabetically according to [CRediT taxonomy](https://credit.niso.org):
-Conceptualization: DEC, JFE, FF, PH, AGM.
-Data curation: JEF, AGM.
-Formal analysis: JFE, FF, AGM.
-Funding acquisition: FF.
-Investigation: DEC, JFE, AGM.
-Methodology: DEC, JFE, FF, AGM, AVS.
-Project administration: FF, AGM.
-Resources: FF, AGM.
-Software: JFE, FF, AGM.
-Supervision: FF, AGM.
-Visualization: FF, AGM.
-Writing – original draft: FF, AGM.
-Writing – review & editing: FF, AGM. (+ others who will provide feedback)
+
+-   Conceptualization: DEC, JFE, FF, PH, AGM.
+-   Data curation: JEF, AGM.
+-   Formal analysis: JFE, FF, AGM.
+-   Funding acquisition: FF.
+-   Investigation: DEC, JFE, AGM.
+-   Methodology: DEC, JFE, FF, AGM, AVS.
+-   Project administration: FF, AGM.
+-   Resources: FF, AGM.
+-   Software: JFE, FF, AGM.
+-   Supervision: FF, AGM.
+-   Visualization: FF, AGM.
+-   Writing – original draft: FF, AGM.
+-   Writing – review & editing: FF, AGM. (+ others who will provide feedback)
 

### 2023-07-13 Manuscript.Rmd
updates

@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the two dermatome conditions.
+```{r, results="hide", fig.width = 15, fig.height = 15, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the two dermatome conditions.
 The top panel shows the difference between proximal and distal cold afferent locations (within dermatomes) and the bottom panel shows the difference between rostral and caudal cold afferent locations, relative to warm, across stimulation type (Non-TGI, TGI) and VAS rating quality (cold, warm and burning).

### 2023-07-13 scripts/models.R

@@ -75,7 +75,7 @@ if(rerun){
                                  ziformula = ~1+manipulation,
                                  data = within_exp1 %>% filter(quality == 'cold'),
                                  na.action = na.omit) 
-
+  
   
   stats_within_cold_exp1_control = summary_stat(model_within_cold_exp1,5,r)
   

### 2023-07-14 Manuscript.Rmd
updates

@@
 author: 
-  - name : "**Jesper Fischer Ehmsen**"
-    affiliation: "1"
+  - name : "Alexandra G. Mitchell"
+    affiliation : "1"
+  - name : "Jesper Fischer Ehmsen"
+    affiliation : "1"
   - name : "Daniel Elmstrom Christensen"
-    affliation : "2"
-affliation:
+    affiliation : "2"
+  - name : "Anna Villaume Stuckert"
+    affiliation : "3"
+  - name : "Patrick Haggard"
+    affiliation : "4"  
+  - name : "Francesca Fardo"
+    affiliation : "1"
 
+affiliation:
   - id : "1"
@@
 always_allow_html: yes
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 Participants were asked to rate their perceptions of cold, warm, and burning sensations in response to TGI and control stimuli.
-Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the TGI that may illuminate processes underlying thermosensory integration in the spinal cord.
+Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the illusion that may illuminate processes underlying thermosensory integration in the spinal cord.
 Our findings revealed that both thermosensory and painful components of TGI perception were modulated similarly, with enhanced warm and burning ratings observed when cold and warm stimuli were confined within the same dermatome.
-Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but a notable enhancement of the TGI effect when the cold stimulus was associated with a more caudal segmental location along the spinal cord compared to the warm stimulus.
+Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but a notable heat enhancement when the cold stimulus was associated with a more caudal segmental location compared to the warm stimulus.
 These results provide insights into the organisation of the spinal cord in relation to the thermosensory integration and generation of the TGI.
@@
 Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors.
-The generation of this illusion is thus attributed to central nervous system mechanisms [@fardo_beyond_2020].
+The generation of this illusion is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020].
 Recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
-However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008, @fardo_beyond_2020].
+However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.
+
+The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008, @fardo_beyond_2020].
 The illusion of heat, also known as synthetic heat [@fruhstorfer_significance_2003; @green_localization_1977; -@green_synthetic_2002; -@green_temperature_2004], refers to non-painful sensations evoked by the thermal grill [@defrin_spatial_2008; @kern_pharmacological_2008; -@kern_effects_2008; @bouhassira_investigation_2005; @adam_relationships_2014].
@@
 Historically, the thermosensory and painful components of the TGI were explained by distinct spinal and supraspinal mechanisms, respectively.
-The enhanced perception of heat in TGI was explained by a spinal inhibitory mechanism, drawing from observations in an animal model where simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone
-[@craig_thermal_1994].
+The enhanced perception of heat in TGI was explained by a spinal inhibitory mechanism, drawing from observations in an animal model where simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone [@craig_thermal_1994].
 Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following a thalamic lesion [@craig_thermal_1994; -@bud_craig_new_1998].
+
 Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
@@
 These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain within the TGI.
+
 In this paper our objective was twofold.
 Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes.
-Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and burning components.
+Cold and warm stimuli were presented at a fixed distance on the skin, but depending on their longitudinal or tangential orientation on the arm, they elicited neural activity in a differing number of spinal segments.
+Our assumption was that cold and warm-related neural activity in the spinal cord was more focal, when the stimuli were presented within the same dermatome, while more widespread, when the stimuli mapped on spinal segments that were further apart.
+Our past work using a similar dermatome manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and burning components.
 Here, to probe possible distinctions between the two qualitative components of the TGI, we measured subjective indices of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations.
@@
 \newpage
+
 # Results and discussion
+
 The Thermal Grill Illusion (TGI) is characterised by two key phenomena: thermosensory enhancement and illusory pain.
-Thermosensory enhancement refers to an amplified perception of heat or cold when cold and warm stimuli are simultaneously applied, as opposed to when each stimulus is presented individually or paired with a neutral temperature.
+Thermosensory enhancement refers to an amplified perception of heat or cold, when cold and warm stimuli are simultaneously applied, as opposed to when each stimulus is presented individually or paired with a neutral temperature.
 Notably, the majority of individuals experience an intensification of heat rather than cold [@fardo_beyond_2020].
@@
 All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments.
-In doing so, the stimuli elicited cold-related and warm-related neural activity that was either more focal or more widespread along the spinal cord.
 For each stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of a sensation, to 100, indicating an extreme sensation.
 For each instance of stimulation, participants were guided to focus their reporting on the sensations originating from a specific thermode.
-While the participants were unaware, this location corresponded to either the colder stimulus (Exp.
-1) or the warmer stimulus (Exp.
-2) of the paired temperatures.
+While the participants were unaware, this location corresponded to either the colder stimulus (Exp. 1) or the warmer stimulus (Exp. 2) of the paired temperatures.
 VAS ratings were analysed using zero-inflated beta regressions.
@@
 ## Thermosensory and burning components of TGI perception are spinally mediated
+
 ```{r, warning = F, message = F, echo = F,include=FALSE}
@@
 2).
-Participants reported a significantly reduced subjective experience of cold (Exp.
-1: $\beta$ = `r stats_model_cold_exp1$beta[2]`, `r make_pvalue(stats_model_cold_exp1$p[2])`; Exp.
-2: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`), alongside a markedly enhanced subjective experience of warmth (Exp.
-1: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`; Exp.
-2: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`) for TGI compared to non-TGI stimuli.
-In addition, a heightened burning sensation was reported in our second experiment (Exp.1: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`; Exp.
-2 $\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2])`) for TGI compared to non-TGI stimuli.
-These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
-These findings are consistent with previous results on the modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation  [@harper_conditioned_2017].
+When rating the cold thermode (Exp.
+1), participants reported a significantly reduced subjective experience of cold ($\beta$ = `r stats_model_cold_exp1$beta[2]`, `r make_pvalue(stats_model_cold_exp1$p[2])`), alongside a markedly enhanced subjective experience of warmth ($\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`) for TGI stimuli applied within a dermatome compared to across dermatomes.
+Burning sensations were enhanced for TGI compared to non-TGI stimuli, but the modulation of the burning ratings by the dermatome condition did not cross the significance threshold ($\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
+In contrast, when rating the warm thermode (Exp.
+2), participants reported markedly enhanced burning sensations for TGI stimuli applied within a dermatome compared to across dermatomes ($\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2])`).
+However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) and warm ($\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`) thermosensory ratings as in the first experiment.
+
+The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
+This interpretation is consistent with a previous study using a similar dermatome manipulation, but a distinct method to quantify TGI perception [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
 All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI.
@@
 ## Undetected proximodistal bias in TGI
+
 Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two warm stimuli presented on the forearm [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
-In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig.
-3).
+In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3).
 Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp1_control$beta[2]`, `r make_pvalue(stats_within_cold_exp1_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_cold_exp1_control$beta[5]`, `r make_pvalue(stats_within_cold_exp1_control$p[5])`.
@@
 ## Directional effects in inter-segmental sensory integration
+
 A main objective of this study was assessing spatial order effects along the rostrocaudal axis at the spinal level.
@@
 These findings were consistent across both experiments for thermosensory ratings, albeit with minor deviations that corresponded with the particular stimulation quality being assessed.
-The observed enhancement of warmth perception in Experiment 2 could be ascribed to the participants’ assessment of the warmer thermode as opposed to the colder one of Experiment 1.
+The observed enhancement of warmth perception in Experiment 2 could be ascribed to the participants' assessment of the warmer thermode as opposed to the colder one of Experiment 1.
 For burning ratings, significant results were seen in Experiment 2, but not in Experiment 1.
@@
 ## Spinal organisation and TGI perception
+
 The complexities of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) enhanced heat and burning sensations when cold-warm thermosensory integration takes place more focally within the spinal cord, and (2) discernible directional inter-segmental effects when distinct cold and warm stimuli elicited broader activity along the spinal cord.
@@
 # Conclusion
+
 Illusions in the thermo-nociceptive system can be leveraged to improve our understanding of mechanisms contributing to pain perception.
@@
 ## Participants
+
 The study entailed two separate experiments, collectively involving 80 healthy volunteers.
@@
 ## Stimuli and procedure
+
 All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3 software (version 5.4b).
@@
 For pain threshold measurements and TGI calibration, we positioned the probes within a single dermatome.
-To address our experimental questions, we presented the calibrated TGI stimuli, as well as cold-neutral (Exp.
-1) or warm-neutral (Exp.
-2) non-TGI stimuli using two thermodes.
+To address our experimental questions, we presented the calibrated TGI stimuli, as well as cold-neutral (Exp. 1) or warm-neutral (Exp. 2) non-TGI stimuli using two thermodes.
 In non-TGI stimuli the cold or warm temperatures were set to match the temperature used for TGI stimulation, but paired with a neutral temperature set at 30ºC.
-The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant’s forearm size.
-The positioning of the thermodes was either within the same dermatome (i.e., C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e.
-C6 - T1).
+The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant's forearm size.
+The positioning of the thermodes was either within the same dermatome (i.e., C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1).
 Further, we manipulated the spatial arrangement of the temperature pairs, by systematically presenting an equal number of trials where the cold thermode was applied on a proximal or distal location within a dermatome, or was applied on a dermatome that mapped onto a rostral or caudal segment along the spinal cord.
@@
 caudal) were pseudo-randomised and counterbalanced between participants.
-During each trial, the experimenter positioned two thermodes, mounted on a stand using two independent clamps, on the participant’s skin for 10 seconds.
-An auditory cue (300Hz, 100ms) indicated the end of the stimulation period, after which the experimenter removed the thermodes from the participant’s skin.
+During each trial, the experimenter positioned two thermodes, mounted on a stand using two independent clamps, on the participant's skin for 10 seconds.
+An auditory cue (300Hz, 100ms) indicated the end of the stimulation period, after which the experimenter removed the thermodes from the participant's skin.
 Participants then rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales.
@@
 The order of the three VAS scales was randomised across trials.
-For each scale,  participants provided their responses using the arrow keys on a keyboard and rated the intensity of their sensations from a specific location (labeled ‘A’ or ‘B’), based on the experimenter’s instruction.
-Unbeknown to the participant, this location systematically corresponded to either the colder temperature (Exp.
-1) or the warmer temperature (Exp.
-2).
+For each scale, participants provided their responses using the arrow keys on a keyboard and rated the intensity of their sensations from a specific location (labeled 'A' or 'B'), based on the experimenter's instruction.
+Unbeknown to the participant, this location systematically corresponded to either the colder temperature (Exp. 1) or the warmer temperature (Exp. 2).
 Participants had max 8 seconds to provide each rating, and if they did not complete a rating within the allowed timeframe, the trial was repeated.
@@
 ## Sample size
+
 An initial pilot study informed the pre-registered calculation of the sample size.
@@
 ## Data analyses
+
 We re-scaled data from cold, warm and burning VAS ratings from their original values to a range of 0 to 1.
@@
 The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.
-We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p < .05.
+We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
 The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [Experiment 1](https://osf.io/4xcn5/) and [Experiment 2](https://osf.io/dhg8u/).
@@
 # Authors contributions
+
 Author contributions listed alphabetically according to [CRediT taxonomy](https://credit.niso.org):
@@
 -   Visualization: FF, AGM.
--   Writing – original draft: FF, AGM.
--   Writing – review & editing: FF, AGM. (+ others who will provide feedback)
+-   Writing -- original draft: FF, AGM.
+-   Writing -- review & editing: FF, AGM. (+ others who will provide feedback)
 
 # Acknowledgements
-We would like to thank XXX for their help with participant recruitment and data collection. This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948788).
+
+We would like to thank XXX for their help with participant recruitment and data collection.
+This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948788).
 

### 2023-07-14 Manuscript.Rmd
updates

@@
 author: 
-  - name : "Alexandra G. Mitchell"
-    affiliation : "1"
-  - name : "Jesper Fischer Ehmsen"
-    affiliation : "1"
+  - name : "**Jesper Fischer Ehmsen**"
+    affiliation: "1"
   - name : "Daniel Elmstrom Christensen"
-    affiliation : "2"
-  - name : "Anna Villaume Stuckert"
-    affiliation : "3"
-  - name : "Patrick Haggard"
-    affiliation : "4"  
-  - name : "Francesca Fardo"
-    affiliation : "1"
+    affliation : "2"
+affliation:
 
-affiliation:
   - id : "1"
@@
 output:
-  word_document:
-  html_document: default
   pdf_document:
     latex_engine: xelatex
+  html_document: default
+  word_document:
 bibliography: knitting files/Citations.bib
@@
 Participants were asked to rate their perceptions of cold, warm, and burning sensations in response to TGI and control stimuli.
-Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the illusion that may illuminate processes underlying thermosensory integration in the spinal cord.
+Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the TGI that may illuminate processes underlying thermosensory integration in the spinal cord.
 Our findings revealed that both thermosensory and painful components of TGI perception were modulated similarly, with enhanced warm and burning ratings observed when cold and warm stimuli were confined within the same dermatome.
-Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but a notable heat enhancement when the cold stimulus was associated with a more caudal segmental location compared to the warm stimulus.
+Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but a notable enhancement of the TGI effect when the cold stimulus was associated with a more caudal segmental location along the spinal cord compared to the warm stimulus.
 These results provide insights into the organisation of the spinal cord in relation to the thermosensory integration and generation of the TGI.
@@
 Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors.
-The generation of this illusion is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020].
+The generation of this illusion is thus attributed to central nervous system mechanisms [@fardo_beyond_2020].
 Recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
-However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.
-
-The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008, @fardo_beyond_2020].
+However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008, @fardo_beyond_2020].
 The illusion of heat, also known as synthetic heat [@fruhstorfer_significance_2003; @green_localization_1977; -@green_synthetic_2002; -@green_temperature_2004], refers to non-painful sensations evoked by the thermal grill [@defrin_spatial_2008; @kern_pharmacological_2008; -@kern_effects_2008; @bouhassira_investigation_2005; @adam_relationships_2014].
@@
 Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following a thalamic lesion [@craig_thermal_1994; -@bud_craig_new_1998].
-
 Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
@@
 These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain within the TGI.
-
 In this paper our objective was twofold.
 Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes.
-Cold and warm stimuli were presented at a fixed distance on the skin, but depending on their longitudinal or tangential orientation on the arm, they elicited neural activity in a differing number of spinal segments.
-Our assumption was that cold and warm-related neural activity in the spinal cord was more focal, when the stimuli were presented within the same dermatome, while more widespread, when the stimuli mapped on spinal segments that were further apart.
-Our past work using a similar dermatome manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and burning components.
+Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and burning components.
 Here, to probe possible distinctions between the two qualitative components of the TGI, we measured subjective indices of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations.
@@
 The Thermal Grill Illusion (TGI) is characterised by two key phenomena: thermosensory enhancement and illusory pain.
-Thermosensory enhancement refers to an amplified perception of heat or cold, when cold and warm stimuli are simultaneously applied, as opposed to when each stimulus is presented individually or paired with a neutral temperature.
+Thermosensory enhancement refers to an amplified perception of heat or cold when cold and warm stimuli are simultaneously applied, as opposed to when each stimulus is presented individually or paired with a neutral temperature.
 Notably, the majority of individuals experience an intensification of heat rather than cold [@fardo_beyond_2020].
@@
 All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments.
+In doing so, the stimuli elicited cold-related and warm-related neural activity that was either more focal or more widespread along the spinal cord.
 For each stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of a sensation, to 100, indicating an extreme sensation.
@@
 source(here::here("scripts","utility.R"))
+source(here::here("scripts","plots.R"))
 
@@
 2).
-When rating the cold thermode (Exp.
-1), participants reported a significantly reduced subjective experience of cold ($\beta$ = `r stats_model_cold_exp1$beta[2]`, `r make_pvalue(stats_model_cold_exp1$p[2])`), alongside a markedly enhanced subjective experience of warmth ($\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`) for TGI stimuli applied within a dermatome compared to across dermatomes.
-Burning sensations were enhanced for TGI compared to non-TGI stimuli, but the modulation of the burning ratings by the dermatome condition did not cross the significance threshold ($\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
-In contrast, when rating the warm thermode (Exp.
-2), participants reported markedly enhanced burning sensations for TGI stimuli applied within a dermatome compared to across dermatomes ($\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2])`).
-However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) and warm ($\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`) thermosensory ratings as in the first experiment.
-
-The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
-This interpretation is consistent with a previous study using a similar dermatome manipulation, but a distinct method to quantify TGI perception [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
+We investigated this difference in subjective cold / warm and burning ratings with a two by two interaction of manipulation (control / TGI) and dermatome (within / across).
+Results showed that participants reported a stronger reduced experience of cold, when the stimulus was presented within determatomes compared to across in the TGI condition compared to the control condition when the reference thermode was cold (experiment 1), but not when the reference thermode was warm (experiment 2)
+(Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`)
+The percept of warm showed no siginifcant interaction with either thermode as reference (Exp.
+1: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; Exp.
+2: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`)
+The percept of burning showed no statistical significant interaction with the reference being cold, but a strong interaction when the reference thermode was warm
+(Exp.1: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; Exp. 2 $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`)
+These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
+These findings are consistent with previous results on the modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
 All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI.
@@
 In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3).
-Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp1_control$beta[2]`, `r make_pvalue(stats_within_cold_exp1_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_cold_exp1_control$beta[5]`, `r make_pvalue(stats_within_cold_exp1_control$p[5])`.
-No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp1_control$beta[2]`, `r make_pvalue(stats_within_warm_exp1_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_warm_exp1_control$beta[5]`, `r make_pvalue(stats_within_warm_exp1_control$p[5])`.
-significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings.
-(TGI: $\beta$ = `r stats_within_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp1_control$beta[2]`, `r make_pvalue(stats_within_burn_exp1_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_burn_exp1_control$beta[5]`, `r make_pvalue(stats_within_burn_exp1_control$p[5])`.
+We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal)
+Results showed no statistical significant interaction effect for the cold ratings in both experiments:
+(Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`)
+Neither a statistically significant effect for warm watings
+(Exp1: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`) 
+and also not for burning ratings
+(Exp1: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`)
 
-The second experiment showed no difference that the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp2_control$beta[2]`, `r make_pvalue(stats_within_cold_exp2_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_cold_exp2_control$beta[5]`, `r make_pvalue(stats_within_cold_exp2_control$p[5])`.
-No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp2_control$beta[2]`, `r make_pvalue(stats_within_warm_exp2_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_warm_exp2_control$beta[5]`, `r make_pvalue(stats_within_warm_exp2_control$p[5])`.
-No significant differences was also found for the burning ratings for both TGI and control.
-(TGI: $\beta$ = `r stats_within_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp2_control$beta[2]`, `r make_pvalue(stats_within_burn_exp2_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_within_burn_exp2_control$beta[5]`, `r make_pvalue(stats_within_burn_exp2_control$p[5])`.
-
-```{r, results="hide", fig.width = 15, fig.height = 15, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the two dermatome conditions.
+```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the two dermatome conditions.
 The top panel shows the difference between proximal and distal cold afferent locations (within dermatomes) and the bottom panel shows the difference between rostral and caudal cold afferent locations, relative to warm, across stimulation type (Non-TGI, TGI) and VAS rating quality (cold, warm and burning).
@@
 We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli.
-
-Firstly the cold intensity was more when the cold probe was located more rostrally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp1_control$beta[2]`, `r make_pvalue(stats_across_cold_exp1_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_across_cold_exp1_control$beta[5]`, `r make_pvalue(stats_across_cold_exp1_control$p[5])`.
-A significant reduction in warm intensity was found for TGI trials, but not for the control trials (TGI: $\beta$ = `r stats_across_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp1_control$beta[2]`, `r make_pvalue(stats_across_warm_exp1_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_across_warm_exp1_control$beta[5]`, `r make_pvalue(stats_across_warm_exp1_control$p[5])`.
-No significant differences was found for the burning ratings.(TGI: $\beta$ = `r stats_across_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp1_control$beta[2]`, `r make_pvalue(stats_across_burn_exp1_control$p[2])`) with no significant interaction between them ($\beta$ = `r stats_across_burn_exp1_control$beta[5]`, `r make_pvalue(stats_across_burn_exp1_control$p[5])`).
-
-The second experiment showed that the cold intensity was more when the cold probe was located more rostrally for TGI trials, but not control trials.
-(TGI: $\beta$ = `r stats_across_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp2_control$beta[2]`, `r make_pvalue(stats_across_cold_exp2_control$p[2])`) with a significant interaction between them $\beta$ = `r stats_across_cold_exp2_control$beta[5]`, `r make_pvalue(stats_across_cold_exp2_control$p[5])`.
-A significant difference in intensity was found for the warm ratings indicating that when the cold probe was located more rostrally the intensity was lower (TGI: $\beta$ = `r stats_across_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp2_control$beta[2]`, `r make_pvalue(stats_across_warm_exp2_control$p[2])`) with no significant interaction between them $\beta$ = `r stats_across_warm_exp2_control$beta[5]`, `r make_pvalue(stats_across_warm_exp2_control$p[5])`.
-A significant differences was also found for the burning ratings in the control condition, but not in the TGI condition, indicating more distally located cold probe decreased ratings in the control condition.
-(TGI: $\beta$ = `r stats_across_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp2_control$beta[2]`, `r make_pvalue(stats_across_burn_exp2_control$p[2])`) with no significant interaction between them ($\beta$ = `r stats_across_burn_exp2_control$beta[5]`, `r make_pvalue(stats_across_burn_exp2_control$p[5])`).
+Like the previous analysis we investigated this relationship with a two way interaction here with the rostral - caudal axis being investigated.
+Results showed no statistical significant interaction effect for the cold ratings in the first experiment, but a statistically significant interaction when the reference thermode was warm:
+(Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
+No statistically significant effect for warm watings
+(Exp1: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`) 
+and also not for burning ratings
+(Exp1: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`)
 

### 2023-07-14 scripts/models.R

@@ -10,33 +10,57 @@ if(rerun){
   experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
   experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
   
-  df_long_exp1 = experiment1$df_long
-  df_long_exp2 = experiment2$df_long
+  df_long_exp1 = experiment1$df_long %>% mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
+  df_long_exp2 = experiment2$df_long %>% mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
+  
+  
+  ## Define constrats such that we both get within / across (i.e. distal & proximal vs rostral & caudual)
+  levels(df_long_exp1$cold_probe)
+  # "caudal"   "distal"   "proximal" "rostral" 
+  
+  #within - across
+  within_across = c(-1/2,1/2,1/2,-1/2)
+  #caudal - rostral
+  caudal_rostral = c(1,0,0,-1)
+  #distral - proximal
+  distal_proximal = c(0,1,-1,0)
+  
+  #define the matrix
+  cold = rbind(1/4,within_across,caudal_rostral,distal_proximal)
+  
+  #solve it 
+  cold = solve(cold)
+  
+  #remove the constant
+  cold = cold[,-1]
   
   
   ######### Exp 1 (Hypothesis 1)
   
   ## hypothsis 1
   # Cold
-  model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
+  model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + trial_n +
                                   (1|ID) + (1|order),
                                 family = glmmTMB::beta_family(),
                                 ziformula = ~1+manipulation,
                                 data = df_long_exp1 %>% filter(quality == 'cold'),
-                                na.action = na.omit) 
-  
-  stats_model_cold_exp1 = summary_stat(model_cold_exp1, 2,r)
+                                na.action = na.omit,
+                                contrasts=list(cold_probe = cold) 
+                                ) 
+  stats_model_cold_exp1 = summary_stat(model_cold_exp1, 8,r)
   
   # Warm
-  model_warm_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
+  model_warm_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe +
[…]

### 2023-07-14 scripts/plots.R

@@ -1,0 +1,135 @@
+
+make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
+  
+  # now plot the difference
+  plot = ggplot(data = vas_h1_diff, aes(colour = quality)) +
+    geom_hline(yintercept = 0, colour = 'grey50') +
+    geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
+               alpha = .5) +
+    geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
+               fill = 'grey15',
+               shape = 21, size = 3) +
+    geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
+                                          ymax = difference+ci), 
+                  width = .1, size = .7, colour = 'grey15') +
+    facet_wrap(~quality) +
+    scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
+    labs(title = paste0(title),
+         y = 'Within - Across VAS Ratings', x = NULL) +
+    theme_classic() +
+    theme(legend.position = 'none')+coord_cartesian(ylim = c(-30,30))+scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
+  
+  return(plot)
+  
+}
+
+
+plot1 = function(){
+  
+  # experiment 1 file
+  
+  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
+  vas_h1_diff_exp1 = experiment1$vas_h1_diff
+  h1_diff_sum_exp1 = experiment1$h1_diff_sum
+  
+  
+  h1_diff_plot_exp1 = make_plot1(vas_h1_diff = vas_h1_diff_exp1,
+                                 h1_diff_sum = h1_diff_sum_exp1,
+                                 title = "Reference: Cold Thermode")
+  
+  
+  # experiment 2 file
+  
+  experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
+  vas_h1_diff_exp2 = experiment2$vas_h1_diff
+  h1_diff_sum_exp2 = experiment2$h1_diff_sum
+  
+  h1_diff_plot_exp2 = make_plot1(vas_h1_diff = vas_h1_diff_exp2,
+                                 h1_diff_sum = h1_diff_sum_exp2,
+                                 title = "Reference: Warm Thermode")+
[…]

### 2023-07-14 scripts/utility.R

@@ -220,134 +220,3 @@ prep_data = function(file){
 }
 
 
-make_plot1 = function(vas_h1_diff,h1_diff_sum, exp){
-  
-  # now plot the difference
-  plot = ggplot(data = vas_h1_diff, aes(colour = quality)) +
-    geom_hline(yintercept = 0, colour = 'grey50') +
-    geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
-               alpha = .5) +
-    geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
-               fill = 'grey15',
-               shape = 21, size = 3) +
-    geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
-                                          ymax = difference+ci), 
-                  width = .1, size = .7, colour = 'grey15') +
-    facet_wrap(~quality) +
-    scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-    labs(title = paste0('Experiment ',exp),
-         y = 'Within - Across VAS Ratings', x = NULL) +
-    theme_classic() +
-    theme(legend.position = 'none')+coord_cartesian(ylim = c(-30,30)) 
-  
-  return(plot)
-  
-}
-
-
-plot1 = function(){
-  
-  # experiment 1 file
-  
-  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
-  vas_h1_diff_exp1 = experiment1$vas_h1_diff
-  h1_diff_sum_exp1 = experiment1$h1_diff_sum
-  
-  
-  h1_diff_plot_exp1 = make_plot1(vas_h1_diff = vas_h1_diff_exp1,
-                                 h1_diff_sum = h1_diff_sum_exp1,
-                                 exp = "1")
-  
-  
-  # experiment 2 file
-  
-  experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
-  vas_h1_diff_exp2 = experiment2$vas_h1_diff
-  h1_diff_sum_exp2 = experiment2$h1_diff_sum
-  
-  h1_diff_plot_exp2 = make_plot1(vas_h1_diff = vas_h1_diff_exp2,
-                                 h1_diff_sum = h1_diff_sum_exp2,
-                                 exp = "2")
-  
[…]

### 2023-07-14 Manuscript.Rmd
updates

@@
 output:
+  word_document:
+  html_document: default
   pdf_document:
     latex_engine: xelatex
-  html_document: default
-  word_document:
 bibliography: knitting files/Citations.bib

### 2023-07-14 Manuscript.Rmd
updated intro

@@
   - id : "1"
-    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University"
+    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
   - id : "2"
-    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University"
+    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
+  - id : "3"
+    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
+  - id : "4"
+    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
+  - id : "4"
+    institution : "Danish Pain Research Center, Aarhus University, Denmark"
 date: "`r Sys.Date()`"
@@
 We investigated this difference in subjective cold / warm and burning ratings with a two by two interaction of manipulation (control / TGI) and dermatome (within / across).
-Results showed that participants reported a stronger reduced experience of cold, when the stimulus was presented within determatomes compared to across in the TGI condition compared to the control condition when the reference thermode was cold (experiment 1), but not when the reference thermode was warm (experiment 2)
-(Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`)
-The percept of warm showed no siginifcant interaction with either thermode as reference (Exp.
+Results showed that participants reported a stronger reduced experience of cold, when the stimulus was presented within determatomes compared to across in the TGI condition compared to the control condition when the reference thermode was cold (experiment 1), but not when the reference thermode was warm (experiment 2) (Exp.
+1: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`; Exp.
+2: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) The percept of warm showed no siginifcant interaction with either thermode as reference (Exp.
 1: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; Exp.
-2: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`)
-The percept of burning showed no statistical significant interaction with the reference being cold, but a strong interaction when the reference thermode was warm
-(Exp.1: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; Exp. 2 $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`)
-These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
+2: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`) The percept of burning showed no statistical significant interaction with the reference being cold, but a strong interaction when the reference thermode was warm (Exp.1: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; Exp.
+2 $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`) These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
 These findings are consistent with previous results on the modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
@@
 In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3).
-We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal)
-Results showed no statistical significant interaction effect for the cold ratings in both experiments:
-(Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`)
-Neither a statistically significant effect for warm watings
-(Exp1: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`) 
-and also not for burning ratings
-(Exp1: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`)
+We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal) Results showed no statistical significant interaction effect for the cold ratings in both experiments: (Exp.
+1: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; Exp.
+2: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`) Neither a statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`) and also not for burning ratings (Exp1: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`)
 
@@
 Like the previous analysis we investigated this relationship with a two way interaction here with the rostral - caudal axis being investigated.
-Results showed no statistical significant interaction effect for the cold ratings in the first experiment, but a statistically significant interaction when the reference thermode was warm:
-(Exp. 1: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; Exp. 2: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
-No statistically significant effect for warm watings
-(Exp1: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`) 
-and also not for burning ratings
-(Exp1: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`)
+Results showed no statistical significant interaction effect for the cold ratings in the first experiment, but a statistically significant interaction when the reference thermode was warm: (Exp.
+1: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; Exp.
+2: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`) No statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`) and also not for burning ratings (Exp1: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`)
 

### 2023-07-14 Manuscript.Rmd
updated intro

--- 2023-07-14 Manuscript.Rmd
@@
   - id : "1"
-    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University"
+    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
   - id : "2"
-    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University"
+    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
+  - id : "3"
+    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
+  - id : "4"
+    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
+  - id : "5"
+    institution : "Danish Pain Research Center, Aarhus University, Denmark"
 date: "`r Sys.Date()`"
@@
 Participants were asked to rate their perceptions of cold, warm, and burning sensations in response to TGI and control stimuli.
-Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the TGI that may illuminate processes underlying thermosensory integration in the spinal cord.
+Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the illusion that may illuminate processes underlying thermosensory integration in the spinal cord.
 Our findings revealed that both thermosensory and painful components of TGI perception were modulated similarly, with enhanced warm and burning ratings observed when cold and warm stimuli were confined within the same dermatome.
-Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but a notable enhancement of the TGI effect when the cold stimulus was associated with a more caudal segmental location along the spinal cord compared to the warm stimulus.
+Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but notable heat enhancement when the cold rather than the warm stimulus was associated with a more caudal segmental location along the spinal cord.
 These results provide insights into the organisation of the spinal cord in relation to the thermosensory integration and generation of the TGI.
@@
 The enhanced perception of heat in TGI was explained by a spinal inhibitory mechanism, drawing from observations in an animal model where simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone [@craig_thermal_1994].
-Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following a thalamic lesion [@craig_thermal_1994; -@bud_craig_new_1998].
+Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following thalamic lesions [@craig_thermal_1994; -@bud_craig_new_1998].
+
 Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
-Two studies posited that the illusory pain of the TGI depends uniquely on supraspinal mechanisms.
+Two studies posited that the illusory pain component of the TGI depends uniquely on supraspinal mechanisms.
 This interpretation was based on the observed modulation of the illusion in accordance with a spatiotopic rather than somatotopic representation of the body [@marotta_transforming_2015].
@@
 This suggests a similar influence of descending modulation, irrespective of whether the painful sensation was triggered by potentially harmful (noxious) or harmless (innocuous) stimuli [@harper_conditioned_2017].
-These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain within the TGI.
+These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain.
+
 In this paper our objective was twofold.

### 2023-07-14 Manuscript.Rmd
updated results and discussion (intro part)

@@
 Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes.
-Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and burning components.
+Cold and warm stimuli were presented at a fixed distance on the skin, but depending on their longitudinal or tangential orientation on the arm, they elicited neural activity in a differing number of spinal segments.
+Our assumption was that cold and warm-related neural activity in the spinal cord was more focal, when the stimuli were presented within the same dermatome, while more widespread, when the stimuli mapped on non-adjacent spinal segments.
+Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and painful components.
 Here, to probe possible distinctions between the two qualitative components of the TGI, we measured subjective indices of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations.
@@
 Illusory pain, on the other hand, denotes the perception of a burning sensation elicited by the pairing of warm and cold stimuli, an experience that is largely absent or significantly diminished when each stimulus is presented alone or combined with a neutral temperature.
-Thus, indicators of a stronger TGI are heightened warm and burning ratings, coupled with reduced cold ratings.
+Thus, indicators of a stronger TGI are reduced cold ratings, coupled with heightened warm and burning ratings.
 To investigate thermosensory and burning components of the TGI, participants received pairs of temperatures on their forearms and were asked to quantify the levels of cold, warmth, and burning they experienced during each stimulation.
@@
 All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments.
-In doing so, the stimuli elicited cold-related and warm-related neural activity that was either more focal or more widespread along the spinal cord.
 For each stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of a sensation, to 100, indicating an extreme sensation.
@@
 We investigated this difference in subjective cold / warm and burning ratings with a two by two interaction of manipulation (control / TGI) and dermatome (within / across).
-Results showed that participants reported a stronger reduced experience of cold, when the stimulus was presented within determatomes compared to across in the TGI condition compared to the control condition when the reference thermode was cold (experiment 1), but not when the reference thermode was warm (experiment 2) (Exp.
+Participants reported a reduced experience of cold, when the stimulus was presented within determatomes compared to across in the TGI condition compared to the control condition when the reference thermode was cold (experiment 1), but not when the reference thermode was warm (experiment 2) (Exp.
 1: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`; Exp.

### 2023-07-14 Manuscript.Rmd
updated results

@@
 2).
-We investigated this difference in subjective cold / warm and burning ratings with a two by two interaction of manipulation (control / TGI) and dermatome (within / across).
-Participants reported a reduced experience of cold, when the stimulus was presented within determatomes compared to across in the TGI condition compared to the control condition when the reference thermode was cold (experiment 1), but not when the reference thermode was warm (experiment 2) (Exp.
-1: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`; Exp.
-2: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) The percept of warm showed no siginifcant interaction with either thermode as reference (Exp.
-1: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; Exp.
-2: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`) The percept of burning showed no statistical significant interaction with the reference being cold, but a strong interaction when the reference thermode was warm (Exp.1: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; Exp.
-2 $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`) These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
+When rating the cold thermode (Exp.
+1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`.
+However we did not observed such interaction effect for warm (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`) and burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; .
+
+In contrast, when rating the warm thermode (Exp.
+2), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
+However, we did not observe a modulation of cold (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) ) and warm thermosensory ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
+
+These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
 These findings are consistent with previous results on the modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].

### 2023-07-14 Manuscript.Rmd
updated result section 1 (2-way stimulation by dermatome interaction)

@@
 
-These findings not only corroborated earlier results regarding the segmental organisation of the TGI [@fardo_organization_2018] but also suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
-These findings are consistent with previous results on the modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
+The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
+This interpretation is consistent with a previous study using a similar dermatome manipulation, but a distinct method to quantify TGI perception [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
 All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI.

### 2023-07-14 Manuscript.Rmd
updasted results

@@
     institution : "Danish Pain Research Center, Aarhus University, Denmark"
-date: "`r Sys.Date()`"
+#date: "`r Sys.Date()`"
 output:
@@
 When rating the cold thermode (Exp.
-1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`.
-However we did not observed such interaction effect for warm (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`) and burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; .
+1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
+However we did not observed such interaction effect for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`) and burning ratings ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`).
 
@@
 2), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
-However, we did not observe a modulation of cold (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) ) and warm thermosensory ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
+However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) ) and warm thermosensory ratings ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
 

### 2023-07-14 Manuscript.Rmd
updates

@@
     affiliation : "1"  
-
 affiliation:

### 2023-07-14 testing.Rmd
updates

---
title: "tester"
output: html_document
date: "2023-07-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r, fig.width=10, fig.height=5}
experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))

df_long_exp1 = experiment1$df_long
df_long_exp2 = experiment2$df_long

######### Exp 1 (Hypothesis 1)
df_long_exp1 = df_long_exp1 %>% mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))

##constats:

levels(df_long_exp1$cold_probe)
#within - across
within_across = c(-1/2,1/2,1/2,-1/2)
caudal_rostral = c(1,0,0,-1)
distal_proximal = c(0,1,-1,0)

cold = rbind(1/4,within_across,caudal_rostral,distal_proximal)

cold = solve(cold)

cold = cold[,-1]

model_cold_exp1 = glmmTMB::glmmTMB(beta ~ cold_probe *manipulation+trial_n+(1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'cold'),
                            na.action = na.omit,
                            contrasts=list(cold_probe = cold)

model_cold_exp = glmmTMB::glmmTMB(beta ~ cold_probe *manipulation+trial_n+(1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'cold'),
                            na.action = na.omit,contrasts=list(cold_probe = cold))

mm = glmmTMB::glmmTMB(beta ~ cold_probe *manipulation+trial_n+(1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'cold') %>% mutate(cold_probe = relevel(cold_probe, ref = "rostral")),
                            na.action = na.omit)

summary(mm)

model_cold = glmmTMB::glmmTMB(beta ~ manipulation * condition + trial_n +
                              (1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'cold'),
                            na.action = na.omit)

summary(model_cold)
summary(model_cold_exp1)
summary(model_cold_exp)

summary(model_cold_exp1)
lsmeans(model_cold_exp1, c("manipulation","cold_probe"))

summary(model_cold)
lsmeans(model_cold, c("manipulation","condition"))

model_warm = glmmTMB::glmmTMB(beta ~ manipulation * condition + trial_n +
                              (1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'warm'),
                            na.action = na.omit)

plot(ggeffect(model_cold, terms = c("condition","manipulation")))

plot(ggeffect(model_warm, terms = c("condition","manipulation")))

meaneffects = df_long_exp1 %>% filter(quality == 'warm', beta != 0) %>% group_by(manipulation,condition) %>% summarize(mean = mean(beta), se = sd(beta)/sqrt(n()))

plot2 = df_long_exp1 %>% filter(quality == 'warm', beta != 0) %>% group_by(ID, manipulation,condition) %>% summarize(mean = mean(beta)) %>% ggplot(aes(x = manipulation, y = mean, col = condition))+geom_point(position = position_dodge(width = 0.3))+
  geom_pointrange(data = meaneffects, aes(x = manipulation, col = condition, y = mean, ymin = mean-2*se, ymax = mean+2*se), size = 0.5, linewidth = 1.5,position = position_dodge(width = 0.5))+theme_classic()+
  geom_line(
    data = meaneffects,
    aes(x = manipulation, y = mean, group = condition, col = condition),
    position = position_dodge(width = 0.5),
    size = 1.2)+ggtitle("Without 0")

meaneffects2 = df_long_exp1 %>% filter(quality == 'warm') %>% group_by(manipulation,condition) %>% summarize(mean = mean(beta), se = sd(beta)/sqrt(n()))

plot1 = df_long_exp1 %>% filter(quality == 'warm') %>% group_by(ID, manipulation,condition) %>% summarize(mean = mean(beta)) %>% ggplot(aes(x = manipulation, y = mean, col = condition))+geom_point(position = position_dodge(width = 0.3))+
  geom_pointrange(data = meaneffects2, aes(x = manipulation, col = condition, y = mean, ymin = mean-2*se, ymax = mean+2*se), size = 0.5, linewidth = 1.5,position = position_dodge(width = 0.5))+theme_classic()+
  geom_line(
    data = meaneffects2,
    aes(x = manipulation, y = mean, group = condition, col = condition),
    position = position_dodge(width = 0.5),
    size = 1.2)+ggtitle("With 0")

plot1+plot2

```

### 2023-07-14 scripts/models.R

@@ -59,7 +59,6 @@ if(rerun){
                                 contrasts=list(cold_probe = cold)
                                 ) 
   
-  
   stats_model_warm_exp1 = summary_stat(model_warm_exp1, 8,r)
   
   # Burn

### 2023-07-14 scripts/plots.R

@@ -2,7 +2,7 @@
 make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
   
   # now plot the difference
-  plot = ggplot(data = vas_h1_diff, aes(colour = quality)) +
+  plot = data = vas_h1_diff %>% ggplot(aes(colour = quality)) +
     geom_hline(yintercept = 0, colour = 'grey50') +
     geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
                alpha = .5) +
@@ -19,6 +19,7 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
     theme_classic() +
     theme(legend.position = 'none')+coord_cartesian(ylim = c(-30,30))+scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
+  plot
   return(plot)
   
 }

### 2023-07-14 Manuscript.Rmd
references

--- 2023-07-14 Manuscript.Rmd
@@
     latex_engine: xelatex
-bibliography: knitting files/Citations.bib
+bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
 link-citations: yes
@@
 The enhanced perception of heat in TGI was explained by a spinal inhibitory mechanism, drawing from observations in an animal model where simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone [@craig_thermal_1994].
-Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following thalamic lesions [@craig_thermal_1994; -@bud_craig_new_1998].
+Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following thalamic lesions [@craig_thermal_1994; -@craig_new_1998].
 

### 2023-07-15 Manuscript.Rmd
maineffects_for_within_/_across

@@
 output:
-  word_document:
-  html_document: default
   pdf_document:
     latex_engine: xelatex
+  html_document: default
+  word_document:
 bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
@@
 2).
+
 When rating the cold thermode (Exp.
 1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
-However we did not observed such interaction effect for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`) and burning ratings ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`).
+
+However we did not observed such interaction effect for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`), but with a strong main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`)
+No significant interaction nor main effect was found for the burning ratings ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`, ($\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`, interaction, main effect respectively).
 
@@
 2), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
-However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) ) and warm thermosensory ratings ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
+However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`), nor main effect ($\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) ) and warm thermosensory ratings ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`), also without a significant main effect of dermatome ($\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`).
 

### 2023-07-15 scripts/plots.R

@@ -133,4 +133,3 @@ plot2 = function(){
   return(plot2)
 }
 
-

### 2023-07-16 Manuscript.Rmd
added_plots_without_0

@@
 
+#save.image("~/tgi-spinal/Workspace/stats.RData")
+
 list2env(stats, envir=environment())
-
-#save.image("~/tgi-spinal/Workspace/stats.RData")
 
@@
 Small dots are individual means, large dots are population means for each condition and error bars are 95% confidence intervals."}
-plot1()
+
+plot1(include_zero = F)
+
+#plot1(include_zero = T)
+
 ```
@@
 In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3).
-We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal) Results showed no statistical significant interaction effect for the cold ratings in both experiments: (Exp.
-1: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; Exp.
-2: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`) Neither a statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`) and also not for burning ratings (Exp1: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`)
+We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal) Results showed no statistical significant interaction effect for the cold ratings in Exp.
+1: ($\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`, however with a strong main effect of dermatome ($\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`); With the same pattern in Exp.
+2 for the interaction and main effect respectively ($\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`,$\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`).
+
+Neither a statistically significant interaction effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`, nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`); with the same pattern in Exp 2 for interaction and main effect respectively $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`, $\beta$ = `r stats_model_warm_exp2$beta[4]`, `r make_pvalue(stats_model_warm_exp2$p[4])` )
+
+We found no significant interaction for the burning ratings for Exp1: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`, but a significant main effect ( $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`), With no significant interaction, nor main effect in Exp 2: ($\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`, $\beta$ = `r stats_model_burn_exp2$beta[4]`, `r make_pvalue(stats_model_burn_exp2$p[4])`)
 
@@
 Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
-plot2()
+
+plot2(include_zero = F)
+
+#plot2(include_zero = T)
+
 ```
@@
 Like the previous analysis we investigated this relationship with a two way interaction here with the rostral - caudal axis being investigated.
-Results showed no statistical significant interaction effect for the cold ratings in the first experiment, but a statistically significant interaction when the reference thermode was warm: (Exp.
-1: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; Exp.
-2: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`) No statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`) and also not for burning ratings (Exp1: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`)
+Results showed no statistical significant interaction effect for the cold ratings in the first experiment (Exp.
+1: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`, but a main effect ($\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`), A statistically significant interaction when the reference thermode was warm was found; (; Exp.
+2: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
+
+No statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`, but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`); The same pattern was found in Exp 2 for interaction and main effect respectively ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`,$\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`)
+
+The burning ratings showed no significant interaction, nor main effect in experiment 1($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`,$\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
+In Exp 2, we found no significant interaction effect ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`)
 

### 2023-07-16 scripts/models.R

@@ -23,10 +23,10 @@ if(rerun){
   #caudal - rostral
   caudal_rostral = c(1,0,0,-1)
   #distral - proximal
-  distal_proximal = c(0,1,-1,0)
+  proximal_distal = c(0,-1,1,0)
   
   #define the matrix
-  cold = rbind(1/4,within_across,caudal_rostral,distal_proximal)
+  cold = rbind(1/4,within_across,caudal_rostral,proximal_distal)
   
   #solve it 
   cold = solve(cold)
@@ -39,8 +39,8 @@ if(rerun){
   
   ## hypothsis 1
   # Cold
-  model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + trial_n +
-                                  (1|ID) + (1|order),
+  model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + 
+                                trial_n + (1|ID) + (1|order),
                                 family = glmmTMB::beta_family(),
                                 ziformula = ~1+manipulation,
                                 data = df_long_exp1 %>% filter(quality == 'cold'),
@@ -70,7 +70,7 @@ if(rerun){
   # check n
   length(unique(df_resp_exp1$ID))
   
-  model_burn_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
+  model_burn_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + 
                                   trial_n + (1|ID) + (1|order),
                                 family = glmmTMB::beta_family(),
                                 ziformula = ~1+manipulation,

### 2023-07-16 scripts/plots.R

@@ -25,11 +25,11 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
 }
 
 
-plot1 = function(){
+plot1 = function(include_zero = T){
   
   # experiment 1 file
   
-  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
+  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), include_zero = include_zero)
   vas_h1_diff_exp1 = experiment1$vas_h1_diff
   h1_diff_sum_exp1 = experiment1$h1_diff_sum
   
@@ -41,7 +41,7 @@ plot1 = function(){
   
   # experiment 2 file
   
-  experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
+  experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'), include_zero = include_zero)
   vas_h1_diff_exp2 = experiment2$vas_h1_diff
   h1_diff_sum_exp2 = experiment2$h1_diff_sum
   
@@ -102,10 +102,10 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
   return(experiment1_h2 = h2_diff_within / h2_diff_across)
 }
 
-plot2 = function(){
+plot2 = function(include_zero = T){
   
   # experiment 1 file
-  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
+  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), include_zero = include_zero)
   vas_h2_diff_exp1 = experiment1$vas_h2_diff
   h2_diff_sum_exp1 = experiment1$h2_diff_sum
   
@@ -117,7 +117,7 @@ plot2 = function(){
   
   
   # experiment 2 file
-  experiment1 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
+  experiment1 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'), include_zero = include_zero)
   vas_h2_diff_exp2 = experiment1$vas_h2_diff
   h2_diff_sum_exp2 = experiment1$h2_diff_sum
   

### 2023-07-16 scripts/utility.R

@@ -60,7 +60,7 @@ gren <- brewer.pal(8, "Greens")
 
 
 
-prep_data = function(file){
+prep_data = function(file, include_zero = T){
   
   if (file.exists(file)){
     df_res <- read.csv(file)
@@ -101,6 +101,13 @@ prep_data = function(file){
   # print
   print(paste0('Non responders: ', nNONRESP, '/', length(test$ID)))
   
+  if(!include_zero){
+    df_res = df_res %>% mutate(VASinit = ifelse(VASinit == 0, NA,VASinit),
+                      VASburn = ifelse(VASburn == 0, NA,VASburn),
+                      VASwarm = ifelse(VASwarm == 0, NA,VASwarm),
+                      VAScold = ifelse(VAScold == 0, NA,VAScold))
+  }
+  
   # Reorganise data-frame 
   # pivot longer the VAS response by each quality of sensation
   # do this for both RT and VAS
@@ -134,6 +141,7 @@ prep_data = function(file){
   # calculate means
   vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
                         median, data = all_vas)
+  
   vas_h1 <- aggregate(VAS ~ quality*manipulation*condition*ID, mean, data = vas_meds)
   # change name of manipulation
   vas_h1$manipulation <- factor(vas_h1$manipulation,
@@ -143,7 +151,7 @@ prep_data = function(file){
                             withinvars = c('manipulation', 'quality', 'condition'))
   
   vas_h1_diff <- vas_h1 %>% 
-    pivot_wider(names_from = condition, values_from = VAS) %>% 
+    pivot_wider(names_from = condition, values_from = VAS) %>% tidyr::replace_na(list(within = 0, across = 0)) %>% 
     mutate(difference = within - across)
   # recode quality
   vas_h1_diff$quality <- factor(vas_h1_diff$quality,
@@ -159,6 +167,8 @@ prep_data = function(file){
   
   # Change name of manipulation
   vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
+  
+  
   h2_sum <- aggregate(VAS~quality*manipulation*cold_probe, median, data = vas_meds)
   
   # organise data for plotting
@@ -184,7 +194,7 @@ prep_data = function(file){
   vas_h2_diff <- vas_meds %>% 
     select(-c(cold_code, xj, cold_probe)) %>% 
[…]

### 2023-07-17 Manuscript.Rmd
updated_phrasing_of_manuscript_and_organization

--- 2023-07-14 Manuscript.Rmd
@@
 output:
-  word_document:
   html_document: default
@@
     latex_engine: xelatex
+  word_document:
 bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
@@
 2).
+
 When rating the cold thermode (Exp.
 1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
-However we did not observed such interaction effect for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`) and burning ratings ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`).
+This interaction was not present for for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`), but we did find a strong main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`) For the burning ratings we found No significant interaction  ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`) nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
 
-In contrast, when rating the warm thermode (Exp.
-2), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
-However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) ) and warm thermosensory ratings ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
+In contrast, when rating the warm thermode, participants reported markedly enhanced burning sensations for TGI, but not non-TGI, (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).However, we did not observe suvh a modulation of cold percepts ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`), with no main effect ($\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) for the warm thermosensory ratings we found no interaction ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`), and no main effect of dermatome ($\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`).
 
@@
 In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3).
-We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal) Results showed no statistical significant interaction effect for the cold ratings in both experiments: (Exp.
-1: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; Exp.
-2: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`) Neither a statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`) and also not for burning ratings (Exp1: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`)
+We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal).
+In the first experiment with the cold thermode as the reference we found no statistical significant interaction effect for the cold ratings ($\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`, however with a strong main effect of dermatome ($\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) For the warm ratings we found no interaction ($\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`), nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`)
+For the burning ratings We found no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`), but a significant main effect ( $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
+
+For the second experiment with the warm thermode as the reference we found no interaction no interaction ($\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`), nor main effect ($\beta$ = `r stats_model_burn_exp2$beta[4]`, `r make_pvalue(stats_model_burn_exp2$p[4])`) for the burning ratings.
+For the warm ratings we found no interaction ($\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`), , nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp2$beta[4]`, `r make_pvalue(stats_model_warm_exp2$p[4])`) and for the cold ratings no interaction ($\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`) but a main effect ($\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`).
 
@@
 Like the previous analysis we investigated this relationship with a two way interaction here with the rostral - caudal axis being investigated.
-Results showed no statistical significant interaction effect for the cold ratings in the first experiment, but a statistically significant interaction when the reference thermode was warm: (Exp.
-1: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; Exp.
-2: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`) No statistically significant effect for warm watings (Exp1: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`) and also not for burning ratings (Exp1: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; Exp 2: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`)
+
+Results showed no statistical significant interaction effect for the cold ratings in the first experiment with the reference thermode being cold ($\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`, but a main effect ($\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`).
+For the warm ratings we found no statistically significant effect for warm watings ($\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`), but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`)
+The burning ratings showed no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`), nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
+
+In Experiment 2, with the warm thermode as the reference we found no significant interaction effect for the burning ratings ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`)
+For the warm ratings we found no statistically significant interaction ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`), but a strong main effect ($\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`)
+For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
 

### 2023-07-26 Manuscript.Rmd
test_dif

@@
 if (!require("pacman")) install.packages("pacman")
+
 pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
@@
                )
+
 source(here::here("scripts","utility.R"))
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = " Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = " Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
 Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.

### 2023-07-26 scripts/models.R

@@ -37,8 +37,9 @@ if(rerun){
   
   ######### Exp 1 (Hypothesis 1)
   
-  ## hypothsis 1
-  # Cold
+  ## hypothsis 1  
+  # Cold.
+
   model_cold_exp1 = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + 
                                 trial_n + (1|ID) + (1|order),
                                 family = glmmTMB::beta_family(),
@@ -81,12 +82,11 @@ if(rerun){
   
   stats_model_burn_exp1 = summary_stat(model_burn_exp1, 8,r)
   
-  
 
-  
-  
   ######### Exp 2 (Hypothesis 1)
 
+  
+  
   # Cold
   model_cold_exp2 = glmmTMB::glmmTMB(beta ~ manipulation*cold_probe  + trial_n +
                                        (1|ID) + (1|order),

### 2023-07-31 Manuscript.Rmd
tables_n_figures

--- 2023-07-17 Manuscript.Rmd
@@
                modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
-                 rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, cowplot
+               rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, cowplot,
+               flextable
                )
+
 source(here::here("scripts","utility.R"))
 source(here::here("scripts","plots.R"))
+source(here::here("scripts","supplementary.R"))
 
@@
 Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
-Small dots are individual means, large dots are population means for each condition and error bars are 95% confidence intervals."}
+Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
+A) first experiment with the cold thermode as the reference, and B second experiment with the warm thermode as referece."}
 
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 7.2, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the two dermatome conditions.
-The top panel shows the difference between proximal and distal cold afferent locations (within dermatomes) and the bottom panel shows the difference between rostral and caudal cold afferent locations, relative to warm, across stimulation type (Non-TGI, TGI) and VAS rating quality (cold, warm and burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the proximal and distal dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
+A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce.
 Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
 
-plot2(include_zero = F)
+#plot2(include_zero = F)
 
 #plot2(include_zero = T)
-
+plot2_3(include_zero = F)[[1]]
 ```
@@
 For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
+
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the Caudal and Rostral dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
+A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce.
+Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
+
+plot2_3(include_zero = F)[[2]]
+```
 
@@
 :::
+
+# Supplementary material
+```{r,warning = F, message = F, echo = F}
+
+get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>% 
+  width(j=1, width = 2.5) %>% 
+  width(j=c(2,3,4,5), width = 1.1)
+
+get_main_tables(model_warm_exp1,round = 2, title = "Cold reference on warm ratings") %>% 
+  width(j=1, width = 2.5) %>% 
+  width(j=c(2,3,4,5), width = 1.1)
+
+get_main_tables(model_burn_exp1,round = 2, title = "Cold reference on burning ratings") %>% 
+  width(j=1, width = 2.5) %>% 
+  width(j=c(2,3,4,5), width = 1.1)
+
+get_main_tables(model_cold_exp2,round = 2, title = "Warm reference on cold ratings") %>% 
+  width(j=1, width = 2.5) %>% 
+  width(j=c(2,3,4,5), width = 1.1)
+
+get_main_tables(model_warm_exp2,round = 2, title = "Warm reference on warm ratings") %>% 
+  width(j=1, width = 2.5) %>% 
+  width(j=c(2,3,4,5), width = 1.1)
+
+get_main_tables(model_burn_exp2,round = 2, title = "Warm reference on burning ratings") %>% 
+  width(j=1, width = 2.5) %>% 
+  width(j=c(2,3,4,5), width = 1.1)
+
+```

### 2023-07-31 scripts/models.R

@@ -1,6 +1,6 @@
 
 statistics = function(rerun){
-  #roudning
+  #rounding
   r = 2
   
   
@@ -157,8 +157,10 @@ if(rerun){
   
   statistics_to_save = ls()[grepl("stats", ls())]
   data_to_save = ls()[grepl("descript_", ls())]
+  models_to_save = ls()[grepl("model",ls())]
   
-  saving = c(statistics_to_save,data_to_save)
+  saving = c(statistics_to_save,data_to_save,models_to_save)
+  
   
   foo = function(name){
     variable = get(name, envir=environment())
@@ -167,15 +169,12 @@ if(rerun){
   
   savings = sapply(saving, foo)
   
-
-  #list2env(statistics, envir = sys.frame(sys.parent(0)))
   
-  #save(list = vars_to_save, file = here::here("Analysis","Workspace","Plotting_workspace.RData"))
   return(savings)
 }else{
   
   load(here::here("Workspace","stats.RData"))
   
-  return(stats)
+  return(savings)
 }
 }

### 2023-07-31 scripts/plots.R

@@ -57,6 +57,8 @@ plot1 = function(include_zero = T){
 }
 
 make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
+  
+  
   h2_diff_within = ggplot(data = vas_h2_diff %>% 
                             filter(condition == 'within'), 
                           aes(manipulation, difference, colour = quality)) +
@@ -99,7 +101,9 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
     facet_wrap(~quality) +
     theme_classic() +
     theme(legend.position = 'none')+coord_cartesian(ylim = c(-60,60))+scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
-  return(experiment1_h2 = h2_diff_within / h2_diff_across)
+  
+  experiment1_h2 = h2_diff_within / h2_diff_across
+  return(list(experiment1_h2,h2_diff_within,h2_diff_across))
 }
 
 plot2 = function(include_zero = T){
@@ -110,10 +114,7 @@ plot2 = function(include_zero = T){
   h2_diff_sum_exp1 = experiment1$h2_diff_sum
   
   
-  experiment1_h2 = make_plot2(vas_h2_diff_exp1,h2_diff_sum_exp1, title = "Reference: Cold Thermode")+plot_annotation(tag_levels = list("A","B"))
-  
-  
-  
+  experiment1_h2 = make_plot2(vas_h2_diff_exp1,h2_diff_sum_exp1, title = "Reference: Cold Thermode")[[1]]+plot_annotation(tag_levels = list("A","B"))
   
   
   # experiment 2 file
@@ -121,8 +122,7 @@ plot2 = function(include_zero = T){
   vas_h2_diff_exp2 = experiment1$vas_h2_diff
   h2_diff_sum_exp2 = experiment1$h2_diff_sum
   
-  experiment2_h2 = make_plot2(vas_h2_diff_exp2,h2_diff_sum_exp2, title = "Reference: Warm Thermode")+plot_annotation(tag_levels = list(c("C","D")))
-  
+  experiment2_h2 = make_plot2(vas_h2_diff_exp2,h2_diff_sum_exp2, title = "Reference: Warm Thermode")[[1]]+plot_annotation(tag_levels = list(c("C","D")))
   
   
   #combine plots
@@ -131,5 +131,31 @@ plot2 = function(include_zero = T){
   plot2
   
[…]

### 2023-07-31 scripts/supplementary.R

@@ -1,0 +1,64 @@
+
+get_main_tables = function(model, round = 2, title){
+  
+  if(is.gamlss(model)){
+    fixedeffecs = parameters::model_parameters(model) %>% 
+      mutate(CI = NULL, CI_low = NULL, CI_high = NULL,df_error = NULL) %>% 
+      dplyr::rename(parameter = Component) %>% 
+      dplyr::select(parameter, everything()) %>% 
+      mutate(parameter = ifelse(str_detect(parameter, "conditional"),"μ (location)",ifelse(str_detect(parameter, "sigma"),"σ (scale)",ifelse(str_detect(parameter, "tau"),"τ (one-inflation)","ν (zero-inflation)"))))
+    
+    names(fixedeffecs) = c("parameter","contrast","β","SE","t","p")
+    formular = as.character(formula(model))
+    
+    
+    fixedeffecs[, 3:6] <- apply(fixedeffecs[, 3:6], 2, function(x) format(x, trim = F, digits = round))
+    fixedeffecs
+    
+    ft = flextable(fixedeffecs) %>% 
+      add_header_row(values = paste0(formular[2],formular[1],formular[3]," family = ZOIB, link = logit"), colwidths = c(ncol(fixedeffecs))) %>% 
+      add_header_lines(values = title) %>% 
+      align(i = 1:2, j = NULL, align = "center", part = "header") %>% width(width = 1)
+    
+    ft
+    
+    return(ft)
+    
+    
+  }else{
+    m1 = summary(model)
+    fixedeffecs = data.frame(m1$coefficients$cond)
+    
+    fixedeffecs[,1:4] <- apply(fixedeffecs[,1:4], 2, function(x) formatC(x, format = "g", digits = round))
+    
+    
+    names(fixedeffecs) = c("β","SE","Z","p")
+    
+    formular = as.character(formula(model))
+    family = model$modelInfo$family[[2]]
+    
+    row.names(fixedeffecs) = c("Intercept","TGI-CNT",
+                               "Within-Across",
+                               "Caudal-Rostral",
+                               "Proximal-Distal","Trial",
+                               "TGI-CNT * Within-CNT",
+                               "TGI-CNT * Caudal-Rostral",
+                               "TGI-CNT * Proximal-Distal")
+    
+    
+    flextable(fixedeffecs %>% rownames_to_column(var = "  ")) %>% 
[…]

### 2023-07-31 scripts/utility.R

@@ -41,15 +41,6 @@ summary_stat = function(model, coefficients, round){
 }
 
 
-
-
-
-
-
-
-
-
-
 # first colours
 blue <- brewer.pal(8, "Blues")
 grey <- brewer.pal(8, "Greys")

### 2023-07-31 Manuscript.Rmd
edits

@@
   - name : "Daniel Elmstrom Christensen"
-    affiliation : "2"
+    affiliation : "1"
   - name : "Anna Villaume Stuckert"
@@
 Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors.
-The generation of this illusion is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020].
-Recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
+Thus researchers have attributed the generation of this illusion to complex mechanisms within the central nervous system [@craig_thermal_1994; @fardo_beyond_2020].
+In particular, recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
 However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.
@@
 We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal).
-In the first experiment with the cold thermode as the reference we found no statistical significant interaction effect for the cold ratings ($\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`, however with a strong main effect of dermatome ($\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) For the warm ratings we found no interaction ($\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`), nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`)
-For the burning ratings We found no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`), but a significant main effect ( $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
+In the first experiment with the cold thermode as the reference we found no statistical significant interaction effect for the cold ratings ($\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`, however with a strong main effect of dermatome ($\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) For the warm ratings we found no interaction ($\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`), nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`) For the burning ratings We found no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`), but a significant main effect ( $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
 
@@
 Results showed no statistical significant interaction effect for the cold ratings in the first experiment with the reference thermode being cold ($\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`, but a main effect ($\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`).
-For the warm ratings we found no statistically significant effect for warm watings ($\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`), but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`)
-The burning ratings showed no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`), nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
+For the warm ratings we found no statistically significant effect for warm watings ($\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`), but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`) The burning ratings showed no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`), nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
 
-In Experiment 2, with the warm thermode as the reference we found no significant interaction effect for the burning ratings ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`)
-For the warm ratings we found no statistically significant interaction ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`), but a strong main effect ($\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`)
-For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
+In Experiment 2, with the warm thermode as the reference we found no significant interaction effect for the burning ratings ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`) For the warm ratings we found no statistically significant interaction ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`), but a strong main effect ($\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`) For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
 
@@
 # Supplementary material
+
 ```{r,warning = F, message = F, echo = F}

### 2023-07-31 Manuscript.Rmd
frontpage

--- 2023-07-31 Manuscript.Rmd
@@
 title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
-author: 
-  - name : "Alexandra G. Mitchell"
-    affiliation : "1"
-  - name : "Jesper Fischer Ehmsen"
-    affiliation : "1"
-  - name : "Daniel Elmstrom Christensen"
-    affiliation : "2"
-  - name : "Anna Villaume Stuckert"
-    affiliation : "3"
-  - name : "Patrick Haggard"
-    affiliation : "4"  
-  - name : "Francesca Fardo"
-    affiliation : "1"  
-affiliation:
-  - id : "1"
-    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
-  - id : "2"
-    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
-  - id : "3"
-    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
-  - id : "4"
-    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
-  - id : "5"
-    institution : "Danish Pain Research Center, Aarhus University, Denmark"
-#date: "`r Sys.Date()`"
+author: Alexandra G. Mitchell^1^,
+        Jesper Fischer Ehmsen^1^,
+        Daniel Elmstrom Christensen^1^,
+        Anna Villaume Stuckert^2^,
+        Patrick Haggard^3^,
+        Francesca Fardo^1,4^
 output:
+  word_document:
+      reference_docx: knitting files/test_markdown.docx
+  html_document:
+    css: knitting files/style.css
   pdf_document:
     latex_engine: xelatex
-  html_document: default
-  word_document:
 bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
@@
 linkcolor: blue
+serif: Times New Roman
 always_allow_html: yes
@@
 ---
+
+::: {custom-style="Title text"}
+^1^Center of Functionally Integrative Neuroscience, Department of Clinical Medicine, Aarhus University, Denmark
+
+^2^Department of Neuroscience, Copenhagen University, Denmark
+
+^3^Institute of Cognitive Neuroscience, University College London, United Kingdom
+
+^4^Danish Pain Research Center, Department of Clinical Medicine, Aarhus University, Denmark
+:::
+
+<br>
+
+Corresponding authors: Alexandra G. Mitchell (agmitchell@cfin.au.dk) and Francesca Fardo (francesca@cfin.au.dk)
 
@@
 
+\newpage
+
 # Supplementary material
 ```{r,warning = F, message = F, echo = F}
-
 get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>%
   width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)
+  width(j=c(2,3,4,5), width = 1.1)%>%
+  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
@@
   width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)
+  width(j=c(2,3,4,5), width = 1.1)%>%
+  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
@@
   width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)
+  width(j=c(2,3,4,5), width = 1.1)%>%
+  fontsize(size = 10, part = "all") %>% flextable::font(fontname = "Times New Roman", part = "all")
 

### 2023-07-31 Manuscript.tex
frontpage

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{multicol}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{hyperref}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion},
  pdfauthor={Alexandra G. Mitchell1, Jesper Fischer Ehmsen1, Daniel Elmstrom Christensen1, Anna Villaume Stuckert2, Patrick Haggard3, Francesca Fardo1,4},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Disentangling the spinal mechanisms of illusory heat and burning
sensations in the Thermal Grill Illusion}
\author{Alexandra G. Mitchell\textsuperscript{1}, Jesper Fischer
Ehmsen\textsuperscript{1}, Daniel Elmstrom
Christensen\textsuperscript{1}, Anna Villaume
Stuckert\textsuperscript{2}, Patrick Haggard\textsuperscript{3},
Francesca Fardo\textsuperscript{1,4}}
\date{}

\begin{document}
\maketitle

\textsuperscript{1}Center of Functionally Integrative Neuroscience,
Department of Clinical Medicine, Aarhus University, Denmark

\textsuperscript{2}Department of Neuroscience, Copenhagen University,
Denmark

\textsuperscript{3}Institute of Cognitive Neuroscience, University
College London, United Kingdom

\textsuperscript{4}Danish Pain Research Center, Department of Clinical
Medicine, Aarhus University, Denmark

Corresponding authors: Alexandra G. Mitchell
(\href{mailto:agmitchell@cfin.au.dk}{\nolinkurl{agmitchell@cfin.au.dk}})
and Francesca Fardo
(\href{mailto:francesca@cfin.au.dk}{\nolinkurl{francesca@cfin.au.dk}})

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

The Thermal Grill Illusion (TGI) is a phenomenon in which the
juxtaposition of innocuous warm and cold temperatures elicits a burning
sensation, offering a unique window to understand how pain can be
perceived in response to harmless stimuli. Much debate has revolved
around whether spinal mechanisms are involved in the generation of
illusory pain, beyond supraspinal mechanisms. In this study, we
investigated the role of the spinal cord in the generation of the TGI,
in two independent experiments, involving a total of 80 healthy
individuals. We applied heat and cold stimuli on dermatomes, namely
areas of skin innervated by a single spinal nerve, mapped onto adjacent
or nonadjacent spinal segments. Participants were asked to rate their
perceptions of cold, warm, and burning sensations in response to TGI and
control stimuli. Our aims were to investigate thermosensory and painful
perceptual components of the TGI, as well as spatial features of the
illusion that may illuminate processes underlying thermosensory
integration in the spinal cord. Our findings revealed that both
thermosensory and painful components of TGI perception were modulated
similarly, with enhanced warm and burning ratings observed when cold and
warm stimuli were confined within the same dermatome. Further, we found
no perceptual differences based on the proximal-distal location of the
cold stimulus within a single dermatome, but notable heat enhancement
when the cold rather than the warm stimulus was associated with a more
caudal segmental location along the spinal cord. These results provide
insights into the organisation of the spinal cord in relation to the
thermosensory integration and generation of the TGI.

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The thermal grill illusion (TGI) is a perceptual phenomenon that
challenges conventional understanding of pain perception. It is a
sensation of burning heat or pain when harmless cold and warm
temperatures are applied to the skin simultaneously
(\protect\hyperlink{ref-craig_thermal_1994}{Craig and Bushnell 1994};
\protect\hyperlink{ref-craig_functional_1996}{Craig et al. 1996}).
Despite cold and warm temperatures being individually innocuous, their
combination produces a contradictory burning sensation, even so the
temperatures are insufficient to activate peripheral nociceptors. The
generation of this illusion is thus attributed to central nervous system
mechanisms (\protect\hyperlink{ref-craig_thermal_1994}{Craig and
Bushnell 1994}; \protect\hyperlink{ref-fardo_beyond_2020}{Fardo et al.
2020}). Recent studies have highlighted the involvement of the spinal
cord as an initial site contributing to the TGI
(\protect\hyperlink{ref-fardo_organization_2018}{Fardo, Finnerup, and
Haggard 2018}; \protect\hyperlink{ref-harper_conditioned_2017}{Harper
and Hollins 2017}). However, the precise mechanisms underpinning
integration of cold and warm thermal afferents in the spinal cord,
alongside those responsible for the distinctive burning quality to this
illusion, are yet to be elucidated.

The TGI is often described as encompassing two distinct perceptual
components - an illusion of heat and an illusion of pain Fardo et al.
(\protect\hyperlink{ref-fardo_beyond_2020}{2020}). The illusion of heat,
also known as synthetic heat
(\protect\hyperlink{ref-fruhstorfer_significance_2003}{Fruhstorfer,
Harju, and Lindblom 2003};
\protect\hyperlink{ref-green_localization_1977}{Green 1977},
\protect\hyperlink{ref-green_synthetic_2002}{2002},
\protect\hyperlink{ref-green_temperature_2004}{2004}), refers to
non-painful sensations evoked by the thermal grill
(\protect\hyperlink{ref-defrin_spatial_2008}{Defrin et al. 2008};
\protect\hyperlink{ref-kern_pharmacological_2008}{Kern et al. 2008};
\protect\hyperlink{ref-kern_effects_2008}{2008};
\protect\hyperlink{ref-bouhassira_investigation_2005}{Bouhassira et al.
2005}; \protect\hyperlink{ref-adam_relationships_2014}{Adam et al.
2014}). The illusion of pain, which is the most recognised aspect of the
TGI, is the distinctive burning sensation that accompanies the
simultaneous presentation of cold and warm stimuli
(\protect\hyperlink{ref-craig_thermal_1994}{Craig and Bushnell 1994};
\protect\hyperlink{ref-craig_functional_1996}{1996};
\protect\hyperlink{ref-bach_thermal_2011}{Bach et al. 2011}). The
hallmark of both illusory components is a qualitative change in
perception when the cold and warm stimuli are applied concurrently,
compared to when they are presented individually. Historically, the
thermosensory and painful components of the TGI were explained by
distinct spinal and supraspinal mechanisms, respectively. The enhanced
perception of heat in TGI was explained by a spinal inhibitory
mechanism, drawing from observations in an animal model where
simultaneous application of cold and warm temperatures reduced the
activity of cold-specific spinal neurons compared to when cold was
applied alone (\protect\hyperlink{ref-craig_thermal_1994}{Craig and
Bushnell 1994}). Instead, the illusory pain component was ascribed to a
disinhibition mechanism at the level of the thalamus, primarily based on
the observations of unremitting pain following thalamic lesions
(\protect\hyperlink{ref-craig_thermal_1994}{Craig and Bushnell 1994};
\protect\hyperlink{ref-craig_new_1998}{1998}).

Recent human studies on TGI provided differing interpretations of the
spinal or supraspinal origin of the illusion. Two studies posited that
the illusory pain component of the TGI depends uniquely on supraspinal
mechanisms. This interpretation was based on the observed modulation of
the illusion in accordance with a spatiotopic rather than somatotopic
representation of the body
(\protect\hyperlink{ref-marotta_transforming_2015}{Marotta, Ferrè, and
Haggard 2015}). Further, the illusion remained unaltered during
concomitant tactile stimulation, suggesting ineffectiveness of tactile
gating - a spinally-mediated process involving inhibition of nociceptive
activity by concurrent somatosensory activity
(\protect\hyperlink{ref-ferre_ineffectiveness_2018}{Ferrè et al. 2018}).
Counter to this perspective, other research endorsed a spinal
contribution to the TGI. These studies demonstrated that the illusion
varied depending on whether cold and warm stimuli were applied to
dermatomes mapped either onto adjacent or non-adjacent spinal segments
(\protect\hyperlink{ref-fardo_organization_2018}{Fardo, Finnerup, and
Haggard 2018}). Participants perceived the stimulation more veridically,
consistently with a reduction in TGI perception, when warm or cold
stimuli triggered more widespread activity along the spinal cord,
corroborating the hypothesis that the spinal cord is an initial site of
thermosensory integration underlying TGI. Further support for spinal
mechanisms comes from research demonstrating that both noxious heat and
the TGI were comparably reduced by conditioned pain modulation in
humans. This suggests a similar influence of descending modulation,
irrespective of whether the painful sensation was triggered by
potentially harmful (noxious) or harmless (innocuous) stimuli
(\protect\hyperlink{ref-harper_conditioned_2017}{Harper and Hollins
2017}). These findings collectively challenge a purely supraspinal
hypothesis of the painful component of the TGI and indicate the
relevance of spinal mechanisms in the manifestation of both illusory
heat and pain.

In this paper our objective was twofold. Firstly, we directly
investigated the hypothesis that thermosensory and burning components of
the TGI experience are mediated by spinal mechanisms in humans, by
manipulating the location of the stimuli within and across dermatomes.
Cold and warm stimuli were presented at a fixed distance on the skin,
but depending on their longitudinal or tangential orientation on the
arm, they elicited neural activity in a differing number of spinal
segments. Our assumption was that cold and warm-related neural activity
in the spinal cord was more focal, when the stimuli were presented
within the same dermatome, while more widespread, when the stimuli
mapped on non-adjacent spinal segments. Our past work using a similar
manipulation involved measuring the experience of the TGI using a
temperature matching task
(\protect\hyperlink{ref-fardo_organization_2018}{Fardo, Finnerup, and
Haggard 2018}), which provides a composite measure of TGI perception,
reflecting both thermosensory and painful components. Here, to probe
possible distinctions between the two qualitative components of the TGI,
we measured subjective indices of TGI perception using three independent
visual analog scale (VAS) ratings of perceived cold, warm and burning
sensations. Secondly, we investigated spatial order effects associated
with the integration of cold and warm sensory information at the
dermatome (skin) and segmental (i.,e., spine) levels. At the dermatome
level, we used body-related coordinates to define proximal (towards the
elbow) and distal (towards the wrist) locations. At the spinal level, we
used segment-related coordinates to define more rostral (towards the
head) and more caudal (towards the lower back) locations. Given the
organisation of the spinal cord along a rostral-caudal axis, where each
dermatome is represented across multiple spinal segments through the
Lissauer tract, this study aimed to glean indirect insights into the
spinal mechanisms underpinning thermosensory integration and the
generation of the TGI.

\newpage

\hypertarget{results-and-discussion}{%
\section{Results and discussion}\label{results-and-discussion}}

The Thermal Grill Illusion (TGI) is characterised by two key phenomena:
thermosensory enhancement and illusory pain. Thermosensory enhancement
refers to an amplified perception of heat or cold when cold and warm
stimuli are simultaneously applied, as opposed to when each stimulus is
presented individually or paired with a neutral temperature. Notably,
the majority of individuals experience an intensification of heat rather
than cold (\protect\hyperlink{ref-fardo_beyond_2020}{Fardo et al.
2020}). Illusory pain, on the other hand, denotes the perception of a
burning sensation elicited by the pairing of warm and cold stimuli, an
experience that is largely absent or significantly diminished when each
stimulus is presented alone or combined with a neutral temperature.
Thus, indicators of a stronger TGI are reduced cold ratings, coupled
with heightened warm and burning ratings. To investigate thermosensory
and burning components of the TGI, participants received pairs of
temperatures on their forearms and were asked to quantify the levels of
cold, warmth, and burning they experienced during each stimulation.
These stimuli consisted of either cold-warm pairs (TGI stimuli), which
potentially evoked an illusion of heat and pain, or control stimuli that
involved pairing a cold or a warm stimulus of identical temperature as
in the TGI condition with a baseline temperature of 30°C (non-TGI
stimuli). All stimulation pairs were presented at a fixed distance on
the skin, either within the same dermatome or across dermatomes that
mapped onto non-adjacent spinal segments. For each stimulation,
participants reported their ratings using three sequential VAS scales
ranging from 0, indicating the lack of a sensation, to 100, indicating
an extreme sensation. For each instance of stimulation, participants
were guided to focus their reporting on the sensations originating from
a specific thermode. While the participants were unaware, this location
corresponded to either the colder stimulus (Exp. 1) or the warmer
stimulus (Exp. 2) of the paired temperatures. VAS ratings were analysed
using zero-inflated beta regressions.

\hypertarget{thermosensory-and-burning-components-of-tgi-perception-are-spinally-mediated}{%
\subsection{Thermosensory and burning components of TGI perception are
spinally
mediated}\label{thermosensory-and-burning-components-of-tgi-perception-are-spinally-mediated}}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Four experimental conditions depicting an exemplar cold and
warm thermode placement within and across dermatomes. Within dermatomes,
the relative location of the cold thermode was proximal or distal.
Across dermatomes, the relative location of the corresponding spinal
segments was rostral or caudal.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Difference in VAS ratings between within and across dermatome
conditions for each type of stimulation (Non-TGI and TGI) in each VAS
rating quality (cold, warm and burning). Positive values represent
higher ratings within dermatomes, negative values represent higher
ratings across dermatomes. Small dots are individual subject means,
large dots are population means for each condition and error bars are
95\% confidence intervals. A) first experiment with the cold thermode as
the reference, and B second experiment with the warm thermode as
referece.}
\end{figure}

In keeping with the unique heat and burning features of TGI, our results
exhibited a more robust TGI when stimuli were confined within dermatomes
compared to when applied across dermatomes, corresponding to
non-adjacent spinal segments (Fig. 2).

When rating the cold thermode (Exp. 1), participants reported a
significantly reduced subjective experience of cold for TGI, but not
non-TGI, stimuli applied within a dermatome compared to across
dermatomes (stimulation by dermatome interaction: \(\beta\) = -0.15, p
\textless{} .01). This interaction was not present for for warm
(\(\beta\) = -0.03, p = 0.77), but we did find a strong main effect of
dermatome (\(\beta\) = 0.26, p \textless{} .001) For the burning ratings
we found No significant interaction (\(\beta\) = 0.10, p = 0.15) nor
main effect (\(\beta\) = -0.04, p = 0.39).

In contrast, when rating the warm thermode, participants reported
markedly enhanced burning sensations for TGI, but not non-TGI,
(stimulation by dermatome interaction: \(\beta\) = 0.21, p \textless{}
.001).However, we did not observe suvh a modulation of cold percepts
(\(\beta\) = 0.08, p = 0.28), with no main effect (\(\beta\) = 0.01, p =
0.83) for the warm thermosensory ratings we found no interaction
(\(\beta\) = 0.07, p = 0.16), and no main effect of dermatome (\(\beta\)
= -0.04, p = 0.28).

The findings suggest that the thermosensory quality of the reference
thermode (cold or warm) showed differential sensitivity to thermosensory
and painful aspects of the TGI experience, and collectively suggested
that both the thermosensory enhancement and illusory pain components of
the illusion are modulated at the spinal cord level. This interpretation
is consistent with a previous study using a similar dermatome
manipulation, but a distinct method to quantify TGI perception
(\protect\hyperlink{ref-fardo_organization_2018}{Fardo, Finnerup, and
Haggard 2018}), as well as another study showing modulation of heat and
pain ratings of TGI stimuli by conditioned pain modulation
(\protect\hyperlink{ref-harper_conditioned_2017}{Harper and Hollins
2017}). All together these results support the role of spinal processes
in the generation of distinct perceptual aspects of the TGI.

\hypertarget{undetected-proximodistal-bias-in-tgi}{%
\subsection{Undetected proximodistal bias in
TGI}\label{undetected-proximodistal-bias-in-tgi}}

Previous research demonstrated a phenomenon known as distal inhibition,
wherein heat pain ratings tend to increase when a participant evaluates
a more distal compared to a more proximal stimulus among two warm
stimuli presented on the forearm
(\protect\hyperlink{ref-quevedo_psychophysicshyperalgesia_2004}{A.
Quevedo and Coghill 2004};
\protect\hyperlink{ref-quevedo_illusion_2007}{A. S. Quevedo and Coghill
2007}). In our study, we sought to investigate whether this effect of
distal inhibition would also influence TGI perception within a single
dermatome (Fig. 3). We tested this effect with a two way interaction
between condition (control / TGI) and the location of the cold thermode
when it was placed within dermatome (distal / proximal). In the first
experiment with the cold thermode as the reference we found no
statistical significant interaction effect for the cold ratings
(\(\beta\) = -0.08, p = 0.3, however with a strong main effect of
dermatome (\(\beta\) = -0.18, p \textless{} .001) For the warm ratings
we found no interaction (\(\beta\) = 0.19, p = 0.14), nor main effect of
dermatome (\(\beta\) = -0.08, p = 0.44) For the burning ratings We found
no significant interaction (\(\beta\) = -0.09, p = 0.37), but a
significant main effect ( \(\beta\) = -0.17, p \textless{} .05 )

For the second experiment with the warm thermode as the reference we
found no interaction no interaction (\(\beta\) = -0.06, p = 0.49), nor
main effect (\(\beta\) = 0.00, p = 0.96) for the burning ratings. For
the warm ratings we found no interaction (\(\beta\) = 0.00, p = 0.96), ,
nor main effect of dermatome (\(\beta\) = -0.04, p = 0.42) and for the
cold ratings no interaction (\(\beta\) = 0.10, p = 0.34) but a main
effect (\(\beta\) = -0.18, p \textless{} .05 ).

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Difference in VAS ratings between the proximal and distal
dermatome conditions and the stimulation type (Non-TGI, TGI) for all VAS
rating types (Cold, warm, Burning). A, first experiment with the cold
thermode as the reference, and B with the warm thermode as referce.
Small points show data from each participant, large dots are means
across trials for each condition, and error bars show 95\% confidence
intervals.}
\end{figure}

\hypertarget{directional-effects-in-inter-segmental-sensory-integration}{%
\subsection{Directional effects in inter-segmental sensory
integration}\label{directional-effects-in-inter-segmental-sensory-integration}}

A main objective of this study was assessing spatial order effects along
the rostrocaudal axis at the spinal level. We delivered an equal number
of trials in which the cold stimulus was applied on a dermatome that
mapped more rostrally or caudally compared to the warm or neutral
stimuli. Like the previous analysis we investigated this relationship
with a two way interaction here with the rostral - caudal axis being
investigated.

Results showed no statistical significant interaction effect for the
cold ratings in the first experiment with the reference thermode being
cold (\(\beta\) = -0.10, p = 0.19, but a main effect (\(\beta\) = -0.15,
p \textless{} .01). For the warm ratings we found no statistically
significant effect for warm watings (\(\beta\) = 0.06, p = 0.65), but a
statistical significant main effect (\(\beta\) = 0.21, p \textless{} .05
) The burning ratings showed no significant interaction (\(\beta\) =
0.06, p = 0.54), nor main effect (\(\beta\) = -0.12, p = 0.11).

In Experiment 2, with the warm thermode as the reference we found no
significant interaction effect for the burning ratings (\(\beta\) =
-0.14, p = 0.1), but a significant main effect (\(\beta\) = 0.17, p
\textless{} .01) For the warm ratings we found no statistically
significant interaction (\(\beta\) = 0.01, p = 0.94), but a strong main
effect (\(\beta\) = 0.19, p \textless{} .001) For the cold ratings we
found a significant interaction (\(\beta\) = -0.23, p \textless{} .05 )

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Difference in VAS ratings between the Caudal and Rostral
dermatome conditions and the stimulation type (Non-TGI, TGI) for all VAS
rating types (Cold, warm, Burning). A, first experiment with the cold
thermode as the reference, and B with the warm thermode as referce.
Small points show data from each participant, large dots are means
across trials for each condition, and error bars show 95\% confidence
intervals.}
\end{figure}

The results indicated a notably enhanced TGI effect when the cold
stimulus induced more caudal activity within the spinal cord, as
depicted in Figure 3. These findings were consistent across both
experiments for thermosensory ratings, albeit with minor deviations that
corresponded with the particular stimulation quality being assessed. The
observed enhancement of warmth perception in Experiment 2 could be
ascribed to the participants' assessment of the warmer thermode as
opposed to the colder one of Experiment 1. For burning ratings,
significant results were seen in Experiment 2, but not in Experiment 1.
One possible reason for this discrepancy could be the relatively low
power in Experiment 1, as the power analysis was specifically focused on
thermosensory ratings. Alternatively, assessing the warmer thermode
might be a more accurate method for measuring TGI perception.

\hypertarget{spinal-organisation-and-tgi-perception}{%
\subsection{Spinal organisation and TGI
perception}\label{spinal-organisation-and-tgi-perception}}

The complexities of spinal neuroanatomy provide insightful perspectives
concerning the two main findings of these experiments: (1) enhanced heat
and burning sensations when cold-warm thermosensory integration takes
place more focally within the spinal cord, and (2) discernible
directional inter-segmental effects when distinct cold and warm stimuli
elicited broader activity along the spinal cord. Small primary
afferents, responsible for mediating temperature and pain sensations,
split into ascending and descending branches that cover one to two
segments before they enter the dorsal horn
(\protect\hyperlink{ref-kerr_neuroanatomical_1975}{Kerr 1975};
\protect\hyperlink{ref-lamotte_distribution_1977}{Lamotte 1977}). This
pattern forms the Lissauer's tract, a structure hypothesised to regulate
sensory transmission to the dorsal horn and influence spinal receptive
field size (\protect\hyperlink{ref-wall_brief_1999}{Wall, Lidierth, and
Hillman 1999}).

Additionally, the endings of small primary afferents within the
superficial laminae of the dorsal horn form synapses with both
propriospinal neurons and projection neurons that target supraspinal
structures known to significantly influence TGI perception
(\protect\hyperlink{ref-craig_functional_1996}{Craig et al. 1996};
\protect\hyperlink{ref-lindstedt_evidence_2011}{Lindstedt et al. 2011};
\protect\hyperlink{ref-leung_supraspinal_2014}{Leung et al. 2014} + any
other neuroimaging studies of the TGI).

Evidence from animal studies shows that propriospinal neurons, confined
within the spinal cord, exhibit bidirectional collateral branches along
the rostrocaudal plane
(\protect\hyperlink{ref-saywell_electrophysiological_2011}{Saywell et
al. 2011}; \protect\hyperlink{ref-skinner_ascending_1989}{Skinner et al.
1989}). These connections shape the network of interneurons that
modulates sensory information delivered to the dorsal horn
(\protect\hyperlink{ref-todd_neuronal_2010}{Todd 2010};
\protect\hyperlink{ref-peirs_neural_2016}{Peirs and Seal 2016}).

Our finding of enhanced TGI perception with cold-warm stimuli applied
within dermatomes might reflect the combined effects of the Lissauer's
tract's short rostrocaudal span (comprising one to two segments,
consistent with a single dermatome's boundary) and the characteristics
of spinal circuits. These circuits, created by propriospinal neurons,
may promote sensory integration within a spinal receptive field while
simultaneously inhibiting activity in adjacent fields. This mechanism
aligns with the concept of lateral inhibition, a ubiquitous process in
sensory processing seen across both the peripheral and central nervous
systems, and multiple sensory modalities, including thermoception and
nociception (\protect\hyperlink{ref-bekesy_lateral_1962}{Békésy 1962};
\protect\hyperlink{ref-quevedo_lateral_2017}{A. S. Quevedo et al. 2017};
\protect\hyperlink{ref-adamczyk_not_2021}{Adamczyk et al. 2021}).
Further, our observation that spatial factors, such as the more caudal
localisation of cold activity relative to warm activity in the spinal
cord, influences TGI perception, suggests possible neuroanatomical and
functional asymmetries. This could mean a greater number of ascending
fibres than descending fibres carrying thermosensory information in the
Lissauer's tract, an uneven distribution of ascending and descending
collaterals of propriospinal neurons (Anatomical Hypotheses), or varying
effects of inter-segmental inhibition along the rostrocaudal axis
(Functional Hypothesis). Additional research is needed to illuminate the
specific anatomical and functional features of the spinal cord that
resulted in the observed effects of this study.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Illusions in the thermo-nociceptive system can be leveraged to improve
our understanding of mechanisms contributing to pain perception. Here,
we presented results supporting the notion that the spinal cord plays a
crucial role in the integration and processing of thermal information,
contributing to the perception of both thermosensory enhancement and the
illusory pain within the TGI. Additionally, we reported findings on
directional inter-segmental effects in spinal integration underlying
TGI. Further research is needed to elucidate the neuroanatomical and
functional properties of the spinal cord, as well as the intricate
interplay between supraspinal and spinal processes, that give rise to
TGI perception.

\newpage

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

The study entailed two separate experiments, collectively involving 80
healthy volunteers. The sample consisted of 27 females and 13 males,
mean age = 25.38 years old (SD = 4.67, range = 18 - 36) in Experiment 1,
and 25 females and 14 males and 1 non-binary (Female at birth), mean age
= 25.73 years old (SD = 4.12, range = 21 - 39), in Experiment 2. The
research methodology complied with the principles set forth in the
Declaration of Helsinki and received ethical approval from the
Institutional Review Board (IRB) at the Danish Neuroscience Center,
Aarhus University, Denmark. Prior to commencing the study, all
participants were fully informed about the procedures and provided their
voluntary consent.

\hypertarget{stimuli-and-procedure}{%
\subsection{Stimuli and procedure}\label{stimuli-and-procedure}}

All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity
Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3
software (version 5.4b). The procedure involved measurements of heat and
cold pain thresholds, calibration of cold-warm temperature pairs
eliciting TGI, and an experimental task where TGI and non-TGI stimuli
were applied on dermatomes that mapped onto adjacent or non-adjacent
spinal segments. To measure cold and heat pain thresholds, we gradually
adjusted the temperature of one thermode until the participant indicated
an experience of pain by pressing a stop button or reached the maximum
temperature cut-offs of 5ºC or 50ºC. We calibrated TGI stimuli by
identifying a cold-warm temperature pair based on specific criteria: (1)
consistently eliciting a burning sensation of at least 15 on a scale
ranging from 0 to 100, (2) consistently avoiding a burning sensation
(less than 15) when the cold-neutral (Exp. 1) or warm-neutral (Exp. 2)
stimuli were presented, (3) both cold and warm temperatures falling
within the innocuous range based on individual cold and heat pain
thresholds. For pain threshold measurements and TGI calibration, we
positioned the probes within a single dermatome. To address our
experimental questions, we presented the calibrated TGI stimuli, as well
as cold-neutral (Exp. 1) or warm-neutral (Exp. 2) non-TGI stimuli using
two thermodes. In non-TGI stimuli the cold or warm temperatures were set
to match the temperature used for TGI stimulation, but paired with a
neutral temperature set at 30ºC. The two thermodes were positioned on
the internal surface of either forearm, with a constant spacing value
between 4 and 5 cm in each direction, depending on the participant's
forearm size. The positioning of the thermodes was either within the
same dermatome (i.e., C6 and T1) or across dermatomes mapped onto
non-adjacent spinal segments (i.e.~C6 - T1). Further, we manipulated the
spatial arrangement of the temperature pairs, by systematically
presenting an equal number of trials where the cold thermode was applied
on a proximal or distal location within a dermatome, or was applied on a
dermatome that mapped onto a rostral or caudal segment along the spinal
cord. We based the demarcation of the dermatome boundaries on the
American Spinal Injury Association (ASIA) map (Fardo et al., 2018) and
positioned the thermodes in relation to standard anatomical landmarks.
Proximo-distal coordinates referred to locations on the skin closer to
the elbow or the wrist, whereas rostral-caudal coordinates referred to
spinal segments closer to the head or the lower back. The possible
spatial arrangements corresponded to the four conditions depicted in
Figure 1. The order of the stimuli (TGI vs.~non-TGI), the dermatome
condition (within vs.~across) and the relative placement of the colder
temperature (proximal vs.~distal or rostral vs.~caudal) were
pseudo-randomised and counterbalanced between participants. During each
trial, the experimenter positioned two thermodes, mounted on a stand
using two independent clamps, on the participant's skin for 10 seconds.
An auditory cue (300Hz, 100ms) indicated the end of the stimulation
period, after which the experimenter removed the thermodes from the
participant's skin. Participants then rated the most intense cold, warm
or burning sensation they perceived during the stimulation period using
three separated computerised VAS scales. VAS scales were presented one
at a time on a computer screen and appeared as a horizontal line,
anchored at 0, representing no sensation (e.g., no burning), and 100,
signifying an extreme sensation (e.g., extreme burning). The order of
the three VAS scales was randomised across trials. For each scale,
participants provided their responses using the arrow keys on a keyboard
and rated the intensity of their sensations from a specific location
(labeled `A' or `B'), based on the experimenter's instruction. Unbeknown
to the participant, this location systematically corresponded to either
the colder temperature (Exp. 1) or the warmer temperature (Exp. 2).
Participants had max 8 seconds to provide each rating, and if they did
not complete a rating within the allowed timeframe, the trial was
repeated. Following the completion of the last of the three VAS ratings,
we presented a 200 ms fixation dot. Each thermode configuration was
tested three consecutive times, on three different skin locations. An
auditory tone of 500Hz lasting 100ms was played to indicate to the
experimenter when to rearrange the thermode configuration to stimulate
different dermatomes depending on a pseudo-randomisation order. Each of
the four experimental conditions was repeated 12 times, with both the
right and left forearms stimulated, and a minimum of five trials between
the re-stimulation of the same skin location. This ensured that the same
skin locations were not stimulated consecutively to minimise carry-over
effects. Experiments 1 and 2 were conducted in two independent groups of
participants and followed exactly the same procedure except for two
elements. In Experiment 1, participants rated the sensations localised
underneath the colder thermode, and the non-TGI stimuli corresponded to
cold-neutral pairs. In Experiment 2, participants rated the sensations
localised underneath the warmer thermode, and the non-TGI stimuli
corresponded to warm-neutral pairs.

\hypertarget{sample-size}{%
\subsection{Sample size}\label{sample-size}}

An initial pilot study informed the pre-registered calculation of the
sample size. To test the directional TGI hypothesis with 95\% power and
detect an effect size of .12 or greater, we determined that we needed a
minimum number of 32 TGI-responsive participants. We defined
TGI-responders as those individuals for whom the median burning ratings
for TGI stimuli significantly exceeded 0. Non-responders were
individuals that did not meet this criterion when tested with the max
cold-warm temperatures allowed in the experiment. The predefined cut-off
for TGI stimulation was (xx-xx). In Experiment 1, recruitment continued
until we achieved the target of 32 TGI-responsive participants. We
verified this criterion every 10 participants, resulting in a total
sample size of 40 participants. In Experiment 2, we stopped recruitment
once we collected data from 40 participants. This decision was based on
meeting both required criteria: (1) matching the sample size of Exp. 1
for consistency, and (2) achieving the minimum requirement of 32
TGI-responsive participants as determined by the power analysis.

\hypertarget{data-analyses}{%
\subsection{Data analyses}\label{data-analyses}}

We re-scaled data from cold, warm and burning VAS ratings from their
original values to a range of 0 to 1. Following re-scaling, we applied
zero-inflated mixed-effects beta regression models separately for each
set of VAS ratings. In these models, we incorporated three fixed
effects. These included the type of stimulation (non-TGI vs.~TGI), the
dermatome condition (within the same dermatome vs.~across different
dermatomes) and the spatial positioning of the cold or neutral thermode
(proximal vs.~distal within dermatomes; rostral vs.~caudal across
dermatomes). These choices allowed us to assess the individual and
interactive effects of these three factors on VAS ratings. Further, we
added random intercepts to our models to account for between-subject
variability and the effects of repeated measures. The variables
introduced as random intercepts included the participant ID, the
counterbalancing order and the trial number. The choices of the
zero-inflated approach and the use of beta regressions were necessitated
by the specific distribution of VAS ratings. The beta distribution is
suitable for modelling VAS rating data, as they are proportional in
nature. Additionally, the zero-inflation was needed due to the presence
of an excess number of zero values in specific ratings and conditions.
Specifically, we anticipated an overrepresentation of zero values for
thermosensory ratings that were counterfactual to the objective
stimulation quality (i.e., cold ratings of warm stimuli and warm ratings
of cold stimuli) and burning ratings of non-TGI stimuli. The latter
stimuli were designed to not elicit an illusion or trigger a weaker
illusion as compared to the TGI stimuli. We carried out the statistical
analyses using the `glmmTMB' package in R (version 1.1.7), and
statistical significance was set at p \textless{} .05. The experimental
procedure, power analyses to determine sample size and statistical
approach were preregistered for both
\href{https://osf.io/4xcn5/}{Experiment 1} and
\href{https://osf.io/dhg8u/}{Experiment 2}. All data and code for the
analysis are available in the
\href{https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript}{github
repository}, ensuring the reproducibility of our findings.

\newpage

\hypertarget{authors-contributions}{%
\section{Authors contributions}\label{authors-contributions}}

Author contributions listed alphabetically according to
\href{https://credit.niso.org}{CRediT taxonomy}:

\begin{itemize}
\tightlist
\item
  Conceptualization: DEC, JFE, FF, PH, AGM.
\item
  Data curation: JEF, AGM.
\item
  Formal analysis: JFE, FF, AGM.
\item
  Funding acquisition: FF.
\item
  Investigation: DEC, JFE, AGM.
\item
  Methodology: DEC, JFE, FF, AGM, AVS.
\item
  Project administration: FF, AGM.
\item
  Resources: FF, AGM.
\item
  Software: JFE, FF, AGM.
\item
  Supervision: FF, AGM.
\item
  Visualization: FF, AGM.
\item
  Writing -- original draft: FF, AGM.
\item
  Writing -- review \& editing: FF, AGM. (+ others who will provide
  feedback)
\end{itemize}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We would like to thank XXX for their help with participant recruitment
and data collection. This study was supported by a European Research
Council Starting Grant (ERC-2020-StG-948788).

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-adam_relationships_2014}{}}%
Adam, Frédéric, Pascal Alfonsi, Delphine Kern, and Didier Bouhassira.
2014. {``Relationships Between the Paradoxical Painful and Nonpainful
Sensations Induced by a Thermal Grill.''} \emph{PAIN} 155 (12): 2612.
\url{https://doi.org/10.1016/j.pain.2014.09.026}.

\leavevmode\vadjust pre{\hypertarget{ref-adamczyk_not_2021}{}}%
Adamczyk, Wacław M., Tibor M. Szikszay, Tiffany Kung, Gabriela F.
Carvalho, and Kerstin Luedtke. 2021. {``Not as "Blurred" as Expected?
{Acuity} and Spatial Summation in the Pain System.''} \emph{PAIN} 162
(3): 794--802. \url{https://doi.org/10.1097/j.pain.0000000000002069}.

\leavevmode\vadjust pre{\hypertarget{ref-bach_thermal_2011}{}}%
Bach, Patrick, Susanne Becker, Dieter Kleinböhl, and Rupert Hölzl. 2011.
{``The Thermal Grill Illusion and What Is Painful about It.''}
\emph{Neuroscience Letters} 505 (1): 31--35.
\url{https://doi.org/10.1016/j.neulet.2011.09.061}.

\leavevmode\vadjust pre{\hypertarget{ref-bekesy_lateral_1962}{}}%
Békésy, G. V. 1962. {``Lateral Inhibition of Heat Sensations on the
Skin.''} \emph{Journal of Applied Physiology} 17 (6): 1003--8.
\url{https://doi.org/10.1152/jappl.1962.17.6.1003}.

\leavevmode\vadjust pre{\hypertarget{ref-bouhassira_investigation_2005}{}}%
Bouhassira, Didier, Delphine Kern, Jean Rouaud, Emilie Pelle-Lancien,
and Françoise Morain. 2005. {``Investigation of the Paradoxical Painful
Sensation ({`Illusion of Pain'}) Produced by a Thermal Grill.''}
\emph{PAIN} 114 (1): 160.
\url{https://doi.org/10.1016/j.pain.2004.12.014}.

\leavevmode\vadjust pre{\hypertarget{ref-craig_new_1998}{}}%
Craig, A. D. 1998. {``A New Version of the Thalamic Disinhibition
Hypothesis of Central Pain.''} \emph{Pain Forum} 7 (1): 1--14.
\url{https://doi.org/10.1016/S1082-3174(98)70004-2}.

\leavevmode\vadjust pre{\hypertarget{ref-craig_thermal_1994}{}}%
Craig, A. D., and M. C. Bushnell. 1994. {``The Thermal Grill Illusion:
Unmasking the Burn of Cold Pain.''} \emph{Science} 265 (5169): 252--55.
\url{https://doi.org/10.1126/science.8023144}.

\leavevmode\vadjust pre{\hypertarget{ref-craig_functional_1996}{}}%
Craig, A. D., E. M. Reiman, A. Evans, and M. C. Bushnell. 1996.
{``Functional Imaging of an Illusion of Pain.''} \emph{Nature} 384
(6606): 258--60. \url{https://doi.org/10.1038/384258a0}.

\leavevmode\vadjust pre{\hypertarget{ref-defrin_spatial_2008}{}}%
Defrin, Ruth, Anat Benstein-Sheraizin, Adva Bezalel, Ofira Mantzur, and
Lars Arendt-Nielsen. 2008. {``The Spatial Characteristics of the Painful
Thermal Grill Illusion.''} \emph{PAIN} 138 (3): 577.
\url{https://doi.org/10.1016/j.pain.2008.02.012}.

\leavevmode\vadjust pre{\hypertarget{ref-fardo_beyond_2020}{}}%
Fardo, Francesca, Brianna Beck, Micah Allen, and Nanna Brix Finnerup.
2020. {``Beyond Labeled Lines: {A} Population Coding Account of the
Thermal Grill Illusion.''} \emph{Neuroscience and Biobehavioral Reviews}
108 (January): 472--79.
\url{https://doi.org/10.1016/j.neubiorev.2019.11.017}.

\leavevmode\vadjust pre{\hypertarget{ref-fardo_organization_2018}{}}%
Fardo, Francesca, Nanna Brix Finnerup, and Patrick Haggard. 2018.
{``Organization of the Thermal Grill Illusion by Spinal Segments.''}
\emph{Annals of Neurology} 84 (3): 463--72.
\url{https://doi.org/10.1002/ana.25307}.

\leavevmode\vadjust pre{\hypertarget{ref-ferre_ineffectiveness_2018}{}}%
Ferrè, E. R., G. D. Iannetti, J. A. van Dijk, and P. Haggard. 2018.
{``Ineffectiveness of Tactile Gating Shows Cortical Basis of Nociceptive
Signaling in the {Thermal} {Grill} {Illusion}.''} \emph{Scientific
Reports} 8 (April): 6584.
\url{https://doi.org/10.1038/s41598-018-24635-1}.

\leavevmode\vadjust pre{\hypertarget{ref-fruhstorfer_significance_2003}{}}%
Fruhstorfer, Heinrich, Eva-Liz Harju, and Ulf F. Lindblom. 2003. {``The
Significance of {A}-Delta and {C} Fibres for the Perception of Synthetic
Heat.''} \emph{European Journal of Pain} 7 (1): 63--71.
\url{https://doi.org/10.1016/s1090-3801(02)00056-3}.

\leavevmode\vadjust pre{\hypertarget{ref-green_localization_1977}{}}%
Green, Barry G. 1977. {``Localization of Thermal Sensation: {An}
Illusion and Synthetic Heat.''} \emph{Perception \& Psychophysics} 22
(4): 331--37. \url{https://doi.org/10.3758/BF03199698}.

\leavevmode\vadjust pre{\hypertarget{ref-green_synthetic_2002}{}}%
---------. 2002. {``Synthetic Heat at Mild Temperatures.''}
\emph{Somatosensory \& Motor Research} 19 (2): 130--38.
\url{https://doi.org/10.1080/08990220220220131524}.

\leavevmode\vadjust pre{\hypertarget{ref-green_temperature_2004}{}}%
---------. 2004. {``Temperature Perception and Nociception.''}
\emph{Journal of Neurobiology} 61 (1): 13--29.
\url{https://doi.org/10.1002/neu.20081}.

\leavevmode\vadjust pre{\hypertarget{ref-harper_conditioned_2017}{}}%
Harper, D. E., and M. Hollins. 2017. {``Conditioned Pain Modulation
Dampens the Thermal Grill Illusion.''} \emph{European Journal of Pain}
21 (9): 1591--601. \url{https://doi.org/10.1002/ejp.1060}.

\leavevmode\vadjust pre{\hypertarget{ref-kern_pharmacological_2008}{}}%
Kern, Delphine, Emilie Pelle-lancien, Virginie Luce, and Didier
Bouhassira. 2008. {``Pharmacological Dissection of the Paradoxical Pain
Induced by a Thermal Grill.''} \emph{PAIN} 135 (3): 291.
\url{https://doi.org/10.1016/j.pain.2007.12.001}.

\leavevmode\vadjust pre{\hypertarget{ref-kern_effects_2008}{}}%
Kern, Delphine, Frédéric Plantevin, and Didier Bouhassira. 2008.
{``Effects of Morphine on the Experimental Illusion of Pain Produced by
a Thermal Grill.''} \emph{PAIN} 139 (3): 653.
\url{https://doi.org/10.1016/j.pain.2008.07.001}.

\leavevmode\vadjust pre{\hypertarget{ref-kerr_neuroanatomical_1975}{}}%
Kerr, Frederick W. L. 1975. {``Neuroanatomical Substrates of Nociception
in the Spinal Cord.''} \emph{PAIN} 1 (4): 325.
\url{https://doi.org/10.1016/0304-3959(75)90072-X}.

\leavevmode\vadjust pre{\hypertarget{ref-lamotte_distribution_1977}{}}%
Lamotte, Carole. 1977. {``Distribution of the Tract of Lissauer and the
Dorsal Root Fibers in the Primate Spinal Cord.''} \emph{Journal of
Comparative Neurology} 172 (3): 529--61.
\url{https://doi.org/10.1002/cne.901720308}.

\leavevmode\vadjust pre{\hypertarget{ref-leung_supraspinal_2014}{}}%
Leung, Albert, Shivshil Shukla, Eric Li, Jeng-Ren Duann, and Tony Yaksh.
2014. {``Supraspinal {Characterization} of the {Thermal} {Grill}
{Illusion} with {fMRI}.''} \emph{Molecular Pain} 10 (January):
1744-8069-10-18. \url{https://doi.org/10.1186/1744-8069-10-18}.

\leavevmode\vadjust pre{\hypertarget{ref-lindstedt_evidence_2011}{}}%
Lindstedt, Fredrik, Bo Johansson, Sofia Martinsen, Eva Kosek, Peter
Fransson, and Martin Ingvar. 2011. {``Evidence for Thalamic Involvement
in the Thermal Grill Illusion: An {FMRI} Study.''} \emph{PloS One} 6
(11): e27075. \url{https://doi.org/10.1371/journal.pone.0027075}.

\leavevmode\vadjust pre{\hypertarget{ref-marotta_transforming_2015}{}}%
Marotta, Angela, Elisa Raffaella Ferrè, and Patrick Haggard. 2015.
{``Transforming the {Thermal} {Grill} {Effect} by {Crossing} the
{Fingers}.''} \emph{Current Biology} 25 (8): 1069--73.
\url{https://doi.org/10.1016/j.cub.2015.02.055}.

\leavevmode\vadjust pre{\hypertarget{ref-peirs_neural_2016}{}}%
Peirs, Cedric, and Rebecca P. Seal. 2016. {``Neural Circuits for Pain:
{Recent} Advances and Current Views.''} \emph{Science} 354 (6312):
578--84. \url{https://doi.org/10.1126/science.aaf8933}.

\leavevmode\vadjust pre{\hypertarget{ref-quevedo_psychophysicshyperalgesia_2004}{}}%
Quevedo, A., and R. Coghill. 2004. {``Psychophysics/Hyperalgesia:
{Spatial} Interactions Between Multiple Painful Stimuli.''} \emph{The
Journal of Pain} 5 (3): S32.
\url{https://doi.org/10.1016/j.jpain.2004.02.094}.

\leavevmode\vadjust pre{\hypertarget{ref-quevedo_illusion_2007}{}}%
Quevedo, Alexandre S., and Robert C. Coghill. 2007. {``An {Illusion} of
{Proximal} {Radiation} of {Pain} {Due} to {Distally} {Directed}
{Inhibition}.''} \emph{The Journal of Pain} 8 (3): 280--86.
\url{https://doi.org/10.1016/j.jpain.2006.09.003}.

\leavevmode\vadjust pre{\hypertarget{ref-quevedo_lateral_2017}{}}%
Quevedo, Alexandre S., Carsten Dahl Mørch, Ole K. Andersen, and Robert
C. Coghill. 2017. {``Lateral Inhibition During Nociceptive
Processing.''} \emph{PAIN} 158 (6): 1046.
\url{https://doi.org/10.1097/j.pain.0000000000000876}.

\leavevmode\vadjust pre{\hypertarget{ref-saywell_electrophysiological_2011}{}}%
Saywell, S. A., T. W. Ford, C. F. Meehan, A. J. Todd, and P. A.
Kirkwood. 2011. {``Electrophysiological and {Morphological}
{Characterization} of {Propriospinal} {Interneurons} in the {Thoracic}
{Spinal} {Cord}.''} \emph{Journal of Neurophysiology} 105 (2): 806--26.
\url{https://doi.org/10.1152/jn.00738.2010}.

\leavevmode\vadjust pre{\hypertarget{ref-skinner_ascending_1989}{}}%
Skinner, R. D., R. Nelson, M. Griebel, and E. Garcia-Rill. 1989.
{``Ascending Projections of Long Descending Propriospinal Tract ({LDPT})
Neurons.''} \emph{Brain Research Bulletin} 22 (2): 253--58.
\url{https://doi.org/10.1016/0361-9230(89)90050-6}.

\leavevmode\vadjust pre{\hypertarget{ref-todd_neuronal_2010}{}}%
Todd, Andrew J. 2010. {``Neuronal Circuitry for Pain Processing in the
Dorsal Horn.''} \emph{Nature Reviews Neuroscience} 11 (12): 823--36.
\url{https://doi.org/10.1038/nrn2947}.

\leavevmode\vadjust pre{\hypertarget{ref-wall_brief_1999}{}}%
Wall, Patrick D., Malcolm Lidierth, and Peter Hillman. 1999. {``Brief
and Prolonged Effects of {Lissauer} Tract Stimulation on Dorsal Horn
Cells.''} \emph{PAIN} 83 (3): 579--89.
\url{https://doi.org/10.1016/S0304-3959(99)00170-0}.

\end{CSLReferences}

\newpage

\hypertarget{supplementary-material}{%
\section{Supplementary material}\label{supplementary-material}}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{2.50in}|p{1.10in}|p{1.10in}|p{1.10in}|p{1.10in}}

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Cold\ reference\ on\ cold\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Cold\ reference\ on\ cold\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Intercept}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.88}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.17}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-5.2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{2.5e-07}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.19}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.027}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ -7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.9e-12}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Within-Across}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.037}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ -4}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{6e-05}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.052}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-2.9}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0038}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.18}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.053}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-3.3}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00094}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Trial}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0074}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00099}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{7.5}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{6.3e-14}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Within-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.054}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-2.7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.007}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.099}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.075}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.3}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.19}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.082}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.079}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ -1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.3}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{2.50in}|p{1.10in}|p{1.10in}|p{1.10in}|p{1.10in}}

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Cold\ reference\ on\ warm\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Cold\ reference\ on\ warm\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Intercept}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ -2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.12}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-17}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{4.5e-63}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.74}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.048}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ 15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.1e-53}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Within-Across}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.26}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.075}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.5}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00053}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.21}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.11}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ 2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.048}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.078}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.78}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.44}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Trial}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0018}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0016}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.26}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Within-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.026}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.092}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.29}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.77}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.062}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.14}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.46}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.65}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.19}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.13}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.5}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.14}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{2.50in}|p{1.10in}|p{1.10in}|p{1.10in}|p{1.10in}}

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Cold\ reference\ on\ burning\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Cold\ reference\ on\ burning\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Intercept}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.4}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.16}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-8.6}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{6.8e-18}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.39}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.035}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ 11}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{4.5e-29}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Within-Across}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.044}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.051}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.86}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.39}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.12}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.072}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.6}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.11}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.17}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.073}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-2.3}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.021}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Trial}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0046}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0013}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00021}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Within-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.069}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.5}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.15}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.06}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.097}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.61}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.54}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.087}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.098}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.89}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.37}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{2.50in}|p{1.10in}|p{1.10in}|p{1.10in}|p{1.10in}}

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Warm\ reference\ on\ cold\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Warm\ reference\ on\ cold\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Intercept}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-2.2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{4.6e-50}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.046}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ 23}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.9e-115}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Within-Across}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.013}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.063}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.22}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.83}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.01}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.089}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.11}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.91}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.18}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.088}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ -2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.044}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Trial}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0099}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0013}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{7.6}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.8e-14}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Within-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.082}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.076}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.28}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.23}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.11}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-2.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.033}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.11}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.96}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.34}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{2.50in}|p{1.10in}|p{1.10in}|p{1.10in}|p{1.10in}}

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Warm\ reference\ on\ warm\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Warm\ reference\ on\ warm\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Intercept}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.52}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.15}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-3.4}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00059}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.035}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.029}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.23}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Within-Across}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.039}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.036}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.1}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.28}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.19}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.051}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00018}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.042}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.051}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.81}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.42}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Trial}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0037}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00094}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.9}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{9.1e-05}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Within-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.074}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.052}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{1.4}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.16}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.006}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.073}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.081}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.94}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0035}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.074}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.047}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.96}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{2.50in}|p{1.10in}|p{1.10in}|p{1.10in}|p{1.10in}}

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Warm\ reference\ on\ burning\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Warm\ reference\ on\ burning\ ratings}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{5}{>{\centering}m{\dimexpr 6.9in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{beta\textasciitilde manipulation\ *\ cold\_probe\ +\ trial\_n\ +\ (1\ |\ ID)\ +\ (1\ |\ order),\ family\ =\ beta(link\ =\ logit)}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ }}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{β}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{SE}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Z}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{p}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Intercept}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.2}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.17}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ -7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{2.7e-12}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.37}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.034}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ 11}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{4.5e-27}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Within-Across}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.068}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.043}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.6}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.11}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.17}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.061}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{2.8}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0054}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.003}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.062}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.049}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.96}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{Trial}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0075}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.0011}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{\ \ 7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.2e-12}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Within-CNT}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.21}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.059}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{3.6}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.00036}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Caudal-Rostral}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.14}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.084}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-1.7}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.096}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{TGI-CNT\ *\ Proximal-Distal}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.058}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.084}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{-0.69}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\global\setmainfont{Times New Roman}{0.49}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{document}

### 2023-07-31 Manuscript.Rmd
frontpage

@@
 
-Corresponding authors: Alexandra G. Mitchell (agmitchell@cfin.au.dk) and Francesca Fardo (francesca@cfin.au.dk)
+Corresponding authors: Alexandra G. Mitchell ([agmitchell\@cfin.au.dk](mailto:agmitchell@cfin.au.dk){.email}) and Francesca Fardo ([francesca\@cfin.au.dk](mailto:francesca@cfin.au.dk){.email})
 
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Four experimental conditions depicting an exemplar cold and warm thermode placement within and across dermatomes.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1) Four experimental conditions depicting an exemplar cold and warm thermode placement within and across dermatomes.
 Within dermatomes, the relative location of the cold thermode was proximal or distal.
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = " Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2) Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
 Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the proximal and distal dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3) Difference in VAS ratings between the proximal and distal dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
 A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce.
@@
 Results showed no statistical significant interaction effect for the cold ratings in the first experiment with the reference thermode being cold ($\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`, but a main effect ($\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`).
-For the warm ratings we found no statistically significant effect for warm watings ($\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`), but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`)
-The burning ratings showed no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`), nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
+For the warm ratings we found no statistically significant effect for warm watings ($\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`), but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`) The burning ratings showed no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`), nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
 
-In Experiment 2, with the warm thermode as the reference we found no significant interaction effect for the burning ratings ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`)
-For the warm ratings we found no statistically significant interaction ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`), but a strong main effect ($\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`)
-For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
+In Experiment 2, with the warm thermode as the reference we found no significant interaction effect for the burning ratings ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`) For the warm ratings we found no statistically significant interaction ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`), but a strong main effect ($\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`) For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the Caudal and Rostral dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4) Difference in VAS ratings between the Caudal and Rostral dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
 A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce.

### 2023-08-01 Manuscript.Rmd
edits in results section 1 (within vs. across)

@@
 
+\newpage
+
 # Abstract
@@
 
-The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008, @fardo_beyond_2020].
-The illusion of heat, also known as synthetic heat [@fruhstorfer_significance_2003; @green_localization_1977; -@green_synthetic_2002; -@green_temperature_2004], refers to non-painful sensations evoked by the thermal grill [@defrin_spatial_2008; @kern_pharmacological_2008; -@kern_effects_2008; @bouhassira_investigation_2005; @adam_relationships_2014].
+The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008; @fardo_beyond_2020].
+The illusion of heat, also known as synthetic heat [@fruhstorfer_significance_2003; @green_localization_1977; -@green_synthetic_2002; -@green_temperature_2004], refers to non-painful heat sensations evoked by the thermal grill [@defrin_spatial_2008; @kern_pharmacological_2008; -@kern_effects_2008; @bouhassira_investigation_2005; @adam_relationships_2014].
 The illusion of pain, which is the most recognised aspect of the TGI, is the distinctive burning sensation that accompanies the simultaneous presentation of cold and warm stimuli [@craig_thermal_1994; -@craig_functional_1996; @bach_thermal_2011].
@@
 These studies demonstrated that the illusion varied depending on whether cold and warm stimuli were applied to dermatomes mapped either onto adjacent or non-adjacent spinal segments [@fardo_organization_2018].
-Participants perceived the stimulation more veridically, consistently with a reduction in TGI perception, when warm or cold stimuli triggered more widespread activity along the spinal cord, corroborating the hypothesis that the spinal cord is an initial site of thermosensory integration underlying TGI.
+Participants perceived the stimulation more veridically, consistently with a reduction in TGI perception, when warm or cold stimuli mapped on segmental locations that were apart along the spinal cord, corroborating the hypothesis that the spinal cord is an initial site of thermosensory integration underlying TGI.
 Further support for spinal mechanisms comes from research demonstrating that both noxious heat and the TGI were comparably reduced by conditioned pain modulation in humans.
-This suggests a similar influence of descending modulation, irrespective of whether the painful sensation was triggered by potentially harmful (noxious) or harmless (innocuous) stimuli [@harper_conditioned_2017].
+This suggests a similar influence of descending modulation, irrespective of whether the painful sensation was triggered by potentially harmful (noxious) or harmless (TGI) stimuli [@harper_conditioned_2017].
 These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain.
@@
 Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes.
-Cold and warm stimuli were presented at a fixed distance on the skin, but depending on their longitudinal or tangential orientation on the arm, they elicited neural activity in a differing number of spinal segments.
-Our assumption was that cold and warm-related neural activity in the spinal cord was more focal, when the stimuli were presented within the same dermatome, while more widespread, when the stimuli mapped on non-adjacent spinal segments.
+Cold and warm stimuli were presented at a fixed distance on the skin, but depending on their longitudinal or tangential orientation on the arm, they elicited differing neural activity in the spinal cord.
+Our assumption was that cold and warm-related neural activity in the spinal cord was more focal (i.e., within the same spinal segments or within a few adjacent segments), when the stimuli were presented within the same dermatome, while more widespread, when the stimuli mapped on non-adjacent spinal segments (i.e., possibly 2 to 4 segments apart).
 Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and painful components.
@@
 At the spinal level, we used segment-related coordinates to define more rostral (towards the head) and more caudal (towards the lower back) locations.
-Given the organisation of the spinal cord along a rostral-caudal axis, where each dermatome is represented across multiple spinal segments through the Lissauer tract, this study aimed to glean indirect insights into the spinal mechanisms underpinning thermosensory integration and the generation of the TGI.
+Given the organisation of the spinal cord along a rostral-caudal axis, where each dermatome is represented across multiple spinal segments through the Lissauer tract [@kerr_neuroanatomical_1975; @lamotte_distribution_1977; @wall_brief_1999], this study aimed to glean indirect insights into the spinal mechanisms underpinning thermosensory integration and the generation of the TGI.
 
@@
 Thus, indicators of a stronger TGI are reduced cold ratings, coupled with heightened warm and burning ratings.
+
 To investigate thermosensory and burning components of the TGI, participants received pairs of temperatures on their forearms and were asked to quantify the levels of cold, warmth, and burning they experienced during each stimulation.
@@
 For each instance of stimulation, participants were guided to focus their reporting on the sensations originating from a specific thermode.
-While the participants were unaware, this location corresponded to either the colder stimulus (Exp. 1) or the warmer stimulus (Exp. 2) of the paired temperatures.
+While the participants were unaware, this location corresponded to either the colder stimulus (Exp.
+1) or the warmer stimulus (Exp.
+2) of the paired temperatures.
 VAS ratings were analysed using zero-inflated beta regressions.
@@
 plot1(include_zero = F)
-
 #plot1(include_zero = T)
@@
 2).
+When rating the cold thermode (Exp.
+1, Fig.
+2A), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
+Further, participants rated both TGI and non-TGI stimuli as warmer within vs across dermatome (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`).
+Finally, participants reported no significant modulation of burning ratings depending on the dermatome condition (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
+Overall, these results indicated that when participants assessed the cold thermode, the greatest modulation in TGI perception was related to cold perception, with within-dermatome TGI stimuli perceived as the least cold.
 
-When rating the cold thermode (Exp.
-1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
-This interaction was not present for for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`), but we did find a strong main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`) For the burning ratings we found No significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`) nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
-
-In contrast, when rating the warm thermode, participants reported markedly enhanced burning sensations for TGI, but not non-TGI, (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).However, we did not observe suvh a modulation of cold percepts ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`), with no main effect ($\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) for the warm thermosensory ratings we found no interaction ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`), and no main effect of dermatome ($\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`).
+When rating the warm thermode (Exp.
+2, Fig.
+2B), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
+However, we did not observe modulation of cold (stimulation by dermatome interaction: n$\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) or warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`) according to the within-across dermatome manipulation.
+Overall, these results indicated that when participants assessed the warm thermode, the greatest modulation in TGI perception was related to burning sensations, with within-dermatome TGI stimuli perceived as the most burning.
 
@@
 This interpretation is consistent with a previous study using a similar dermatome manipulation, but a distinct method to quantify TGI perception [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
-All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI.
+All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI, and highlight the importance of the reference stimulus when assessing TGI perception.
 

### 2023-08-02 Manuscript.Rmd
edits: prosimodistal bias

@@
 For each instance of stimulation, participants were guided to focus their reporting on the sensations originating from a specific thermode.
-While the participants were unaware, this location corresponded to either the colder stimulus (Exp.
-1) or the warmer stimulus (Exp.
-2) of the paired temperatures.
+While the participants were unaware, this location corresponded to either the colder stimulus (Exp. 1) or the warmer stimulus (Exp. 2) of the paired temperatures.
 VAS ratings were analysed using zero-inflated beta regressions.
@@
 
-In keeping with the unique heat and burning features of TGI, our results exhibited a more robust TGI when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments (Fig.
-2).
+In keeping with the unique heat and burning features of TGI, our results exhibited a more robust TGI when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments.
 When rating the cold thermode (Exp.
 1, Fig.
-2A), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
-Further, participants rated both TGI and non-TGI stimuli as warmer within vs across dermatome (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`).
-Finally, participants reported no significant modulation of burning ratings depending on the dermatome condition (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
+2A), participants reported a reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`), alongside an increased subjective experience of warmth for both TGI and non-TGI stimuli (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`).
+Further, participants reported no significant modulation of burning ratings depending on the dermatome condition (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
 Overall, these results indicated that when participants assessed the cold thermode, the greatest modulation in TGI perception was related to cold perception, with within-dermatome TGI stimuli perceived as the least cold.
+While the modulation of cold perception was specific for TGI, increased warmth was reported irrespective of whether the cold thermode was paired with a warm (TGI stimuli) or neutral temperature (non-TGI stimuli) within a dermatome.
+These findings are in line with the notion that TGI can be considered a misperception of cold [@fardo_organization_2018; @fardo_beyond_2020].
 
@@
 
-The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both the thermosensory enhancement and illusory pain components of the illusion are modulated at the spinal cord level.
+The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both qualitative components of the illusion are modulated at the spinal cord level.
 This interpretation is consistent with a previous study using a similar dermatome manipulation, but a distinct method to quantify TGI perception [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
-All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI, and highlight the importance of the reference stimulus when assessing TGI perception.
+All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI, and highlight the importance of the reference stimulus when assessing thermosensory and burning components of TGI perception.
 
-## Undetected proximodistal bias in TGI
+## Proximodistal bias in cold perception
 
-Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two warm stimuli presented on the forearm [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
-In our study, we sought to investigate whether this effect of distal inhibition would also influence TGI perception within a single dermatome (Fig. 3).
-We tested this effect with a two way interaction between condition (control / TGI) and the location of the cold thermode when it was placed within dermatome (distal / proximal).
-In the first experiment with the cold thermode as the reference we found no statistical significant interaction effect for the cold ratings ($\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`, however with a strong main effect of dermatome ($\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) For the warm ratings we found no interaction ($\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`), nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`) For the burning ratings We found no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`), but a significant main effect ( $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
-
-For the second experiment with the warm thermode as the reference we found no interaction no interaction ($\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`), nor main effect ($\beta$ = `r stats_model_burn_exp2$beta[4]`, `r make_pvalue(stats_model_burn_exp2$p[4])`) for the burning ratings.
-For the warm ratings we found no interaction ($\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`), , nor main effect of dermatome ($\beta$ = `r stats_model_warm_exp2$beta[4]`, `r make_pvalue(stats_model_warm_exp2$p[4])`) and for the cold ratings no interaction ($\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`) but a main effect ($\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`).
+Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two warm stimuli [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
+We tested the generazability of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
+We found that cold perception was modulated by the proximodistal location of the reference thermode, with enhanced cold ratings when the reference thermode was located more proximally, irrespective of whether the stimulus was TGI or non-TGI, in both Exp.
+1 (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) and Exp.
+2 (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`).
+These findings extend the notion of distal inhibition to innocuous cold perception.
 
@@
 ```
+
+Cuts
+
+From "Proximodistal bias in cold perception":
+
+Experiment 1: warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
+
+Experiment 2: warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`); dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[4]`, `r make_pvalue(stats_model_warm_exp2$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`); dermatome main effect: $\beta$ = `r stats_model_burn_exp2$beta[4]`, `r make_pvalue(stats_model_burn_exp2$p[4])`).

### 2023-08-02 Manuscript.Rmd
edits: proximodistal bias

@@
 
-Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two warm stimuli [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
-We tested the generazability of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
+Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two heat stimuli [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
+We tested the occurence of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
 We found that cold perception was modulated by the proximodistal location of the reference thermode, with enhanced cold ratings when the reference thermode was located more proximally, irrespective of whether the stimulus was TGI or non-TGI, in both Exp.
@@
 2 (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`).
-These findings extend the notion of distal inhibition to innocuous cold perception.
+These findings suggest that the notion of distal inhibition can be extended to innocuous cold perception.
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3) Difference in VAS ratings between the proximal and distal dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
-A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3) Difference in VAS ratings between the proximal and distal location of the reference thermode in the within dermatome condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+A, experiment with the cold thermode as reference, and B with the warm thermode as reference.
 Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
 
-#plot2(include_zero = F)
-
-#plot2(include_zero = T)
 plot2_3(include_zero = F)[[1]]
@@
 We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli.
-Like the previous analysis we investigated this relationship with a two way interaction here with the rostral - caudal axis being investigated.
 

### 2023-08-02 Manuscript.Rmd
edits: inter-segmental effects

@@
 
-\newpage
-
 # Results and discussion
@@
 Further, participants reported no significant modulation of burning ratings depending on the dermatome condition (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
-Overall, these results indicated that when participants assessed the cold thermode, the greatest modulation in TGI perception was related to cold perception, with within-dermatome TGI stimuli perceived as the least cold.
+These results indicated that when participants assessed the cold thermode, the greatest modulation in TGI perception was related to cold perception, with within-dermatome TGI stimuli perceived as the least cold.
 While the modulation of cold perception was specific for TGI, increased warmth was reported irrespective of whether the cold thermode was paired with a warm (TGI stimuli) or neutral temperature (non-TGI stimuli) within a dermatome.
-These findings are in line with the notion that TGI can be considered a misperception of cold [@fardo_organization_2018; @fardo_beyond_2020].
+Overall, these findings are in line with the notion that TGI can be considered a misperception of cold [@fardo_organization_2018; @fardo_beyond_2020].
 
@@
 A main objective of this study was assessing spatial order effects along the rostrocaudal axis at the spinal level.
-We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli.
+We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli, in the across dermatome condition.
+When rating either the cold thermode (Exp.
+1, Fig.
+4A) or the warm thermode (Exp.2, Fig.
+4B), participants reported a reduced subjective experience of cold, alongside an enhanced perception of warmth when the cold thermode was applied on a dermatome that mapped onto a more caudal segment.
+In Exp.
+1, the modulation of thermosensory ratings corresponded to significant rostralcaudal main effects for both cold ratings (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`), and warm ratings (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`).
+In Exp.
+2, the modulation of cold ratings was specific for TGI stimuli (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`), while the modulation of warm ratings was significant irrespective of stimulation type (stimulation by rostrocaudal interaction: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`); rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`).
+We observed no modulation of burning ratings depending on the rostrocaudal mapping of cold-related activity in either Exp.
+1 (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; rostrocaudal main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`) or Exp.
+2 (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`); rostrocaudal main effect: $\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`).
+The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord.
+While reduced cold perception was specific for TGI stimuli, participants reported enhanced warm perception irrespective of stimulation type.
 
-Results showed no statistical significant interaction effect for the cold ratings in the first experiment with the reference thermode being cold ($\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`, but a main effect ($\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`).
-For the warm ratings we found no statistically significant effect for warm watings ($\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`), but a statistical significant main effect ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`) The burning ratings showed no significant interaction ($\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`), nor main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`).
-
-In Experiment 2, with the warm thermode as the reference we found no significant interaction effect for the burning ratings ($\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`), but a significant main effect ($\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`) For the warm ratings we found no statistically significant interaction ($\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`), but a strong main effect ($\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`) For the cold ratings we found a significant interaction ($\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`)
+##
 
@@
 
-The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord, as depicted in Figure 3.
-These findings were consistent across both experiments for thermosensory ratings, albeit with minor deviations that corresponded with the particular stimulation quality being assessed.
-The observed enhancement of warmth perception in Experiment 2 could be ascribed to the participants' assessment of the warmer thermode as opposed to the colder one of Experiment 1.
-For burning ratings, significant results were seen in Experiment 2, but not in Experiment 1.
-One possible reason for this discrepancy could be the relatively low power in Experiment 1, as the power analysis was specifically focused on thermosensory ratings.
-Alternatively, assessing the warmer thermode might be a more accurate method for measuring TGI perception.
-
 ## Spinal organisation and TGI perception
 
-The complexities of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) enhanced heat and burning sensations when cold-warm thermosensory integration takes place more focally within the spinal cord, and (2) discernible directional inter-segmental effects when distinct cold and warm stimuli elicited broader activity along the spinal cord.
+The complexities of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) reduced cold, enhanced heat and burning sensations when thermosensory integration takes place more focally within a few spinal segments, and (2) discernible directional inter-segmental effects when distinct cold and warm stimuli elicited a differential spatial pattern of neural activity along several spinal cord segments.
+
 Small primary afferents, responsible for mediating temperature and pain sensations, split into ascending and descending branches that cover one to two segments before they enter the dorsal horn [@kerr_neuroanatomical_1975; @lamotte_distribution_1977].
 This pattern forms the Lissauer's tract, a structure hypothesised to regulate sensory transmission to the dorsal horn and influence spinal receptive field size [@wall_brief_1999].
-
-Additionally, the endings of small primary afferents within the superficial laminae of the dorsal horn form synapses with both propriospinal neurons and projection neurons that target supraspinal structures known to significantly influence TGI perception [@craig_functional_1996; @lindstedt_evidence_2011; @leung_supraspinal_2014 + any other neuroimaging studies of the TGI].
-
+Additionally, the endings of small primary afferents within the superficial laminae of the dorsal horn form synapses with both propriospinal neurons and projection neurons that target supraspinal structures known to significantly influence TGI perception [@craig_functional_1996; @lindstedt_evidence_2011; @leung_supraspinal_2014].
 Evidence from animal studies shows that propriospinal neurons, confined within the spinal cord, exhibit bidirectional collateral branches along the rostrocaudal plane [@saywell_electrophysiological_2011; @skinner_ascending_1989].
@@
 These circuits, created by propriospinal neurons, may promote sensory integration within a spinal receptive field while simultaneously inhibiting activity in adjacent fields.
-This mechanism aligns with the concept of lateral inhibition, a ubiquitous process in sensory processing seen across both the peripheral and central nervous systems, and multiple sensory modalities, including thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021].
-Further, our observation that spatial factors, such as the more caudal localisation of cold activity relative to warm activity in the spinal cord, influences TGI perception, suggests possible neuroanatomical and functional asymmetries.
+This mechanism aligns with the concept of lateral inhibition, a ubiquitous process in sensory processing across both the peripheral and central nervous systems, and multiple sensory modalities, including thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021].
+Further, our observation that spatial factors, such as the more caudal mapping of a cold stimulus relative to a warm stimulus in the spinal cord, influences TGI perception, suggests possible neuroanatomical and functional asymmetries.
 This could mean a greater number of ascending fibres than descending fibres carrying thermosensory information in the Lissauer's tract, an uneven distribution of ascending and descending collaterals of propriospinal neurons (Anatomical Hypotheses), or varying effects of inter-segmental inhibition along the rostrocaudal axis (Functional Hypothesis).
@@
 Additionally, the zero-inflation was needed due to the presence of an excess number of zero values in specific ratings and conditions.
-Specifically, we anticipated an overrepresentation of zero values for thermosensory ratings that were counterfactual to the objective stimulation quality (i.e., cold ratings of warm stimuli and warm ratings of cold stimuli) and burning ratings of non-TGI stimuli.
+Specifically, we anticipated an over-representation of zero values for thermosensory ratings that were counterfactual to the objective stimulation quality (i.e., cold ratings of warm stimuli and warm ratings of cold stimuli) and burning ratings of non-TGI stimuli.
 The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.

### 2023-08-02 Manuscript.Rmd
word template

@@
     latex_engine: xelatex
+    indent: true
 bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
@@
 
-Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
+&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
 Two studies posited that the illusory pain component of the TGI depends uniquely on supraspinal mechanisms.
@@
 To measure cold and heat pain thresholds, we gradually adjusted the temperature of one thermode until the participant indicated an experience of pain by pressing a stop button or reached the maximum temperature cut-offs of 5ºC or 50ºC.
+
 We calibrated TGI stimuli by identifying a cold-warm temperature pair based on specific criteria: (1) consistently eliciting a burning sensation of at least 15 on a scale ranging from 0 to 100, (2) consistently avoiding a burning sensation (less than 15) when the cold-neutral (Exp.
@@
 In non-TGI stimuli the cold or warm temperatures were set to match the temperature used for TGI stimulation, but paired with a neutral temperature set at 30ºC.
+
 The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant's forearm size.
@@
 Further, we manipulated the spatial arrangement of the temperature pairs, by systematically presenting an equal number of trials where the cold thermode was applied on a proximal or distal location within a dermatome, or was applied on a dermatome that mapped onto a rostral or caudal segment along the spinal cord.
-We based the demarcation of the dermatome boundaries on the American Spinal Injury Association (ASIA) map (Fardo et al., 2018) and positioned the thermodes in relation to standard anatomical landmarks.
+We based the demarcation of the dermatome boundaries on the American Spinal Injury Association (ASIA) map and positioned the thermodes in relation to standard anatomical landmarks.
 Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head or the lower back.
@@
 caudal) were pseudo-randomised and counterbalanced between participants.
+
 During each trial, the experimenter positioned two thermodes, mounted on a stand using two independent clamps, on the participant's skin for 10 seconds.
@@
 This ensured that the same skin locations were not stimulated consecutively to minimise carry-over effects.
+
 Experiments 1 and 2 were conducted in two independent groups of participants and followed exactly the same procedure except for two elements.
@@
 ```{r,warning = F, message = F, echo = F}
-get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>%
-  width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)%>%
+get_main_tables(model_cold_exp1,round = 2, title = "Exp. 1: Cold reference on cold ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
-get_main_tables(model_warm_exp1,round = 2, title = "Cold reference on warm ratings") %>%
-  width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)%>%
+get_main_tables(model_warm_exp1,round = 2, title = "Exp. 1: Cold reference on warm ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
-get_main_tables(model_burn_exp1,round = 2, title = "Cold reference on burning ratings") %>%
-  width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)%>%
+get_main_tables(model_burn_exp1,round = 2, title = "Exp.1: Cold reference on burning ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
-get_main_tables(model_cold_exp2,round = 2, title = "Warm reference on cold ratings") %>%
-  width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)%>%
+get_main_tables(model_cold_exp2,round = 2, title = "Exp. 2: Warm reference on cold ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
-get_main_tables(model_warm_exp2,round = 2, title = "Warm reference on warm ratings") %>%
-  width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)%>%
+get_main_tables(model_warm_exp2,round = 2, title = "Exp. 2: Warm reference on warm ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
 
-get_main_tables(model_burn_exp2,round = 2, title = "Warm reference on burning ratings") %>%
-  width(j=1, width = 2.5) %>%
-  width(j=c(2,3,4,5), width = 1.1)%>%
+get_main_tables(model_burn_exp2,round = 2, title = "Exp. 2: Warm reference on burning ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
   fontsize(size = 10, part = "all") %>% flextable::font(fontname = "Times New Roman", part = "all")
@@
 
-Cuts
+\newpage
 
-From "Proximodistal bias in cold perception":
+## Proximodistal bias in cold perceptionxs
 

### 2023-08-02 Manuscript.Rmd
ms

@@
 
-&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
+Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
 Two studies posited that the illusory pain component of the TGI depends uniquely on supraspinal mechanisms.
@@
 We tested the occurence of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
-We found that cold perception was modulated by the proximodistal location of the reference thermode, with enhanced cold ratings when the reference thermode was located more proximally, irrespective of whether the stimulus was TGI or non-TGI, in both Exp.
-1 (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) and Exp.
-2 (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`).
-These findings suggest that the notion of distal inhibition can be extended to innocuous cold perception.
+We found that cold and burn perception was modulated by the proximodistal location of the cold thermode, with enhanced cold ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) and burn ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`) when the cold thermode was located more proximally, irrespective of whether the stimulus was TGI or non-TGI.
+We found a similar finding for cold perception (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`), when participants assessed the warm thermode.
+These findings suggest that the notion of distal inhibition can be extended to innocuous cold perception and burning sensations at objectively mild temperatures.
 
@@
 In Exp.
-2, the modulation of cold ratings was specific for TGI stimuli (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`), while the modulation of warm ratings was significant irrespective of stimulation type (stimulation by rostrocaudal interaction: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`); rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`).
-We observed no modulation of burning ratings depending on the rostrocaudal mapping of cold-related activity in either Exp.
-1 (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; rostrocaudal main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`) or Exp.
-2 (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`); rostrocaudal main effect: $\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`).
+2, the modulation of cold ratings was specific for TGI stimuli (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`), while the modulation of warm ratings was significant irrespective of stimulation type (stimulation by rostrocaudal interaction: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`).
+Similarly to warm ratings, we showed a modulation of burning ratings depending on the rostrocaudal mapping of cold-related activity irrespective of stimulation type in Exp.
+2 (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`).
 The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord.
-While reduced cold perception was specific for TGI stimuli, participants reported enhanced warm perception irrespective of stimulation type.
-
-##
+While reduced cold perception was more specific for TGI stimuli, participants reported enhanced warm and burning perception irrespective of stimulation type.
+Overall these effects are in line with the interpretation that the reference stimulation is a crucial factor in assessing thermosensory and burning components of TGI perception.
 
@@
 
-get_main_tables(model_warm_exp1,round = 2, title = "Exp. 1: Cold reference on warm ratings") %>%
+get_main_tables(model_cold_exp2,round = 2, title = "Exp. 1: Cold reference on warm ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
 
-get_main_tables(model_burn_exp1,round = 2, title = "Exp.1: Cold reference on burning ratings") %>%
+get_main_tables(model_warm_exp1,round = 2, title = "Exp.1: Cold reference on burning ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
 
-get_main_tables(model_cold_exp2,round = 2, title = "Exp. 2: Warm reference on cold ratings") %>%
+get_main_tables(model_warm_exp2,round = 2, title = "Exp. 2: Warm reference on cold ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
 
-get_main_tables(model_warm_exp2,round = 2, title = "Exp. 2: Warm reference on warm ratings") %>%
+get_main_tables(model_burn_exp1,round = 2, title = "Exp. 2: Warm reference on warm ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
 
-## Proximodistal bias in cold perceptionxs
+## Proximodistal bias in cold perception
 
-Experiment 1: warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[8]`, `r make_pvalue(stats_model_warm_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
+Experiment 1: warm ratings (stimulation by dermatome interaction: \$\\beta\$ = r stats_model_warm_exp1\$beta[8], r make_pvalue(stats_model_warm_exp1\$p[8]); dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
 
 Experiment 2: warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`); dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[4]`, `r make_pvalue(stats_model_warm_exp2$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`); dermatome main effect: $\beta$ = `r stats_model_burn_exp2$beta[4]`, `r make_pvalue(stats_model_burn_exp2$p[4])`).
+
+## Directional effects in inter-segmental sensory integration
+
+Experiment 1: burn ratings (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; rostrocaudal main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`)

### 2023-08-02 Manuscript.Rmd
updated suppl material

@@
 
-get_main_tables(model_cold_exp2,round = 2, title = "Exp. 1: Cold reference on warm ratings") %>%
+get_main_tables(model_cold_exp2,round = 2, title = "Exp. 2: Warm reference on cold ratings") %>%
+  width(j = 1, width = 2.5) %>%
+  width(j = c(2,3,4,5), width = 1.1)%>%
+  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
+```
+
+\newpage
+
+```{r,warning = F, message = F, echo = F}
+
+get_main_tables(model_warm_exp1,round = 2, title = "Exp.1: Cold reference on warm ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
 
-get_main_tables(model_warm_exp1,round = 2, title = "Exp.1: Cold reference on burning ratings") %>%
+get_main_tables(model_warm_exp2,round = 2, title = "Exp. 2: Warm reference on warm ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
+```
 
-get_main_tables(model_warm_exp2,round = 2, title = "Exp. 2: Warm reference on cold ratings") %>%
-  width(j = 1, width = 2.5) %>%
-  width(j = c(2,3,4,5), width = 1.1)%>%
-  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
+\newpage
 
-get_main_tables(model_burn_exp1,round = 2, title = "Exp. 2: Warm reference on warm ratings") %>%
+```{r,warning = F, message = F, echo = F}
+
+get_main_tables(model_burn_exp1,round = 2, title = "Exp. 1: Cold reference on burning ratings") %>%
   width(j = 1, width = 2.5) %>%
@@
   fontsize(size = 10, part = "all") %>% flextable::font(fontname = "Times New Roman", part = "all")
-
 ```

### 2023-08-03 Manuscript.Rmd
updated contributions
update_on_template

@@
 
+::: {custom-style="Corresponding authors text"}
 Corresponding authors: Alexandra G. Mitchell ([agmitchell\@cfin.au.dk](mailto:agmitchell@cfin.au.dk){.email}) and Francesca Fardo ([francesca\@cfin.au.dk](mailto:francesca@cfin.au.dk){.email})
+:::
 
@@
 -   Conceptualization: DEC, JFE, FF, PH, AGM.
--   Data curation: JEF, AGM.
+-   Data curation: JFE, AGM.
 -   Formal analysis: JFE, FF, AGM.
@@
 -   Supervision: FF, AGM.
--   Visualization: FF, AGM.
+-   Visualization: JFE, FF, AGM.
 -   Writing -- original draft: FF, AGM.
--   Writing -- review & editing: FF, AGM. (+ others who will provide feedback)
+-   Writing -- review & editing: JFE, FF, PH, AGM, AVS.
 

### 2023-08-21 Manuscript.Rmd
updating intro

@@
 indent: true
-bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
+bibliography: knitting files/tgi-spine2.bib
 link-citations: yes
@@
 
-The Thermal Grill Illusion (TGI) is a phenomenon in which the juxtaposition of innocuous warm and cold temperatures elicits a burning sensation, offering a unique window to understand how pain can be perceived in response to harmless stimuli.
-Much debate has revolved around whether spinal mechanisms are involved in the generation of illusory pain, beyond supraspinal mechanisms.
-In this study, we investigated the role of the spinal cord in the generation of the TGI, in two independent experiments, involving a total of 80 healthy individuals.
-We applied heat and cold stimuli on dermatomes, namely areas of skin innervated by a single spinal nerve, mapped onto adjacent or nonadjacent spinal segments.
-Participants were asked to rate their perceptions of cold, warm, and burning sensations in response to TGI and control stimuli.
-Our aims were to investigate thermosensory and painful perceptual components of the TGI, as well as spatial features of the illusion that may illuminate processes underlying thermosensory integration in the spinal cord.
-Our findings revealed that both thermosensory and painful components of TGI perception were modulated similarly, with enhanced warm and burning ratings observed when cold and warm stimuli were confined within the same dermatome.
-Further, we found no perceptual differences based on the proximal-distal location of the cold stimulus within a single dermatome, but notable heat enhancement when the cold rather than the warm stimulus was associated with a more caudal segmental location along the spinal cord.
-These results provide insights into the organisation of the spinal cord in relation to the thermosensory integration and generation of the TGI.
+The Thermal Grill Illusion (TGI), a phenomenon in which the juxtaposition of innocuous warm and cold temperatures on the skin elicits a burning sensation, offers a unique perspective to how pain occurs in response to harmless stimuli.
+We investigated the role of the spinal cord in the generation of the TGI across two experiments (total n = 80).
+We applied heat and cold stimuli to dermatomes, areas of skin innervated by a single spinal nerve, that mapped onto adjacent or nonadjacent spinal segments.
+Enhanced warm and burning ratings during the TGI were observed when cold and warm stimuli were confined within the same dermatome.
+Further, heat perception was enhanced when the cold stimulus projected to the segment caudal to the warm stimulus, compared to the opposite spatial arrangement.
+Our results are consistent with spatial spread and integration of thermosensory information in the spinal cord.
 
@@
 It is a sensation of burning heat or pain when harmless cold and warm temperatures are applied to the skin simultaneously [@craig_thermal_1994; @craig_functional_1996].
-Despite cold and warm temperatures being individually innocuous, their combination produces a contradictory burning sensation, even so the temperatures are insufficient to activate peripheral nociceptors.
+Despite cold and warm temperatures being individually innocuous, and therefore insufficient to activate peripheral nociceptors, their combination produces a paradoxical burning sensation.
 The generation of this illusion is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020].
-Recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017].
-However, the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.
+While recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017], the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.
 
@@
 Historically, the thermosensory and painful components of the TGI were explained by distinct spinal and supraspinal mechanisms, respectively.
-The enhanced perception of heat in TGI was explained by a spinal inhibitory mechanism, drawing from observations in an animal model where simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone [@craig_thermal_1994].
+Observations in the spinothalamic tract of cats showed that the simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone [@craig_thermal_1994], which implied the enhanced perception of heat in TGI is explained by a spinal inhibitory mechanism.
 Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following thalamic lesions [@craig_thermal_1994; -@craig_new_1998].
@@
 This interpretation was based on the observed modulation of the illusion in accordance with a spatiotopic rather than somatotopic representation of the body [@marotta_transforming_2015].
-Further, the illusion remained unaltered during concomitant tactile stimulation, suggesting ineffectiveness of tactile gating - a spinally-mediated process involving inhibition of nociceptive activity by concurrent somatosensory activity [@ferre_ineffectiveness_2018].
-Counter to this perspective, other research endorsed a spinal contribution to the TGI.
-These studies demonstrated that the illusion varied depending on whether cold and warm stimuli were applied to dermatomes mapped either onto adjacent or non-adjacent spinal segments [@fardo_organization_2018].
-Participants perceived the stimulation more veridically, consistently with a reduction in TGI perception, when warm or cold stimuli mapped on segmental locations that were apart along the spinal cord, corroborating the hypothesis that the spinal cord is an initial site of thermosensory integration underlying TGI.
+Further, the experience of the illusion was similar in a condition involving concomitant tactile stimulation and a contact-free condition, suggesting the TGI is not modulated by tactile gating - a spinally mediated process involving inhibition of nociceptive activity by concurrent somatosensory activity [@ferre_ineffectiveness_2018].
+
+Counter to this perspective, other research has endorsed a spinal contribution to the TGI.
+These studies found that the illusion varied depending on whether cold and warm stimuli were applied to dermatomes mapped either onto adjacent or non-adjacent spinal segments [@fardo_organization_2018].
+Participants perceived stimulus temperature more veridically, consistent with a reduction in the effectiveness of the TGI, when warm and cold stimuli were placed on the skin in such a way that they mapped on to different segmental locations along the spinal cord, compared to when they mapped onto the same spinal segment.
+This corroborates the hypothesis that the spinal cord is an initial site of thermosensory integration underlying the TGI.
 Further support for spinal mechanisms comes from research demonstrating that both noxious heat and the TGI were comparably reduced by conditioned pain modulation in humans.
-This suggests a similar influence of descending modulation, irrespective of whether the painful sensation was triggered by potentially harmful (noxious) or harmless (TGI) stimuli [@harper_conditioned_2017].
-These findings collectively challenge a purely supraspinal hypothesis of the painful component of the TGI and indicate the relevance of spinal mechanisms in the manifestation of both illusory heat and pain.
+Since conditioned pain modulation is thought to be mediated by descending modulatory systems that originate in the brain but act on the spinal cord, this finding suggests a similar engagement of descending modulation, leading to similar effects on spinal cord activity.
+This pattern is consistent regardless of whether the painful sensation was triggered by potentially harmful, as in the case of noxious heat, or harmless, as with the TGI [@harper_conditioned_2017].
+These findings collectively refute the notion of a purely supraspinal hypothesis of the painful component of the TGI and underscore the significance of spinal mechanisms in the manifestation of both illusory heat and pain.
 
@@
 Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes.
-Cold and warm stimuli were presented at a fixed distance on the skin, but depending on their longitudinal or tangential orientation on the arm, they elicited differing neural activity in the spinal cord.
-Our assumption was that cold and warm-related neural activity in the spinal cord was more focal (i.e., within the same spinal segments or within a few adjacent segments), when the stimuli were presented within the same dermatome, while more widespread, when the stimuli mapped on non-adjacent spinal segments (i.e., possibly 2 to 4 segments apart).
-Our past work using a similar manipulation involved measuring the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both thermosensory and painful components.
-Here, to probe possible distinctions between the two qualitative components of the TGI, we measured subjective indices of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations.
-Secondly, we investigated spatial order effects associated with the integration of cold and warm sensory information at the dermatome (skin) and segmental (i.,e., spine) levels.
+Cold and warm stimuli were presented at a fixed distance on the skin but depending on their orientation on the arm, they elicited differing neural activity in the spinal cord (Figure 1 A and B).
+Our assumption was that cold and warm-related neural activity would show stronger integration, and thus stronger TGI effects, when the stimuli were presented within the same dermatome and therefore mapped to the same or adjacent spinal segments, than when they mapped onto segments that were anatomically further apart.
+In each case, we compared stimuli that could either induce the TGI (combined innocuous cold and warm) with control stimuli that could not induce the TGI (i.e.
+a neutral temperature, 30ºC, paired with either innocuous cold in experiment 1 or innocuous warm in experiment 2).
+
+Our past work quantified the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both the thermosensory and painful components.
+Here, to probe possible distinctions between these two qualitative components of the TGI, we obtained subjective measures of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations (Figure 1C).
+Additionally, we investigated spatial order effects associated with the integration of cold and warm sensory information at the dermatome (skin) and segmental (spine) levels.
 At the dermatome level, we used body-related coordinates to define proximal (towards the elbow) and distal (towards the wrist) locations.
-At the spinal level, we used segment-related coordinates to define more rostral (towards the head) and more caudal (towards the lower back) locations.
-Given the organisation of the spinal cord along a rostral-caudal axis, where each dermatome is represented across multiple spinal segments through the Lissauer tract [@kerr_neuroanatomical_1975; @lamotte_distribution_1977; @wall_brief_1999], this study aimed to glean indirect insights into the spinal mechanisms underpinning thermosensory integration and the generation of the TGI.
+At the spinal level, we used segment-related coordinates to define more rostral (towards the head) and more caudal (towards the lower back) locations (Figure 1B).
+Given that the spinal cord is organised along a rostral-caudal axis, where each dermatome is represented across multiple spinal segments through the Lissauer tract [@kerr_neuroanatomical_1975; @lamotte_distribution_1977; @wall_brief_1999], this study provides indirect insights into the spinal mechanisms underpinning thermosensory integration and the generation of the TGI.
+If the experience of the TGI is influenced by the relative location of warm and cold afferents in different spinal segments, this finding would provide compelling, additional evidence that the spine serves as an initial site for the cold-warm integration that produces perceptions of illusory heat and pain.
 
@@
 ggdraw() +
-    draw_image(magick::image_read(here::here("figures","figure1.PNG")), scale = 1)
+    draw_image(magick::image_read(here::here("figures","figure1_v2.PNG")), scale = 1)
 ```

### 2023-08-21 Manuscript.Rmd
updating results

@@
 Thus, indicators of a stronger TGI are reduced cold ratings, coupled with heightened warm and burning ratings.
+The last of these is generally considered to be the most salient feature of the TGI, and has received the most attention within the TGI literature.
 
-To investigate thermosensory and burning components of the TGI, participants received pairs of temperatures on their forearms and were asked to quantify the levels of cold, warmth, and burning they experienced during each stimulation.
-These stimuli consisted of either cold-warm pairs (TGI stimuli), which potentially evoked an illusion of heat and pain, or control stimuli that involved pairing a cold or a warm stimulus of identical temperature as in the TGI condition with a baseline temperature of 30°C (non-TGI stimuli).
-All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments.
-For each stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of a sensation, to 100, indicating an extreme sensation.
-For each instance of stimulation, participants were guided to focus their reporting on the sensations originating from a specific thermode.
-While the participants were unaware, this location corresponded to either the colder stimulus (Exp. 1) or the warmer stimulus (Exp. 2) of the paired temperatures.
-VAS ratings were analysed using zero-inflated beta regressions.
+While most previous studies have focused on the TGI as a single experience, explicitly understood as an experience of or like pain, our approach differed.
+We instructed participants to report the sensation from just one of the thermal components, corresponding to the cold thermode location (Experiment 1) or the warm thermode location (Experiment 2).
+Importantly, the aim of this method was not to isolate any possible independent effect of warm and cold stimulation during TGI, but rather to ensure consistency in participants\' ratings across trials and different stimulus conditions.
 
-## Thermosensory and burning components of TGI perception are spinally mediated
+To investigate both the thermosensory and burning components in each experiment, we asked participants to provide a subjective evaluation of multiple sensory qualities - cold, warmth and burning (pain).
+Stimuli consisted of either cold-warm pairs (TGI stimuli), which potentially evoked an illusion of heat and pain, or control stimuli that involved pairing a cold (Exp.
+1) or a warm (Exp.
+2) stimulus of identical temperature as in the TGI condition with a baseline temperature of 30°C (non-TGI stimuli).
+All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments (Figure 1A and B).
+After ten seconds of stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of the corresponding sensory quality, to 100, indicating an extreme sensation (Figure 1C), presented in a random order.
+For each instance of stimulation, participants were guided to focus their reporting on the sensations originating either thermode \'A\' or \'B\' which corresponded to either the cold (Exp.
+1) or warm (Exp.
+2) thermode.
+This labelling was used to ensure participants were not immediately aware of the temperature associated with each probe.
+VAS ratings for each sensation were analysed using mixed-effects zero-inflated beta regressions, where VAS ratings that equaled zero for non-TGI and TGI stimulation were modelled separately to VAS ratings above zero.
 
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1) Four experimental conditions depicting an exemplar cold and warm thermode placement within and across dermatomes.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1) A and B) Placement and distance of thermodes on the inner forearm, showing corresponding spinal mapping for all four conditions.
 Within dermatomes, the relative location of the cold thermode was proximal or distal.
 Across dermatomes, the relative location of the corresponding spinal segments was rostral or caudal.
-"}
+Within dermatome conditions also included warm and cold thermodes in C6 (not depicted here), as well as T1.
+C) The three VAS participants used to report sensation coming from the reference probe, presented for each trial in a randomised order."}
 ggdraw() +
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2) Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
-Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
-Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
-A) first experiment with the cold thermode as the reference, and B second experiment with the warm thermode as referece."}
+## Thermosensory and burning components of TGI perception are spinally mediated
 
-plot1(include_zero = F)
-#plot1(include_zero = T)
-
-```
-
-In keeping with the unique heat and burning features of TGI, our results exhibited a more robust TGI when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments.
+The typical heat and burning perception associated with TGI was more robust when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments.
 When rating the cold thermode (Exp.
 1, Fig.
-2A), participants reported a reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`), alongside an increased subjective experience of warmth for both TGI and non-TGI stimuli (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`).
+2A), participants reported a stronger reduction in the subjective experience of cold specifically for TGI stimuli applied within a dermatome compared to across dermatomes.
+The results of the zero-inflated beta regression show a stimulation by dermatome interaction (cold ratings: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`), alongside an increased subjective experience of warmth for both TGI and non-TGI stimuli (dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`).
 Further, participants reported no significant modulation of burning ratings depending on the dermatome condition (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
-These results indicated that when participants assessed the cold thermode, the greatest modulation in TGI perception was related to cold perception, with within-dermatome TGI stimuli perceived as the least cold.
+These results indicated that when participants judged the cold thermode, the greatest modulation in TGI perception was related to cold perception, with within-dermatome TGI stimuli perceived as the least cold.
 While the modulation of cold perception was specific for TGI, increased warmth was reported irrespective of whether the cold thermode was paired with a warm (TGI stimuli) or neutral temperature (non-TGI stimuli) within a dermatome.
@@
 All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI, and highlight the importance of the reference stimulus when assessing thermosensory and burning components of TGI perception.
+
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2) Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
+Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
+Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
+A) first experiment with the cold thermode as the reference, and B second experiment with the warm thermode as referece."}
+
+plot1(include_zero = F)
+#plot1(include_zero = T)
+
+```
 

### 2023-08-22 Manuscript.Rmd
updating results, discussion and conclusion

@@
 While most previous studies have focused on the TGI as a single experience, explicitly understood as an experience of or like pain, our approach differed.
-We instructed participants to report the sensation from just one of the thermal components, corresponding to the cold thermode location (Experiment 1) or the warm thermode location (Experiment 2).
+We instructed participants to report the sensation from just one of the thermal components, corresponding to the cold thermode location (Exp. 1) or the warm thermode location (Exp. 2).
 Importantly, the aim of this method was not to isolate any possible independent effect of warm and cold stimulation during TGI, but rather to ensure consistency in participants\' ratings across trials and different stimulus conditions.
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1) A and B) Placement and distance of thermodes on the inner forearm, showing corresponding spinal mapping for all four conditions.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1: A and B) Placement and distance of thermodes on the inner forearm, showing corresponding spinal mapping for all four conditions.
 Within dermatomes, the relative location of the cold thermode was proximal or distal.
@@
 2, Fig.
-2B), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
-However, we did not observe modulation of cold (stimulation by dermatome interaction: n$\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) or warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`; dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`) according to the within-across dermatome manipulation.
-Overall, these results indicated that when participants assessed the warm thermode, the greatest modulation in TGI perception was related to burning sensations, with within-dermatome TGI stimuli perceived as the most burning.
+2B), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (dermatome main effect: $\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
+However, we did not observe modulation of cold (dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) or warm ratings by dermatome (dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
+Overall, these results indicated that when participants judged the warm thermode, the greatest modulation in TGI perception was related to burning sensations, with within-dermatome TGI stimuli perceived as the most burning.
 
 The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both qualitative components of the illusion are modulated at the spinal cord level.
-This interpretation is consistent with a previous study using a similar dermatome manipulation, but a distinct method to quantify TGI perception [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
-All together these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI, and highlight the importance of the reference stimulus when assessing thermosensory and burning components of TGI perception.
+This interpretation is consistent with a previous study using a similar dermatome manipulation [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
+These results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI and highlight the importance of the veridical temperature of the stimulus being judged when assessing thermosensory and burning components of TGI perception.
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2) Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2: Difference between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) for each VAS rating quality (cold, warm and burning).
 Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
-Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
-A) first experiment with the cold thermode as the reference, and B second experiment with the warm thermode as referece."}
+A) experiment one where participants judged sensations at the location of the cold thermode and B) experiment two where participants judged sensations at the location of the warm thermode.
+Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals."}
 
@@
 
-Previous research demonstrated a phenomenon known as distal inhibition, wherein heat pain ratings tend to increase when a participant evaluates a more distal compared to a more proximal stimulus among two heat stimuli [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
-We tested the occurence of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
-We found that cold and burn perception was modulated by the proximodistal location of the cold thermode, with enhanced cold ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`) and burn ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`) when the cold thermode was located more proximally, irrespective of whether the stimulus was TGI or non-TGI.
-We found a similar finding for cold perception (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`; dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`), when participants assessed the warm thermode.
-These findings suggest that the notion of distal inhibition can be extended to innocuous cold perception and burning sensations at objectively mild temperatures.
+Previous research has demonstrated a phenomenon known as distal inhibition which occurs when two heat stimuli are presented simultaneously.
+Typically, heat pain ratings at the proximal location are lower, and therefore inhibited, when the temperature at the distal location also produces heat pain, compared to when it is neutral [@quevedo_psychophysicshyperalgesia_2004; @quevedo_illusion_2007].
+When applied to our study, distal inhibition would result in higher ratings associated with both burning and the congruent sensation when the reference thermode (cold for Exp.
+1, warm for Exp.
+2) is in a more distal location compared to the other thermode.
+We tested the occurrence of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3) Difference in VAS ratings between the proximal and distal location of the reference thermode in the within dermatome condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
-A, experiment with the cold thermode as reference, and B with the warm thermode as reference.
+We found that cold and burn perception were modulated by the proximodistal location of the cold thermode.
+In experiment 1, cold ratings (dermatome main effect: $\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`) and burn ratings (dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`) were enhanced when the reference (cold) thermode was located more distally than the warm probe, irrespective of whether the stimulus was TGI or non-TGI (Fig.
+3A).
+We found a similar finding for cold perception in experiment 2 (dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`), where cold ratings were higher when the reference (warm) thermode was more proximal than the cold thermode (Fig.
+3B).
+These findings suggest that the notion of distal inhibition can be extended to innocuous cold perception and burning sensations that are not specific to TGI at objectively mild temperatures.
+
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3: Difference between the proximal and distal location of the reference thermode in the within dermatome condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+Higher values show higher ratings when the cold probe is more proximal than the warm probe.
+A) experiment one where participants judged sensations at the location of the cold thermode and B) experiment two where participants judged sensations at the location of the warm thermode.
 Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
@@
 A main objective of this study was assessing spatial order effects along the rostrocaudal axis at the spinal level.
-We delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm or neutral stimuli, in the across dermatome condition.
-When rating either the cold thermode (Exp.
+In the across dermatome condition, we delivered an equal number of trials in which the cold stimulus was applied on a dermatome that mapped more rostrally or caudally compared to the warm.
+We found thermosensory components of the TGI were enhanced when cold sensory afferents mapped on to more caudal spinal segments, compared to warm sensory afferents.
+
+In experiment 1, the modulation of thermosensory ratings corresponded to significant rostrocaudal main effects for both cold ratings ($\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`) and warm ratings ($\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`), but this effect was not specific for TGI stimuli (stimulation by rostrocaudal location interaction, cold ratings: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; warm ratings: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`).
+In experiment 2, the modulation of cold ratings was specific for TGI stimuli (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`), while the modulation of warm ratings was significant irrespective of stimulation type (rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`; stimulation by rostrocaudal interaction: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`).
+The rostrocaudal mapping of cold-related activity also modulated burning ratings irrespective of stimulation type, in experiment 2 (rostrocaudal main effect: $\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`; stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`).
+
+Therefore, when rating either the cold thermode (Exp.
 1, Fig.
@@
 4B), participants reported a reduced subjective experience of cold, alongside an enhanced perception of warmth when the cold thermode was applied on a dermatome that mapped onto a more caudal segment.
-In Exp.
-1, the modulation of thermosensory ratings corresponded to significant rostralcaudal main effects for both cold ratings (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp1$beta[7]`, `r make_pvalue(stats_model_cold_exp1$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_cold_exp1$beta[3]`, `r make_pvalue(stats_model_cold_exp1$p[3])`), and warm ratings (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_warm_exp1$beta[7]`, `r make_pvalue(stats_model_warm_exp1$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp1$beta[3]`, `r make_pvalue(stats_model_warm_exp1$p[3])`).
-In Exp.
-2, the modulation of cold ratings was specific for TGI stimuli (stimulation by rostrocaudal location interaction: $\beta$ = `r stats_model_cold_exp2$beta[7]`, `r make_pvalue(stats_model_cold_exp2$p[7])`), while the modulation of warm ratings was significant irrespective of stimulation type (stimulation by rostrocaudal interaction: $\beta$ = `r stats_model_warm_exp2$beta[7]`, `r make_pvalue(stats_model_warm_exp2$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_warm_exp2$beta[3]`, `r make_pvalue(stats_model_warm_exp2$p[3])`).
-Similarly to warm ratings, we showed a modulation of burning ratings depending on the rostrocaudal mapping of cold-related activity irrespective of stimulation type in Exp.
-2 (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp2$beta[7]`, `r make_pvalue(stats_model_burn_exp2$p[7])`; rostrocaudal main effect: $\beta$ = `r stats_model_burn_exp2$beta[3]`, `r make_pvalue(stats_model_burn_exp2$p[3])`).
 The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord.
 While reduced cold perception was more specific for TGI stimuli, participants reported enhanced warm and burning perception irrespective of stimulation type.
-Overall these effects are in line with the interpretation that the reference stimulation is a crucial factor in assessing thermosensory and burning components of TGI perception.
+Overall these effects are in line with the interpretation that the thermosensory and burning components of the TGI can differ strongly according to the location of cold-warm primary sensory afferents on the spinal cord.
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4) Difference in VAS ratings between the Caudal and Rostral dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning).
-A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4: Difference between the caudal and rostral dermatome conditions and the stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+Higher values represent higher ratings when the cold probe is located in dermatomes that are related to more caudal spinal segments (T1) than the warm probe (C6).
+A) experiment one where participants judged sensations at the location of the cold thermode and B) experiment two where participants judged sensations at the location of the warm thermode.
 Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
@@
 
-## Spinal organisation and TGI perception
+## Spinal organisation mediates the TGI
 
-The complexities of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) reduced cold, enhanced heat and burning sensations when thermosensory integration takes place more focally within a few spinal segments, and (2) discernible directional inter-segmental effects when distinct cold and warm stimuli elicited a differential spatial pattern of neural activity along several spinal cord segments.
+The details of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) reduced cold, enhanced heat and burning sensations when thermosensory integration takes place more focally within a few spinal segments, and (2) clear effects when distinct cold and warm stimuli elicited a differential spatial pattern of neural activity along several spinal cord segments.
 
@@
 
-Our finding of enhanced TGI perception with cold-warm stimuli applied within dermatomes might reflect the combined effects of the Lissauer's tract's short rostrocaudal span (comprising one to two segments, consistent with a single dermatome's boundary) and the characteristics of spinal circuits.
-These circuits, created by propriospinal neurons, may promote sensory integration within a spinal receptive field while simultaneously inhibiting activity in adjacent fields.
-This mechanism aligns with the concept of lateral inhibition, a ubiquitous process in sensory processing across both the peripheral and central nervous systems, and multiple sensory modalities, including thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021].
-Further, our observation that spatial factors, such as the more caudal mapping of a cold stimulus relative to a warm stimulus in the spinal cord, influences TGI perception, suggests possible neuroanatomical and functional asymmetries.
-This could mean a greater number of ascending fibres than descending fibres carrying thermosensory information in the Lissauer's tract, an uneven distribution of ascending and descending collaterals of propriospinal neurons (Anatomical Hypotheses), or varying effects of inter-segmental inhibition along the rostrocaudal axis (Functional Hypothesis).
-Additional research is needed to illuminate the specific anatomical and functional features of the spinal cord that resulted in the observed effects of this study.
+Our results indicate that enhanced TGI perception when cold-warm stimuli are applied within dermatomes may be attributed to a confluence of interconnected mechanisms.
+First, the Lissauer's tract, with its short rostrocaudal span of only one to two segments, aligns with the constraints of individual dermatome boundaries.
+This tract potentially facilitates the integration of warm and cold sensory information within the spinal cord, explaining reduced TGI percepts when cold-warm afferents span multiple spinal segments.
+Second, spinal circuits formed by propriospinal neurons may promote this sensory integration within a given spinal receptive field.
+They may do this by inhibiting activity in adjacent fields, a mechanism that corresponds to the principle of lateral inhibition which is present in both peripheral and central nervous systems and influences various sensory modalities, such as thermoception and nociception [@bekesy_lateral_1962; @quevedo_lateral_2017; @adamczyk_not_2021].
+In the specific framework of the TGI, previous studies have suggested that TGI perception is related to the difference between cold and warm temperatures, with a greater difference leading to a higher likelihood of TGI perception [@bouhassira_investigation_2005].
+If lateral inhibition is involved, enhanced TGI perception when cold-warm afferents are within dermatomes is expected, as the larger the difference, the greater the contrast and the greater the lateral inhibition.
+This understanding aligns with the potential role of lateral inhibition in accentuating the illusory sensations of heat and pain in the TGI by amplifying the differences between  simultaneous cold and warm stimulation.
+Taken together, the spatial characteristics of the Lissauer\'s tract, the functional dynamics of spinal circuits, and the underlying process of lateral inhibition, illuminate potential spinal mechanisms that could be instrumental in shaping the perception of the TGI.
+
+Further, our observation that spatial factors influence the TGI suggests possible neuroanatomical and functional asymmetries in thermosensory and pain mechanisms.
+Notably the increase in the intensity of the TGI when afferents map onto caudal cold and rostral warm segments in the spinal cord could mean a greater number of ascending fibres carrying thermosensory information in the Lissauer\'s tract, or an uneven distribution of ascending and descending collaterals of propriospinal neurons (Anatomical Hypotheses).
+Additionally, there could be differing effects of inter-segmental inhibition between cold and warm projections along the rostrocaudal axis that lead to the effects of segmental location on TGI perception (Functional Hypothesis).
+This inter-segmental inhibition might reveal a directional pattern, such as stronger inhibitory signals from higher to lower spinal segments that are specific to cold, which are  weaker in the opposite direction.
+Further research is needed to illuminate the specific anatomical and functional features of the spinal cord that influence the changes to thermosensory and painful sensations associated with the TGI identified in this study.
 
@@
 Illusions in the thermo-nociceptive system can be leveraged to improve our understanding of mechanisms contributing to pain perception.
-Here, we presented results supporting the notion that the spinal cord plays a crucial role in the integration and processing of thermal information, contributing to the perception of both thermosensory enhancement and the illusory pain within the TGI.
-Additionally, we reported findings on directional inter-segmental effects in spinal integration underlying TGI.
-Further research is needed to elucidate the neuroanatomical and functional properties of the spinal cord, as well as the intricate interplay between supraspinal and spinal processes, that give rise to TGI perception.
+Here, we presented results supporting the notion that the spinal cord plays a crucial role in the integration and processing of thermal information, contributing to the perception of both thermosensory enhancement and illusory pain within the TGI.
+Therefore, the initial mechanisms that lead to TGI percepts are likely to take place in the spinal cord.
+Additionally, we reported findings on directional inter-segmental effects in spinal integration underlying TGI, particularly when cold sensory afferents terminated in more caudal spinal segments than warm.
+Further research is needed to elucidate the neuroanatomical and functional properties of the spinal cord, as well as the intricate interplay between supraspinal and spinal processes that give rise to both the synthetic heat and burning sensations of the TGI.
 
@@
 The study entailed two separate experiments, collectively involving 80 healthy volunteers.
-The sample consisted of `r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old (SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) in Experiment 1, and `r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary (Female at birth), mean age = `r descript_exp2_age$mean_age` years old (SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`), in Experiment 2.
+The sample consisted of `r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old (SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) in experiment 1, and `r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary (Female at birth), mean age = `r descript_exp2_age$mean_age` years old (SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`), in experiment 2.
 The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
@@
 Experiments 1 and 2 were conducted in two independent groups of participants and followed exactly the same procedure except for two elements.
-In Experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs.
-In Experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs.
+In experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs.
+In experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs.
 
@@
 Non-responders were individuals that did not meet this criterion when tested with the max cold-warm temperatures allowed in the experiment.
-The predefined cut-off for TGI stimulation was (xx-xx).
-In Experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants.
+In experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants.
 We verified this criterion every 10 participants, resulting in a total sample size of 40 participants.
-In Experiment 2, we stopped recruitment once we collected data from 40 participants.
-This decision was based on meeting both required criteria: (1) matching the sample size of Exp.
-1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.
+In experiment 2, we stopped recruitment once we collected data from 40 participants.
+This decision was based on meeting both required criteria: (1) matching the sample size of experiment 1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.
 
@@
 We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
-The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [Experiment 1](https://osf.io/4xcn5/) and [Experiment 2](https://osf.io/dhg8u/).
+The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [experiment 1](https://osf.io/4xcn5/) and [experiment 2](https://osf.io/dhg8u/).
 All data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript), ensuring the reproducibility of our findings.

### 2023-08-22 Manuscript.Rmd
updating Methods

@@
 We instructed participants to report the sensation from just one of the thermal components, corresponding to the cold thermode location (Exp. 1) or the warm thermode location (Exp. 2).
-Importantly, the aim of this method was not to isolate any possible independent effect of warm and cold stimulation during TGI, but rather to ensure consistency in participants\' ratings across trials and different stimulus conditions.
+Importantly, the aim of this method was not to isolate any possible independent effect of warm and cold stimulation during TGI, but rather to ensure consistency in participants' ratings across trials and different stimulus conditions.
 
@@
 After ten seconds of stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of the corresponding sensory quality, to 100, indicating an extreme sensation (Figure 1C), presented in a random order.
-For each instance of stimulation, participants were guided to focus their reporting on the sensations originating either thermode \'A\' or \'B\' which corresponded to either the cold (Exp.
+For each instance of stimulation, participants were guided to focus their reporting on the sensations originating either thermode 'A' or 'B' which corresponded to either the cold (Exp.
 1) or warm (Exp.
@@
 This understanding aligns with the potential role of lateral inhibition in accentuating the illusory sensations of heat and pain in the TGI by amplifying the differences between  simultaneous cold and warm stimulation.
-Taken together, the spatial characteristics of the Lissauer\'s tract, the functional dynamics of spinal circuits, and the underlying process of lateral inhibition, illuminate potential spinal mechanisms that could be instrumental in shaping the perception of the TGI.
+Taken together, the spatial characteristics of the Lissauer's tract, the functional dynamics of spinal circuits, and the underlying process of lateral inhibition, illuminate potential spinal mechanisms that could be instrumental in shaping the perception of the TGI.
 
 Further, our observation that spatial factors influence the TGI suggests possible neuroanatomical and functional asymmetries in thermosensory and pain mechanisms.
-Notably the increase in the intensity of the TGI when afferents map onto caudal cold and rostral warm segments in the spinal cord could mean a greater number of ascending fibres carrying thermosensory information in the Lissauer\'s tract, or an uneven distribution of ascending and descending collaterals of propriospinal neurons (Anatomical Hypotheses).
+Notably the increase in the intensity of the TGI when afferents map onto caudal cold and rostral warm segments in the spinal cord could mean a greater number of ascending fibres carrying thermosensory information in the Lissauer's tract, or an uneven distribution of ascending and descending collaterals of propriospinal neurons (Anatomical Hypotheses).
 Additionally, there could be differing effects of inter-segmental inhibition between cold and warm projections along the rostrocaudal axis that lead to the effects of segmental location on TGI perception (Functional Hypothesis).
@@
 The study entailed two separate experiments, collectively involving 80 healthy volunteers.
-The sample consisted of `r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old (SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) in experiment 1, and `r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary (Female at birth), mean age = `r descript_exp2_age$mean_age` years old (SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`), in experiment 2.
+Forty participants took part in experiment 1 (`r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old, SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) and another 40 participants in experiment 2 (`r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary, mean age = `r descript_exp2_age$mean_age` years old, SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`).
 The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
@@
 All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3 software (version 5.4b).
-The procedure involved measurements of heat and cold pain thresholds, calibration of cold-warm temperature pairs eliciting TGI, and an experimental task where TGI and non-TGI stimuli were applied on dermatomes that mapped onto adjacent or non-adjacent spinal segments.
-To measure cold and heat pain thresholds, we gradually adjusted the temperature of one thermode until the participant indicated an experience of pain by pressing a stop button or reached the maximum temperature cut-offs of 5ºC or 50ºC.
+The procedure involved measurements of heat and cold pain thresholds, calibration of cold-warm temperature pairs eliciting TGI, and an experimental task where TGI and non-TGI stimuli were applied on dermatomes that mapped onto adjacent or nonadjacent spinal segments.
+
+We measured cold and heat pain thresholds in a stepwise manner, the order of which was counterbalanced across participants.
+For cold pain, a single thermode at a starting temperature of 25ºC was held on the participant's dorsal forearm for five seconds.
+After which, the participant verbally reported (yes/no) any experience of pain.
+If the participant reported no pain, the temperature of the thermode was lowered by 5ºC, and placed back on the skin for another five seconds after which the participant reported whether they experienced pain.
+This step was repeated either until the participant responded 'yes' or the thermode reached the set minimum temperature of 5ºC.
+If the participant responded 'yes' before the minimum temperature, the temperature of the thermode was increased by 1ºC until the participant no longer experienced pain.
+The cold pain threshold was identified as the highest temperature at which the participant reported a painful experience.
+The same steps were repeated for heat pain, but with increasing intervals of 5ºC and with a starting temperature of 35ºC and a maximum temperature of 45ºC.
+The heat pain threshold was identified as the lowest temperature at which the participant reported a painful experience.
 
@@
 The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant's forearm size.
-The positioning of the thermodes was either within the same dermatome (i.e., C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1).
+The positioning of the thermodes was either within the same dermatome (C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1).
 Further, we manipulated the spatial arrangement of the temperature pairs, by systematically presenting an equal number of trials where the cold thermode was applied on a proximal or distal location within a dermatome, or was applied on a dermatome that mapped onto a rostral or caudal segment along the spinal cord.
 We based the demarcation of the dermatome boundaries on the American Spinal Injury Association (ASIA) map and positioned the thermodes in relation to standard anatomical landmarks.
-Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head or the lower back.
-The possible spatial arrangements corresponded to the four conditions depicted in Figure 1.
-The order of the stimuli (TGI vs.
-non-TGI), the dermatome condition (within vs.
-across) and the relative placement of the colder temperature (proximal vs.
-distal or rostral vs.
-caudal) were pseudo-randomised and counterbalanced between participants.
+Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head (C6) or the lower back (T1).
+Spatial arrangements of stimuli are depicted in Figure 1B.
+The order of the stimuli (TGI vs. non-TGI), the dermatome condition (within vs. across) and the relative placement of the colder temperature (proximal vs. distal or rostral vs. caudal) were pseudo-randomised and counterbalanced between participants.
 
-During each trial, the experimenter positioned two thermodes, mounted on a stand using two independent clamps, on the participant's skin for 10 seconds.
-An auditory cue (300Hz, 100ms) indicated the end of the stimulation period, after which the experimenter removed the thermodes from the participant's skin.
-Participants then rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales.
+During each trial, the experimenter positioned two thermodes on the participant's skin for 10 seconds, after which participants rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales.
 VAS scales were presented one at a time on a computer screen and appeared as a horizontal line, anchored at 0, representing no sensation (e.g., no burning), and 100, signifying an extreme sensation (e.g., extreme burning).
-The order of the three VAS scales was randomised across trials.
+The order of the three VAS scales was randomised across trials and participants had a maximum of eight seconds to respond to each scale.
 For each scale, participants provided their responses using the arrow keys on a keyboard and rated the intensity of their sensations from a specific location (labeled 'A' or 'B'), based on the experimenter's instruction.
 Unbeknown to the participant, this location systematically corresponded to either the colder temperature (Exp. 1) or the warmer temperature (Exp. 2).
-Participants had max 8 seconds to provide each rating, and if they did not complete a rating within the allowed timeframe, the trial was repeated.
-Following the completion of the last of the three VAS ratings, we presented a 200 ms fixation dot.
-Each thermode configuration was tested three consecutive times, on three different skin locations.
-An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter when to rearrange the thermode configuration to stimulate different dermatomes depending on a pseudo-randomisation order.
+An auditory cue (300Hz, 100ms) indicated when the participants completed all ratings, after which the experimenter removed the thermodes from their skin.
+We presented a 200ms fixation dot before beginning the next trial.
+Each thermode configuration was tested three consecutive times on each arm, on three different and non-overlapping skin locations.
+An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter when to rearrange the thermode configuration or change arms to stimulate different dermatomes depending on a pseudo-randomisation order.
 Each of the four experimental conditions was repeated 12 times, with both the right and left forearms stimulated, and a minimum of five trials between the re-stimulation of the same skin location.
-This ensured that the same skin locations were not stimulated consecutively to minimise carry-over effects.
+This method ensured that the same skin locations were not stimulated consecutively to minimise the potential of carry-over effects.
 
 Experiments 1 and 2 were conducted in two independent groups of participants and followed exactly the same procedure except for two elements.
-In experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs.
-In experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs.
+In Experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs, where the temperature of the cold thermode in both conditions was the same.
+In Experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs, where the temperature of the warm thermode in both conditions was the same.
 
@@
 
-An initial pilot study informed the pre-registered calculation of the sample size.
-To test the directional TGI hypothesis with 95% power and detect an effect size of .12 or greater, we determined that we needed a minimum number of 32 TGI-responsive participants.
+An initial pilot study informed the [pre-registered](https://osf.io/4xcn5/) calculation of the sample size.
+To test the directional TGI hypothesis with 95% power and detect an effect size for the coefficient of .12 or greater, we determined that we needed a minimum number of 32 TGI-responsive participants.
 We defined TGI-responders as those individuals for whom the median burning ratings for TGI stimuli significantly exceeded 0.
 Non-responders were individuals that did not meet this criterion when tested with the max cold-warm temperatures allowed in the experiment.
-In experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants.
-We verified this criterion every 10 participants, resulting in a total sample size of 40 participants.
-In experiment 2, we stopped recruitment once we collected data from 40 participants.
-This decision was based on meeting both required criteria: (1) matching the sample size of experiment 1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.
+The predefined cut-off for TGI stimulation was 10ºC and 44ºC, due to both limitations of the thermode and to reduce likelihood of sensitization to heat stimuli.
+In Experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants.
+We verified this criterion every 10 participants, resulting in a total sample size of 40 participants with 32 TGI responders.
+In Experiment 2, we stopped recruitment once we collected data from 40 participants, which resulted in a total of 37 TGI responders.
+This decision was based on meeting both required criteria: (1) matching the sample size of Exp.
+1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.
 
@@
 Following re-scaling, we applied zero-inflated mixed-effects beta regression models separately for each set of VAS ratings.
-In these models, we incorporated three fixed effects.
-These included the type of stimulation (non-TGI vs.
-TGI), the dermatome condition (within the same dermatome vs.
-across different dermatomes) and the spatial positioning of the cold or neutral thermode (proximal vs.
-distal within dermatomes; rostral vs.
-caudal across dermatomes).
-These choices allowed us to assess the individual and interactive effects of these three factors on VAS ratings.
-Further, we added random intercepts to our models to account for between-subject variability and the effects of repeated measures.
-The variables introduced as random intercepts included the participant ID, the counterbalancing order and the trial number.
+In these models, we incorporated three fixed effects; the type of stimulation (non-TGI vs. TGI), the dermatome condition (within the same dermatome vs. across different dermatomes) and the spatial positioning of the cold or neutral thermode (proximal vs. distal within dermatomes; rostral vs. caudal across dermatomes).
+This allowed us to assess the individual and interactive effects of these three factors on VAS ratings.
+Further, we added random intercepts of subject and trial order to our models to account for between-subject variability and the effects of repeated measures.
+
 The choices of the zero-inflated approach and the use of beta regressions were necessitated by the specific distribution of VAS ratings.
@@
 The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.
-We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
+We carried out the statistical analyses using the \'glmmTMB\' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
+
+For data presentation purposes, the median VAS ratings for each sensory quality (cold, warm, burning) were calculated per simulation type (TGI, non-TGI), dermatome (within, across) and spatial location (proximo-distal, rostro-caudal) for each participant.
+For hypothesis one, these values were further averaged so there were only four values per participant, for each sensory quality (within and across dermatome ratings for TGI and non-TGI stimuli).
+For analysis of burning VAS ratings, only those participants who were deemed as TGI responders (n = 32 for Exp. 1 and n = 37 for Exp. 2) were included.
+
 The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [experiment 1](https://osf.io/4xcn5/) and [experiment 2](https://osf.io/dhg8u/).

### 2023-08-22 Manuscript.Rmd
updating figures

@@
 
-source(here::here("scripts","utility.R"))
-source(here::here("scripts","plots.R"))
-source(here::here("scripts","supplementary.R"))
-
-#get models
-source(here::here("scripts","models.R"))
+# functions and data
+source(file.path("scripts","utility.R"))
+source(file.path("scripts","plots.R"))
+source(file.path("scripts","supplementary.R"))
+source(file.path("scripts","models.R"))
 
@@
 list2env(stats, envir=environment())
-
 ```
@@
 ggdraw() +
-    draw_image(magick::image_read(here::here("figures","figure1_v2.PNG")), scale = 1)
+    draw_image(magick::image_read(file.path("figures","figure1_v2.PNG")), scale = 1)
 ```
@@
 The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.
-We carried out the statistical analyses using the \'glmmTMB\' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
+We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
 
@@
 
-We would like to thank XXX for their help with participant recruitment and data collection.
+We thank Małgorzata Basińska, Patrik Molnár, Sára A. Szabó for their help with participant recruitment and data collection.
+We also thank Michael Clements for the collection of pilot data that was instrumental in refining the experimental design.
 This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948788).
@@
 
+Tables of main effects and interactions for each sensory quality (cold, warm, burning) for experiment 1 and experiment 2.
+
+## Cold ratings
+
 ```{r,warning = F, message = F, echo = F}
@@
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
+```
 
+```{r,warning = F, message = F, echo = F}
 get_main_tables(model_cold_exp2,round = 2, title = "Exp. 2: Warm reference on cold ratings") %>%
@@
 
+## Warm ratings
+
 ```{r,warning = F, message = F, echo = F}
-
 get_main_tables(model_warm_exp1,round = 2, title = "Exp.1: Cold reference on warm ratings") %>%
@@
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
+```
 
+```{r,warning = F, message = F, echo = F}
 get_main_tables(model_warm_exp2,round = 2, title = "Exp. 2: Warm reference on warm ratings") %>%
@@
 
+## Burning ratings
+
 ```{r,warning = F, message = F, echo = F}
-
 get_main_tables(model_burn_exp1,round = 2, title = "Exp. 1: Cold reference on burning ratings") %>%
@@
   fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
+```
 
+```{r,warning = F, message = F, echo = F}
 get_main_tables(model_burn_exp2,round = 2, title = "Exp. 2: Warm reference on burning ratings") %>%
@@
 \newpage
-
-## Proximodistal bias in cold perception
-
-Experiment 1: warm ratings (stimulation by dermatome interaction: \$\\beta\$ = r stats_model_warm_exp1\$beta[8], r make_pvalue(stats_model_warm_exp1\$p[8]); dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[4]`, `r make_pvalue(stats_model_warm_exp1$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`)
-
-Experiment 2: warm ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[8]`, `r make_pvalue(stats_model_warm_exp2$p[8])`); dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[4]`, `r make_pvalue(stats_model_warm_exp2$p[4])`) or burning ratings (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[8]`, `r make_pvalue(stats_model_burn_exp2$p[8])`); dermatome main effect: $\beta$ = `r stats_model_burn_exp2$beta[4]`, `r make_pvalue(stats_model_burn_exp2$p[4])`).
-
-## Directional effects in inter-segmental sensory integration
-
-Experiment 1: burn ratings (stimulation by rostrocaudal location: $\beta$ = `r stats_model_burn_exp1$beta[7]`, `r make_pvalue(stats_model_burn_exp1$p[7])`; rostrocaudal main effect ($\beta$ = `r stats_model_burn_exp1$beta[3]`, `r make_pvalue(stats_model_burn_exp1$p[3])`)

### 2023-08-22 scripts/models.R

@@ -173,7 +173,7 @@ if(rerun){
   return(savings)
 }else{
   
-  load(here::here("Workspace","stats.RData"))
+  load(file.path("Workspace","stats.RData"))
   
   return(savings)
 }

### 2023-08-22 scripts/plots.R

@@ -5,19 +5,21 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
   plot = data = vas_h1_diff %>% ggplot(aes(colour = quality)) +
     geom_hline(yintercept = 0, colour = 'grey50') +
     geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
-               alpha = .5) +
+               alpha = .5, size = 1.7) +
     geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
                fill = 'grey15',
                shape = 21, size = 3) +
     geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
                                           ymax = difference+ci), 
-                  width = .1, size = .7, colour = 'grey15') +
+                  width = .15, size = .75, colour = 'grey15') +
     facet_wrap(~quality) +
     scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
     labs(title = paste0(title),
          y = 'Within - Across VAS Ratings', x = NULL) +
     theme_classic() +
-    theme(legend.position = 'none')+coord_cartesian(ylim = c(-30,30))+scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
+    theme(legend.position = 'none')+
+    coord_cartesian(ylim = c(-30,30))+
+    scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
   plot
   return(plot)
@@ -36,7 +38,8 @@ plot1 = function(include_zero = T){
   
   h1_diff_plot_exp1 = make_plot1(vas_h1_diff = vas_h1_diff_exp1,
                                  h1_diff_sum = h1_diff_sum_exp1,
-                                 title = "Reference: Cold Thermode")
+                                 title = "Reference: Cold Thermode") +
+                                 theme(title = element_text(size = 10))
   
   
   # experiment 2 file
@@ -47,10 +50,14 @@ plot1 = function(include_zero = T){
   
   h1_diff_plot_exp2 = make_plot1(vas_h1_diff = vas_h1_diff_exp2,
                                  h1_diff_sum = h1_diff_sum_exp2,
-                                 title = "Reference: Warm Thermode")+
-                                theme(axis.text.y=element_blank(),axis.ticks.y=element_blank(),axis.title.y=element_blank())
[…]

### 2023-08-22 scripts/supplementary.R

@@ -62,3 +62,38 @@ FitFlextableToPage <- function(ft, pgwidth = 6){
   ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
   return(ft_out)
 }
+
+make_sPlot = function(vas_h1_diff, h1_diff_sum, title){
+  
+  # now plot the difference
+  plot = data = vas_h1_diff %>% ggplot(aes(colour = quality)) +
+    geom_hline(yintercept = 0, colour = 'grey50') +
+    geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
+               alpha = .5, size = 1.7) +
+    geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
+               fill = 'grey15',
+               shape = 21, size = 3) +
+    geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
+                                          ymax = difference+ci), 
+                  width = .15, size = .75, colour = 'grey15') +
+    facet_wrap(~quality) +
+    scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
+    labs(title = paste0(title),
+         y = 'Within - Across VAS Ratings', x = NULL) +
+    theme_classic() +
+    theme(legend.position = 'none')+
+    coord_cartesian(ylim = c(-30,30))+
+    scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
+  
+  plot
+  return(plot)
+  
+}
+
+# make supplementary figures for experiment 1 and experiment 2
+sPlot = function(include_zero = T){
+  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), include_zero = include_zero)
+  vas_meds_exp1 = experiment1$vas_meds
+  
+}
+

### 2023-08-22 scripts/utility.R

@@ -213,6 +213,7 @@ prep_data = function(file, include_zero = T){
   
   return(list(all_vas = all_vas,
               init_burn = init_burn,
+              vas_meds = vas_meds,
               vas_h1_diff = vas_h1_diff,
               h1_diff_sum = h1_diff_sum,
               vas_h2_diff = vas_h2_diff,

### 2023-08-22 Manuscript.Rmd
adding supplementary figure with all data

@@
 \newpage
+
+```{r, results="hide", fig.width = 8, fig.height = 10, warning = F, message = F, echo = F, fig.cap = "Figure S1: Individual median VAS ratings for Experiment 1 (A-C) and Experiment 2 (D-F) across stimulus manipulation, and spatial location.
+Proximal and distal locations are within dermatome, rostral and caudal locations are across dermatomes.
+All spatial locations refer to the location of the cold thermode, compared to the warm.
+Box plots show median and interquartile range."}
+
+# supplementary first panel
+sPlot(include_zero = T)
+#plot1(include_zero = F)
+```

### 2023-08-22 scripts/supplementary.R

@@ -63,27 +63,70 @@ FitFlextableToPage <- function(ft, pgwidth = 6){
   return(ft_out)
 }
 
-make_sPlot = function(vas_h1_diff, h1_diff_sum, title){
+make_sPlot = function(vas_meds, h2_sum, VAS_type, title, l_pos){
   
-  # now plot the difference
-  plot = data = vas_h1_diff %>% ggplot(aes(colour = quality)) +
-    geom_hline(yintercept = 0, colour = 'grey50') +
-    geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
-               alpha = .5, size = 1.7) +
-    geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
-               fill = 'grey15',
-               shape = 21, size = 3) +
-    geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
-                                          ymax = difference+ci), 
-                  width = .15, size = .75, colour = 'grey15') +
-    facet_wrap(~quality) +
-    scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
-    labs(title = paste0(title),
-         y = 'Within - Across VAS Ratings', x = NULL) +
+  # plot all data, with 0s
+  plot = ggplot(data = vas_meds %>% 
+           filter(quality == VAS_type),
+         mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'proximal', manipulation == 'Non-TGI'),
+                   position = position_nudge(x = -.1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'proximal', manipulation == 'TGI'),
+                   position = position_nudge(x = .1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'distal', manipulation == 'Non-TGI'),
[…]

### 2023-08-22 scripts/utility.R

@@ -214,6 +214,7 @@ prep_data = function(file, include_zero = T){
   return(list(all_vas = all_vas,
               init_burn = init_burn,
               vas_meds = vas_meds,
+              h2_sum = h2_sum,
               vas_h1_diff = vas_h1_diff,
               h1_diff_sum = h1_diff_sum,
               vas_h2_diff = vas_h2_diff,

### 2023-08-22 Manuscript.Rmd
finalising all changes and knitting

--- 2023-08-22 Manuscript.Rmd
@@
 \newpage
+
+```{r, results="hide", fig.width = 7.2, fig.height = 9, warning = F, message = F, echo = F, fig.cap = "Figure S1: Individual median VAS ratings for Experiment 1 (A-C) and Experiment 2 (D-F) across stimulus manipulation, and spatial location.
+Proximal and distal locations are within dermatome, rostral and caudal locations are across dermatomes.
+All spatial locations refer to the location of the cold thermode, compared to the warm.
+Box plots show median and interquartile range.
+Data presented here include trials where VAS ratings equal 0, which are modelled seperately in the main analyses"}
+
+# supplementary first panel
+sPlot(include_zero = T)
+#plot1(include_zero = F)
+```

### 2023-08-22 scripts/supplementary.R

@@ -142,7 +142,7 @@ sPlot = function(include_zero = T){
   experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), include_zero = include_zero)
   vas_meds = experiment1$vas_meds
   h2_sum = experiment1$h2_sum
-  main_title = 'Experiment 1: Cold thermode'
+  main_title = 'Reference: Cold Thermode'
     
   
   s_plotA = make_sPlot(vas_meds = vas_meds, h2_sum = h2_sum, 
@@ -172,7 +172,7 @@ sPlot = function(include_zero = T){
   experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'), include_zero = include_zero)
   vas_meds = experiment2$vas_meds
   h2_sum = experiment2$h2_sum
-  main_title = 'Experiment 2: warm thermode'
+  main_title = 'Reference: Warm Thermode'
   
   s_plotD = make_sPlot(vas_meds = vas_meds, h2_sum = h2_sum, 
                        VAS_type = 'cold', title = 'Cold ratings', l_pos = 'right') +
@@ -200,7 +200,7 @@ sPlot = function(include_zero = T){
   #compile the two experiments
   s_plot_out = ggarrange(s_plot_1, s_plot_2,
                          nrow = 1, ncol = 2,
-                         widths = c(1,1.5))
+                         widths = c(1,1.2))
   
   s_plot_out
   

### 2023-08-22 scripts/supplementary.R
minor figure size changes

@@ -200,7 +200,7 @@ sPlot = function(include_zero = T){
   #compile the two experiments
   s_plot_out = ggarrange(s_plot_1, s_plot_2,
                          nrow = 1, ncol = 2,
-                         widths = c(1,1.2))
+                         widths = c(1,1.4))
   
   s_plot_out
   

### 2023-08-23 Manuscript.Rmd
adding .csl file for references

@@
         Jesper Fischer Ehmsen^1^,
-        Daniel Elmstrom Christensen^1^,
+        Daniel Elmstrøm Christensen^1^,
         Anna Villaume Stuckert^2^,
@@
   word_document:
-      reference_docx: knitting files/test_markdown.docx
+      reference_docx: knitting_files/test_markdown.docx
   html_document:
-    css: knitting files/style.css
+    css: knitting_files/style.css
   pdf_document:
@@
 indent: true
-bibliography: knitting files/tgi-spine2.bib
+bibliography: knitting_files/tgi-spine2.bib
+csl: knitting_files/nature.csl
 link-citations: yes

### 2023-08-23 scripts/plots.R
doing a bit of organising

@@ -1,4 +1,4 @@
-
+# plots for hypothesis 1
 make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
   
   # now plot the difference
@@ -17,7 +17,8 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
     labs(title = paste0(title),
          y = 'Within - Across VAS Ratings', x = NULL) +
     theme_classic() +
-    theme(legend.position = 'none')+
+    theme(legend.position = 'none',
+          axis.text = element_text(size = 10)) +
     coord_cartesian(ylim = c(-30,30))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
@@ -60,9 +61,15 @@ plot1 = function(include_zero = T){
           plot_annotation(tag_levels = list(c("A","B")))
   
   plot1
+  
+  # save plot
+  ggsave(file.path("figures", "Figure2.tiff"), plot = plot1, device = NULL, 
+         width = 7.2, height = 5, dpi = 600)
+  
   return(plot1)
 }
 
+# plots for hypothesis 2
 make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
   
   
@@ -182,7 +189,13 @@ plot2_3 = function(include_zero = T){
              title = element_text(size = 10)))+
     plot_annotation(tag_levels = list("A","B"))
   
+  # save plots
+  ggsave(file.path("figures", "Figure3.tiff"), plot = plot2, device = NULL, 
+         width = 7.2, height = 5, dpi = 600)
+  ggsave(file.path("figures", "Figure4.tiff"), plot = plot3, device = NULL, 
+         width = 7.2, height = 5, dpi = 600)
   
   return(list(plot2,plot3))
+
 }
 

### 2023-08-23 scripts/plots.R
small figure changes

@@ -18,7 +18,10 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
          y = 'Within - Across VAS Ratings', x = NULL) +
     theme_classic() +
     theme(legend.position = 'none',
-          axis.text = element_text(size = 10)) +
+          axis.text = element_text(size = 9),
+          axis.title = element_text(size = 11),
+          strip.text = element_text(size = 10),
+          title = element_text(size=10)) +
     coord_cartesian(ylim = c(-30,30))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
@@ -39,8 +42,7 @@ plot1 = function(include_zero = T){
   
   h1_diff_plot_exp1 = make_plot1(vas_h1_diff = vas_h1_diff_exp1,
                                  h1_diff_sum = h1_diff_sum_exp1,
-                                 title = "Reference: Cold Thermode") +
-                                 theme(title = element_text(size = 10))
+                                 title = "Reference: Cold Thermode") 
   
   
   # experiment 2 file
@@ -54,8 +56,7 @@ plot1 = function(include_zero = T){
                                  title = "Reference: Warm Thermode") +
                                  theme(axis.text.y=element_blank(),
                                        axis.ticks.y=element_blank(),
-                                       axis.title.y=element_blank(),
-                                       title = element_text(size = 10))
+                                       axis.title.y=element_blank())
   
   plot1 = h1_diff_plot_exp1+h1_diff_plot_exp2 +
           plot_annotation(tag_levels = list(c("A","B")))
@@ -93,7 +94,11 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
          y = 'Proximal - Distal VAS Ratings', x = NULL) +
     facet_wrap(~quality) +
     theme_classic() +
-    theme(legend.position = 'none')+
+    theme(legend.position = 'none',
+          axis.text = element_text(size = 9),
+          axis.title = element_text(size = 11),
+          strip.text = element_text(size = 10),
+          title = element_text(size = 10))+
     coord_cartesian(ylim = c(-60,60))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
@@ -117,7 +122,11 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
          y = 'Caudal - Rostral VAS Ratings', x = NULL) +
     facet_wrap(~quality) +
     theme_classic() +
[…]

### 2023-08-23 Manuscript.Rmd

@@
 
+## Data availability
+
 The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [experiment 1](https://osf.io/4xcn5/) and [experiment 2](https://osf.io/dhg8u/).
-All data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript), ensuring the reproducibility of our findings.
+
+All raw data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript).
+This, and a wiki guide to analysing the data, can be accessed through the project's [OSF page](https://osf.io/uyrtq/).
 

### 2023-08-23 old/testing.Rmd

--- 2023-07-14 testing.Rmd
@@
                             na.action = na.omit,
-                            contrasts=list(cold_probe = cold)
+                            contrasts=list(cold_probe = cold))
 
@@
 
+model_burn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + trial_n +
+                              (1|ID) + (1|order),
+                            family = glmmTMB::beta_family(),
+                            ziformula = ~1+manipulation,
+                            data = df_long_exp1 %>% filter(quality == 'burn'),
+                            na.action = na.omit)
+
+plot(ggeffect(model_burn, terms = c("manipulation")))
+
+quality = "burn"
+
+meaneffects = df_long_exp1 %>% filter(quality == 'burn', beta != 0) %>% group_by(manipulation,cold_probe) %>% summarize(mean = mean(beta), se = sd(beta)/sqrt(n()))
+
+plot2 = df_long_exp1 %>% filter(quality == 'burn', beta != 0) %>% group_by(ID, manipulation,cold_probe) %>% summarize(mean = mean(beta)) %>% ggplot(aes(x = manipulation, y = mean, col = cold_probe))+geom_point(position = position_dodge(width = 0.3))+
+  geom_pointrange(data = meaneffects, aes(x = manipulation, col = cold_probe, y = mean, ymin = mean-2*se, ymax = mean+2*se), size = 0.5, linewidth = 1.5,position = position_dodge(width = 0.5))+theme_classic()+
+  geom_line(
+    data = meaneffects,
+    aes(x = manipulation, y = mean, group = cold_probe, col = cold_probe),
+    position = position_dodge(width = 0.5),
+    size = 1.2)+ggtitle("Without 0")
+
+meaneffects2 = df_long_exp1 %>% filter(quality == 'burn') %>% group_by(manipulation,cold_probe) %>% summarize(mean = mean(beta, na.rm = T), se = sd(beta, na.rm =T)/sqrt(n()))
+
+plot1 = df_long_exp1 %>% filter(quality == 'burn') %>% group_by(ID, manipulation,cold_probe) %>% summarize(mean = mean(beta)) %>% ggplot(aes(x = manipulation, y = mean, col = cold_probe))+geom_point(position = position_dodge(width = 0.3))+
+  geom_pointrange(data = meaneffects2, aes(x = manipulation, col = cold_probe, y = mean, ymin = mean-2*se, ymax = mean+2*se), size = 0.5, linewidth = 1.5,position = position_dodge(width = 0.5))+theme_classic()+
+  geom_line(
+    data = meaneffects2,
+    aes(x = manipulation, y = mean, group = cold_probe, col = cold_probe),
+    position = position_dodge(width = 0.5),
+    size = 1.2)+ggtitle("With 0")
+
+plot1+plot2
 ```

### 2023-08-23 testing the differencea.Rmd

---
title: "testing"
author: "jesper fischer ehmsen"
date: "2023-07-26"
output:
  html_document: default
  pdf_document: default
---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
               ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
               modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
               rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, cowplot,
               sjPlot
               )

source(here::here("scripts","utility.R"))
source(here::here("scripts","plots.R"))
source(here::here("scripts","models.R"))
```

Loading the data and defining the contrast:

```{r, warning=FALSE, results='hide'}
experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))

df_long_exp2 = experiment2$df_long %>% 
  mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
## Define constrats such that we both get within / across (i.e. distal & proximal vs rostral & caudual)
levels(df_long_exp2$cold_probe)
# "caudal"   "distal"   "proximal" "rostral"

#within - across
within_across = c(-1/2,1/2,1/2,-1/2)
#caudal - rostral
caudal_rostral = c(1,0,0,-1)
#distral - proximal
proximal_distal = c(0,-1,1,0)

#define the matrix
cold = rbind(1/4,within_across,caudal_rostral,proximal_distal)

#solve it 
cold = solve(cold)
```

looking at just one subject and modeling it with a normal linear regression.

First my way:

```{r, warning=FALSE}
df_long_exp1_cold = df_long_exp2 %>% filter(quality == 'cold') %>% filter(ID == 45)

model_cold_exp = lm(beta ~ manipulation * cold_probe,
                              data = df_long_exp1_cold,
                              na.action = na.omit,
                              contrasts=list(cold_probe = cold) 
                              ) 
tab_model(model_cold_exp, digits = 4)
```
<br>
<br>

The interaction between TGI and Within / across is here $\beta$ = 0.0592 p = 0.180

Then the other way:

```{r, warning=FALSE}
model_cold_exp1 = lm(beta ~ manipulation * cold_cond * condition,
                              data = df_long_exp1_cold,
                              na.action = na.omit
                              )

tab_model(model_cold_exp1, digits = 4)
```
<br>
<br>
here the interaction between TGI and Within / across is $\beta$ = -0.0456 p = 0.464

The difference seems to be the following:
<br>
if we group by the three conditions and then take only take the reference level for the cold_condition i.e. dist_rostr and then compute the difference in manipulation (control / TGI) across the difference in condition (within / across) (i.e the manipulation * condition interaction), we get the estimate from the second model i.e. -0.0456.

```{r, warning=FALSE}
df_long_exp1_cold %>% group_by(manipulation,condition, cold_cond) %>% 
  summarize(mean = mean(beta)) %>% filter(cold_cond == "dist_rostr") %>% mutate(cold_cond = NULL) %>% 
  pivot_wider(names_from = c(condition,manipulation), values_from = mean) %>%
  mutate(dif_cnt = within_CNT-across_CNT,
         dif_TGI = within_TGI-across_TGI) %>% 
  mutate(dif_dif = dif_TGI-dif_cnt) %>% .$dif_dif
```

<br>
<br>

If we on the other hand just group by manipulation and condition i.e. not filtering by dist_rostr we get the second estimate i.e. 0.0592.

```{r, warning=FALSE}
df_long_exp1_cold %>% group_by(manipulation,condition) %>% 
  summarize(mean = mean(beta)) %>% 
  pivot_wider(names_from = c(condition,manipulation), values_from = mean) %>%
  mutate(dif_cnt = within_CNT-across_CNT,dif_TGI = within_TGI-across_TGI) %>% 
  mutate(dif_dif = dif_TGI-dif_cnt) %>% .$dif_dif

```

<br>
<br>

One can also double check this with a model that only contained the manipulation and condition as factors:
```{r, warning=FALSE}
model_cold_exp2 = lm(beta ~ manipulation * condition,
                              data = df_long_exp1_cold,
                              na.action = na.omit
                              )

tab_model(model_cold_exp2, digits = 4)
```

### 2023-08-29 Manuscript.Rmd
removing hyperlinks, as they do not work in submission

--- 2023-08-23 Manuscript.Rmd
@@
 
-The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [experiment 1](https://osf.io/4xcn5/) and [experiment 2](https://osf.io/dhg8u/).
-All data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript), ensuring the reproducibility of our findings.
+## Data availability
+
+The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both experiment 1 (https://osf.io/4xcn5/) and experiment 2 (https://osf.io/dhg8u/).
+
+All raw data and code for the analysis are available in the GitHub repository (https://github.com/Body-Pain-Perception-Lab/tgi-spinal).
+This, and a wiki guide to analysing the data, can be accessed through the project's OSF page (https://osf.io/uyrtq/).
 

### 2023-09-14 Manuscript.Rmd
editing for PAIN

@@
 bibliography: knitting_files/tgi-spine2.bib
-csl: knitting_files/nature.csl
+csl: knitting_files/ieee.csl
 link-citations: yes
@@
 :::
+
+```{r, warning = F, message = F, echo = F,include=FALSE}
+if (!require("pacman")) install.packages("pacman")
+
+pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
+               ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest,
+               modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
+               rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, 
+               cowplot, flextable
+               )
+
+# functions and data
+source(file.path("scripts","utility.R"))
+source(file.path("scripts","plots.R"))
+source(file.path("scripts","supplementary.R"))
+source(file.path("scripts","models.R"))
+
+stats = statistics(rerun = F)
+
+#save.image("~/tgi-spinal/Workspace/stats.RData")
+
+list2env(stats, envir=environment())
+```
 
@@
 
-# Results and discussion
+# Methods
+
+## Participants
+
+The study entailed two separate experiments, collectively involving 80 healthy volunteers.
+Forty participants took part in experiment 1 (`r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old, SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) and another 40 participants in experiment 2 (`r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary, mean age = `r descript_exp2_age$mean_age` years old, SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`).
+The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
+Prior to commencing the study, all participants were fully informed about the procedures and provided their voluntary consent.
+
+## Stimuli and procedure
+
+All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3 software (version 5.4b).
+The procedure involved measurements of heat and cold pain thresholds, calibration of cold-warm temperature pairs eliciting TGI, and an experimental task where TGI and non-TGI stimuli were applied on dermatomes that mapped onto adjacent or nonadjacent spinal segments.
 
@@
 We instructed participants to report the sensation from just one of the thermal components, corresponding to the cold thermode location (Exp. 1) or the warm thermode location (Exp. 2).
-Importantly, the aim of this method was not to isolate any possible independent effect of warm and cold stimulation during TGI, but rather to ensure consistency in participants' ratings across trials and different stimulus conditions.
-
-To investigate both the thermosensory and burning components in each experiment, we asked participants to provide a subjective evaluation of multiple sensory qualities - cold, warmth and burning (pain).
+Importantly, the aim of this method was not to isolate any possible independent effect of warm and cold stimulation during TGI, but rather to ensure consistency in participants' ratings across trials and different stimulus conditions.To investigate both the thermosensory and burning components in each experiment, we asked participants to provide a subjective evaluation of multiple sensory qualities - cold, warmth and burning (pain).
 Stimuli consisted of either cold-warm pairs (TGI stimuli), which potentially evoked an illusion of heat and pain, or control stimuli that involved pairing a cold (Exp.
@@
 All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments (Figure 1A and B).
-After ten seconds of stimulation, participants reported their ratings using three sequential VAS scales ranging from 0, indicating the lack of the corresponding sensory quality, to 100, indicating an extreme sensation (Figure 1C), presented in a random order.
-For each instance of stimulation, participants were guided to focus their reporting on the sensations originating either thermode 'A' or 'B' which corresponded to either the cold (Exp.
-1) or warm (Exp.
-2) thermode.
-This labelling was used to ensure participants were not immediately aware of the temperature associated with each probe.
-VAS ratings for each sensation were analysed using mixed-effects zero-inflated beta regressions, where VAS ratings that equaled zero for non-TGI and TGI stimulation were modelled separately to VAS ratings above zero.
-
-```{r, warning = F, message = F, echo = F,include=FALSE}
-if (!require("pacman")) install.packages("pacman")
-
-pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
-               ggeffects, gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
-               modelsummary, MuMIn, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
-               rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, cowplot,
-               flextable
-               )
-
-# functions and data
-source(file.path("scripts","utility.R"))
-source(file.path("scripts","plots.R"))
-source(file.path("scripts","supplementary.R"))
-source(file.path("scripts","models.R"))
-
-stats = statistics(rerun = F)
-
-#save.image("~/tgi-spinal/Workspace/stats.RData")
-
-list2env(stats, envir=environment())
-```
 
@@
 
+## Procedure
+
+We measured cold and heat pain thresholds in a stepwise manner, the order of which was counterbalanced across participants.
+For cold pain, a single thermode at a starting temperature of 25ºC was held on the participant's dorsal forearm for five seconds.
+After which, the participant verbally reported (yes/no) any experience of pain.
+If the participant reported no pain, the temperature of the thermode was lowered by 5ºC, and placed back on the skin for another five seconds after which the participant reported whether they experienced pain.
+This step was repeated either until the participant responded 'yes' or the thermode reached the set minimum temperature of 5ºC.
+If the participant responded 'yes' before the minimum temperature, the temperature of the thermode was increased by 1ºC until the participant no longer experienced pain.
+The cold pain threshold was identified as the highest temperature at which the participant reported a painful experience.
+The same steps were repeated for heat pain, but with increasing intervals of 5ºC and with a starting temperature of 35ºC and a maximum temperature of 45ºC.
+The heat pain threshold was identified as the lowest temperature at which the participant reported a painful experience.
+
+We calibrated TGI stimuli by identifying a cold-warm temperature pair based on specific criteria: (1) consistently eliciting a burning sensation of at least 15 on a scale ranging from 0 to 100, (2) consistently avoiding a burning sensation (less than 15) when the cold-neutral (Exp.
+1) or warm-neutral (Exp.
+2) stimuli were presented, (3) both cold and warm temperatures falling within the innocuous range based on individual cold and heat pain thresholds.
+For pain threshold measurements and TGI calibration, we positioned the probes within a single dermatome.
+To address our experimental questions, we presented the calibrated TGI stimuli, as well as cold-neutral (Exp. 1) or warm-neutral (Exp. 2) non-TGI stimuli using two thermodes.
+In non-TGI stimuli the cold or warm temperatures were set to match the temperature used for TGI stimulation, but paired with a neutral temperature set at 30ºC.
+
+The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant's forearm size.
+The positioning of the thermodes was either within the same dermatome (C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1).
+Further, we manipulated the spatial arrangement of the temperature pairs, by systematically presenting an equal number of trials where the cold thermode was applied on a proximal or distal location within a dermatome, or was applied on a dermatome that mapped onto a rostral or caudal segment along the spinal cord.
+We based the demarcation of the dermatome boundaries on the American Spinal Injury Association (ASIA) map and positioned the thermodes in relation to standard anatomical landmarks.
+Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head (C6) or the lower back (T1).
+Spatial arrangements of stimuli are depicted in Figure 1B.
+The order of the stimuli (TGI vs. non-TGI), the dermatome condition (within vs. across) and the relative placement of the colder temperature (proximal vs. distal or rostral vs. caudal) were pseudo-randomised and counterbalanced between participants.
+
+During each trial, the experimenter positioned two thermodes on the participant's skin for 10 seconds, after which participants rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales.
+VAS scales were presented one at a time on a computer screen and appeared as a horizontal line, anchored at 0, representing no sensation (e.g., no burning), and 100, signifying an extreme sensation (e.g., extreme burning).
+The order of the three VAS scales was randomised across trials and participants had a maximum of eight seconds to respond to each scale.
+For each scale, participants provided their responses using the arrow keys on a keyboard and rated the intensity of their sensations from a specific location (labeled 'A' or 'B'), based on the experimenter's instruction.
+Unbeknown to the participant, this location systematically corresponded to either the colder temperature (Exp. 1) or the warmer temperature (Exp. 2).
+An auditory cue (300Hz, 100ms) indicated when the participants completed all ratings, after which the experimenter removed the thermodes from their skin.
+We presented a 200ms fixation dot before beginning the next trial.
+Each thermode configuration was tested three consecutive times on each arm, on three different and non-overlapping skin locations.
+An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter when to rearrange the thermode configuration or change arms to stimulate different dermatomes depending on a pseudo-randomisation order.
+Each of the four experimental conditions was repeated 12 times, with both the right and left forearms stimulated, and a minimum of five trials between the re-stimulation of the same skin location.
+This method ensured that the same skin locations were not stimulated consecutively to minimise the potential of carry-over effects.
+
+Experiments 1 and 2 were conducted in two independent groups of participants and followed exactly the same procedure except for two elements.
+In Experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs, where the temperature of the cold thermode in both conditions was the same.
+In Experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs, where the temperature of the warm thermode in both conditions was the same.
+
+## Sample size
+
+An initial pilot study informed the [pre-registered](https://osf.io/4xcn5/) calculation of the sample size.
+To test the directional TGI hypothesis with 95% power and detect an effect size for the coefficient of .12 or greater, we determined that we needed a minimum number of 32 TGI-responsive participants.
+We defined TGI-responders as those individuals for whom the median burning ratings for TGI stimuli significantly exceeded 0.
+Non-responders were individuals that did not meet this criterion when tested with the max cold-warm temperatures allowed in the experiment.
+The predefined cut-off for TGI stimulation was 10ºC and 44ºC, due to both limitations of the thermode and to reduce likelihood of sensitization to heat stimuli.
+In Experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants.
+We verified this criterion every 10 participants, resulting in a total sample size of 40 participants with 32 TGI responders.
+In Experiment 2, we stopped recruitment once we collected data from 40 participants, which resulted in a total of 37 TGI responders.
+This decision was based on meeting both required criteria: (1) matching the sample size of Exp.
+1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.
+
+## Data analyses
+
+We re-scaled data from cold, warm and burning VAS ratings from their original values to a range of 0 to 1.
+Following re-scaling, we applied zero-inflated mixed-effects beta regression models separately for each set of VAS ratings.
+In these models, we incorporated three fixed effects; the type of stimulation (non-TGI vs. TGI), the dermatome condition (within the same dermatome vs. across different dermatomes) and the spatial positioning of the cold or neutral thermode (proximal vs. distal within dermatomes; rostral vs. caudal across dermatomes).
+This allowed us to assess the individual and interactive effects of these three factors on VAS ratings.
+Further, we added random intercepts of subject and trial order to our models to account for between-subject variability and the effects of repeated measures.
+
+The choices of the zero-inflated approach and the use of beta regressions were necessitated by the specific distribution of VAS ratings.
+The beta distribution is suitable for modelling VAS rating data, as they are proportional in nature.
+Additionally, the zero-inflation was needed due to the presence of an excess number of zero values in specific ratings and conditions.
+Specifically, we anticipated an over-representation of zero values for thermosensory ratings that were counterfactual to the objective stimulation quality (i.e., cold ratings of warm stimuli and warm ratings of cold stimuli) and burning ratings of non-TGI stimuli.
+The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.
+We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
+
+For data presentation purposes, the median VAS ratings for each sensory quality (cold, warm, burning) were calculated per simulation type (TGI, non-TGI), dermatome (within, across) and spatial location (proximo-distal, rostro-caudal) for each participant.
+For hypothesis one, these values were further averaged so there were only four values per participant, for each sensory quality (within and across dermatome ratings for TGI and non-TGI stimuli).
+For analysis of burning VAS ratings, only those participants who were deemed as TGI responders (n = 32 for Exp. 1 and n = 37 for Exp. 2) were included.
+
+## Data availability
+
+The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both experiment 1 (https://osf.io/4xcn5/) and experiment 2 (https://osf.io/dhg8u/).
+
+All raw data and code for the analysis are available in the GitHub repository (https://github.com/Body-Pain-Perception-Lab/tgi-spinal).
+This, and a wiki guide to analysing the data, can be accessed through the project's OSF page (https://osf.io/uyrtq/).
+
+\newpage
+
+# Results
 ## Thermosensory and burning components of TGI perception are spinally mediated
@@
 
-## Spinal organisation mediates the TGI
+# Discussion
 
@@
 Further research is needed to elucidate the neuroanatomical and functional properties of the spinal cord, as well as the intricate interplay between supraspinal and spinal processes that give rise to both the synthetic heat and burning sensations of the TGI.
-
-\newpage
-
-# Methods
-
-## Participants
-
-The study entailed two separate experiments, collectively involving 80 healthy volunteers.
-Forty participants took part in experiment 1 (`r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old, SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) and another 40 participants in experiment 2 (`r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary, mean age = `r descript_exp2_age$mean_age` years old, SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`).
-The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
-Prior to commencing the study, all participants were fully informed about the procedures and provided their voluntary consent.
-
-## Stimuli and procedure
-
-All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3 software (version 5.4b).
-The procedure involved measurements of heat and cold pain thresholds, calibration of cold-warm temperature pairs eliciting TGI, and an experimental task where TGI and non-TGI stimuli were applied on dermatomes that mapped onto adjacent or nonadjacent spinal segments.
-
-We measured cold and heat pain thresholds in a stepwise manner, the order of which was counterbalanced across participants.
-For cold pain, a single thermode at a starting temperature of 25ºC was held on the participant's dorsal forearm for five seconds.
-After which, the participant verbally reported (yes/no) any experience of pain.
-If the participant reported no pain, the temperature of the thermode was lowered by 5ºC, and placed back on the skin for another five seconds after which the participant reported whether they experienced pain.
-This step was repeated either until the participant responded 'yes' or the thermode reached the set minimum temperature of 5ºC.
-If the participant responded 'yes' before the minimum temperature, the temperature of the thermode was increased by 1ºC until the participant no longer experienced pain.
-The cold pain threshold was identified as the highest temperature at which the participant reported a painful experience.
-The same steps were repeated for heat pain, but with increasing intervals of 5ºC and with a starting temperature of 35ºC and a maximum temperature of 45ºC.
-The heat pain threshold was identified as the lowest temperature at which the participant reported a painful experience.
-
-We calibrated TGI stimuli by identifying a cold-warm temperature pair based on specific criteria: (1) consistently eliciting a burning sensation of at least 15 on a scale ranging from 0 to 100, (2) consistently avoiding a burning sensation (less than 15) when the cold-neutral (Exp.
-1) or warm-neutral (Exp.
-2) stimuli were presented, (3) both cold and warm temperatures falling within the innocuous range based on individual cold and heat pain thresholds.
-For pain threshold measurements and TGI calibration, we positioned the probes within a single dermatome.
-To address our experimental questions, we presented the calibrated TGI stimuli, as well as cold-neutral (Exp. 1) or warm-neutral (Exp. 2) non-TGI stimuli using two thermodes.
-In non-TGI stimuli the cold or warm temperatures were set to match the temperature used for TGI stimulation, but paired with a neutral temperature set at 30ºC.
-
-The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant's forearm size.
-The positioning of the thermodes was either within the same dermatome (C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1).
-Further, we manipulated the spatial arrangement of the temperature pairs, by systematically presenting an equal number of trials where the cold thermode was applied on a proximal or distal location within a dermatome, or was applied on a dermatome that mapped onto a rostral or caudal segment along the spinal cord.
-We based the demarcation of the dermatome boundaries on the American Spinal Injury Association (ASIA) map and positioned the thermodes in relation to standard anatomical landmarks.
-Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head (C6) or the lower back (T1).
-Spatial arrangements of stimuli are depicted in Figure 1B.
-The order of the stimuli (TGI vs. non-TGI), the dermatome condition (within vs. across) and the relative placement of the colder temperature (proximal vs. distal or rostral vs. caudal) were pseudo-randomised and counterbalanced between participants.
-
-During each trial, the experimenter positioned two thermodes on the participant's skin for 10 seconds, after which participants rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales.
-VAS scales were presented one at a time on a computer screen and appeared as a horizontal line, anchored at 0, representing no sensation (e.g., no burning), and 100, signifying an extreme sensation (e.g., extreme burning).
-The order of the three VAS scales was randomised across trials and participants had a maximum of eight seconds to respond to each scale.
-For each scale, participants provided their responses using the arrow keys on a keyboard and rated the intensity of their sensations from a specific location (labeled 'A' or 'B'), based on the experimenter's instruction.
-Unbeknown to the participant, this location systematically corresponded to either the colder temperature (Exp. 1) or the warmer temperature (Exp. 2).
-An auditory cue (300Hz, 100ms) indicated when the participants completed all ratings, after which the experimenter removed the thermodes from their skin.
-We presented a 200ms fixation dot before beginning the next trial.
-Each thermode configuration was tested three consecutive times on each arm, on three different and non-overlapping skin locations.
-An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter when to rearrange the thermode configuration or change arms to stimulate different dermatomes depending on a pseudo-randomisation order.
-Each of the four experimental conditions was repeated 12 times, with both the right and left forearms stimulated, and a minimum of five trials between the re-stimulation of the same skin location.
-This method ensured that the same skin locations were not stimulated consecutively to minimise the potential of carry-over effects.
-
-Experiments 1 and 2 were conducted in two independent groups of participants and followed exactly the same procedure except for two elements.
-In Experiment 1, participants rated the sensations localised underneath the colder thermode, and the non-TGI stimuli corresponded to cold-neutral pairs, where the temperature of the cold thermode in both conditions was the same.
-In Experiment 2, participants rated the sensations localised underneath the warmer thermode, and the non-TGI stimuli corresponded to warm-neutral pairs, where the temperature of the warm thermode in both conditions was the same.
-
-## Sample size
-
-An initial pilot study informed the [pre-registered](https://osf.io/4xcn5/) calculation of the sample size.
-To test the directional TGI hypothesis with 95% power and detect an effect size for the coefficient of .12 or greater, we determined that we needed a minimum number of 32 TGI-responsive participants.
-We defined TGI-responders as those individuals for whom the median burning ratings for TGI stimuli significantly exceeded 0.
-Non-responders were individuals that did not meet this criterion when tested with the max cold-warm temperatures allowed in the experiment.
-The predefined cut-off for TGI stimulation was 10ºC and 44ºC, due to both limitations of the thermode and to reduce likelihood of sensitization to heat stimuli.
-In Experiment 1, recruitment continued until we achieved the target of 32 TGI-responsive participants.
-We verified this criterion every 10 participants, resulting in a total sample size of 40 participants with 32 TGI responders.
-In Experiment 2, we stopped recruitment once we collected data from 40 participants, which resulted in a total of 37 TGI responders.
-This decision was based on meeting both required criteria: (1) matching the sample size of Exp.
-1 for consistency, and (2) achieving the minimum requirement of 32 TGI-responsive participants as determined by the power analysis.
-
-## Data analyses
-
-We re-scaled data from cold, warm and burning VAS ratings from their original values to a range of 0 to 1.
-Following re-scaling, we applied zero-inflated mixed-effects beta regression models separately for each set of VAS ratings.
-In these models, we incorporated three fixed effects; the type of stimulation (non-TGI vs. TGI), the dermatome condition (within the same dermatome vs. across different dermatomes) and the spatial positioning of the cold or neutral thermode (proximal vs. distal within dermatomes; rostral vs. caudal across dermatomes).
-This allowed us to assess the individual and interactive effects of these three factors on VAS ratings.
-Further, we added random intercepts of subject and trial order to our models to account for between-subject variability and the effects of repeated measures.
-
-The choices of the zero-inflated approach and the use of beta regressions were necessitated by the specific distribution of VAS ratings.
-The beta distribution is suitable for modelling VAS rating data, as they are proportional in nature.
-Additionally, the zero-inflation was needed due to the presence of an excess number of zero values in specific ratings and conditions.
-Specifically, we anticipated an over-representation of zero values for thermosensory ratings that were counterfactual to the objective stimulation quality (i.e., cold ratings of warm stimuli and warm ratings of cold stimuli) and burning ratings of non-TGI stimuli.
-The latter stimuli were designed to not elicit an illusion or trigger a weaker illusion as compared to the TGI stimuli.
-We carried out the statistical analyses using the 'glmmTMB' package in R (version `r sessionInfo()$otherPkgs$glmmTMB$Version`), and statistical significance was set at p \< .05.
-
-For data presentation purposes, the median VAS ratings for each sensory quality (cold, warm, burning) were calculated per simulation type (TGI, non-TGI), dermatome (within, across) and spatial location (proximo-distal, rostro-caudal) for each participant.
-For hypothesis one, these values were further averaged so there were only four values per participant, for each sensory quality (within and across dermatome ratings for TGI and non-TGI stimuli).
-For analysis of burning VAS ratings, only those participants who were deemed as TGI responders (n = 32 for Exp. 1 and n = 37 for Exp. 2) were included.
-
-## Data availability
-
-The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both experiment 1 (https://osf.io/4xcn5/) and experiment 2 (https://osf.io/dhg8u/).
-
-All raw data and code for the analysis are available in the GitHub repository (https://github.com/Body-Pain-Perception-Lab/tgi-spinal).
-This, and a wiki guide to analysing the data, can be accessed through the project's OSF page (https://osf.io/uyrtq/).
 

### 2023-10-17 Manuscript.Rmd
cutting down intro for pain

@@
 bibliography: knitting_files/tgi-spine2.bib
-csl: knitting_files/ieee.csl
+csl: knitting_files/pain.csl
 link-citations: yes
@@
 
-The thermal grill illusion (TGI) is a perceptual phenomenon that challenges conventional understanding of pain perception.
-It is a sensation of burning heat or pain when harmless cold and warm temperatures are applied to the skin simultaneously [@craig_thermal_1994; @craig_functional_1996].
-Despite cold and warm temperatures being individually innocuous, and therefore insufficient to activate peripheral nociceptors, their combination produces a paradoxical burning sensation.
-The generation of this illusion is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020].
-While recent studies have highlighted the involvement of the spinal cord as an initial site contributing to the TGI [@fardo_organization_2018; @harper_conditioned_2017], the precise mechanisms underpinning integration of cold and warm thermal afferents in the spinal cord, alongside those responsible for the distinctive burning quality to this illusion, are yet to be elucidated.
+The thermal grill illusion (TGI) is the sensation of burning heat or pain when harmless cold and warm temperatures are simultaneously applied to the skin [@craig_thermal_1994; @craig_functional_1996].
+As the cold and warm temperatures are innocuous and therefore insufficient to activate peripheral nociceptors, the generation of illusory heat is thus attributed to central nervous system mechanisms [@craig_thermal_1994; @fardo_beyond_2020; @fardo_organization_2018; @harper_conditioned_2017].
 
 The TGI is often described as encompassing two distinct perceptual components - an illusion of heat and an illusion of pain [@defrin_spatial_2008; @fardo_beyond_2020]. 
-The illusion of heat, also known as synthetic heat [@fruhstorfer_significance_2003; @green_localization_1977; -@green_synthetic_2002; -@green_temperature_2004], refers to non-painful heat sensations evoked by the thermal grill [@defrin_spatial_2008; @kern_pharmacological_2008; -@kern_effects_2008; @bouhassira_investigation_2005; @adam_relationships_2014].
-The illusion of pain, which is the most recognised aspect of the TGI, is the distinctive burning sensation that accompanies the simultaneous presentation of cold and warm stimuli [@craig_thermal_1994; -@craig_functional_1996; @bach_thermal_2011].
-The hallmark of both illusory components is a qualitative change in perception when the cold and warm stimuli are applied concurrently, compared to when they are presented individually.
-Historically, the thermosensory and painful components of the TGI were explained by distinct spinal and supraspinal mechanisms, respectively.
-Observations in the spinothalamic tract of cats showed that the simultaneous application of cold and warm temperatures reduced the activity of cold-specific spinal neurons compared to when cold was applied alone [@craig_thermal_1994], which implied the enhanced perception of heat in TGI is explained by a spinal inhibitory mechanism.
-Instead, the illusory pain component was ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following thalamic lesions [@craig_thermal_1994; -@craig_new_1998].
+Historically, the thermosensory and painful components of the TGI were explained by distinct spinal and supraspinal mechanisms, respectively [@craig_thermal_1994].
+The illusory pain component has been ascribed to a disinhibition mechanism at the level of the thalamus, primarily based on the observations of unremitting pain following thalamic lesions [@craig_thermal_1994; -@craig_new_1998].
+Some more recent human studies on TGI have posited that the illusory pain component of the TGI depends uniquely on supraspinal mechanisms, based on the observed modulation of the illusion in accordance with a spatiotopic rather than somatotopic representation of the body [@marotta_transforming_2015] and that the experience of TGI is not modulated by tactile gating - a spinally mediated process involving inhibition of nociceptive activity by concurrent somatosensory activity [@ferre_ineffectiveness_2018].
 
-Recent human studies on TGI provided differing interpretations of the spinal or supraspinal origin of the illusion.
-Two studies posited that the illusory pain component of the TGI depends uniquely on supraspinal mechanisms.
-This interpretation was based on the observed modulation of the illusion in accordance with a spatiotopic rather than somatotopic representation of the body [@marotta_transforming_2015].
-Further, the experience of the illusion was similar in a condition involving concomitant tactile stimulation and a contact-free condition, suggesting the TGI is not modulated by tactile gating - a spinally mediated process involving inhibition of nociceptive activity by concurrent somatosensory activity [@ferre_ineffectiveness_2018].
+Counter to this perspective, other research has found the TGI varies depending on whether cold and warm afferents mapped either onto adjacent or non-adjacent spinal segments [@fardo_organization_2018].
+This suggests that the spinal cord is an initial site of thermosensory integration underlying the TGI.
+Further support for spinal mechanisms comes from research demonstrating that noxious heat and the TGI were comparably reduced by conditioned pain modulation in humans, a mechanism that is mediated by descending modulatory systems that originate in the brain but acts on the spinal cord [@harper_conditioned_2017].
+These findings collectively refute the notion of a purely supraspinal hypothesis of TGI and underscore the significance of spinal mechanisms in the manifestation of both illusory heat and pain.
 
-Counter to this perspective, other research has endorsed a spinal contribution to the TGI.
-These studies found that the illusion varied depending on whether cold and warm stimuli were applied to dermatomes mapped either onto adjacent or non-adjacent spinal segments [@fardo_organization_2018].
-Participants perceived stimulus temperature more veridically, consistent with a reduction in the effectiveness of the TGI, when warm and cold stimuli were placed on the skin in such a way that they mapped on to different segmental locations along the spinal cord, compared to when they mapped onto the same spinal segment.
-This corroborates the hypothesis that the spinal cord is an initial site of thermosensory integration underlying the TGI.
-Further support for spinal mechanisms comes from research demonstrating that both noxious heat and the TGI were comparably reduced by conditioned pain modulation in humans.
-Since conditioned pain modulation is thought to be mediated by descending modulatory systems that originate in the brain but act on the spinal cord, this finding suggests a similar engagement of descending modulation, leading to similar effects on spinal cord activity.
-This pattern is consistent regardless of whether the painful sensation was triggered by potentially harmful, as in the case of noxious heat, or harmless, as with the TGI [@harper_conditioned_2017].
-These findings collectively refute the notion of a purely supraspinal hypothesis of the painful component of the TGI and underscore the significance of spinal mechanisms in the manifestation of both illusory heat and pain.
-
-In this paper our objective was twofold.
-Firstly, we directly investigated the hypothesis that thermosensory and burning components of the TGI experience are mediated by spinal mechanisms in humans, by manipulating the location of the stimuli within and across dermatomes.
+In this paper our objective was to directly investigate the hypothesis that thermosensory and burning components of the TGI are mediated by spinal mechanisms in humans.
 Cold and warm stimuli were presented at a fixed distance on the skin but depending on their orientation on the arm, they elicited differing neural activity in the spinal cord (Figure 1 A and B).
-Our assumption was that cold and warm-related neural activity would show stronger integration, and thus stronger TGI effects, when the stimuli were presented within the same dermatome and therefore mapped to the same or adjacent spinal segments, than when they mapped onto segments that were anatomically further apart.
-In each case, we compared stimuli that could either induce the TGI (combined innocuous cold and warm) with control stimuli that could not induce the TGI (i.e.
-a neutral temperature, 30ºC, paired with either innocuous cold in experiment 1 or innocuous warm in experiment 2).
-
-Our past work quantified the experience of the TGI using a temperature matching task [@fardo_organization_2018], which provides a composite measure of TGI perception, reflecting both the thermosensory and painful components.
-Here, to probe possible distinctions between these two qualitative components of the TGI, we obtained subjective measures of TGI perception using three independent visual analog scale (VAS) ratings of perceived cold, warm and burning sensations (Figure 1C).
-Additionally, we investigated spatial order effects associated with the integration of cold and warm sensory information at the dermatome (skin) and segmental (spine) levels.
-At the dermatome level, we used body-related coordinates to define proximal (towards the elbow) and distal (towards the wrist) locations.
-At the spinal level, we used segment-related coordinates to define more rostral (towards the head) and more caudal (towards the lower back) locations (Figure 1B).
-Given that the spinal cord is organised along a rostral-caudal axis, where each dermatome is represented across multiple spinal segments through the Lissauer tract [@kerr_neuroanatomical_1975; @lamotte_distribution_1977; @wall_brief_1999], this study provides indirect insights into the spinal mechanisms underpinning thermosensory integration and the generation of the TGI.
+Our assumption was that cold and warm-related neural activity would show stronger integration, and thus stronger TGI effects, when the stimuli mapped to the same or adjacent spinal segments, than when they mapped onto segments that were anatomically further apart.
+Additionally, we investigated spatial order effects associated with the integration of cold and warm sensory information at the dermatome (skin) and segmental (spine) levels (Figure 1B).
 If the experience of the TGI is influenced by the relative location of warm and cold afferents in different spinal segments, this finding would provide compelling, additional evidence that the spine serves as an initial site for the cold-warm integration that produces perceptions of illusory heat and pain.
@@
 ggdraw() +
-    draw_image(magick::image_read(file.path("figures","figure1_v2.PNG")), scale = 1)
+    draw_image(magick::image_read(file.path("figures","figure1_v2.tiff")), scale = 1)
 ```
@@
 
+# Conflict of Interest
+
+The authors declare no competing conflicts of interest for this manuscript.
+
 \newpage

### 2024-01-08 tgi-spinal_analysis-exp1.Rmd
adding lines between results figures

@@
 
+# get confidence intervals
+h2_conf <- aggregate(VAS~quality*manipulation*cold_probe, IQR, data = vas_meds)
+h2_conf <- h2_conf %>% 
+  dplyr::rename(iqr = VAS)
+
+h2_sum <- merge(h2_sum, h2_conf, by = c('quality','manipulation','cold_probe'))
+
 # organise data for plotting
@@
                                 c('proximal', 'distal', 'rostral', 'caudal'))
-h2_sum$cold_probe <- factor(h2_sum$cold_probe, levels = 
+h2_sum$cold_probe <- factor(h2_sum$cold_probe, labels = 
                                 c('proximal', 'distal', 'rostral', 'caudal'))
@@
                                 c(1,2,3,4))
-# creating jitter
-vas_meds$xj <- jitter(as.numeric(vas_meds$cold_code), amount = .05)
-
-nudge1 = -.1
-nudge2 = .1
+
+```
+
+# Plot all summary data - for poster :)
+
+```{r}
+ggplot(data = h2_sum %>% 
+         filter(quality == 'burn'), aes(group = manipulation, colour = manipulation)) +
+  geom_point(aes(cold_probe, VAS),
+             position = position_dodge(.3), size = 5) +
+  geom_errorbar(aes(x = cold_probe, ymin = VAS-iqr, ymax = VAS+iqr),
+                position = position_dodge(.3), width = .2, linewidth = 1.1) +
+  geom_line(aes(cold_probe, VAS), position = position_dodge(.3),
+            linewidth = 1.7) +
+  labs(y = 'Burn ratings (0 - 100)', x = '') +
+  scale_colour_manual(values = c(purp[5], purp[8])) +
+  #ylim(0, 40) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 18)) -> h2_means
+
+# save
+ggsave(here::here("figures", "E1_H2_means.png"), plot = h2_means, 
+       device = NULL, width = 7, height = 5, dpi = 600)
 ```
@@
 ```{r}
+# creating jitter
+vas_meds$xj <- jitter(as.numeric(vas_meds$cold_code), amount = .1)
+
+nudge1 = -.15
+nudge2 = .15
+
 # plot all data
@@
     filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_line(data = h2_sum %>% 
@@
     aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge1)) + 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
   geom_line(data = h2_sum %>% 
@@
     aes(as.numeric(cold_code), VAS), 
-    position = position_nudge(nudge2)) +
+    position = position_nudge(nudge2), linewidth = 1.5) +
   scale_colour_manual(values = c(blue[5], blue[7])) +
@@
   scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
-  labs(title = 'Cold ratings', x = NULL, 
-         y = 'VAS Rating (0-100)') +
+  labs(x = NULL, y = 'Cold Rating (0-100)') +
   ylim(-0.5,100) +
@@
     filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
-    position = position_nudge(x = nudge1), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge1), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_boxjitter(data = vas_meds %>% 
     filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
-    position = position_nudge(x = nudge2), width = .2,
-      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    position = position_nudge(x = nudge2), width = .5,
+      errorbar.length = .3, jitter.shape = 21, jitter.size = 2,
+      outlier.shape = NA, errorbar.draw = TRUE, lwd = 1) +
   geom_line(data = h2_sum %>% 
@@
 h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
-                     nrow = 2, ncol = 2)
+                     nrow = 3, ncol = 1)
 h2_plot
@@
 ggsave(here::here("figures", "E1_H2_allDat.png"), plot = h2_plot, 
-       device = NULL, width = 9, height = 5, dpi = 600)
+       device = NULL, width = 7, height = 15, dpi = 600)
+```
+# Same but box plots
+```{r}
+# cold 
+ggplot(data = vas_meds %>% filter(quality == 'cold'),
+        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2), linewidth = 1.5) +
+  scale_colour_manual(values = c(blue[5], blue[7])) +
+  scale_fill_manual(values = c(blue[2], blue[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(x = NULL, y = 'Cold Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 19)) -> cold_box
+
+# warm
+ggplot(data = vas_meds %>% filter(quality == 'warm'),
+        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2), linewidth = 1.5) +
+  scale_colour_manual(values = c(oran[5], oran[7])) +
+  scale_fill_manual(values = c(oran[2], oran[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(x = NULL, y = 'Warm Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 19)) -> warm_box
+
+# burn
+ggplot(data = vas_meds %>% filter(quality == 'burn'),
+        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2), linewidth = 1.5) +
+  scale_colour_manual(values = c(purp[5], purp[7])) +
+  scale_fill_manual(values = c(purp[2], purp[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(x = NULL, y = 'Burn Rating (0-100)') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 19)) -> burn_box
+```
+
+# Put them all together
+```{r}
+p_plot <- ggarrange(cold_box, warm_box, burn_box,
+                     nrow = 3, ncol = 1)
+p_plot
+
+ggsave(here::here("figures", "E1_posterPlot.png"), plot = p_plot, 
+       device = NULL, width = 7, height = 15, dpi = 600)
 ```

### 2024-01-08 tgi-spinal_analysis-exp2.Rmd
adding lines between results figures

@@
 Hypothesis 2 a & b: relative location of warm and cold
-```{r h2}
+````{r h2}
 # Change name of manipulation
@@
                                 c(1,2,3,4))
-# creating jitter
-vas_meds$xj <- jitter(as.numeric(vas_meds$cold_code), amount = .05)
-
-nudge1 = -.1
-nudge2 = .1
+
+```
+
+# Plot all summary data - for poster :)
+```{r}
+ggplot(data = h2_sum, aes(group = manipulation, colour = manipulation)) +
+  geom_point(aes(cold_probe, VAS),
+             position = position_dodge(.3), size = 5) +
+  geom_errorbar(aes(x = cold_probe, ymin = VAS-iqr, ymax = VAS+iqr),
+                position = position_dodge(.3), width = .2, linewidth = 1.1) +
+  geom_line(aes(cold_probe, VAS), position = position_dodge(.3),
+            linewidth = 1.7) +
+  labs(y = 'Burn ratings (0 - 100)', x = '') +
+  scale_colour_manual(values = c(purp[5], purp[8])) +
+  #ylim(, 60) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 18)) -> h2_means
+
+# save
+ggsave(here::here("figures", "E2_H2_means.png"), plot = h2_means, 
+       device = NULL, width = 7, height = 5, dpi = 600)
 ```
@@
        device = NULL, width = 9, height = 5, dpi = 600)
+```
+
+# make box plots for poster
+```{r}
+# cold 
+ggplot(data = vas_meds %>% filter(quality == 'cold'),
+        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'cold', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2), linewidth = 1.5) +
+  scale_colour_manual(values = c(blue[5], blue[7])) +
+  scale_fill_manual(values = c(blue[2], blue[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(x = NULL, y = '') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 19)) -> cold_box
+
+# warm
+ggplot(data = vas_meds %>% filter(quality == 'warm'),
+        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'warm', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2), linewidth = 1.5) +
+  scale_colour_manual(values = c(oran[5], oran[7])) +
+  scale_fill_manual(values = c(oran[2], oran[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(x = NULL, y = '') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 19)) -> warm_box
+
+# burn
+ggplot(data = vas_meds %>% filter(quality == 'burn'),
+        mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
+    position = position_nudge(x = nudge1), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_boxplot(data = vas_meds %>% 
+    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
+    position = position_nudge(x = nudge2), size = 1.2, outlier.size = 2, 
+    outlier.alpha = .5) +
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'Non-TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge1), linewidth = 1.5) + 
+  geom_line(data = h2_sum %>% 
+    filter(quality == 'burn', manipulation == 'TGI'),
+    aes(as.numeric(cold_code), VAS), 
+    position = position_nudge(nudge2), linewidth = 1.5) +
+  scale_colour_manual(values = c(purp[5], purp[7])) +
+  scale_fill_manual(values = c(purp[2], purp[4])) +
+  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
+  labs(x = NULL, y = '') +
+  ylim(-0.5,100) +
+  theme_classic() +
+  theme(legend.position = 'none',
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 19)) -> burn_box
+```
+
+# put them all together
+```{r}
+p_plot <- ggarrange(cold_box, warm_box, burn_box,
+                     nrow = 3, ncol = 1)
+p_plot
+
+ggsave(here::here("figures", "E2_posterPlot.png"), plot = p_plot, 
+       device = NULL, width = 7, height = 15, dpi = 600)
 ```

### 2024-01-08 scripts/plots.R

@@ -6,6 +6,8 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
     geom_hline(yintercept = 0, colour = 'grey50') +
     geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
                alpha = .5, size = 1.7) +
+    geom_line(aes(manipulation, difference, group = ID), position = position_dodge(.2),
+               alpha = .3) +
     geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
                fill = 'grey15',
                shape = 21, size = 3) +
@@ -22,7 +24,7 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
           axis.title = element_text(size = 11),
           strip.text = element_text(size = 10),
           title = element_text(size=10)) +
-    coord_cartesian(ylim = c(-30,30))+
+    coord_cartesian(ylim = c(-60,60))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
   plot
@@ -80,6 +82,8 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
     geom_hline(yintercept = 0) +
     geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5,
                size = 1.7) +
+    geom_line(aes(manipulation, difference, group = ID), position = position_dodge(.2),
+              alpha = .3) +
     geom_point(data = h2_diff_sum %>% 
                  filter(condition == 'within'), 
                aes(manipulation, difference), colour = 'grey15',
@@ -108,6 +112,8 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
                           aes(manipulation, difference, colour = quality)) +
     geom_hline(yintercept = 0) +
     geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5, size = 1.7) +
+    geom_line(aes(manipulation, difference, group = ID), position = position_dodge(.2),
+              alpha = .3) +
     geom_point(data = h2_diff_sum %>% 
                  filter(condition == 'across'), 
                aes(manipulation, difference), colour = 'grey15',

### 2024-01-08 Manuscript.Rmd
adding lines between results figures
adding supplementary figure as fig 2

@@
 # Results
+The results for both experiments 1 and 2 are summarised in Figure 2, panels A - C and D - F respectively.
+
 ## Thermosensory and burning components of TGI perception are spinally mediated
@@
 1, Fig.
-2A), participants reported a stronger reduction in the subjective experience of cold specifically for TGI stimuli applied within a dermatome compared to across dermatomes.
-The results of the zero-inflated beta regression show a stimulation by dermatome interaction (cold ratings: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`), alongside an increased subjective experience of warmth for both TGI and non-TGI stimuli (dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`).
+3A), participants reported a stronger reduction in the subjective experience of cold specifically for TGI stimuli applied within a dermatome compared to across dermatomes.
+The results of the zero-inflated beta regression show a stimulation by dermatome interaction (cold ratings: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`), alongside an increased subjective experience of warmth for both TGI and non-TGI stimuli (dermatome main effect: $\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`).
 Further, participants reported no significant modulation of burning ratings depending on the dermatome condition (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`; dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`).
@@
 2, Fig.
-2B), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (dermatome main effect: $\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
-However, we did not observe modulation of cold (dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) or warm ratings by dermatome (dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2]);`stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
+3B), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (dermatome main effect: $\beta$ = `r stats_model_burn_exp2$beta[2]`, `r make_pvalue(stats_model_burn_exp2$p[2])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
+However, we did not observe modulation of cold (dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) or warm ratings by dermatome (dermatome main effect: $\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).
 Overall, these results indicated that when participants judged the warm thermode, the greatest modulation in TGI perception was related to burning sensations, with within-dermatome TGI stimuli perceived as the most burning.
+
+```{r, results="hide", fig.width = 7.2, fig.height = 9, warning = F, message = F, echo = F, fig.cap = "Figure 2: Individual median VAS ratings for Experiment 1 (A-C) and Experiment 2 (D-F) across stimulus manipulation, and spatial location.
+Proximal and distal locations are within dermatome, rostral and caudal locations are across dermatomes.
+All spatial locations refer to the location of the cold thermode, compared to the warm.
+Box plots show median and interquartile range.
+Data presented here include trials where VAS ratings equal 0, which are modelled seperately in the main analyses"}
+
+# Figure2
+sPlot(include_zero = T)
+```
 
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2: Difference between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) for each VAS rating quality (cold, warm and burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3: Difference between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) for each VAS rating quality (cold, warm and burning).
 Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
@@
 2) is in a more distal location compared to the other thermode.
-We tested the occurrence of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 3).
+We tested the occurrence of this distal inhibition effect to the perception of mild temperatures in TGI and non-TGI stimuli within single dermatomes (Fig. 4).
 
@@
 In experiment 1, cold ratings (dermatome main effect: $\beta$ = `r stats_model_cold_exp1$beta[4]`, `r make_pvalue(stats_model_cold_exp1$p[4])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[8]`, `r make_pvalue(stats_model_cold_exp1$p[8])`) and burn ratings (dermatome main effect: $\beta$ = `r stats_model_burn_exp1$beta[4]`, `r make_pvalue(stats_model_burn_exp1$p[4])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp1$beta[8]`, `r make_pvalue(stats_model_burn_exp1$p[8])`) were enhanced when the reference (cold) thermode was located more distally than the warm probe, irrespective of whether the stimulus was TGI or non-TGI (Fig.
-3A).
+4A).
 We found a similar finding for cold perception in experiment 2 (dermatome main effect: $\beta$ = `r stats_model_cold_exp2$beta[4]`, `r make_pvalue(stats_model_cold_exp2$p[4])`; stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp2$beta[8]`, `r make_pvalue(stats_model_cold_exp2$p[8])`), where cold ratings were higher when the reference (warm) thermode was more proximal than the cold thermode (Fig.
-3B).
+4B).
 These findings suggest that the notion of distal inhibition can be extended to innocuous cold perception and burning sensations that are not specific to TGI at objectively mild temperatures.
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3: Difference between the proximal and distal location of the reference thermode in the within dermatome condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4: Difference between the proximal and distal location of the reference thermode in the within dermatome condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
 Higher values show higher ratings when the cold probe is more proximal than the warm probe.
@@
 1, Fig.
-4A) or the warm thermode (Exp.2, Fig.
-4B), participants reported a reduced subjective experience of cold, alongside an enhanced perception of warmth when the cold thermode was applied on a dermatome that mapped onto a more caudal segment.
+5A) or the warm thermode (Exp.2, Fig.
+5B), participants reported a reduced subjective experience of cold, alongside an enhanced perception of warmth when the cold thermode was applied on a dermatome that mapped onto a more caudal segment.
 The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord.
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4: Difference between the caudal and rostral dermatome conditions and the stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 5: Difference between the caudal and rostral dermatome conditions and the stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
 Higher values represent higher ratings when the cold probe is located in dermatomes that are related to more caudal spinal segments (T1) than the warm probe (C6).
@@
 ```
-
-\newpage
-
-```{r, results="hide", fig.width = 7.2, fig.height = 9, warning = F, message = F, echo = F, fig.cap = "Figure S1: Individual median VAS ratings for Experiment 1 (A-C) and Experiment 2 (D-F) across stimulus manipulation, and spatial location.
-Proximal and distal locations are within dermatome, rostral and caudal locations are across dermatomes.
-All spatial locations refer to the location of the cold thermode, compared to the warm.
-Box plots show median and interquartile range.
-Data presented here include trials where VAS ratings equal 0, which are modelled seperately in the main analyses"}
-
-# supplementary first panel
-sPlot(include_zero = T)
-#plot1(include_zero = F)
-```

### 2024-01-09 scripts/supplementary.R
adding thresholds as supplementary figure

@@ -208,3 +208,52 @@ sPlot = function(include_zero = T){
   
 }
 
+sPlot1 = function(include_zero = T){
+  ## figures with thresholds and TGI temperatures
+  exp1_temps <- read.csv(file.path("data", 'STGI_exp1_temperatures.csv'))
+  exp2_temps <- read.csv(file.path("data", 'STGI_exp2_temperatures.csv'))
+  # modify data
+  exp1_temps <- exp1_temps %>% 
+    mutate(EXP = 'exp1') 
+  exp2_temps <- exp2_temps %>% 
+    mutate(EXP = 'exp2')
+  # combine both
+  temps <- rbind(exp1_temps, exp2_temps)
+  
+  thresh <- temps %>% 
+    pivot_longer(cols = c(CPT,HPT), names_to = 'TEMP', values_to = 'THRESH') %>% 
+    select(-c(CTGI, WTGI))
+  
+  tgi <- temps %>%   
+    pivot_longer(cols = c(CTGI, WTGI), names_to = 'TEMP', values_to = 'TGI') %>% 
+    mutate(TEMP = fct_recode(TEMP, 'cold' = 'CTGI', 'warm' = 'WTGI')) %>% 
+    select(-c(CPT,HPT))
+  
+  thr_plot <- ggplot(data = thresh, aes(color = TEMP, fill = TEMP)) +
+    geom_point(aes(TEMP, THRESH, group = ID), position = position_dodge(.2),
+               shape = 20, alpha = .8, size = 2) +
+    #geom_line(aes(TEMP, THRESH, group = ID), position = position_dodge(.2),
+    #          alpha = .2) +
+    scale_color_manual(values = c(blue[5], oran[5])) +
+    labs(x = NULL, y = 'Temperature (ºC)', title = 'Pain thresholds') +
+    ylim(0,50) +
+    facet_wrap(~EXP) +
+    theme_classic() +
+    theme(legend.position = 'none')
+  
+  tgi_plot <- ggplot(data = tgi, aes(color = TEMP, fill = TEMP)) +
+    geom_line(aes(TEMP, TGI, group = ID), position = position_dodge(.2),
+              alpha = .3, colour = 'grey75', size = .8) +
+    geom_point(aes(TEMP, TGI, group = ID), position = position_dodge(.2),
+               shape = 20, alpha = .8, size = 2) +
+    scale_color_manual(values = c(blue[5], oran[5])) +
[…]

### 2024-01-09 scripts/utility.R

@@ -49,8 +49,6 @@ oran <- brewer.pal(8, "Oranges")
 gren <- brewer.pal(8, "Greens")
 
 
-
-
 prep_data = function(file, include_zero = T){
   
   if (file.exists(file)){

### 2024-01-10 Manuscript.Rmd
adding thresholds as supplementary figure
suggested changesø

@@
 # Figure2
-sPlot(include_zero = T)
+f2_plot(include_zero = T)
 ```
@@
 
-plot1(include_zero = F)
+f3_plot(include_zero = F)
 #plot1(include_zero = T)
@@
 
-plot2_3(include_zero = F)[[1]]
+f45_plot(include_zero = F)[[1]]
 ```
@@
 
-plot2_3(include_zero = F)[[2]]
+f45_plot(include_zero = F)[[2]]
 ```
@@
 ```
+
+\newpage
+## Temperatures by participant
+
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure S1: Pain thresholds (left) and TGI temperatures (right) for each participant in experiment 1 and experiment 2.
+As we did not go below 5ºC or above 45ºC for the TGI stimuli, CPT and HPT were capped at 5ºC and 45ºC respectively"}
+
+sPlot1(include_zero = F)
+```

### 2024-01-10 scripts/plots.R

@@ -1,3 +1,147 @@
+make_sPlot = function(vas_meds, h2_sum, VAS_type, title, l_pos){
+  
+  # plot all data, with 0s
+  plot = ggplot(data = vas_meds %>% 
+                  filter(quality == VAS_type),
+                mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'proximal', manipulation == 'Non-TGI'),
+                   position = position_nudge(x = -.1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'proximal', manipulation == 'TGI'),
+                   position = position_nudge(x = .1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'distal', manipulation == 'Non-TGI'),
+                   position = position_nudge(x = -.1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'distal', manipulation == 'TGI'),
+                   position = position_nudge(x = .1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
+                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
+    geom_boxjitter(data = vas_meds %>% 
+                     filter(quality == VAS_type, cold_probe == 'rostral', manipulation == 'Non-TGI'),
+                   position = position_nudge(x = -.1), width = .2,
+                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
[…]

### 2024-01-10 scripts/supplementary.R

@@ -63,150 +63,11 @@ FitFlextableToPage <- function(ft, pgwidth = 6){
   return(ft_out)
 }
 
-make_sPlot = function(vas_meds, h2_sum, VAS_type, title, l_pos){
-  
-  # plot all data, with 0s
-  plot = ggplot(data = vas_meds %>% 
-           filter(quality == VAS_type),
-         mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
-    geom_boxjitter(data = vas_meds %>% 
-                     filter(quality == VAS_type, cold_probe == 'proximal', manipulation == 'Non-TGI'),
-                   position = position_nudge(x = -.1), width = .2,
-                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-    geom_boxjitter(data = vas_meds %>% 
-                     filter(quality == VAS_type, cold_probe == 'proximal', manipulation == 'TGI'),
-                   position = position_nudge(x = .1), width = .2,
-                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-    geom_boxjitter(data = vas_meds %>% 
-                     filter(quality == VAS_type, cold_probe == 'distal', manipulation == 'Non-TGI'),
-                   position = position_nudge(x = -.1), width = .2,
-                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-    geom_boxjitter(data = vas_meds %>% 
-                     filter(quality == VAS_type, cold_probe == 'distal', manipulation == 'TGI'),
-                   position = position_nudge(x = .1), width = .2,
-                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
-                   outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
-    geom_boxjitter(data = vas_meds %>% 
-                     filter(quality == VAS_type, cold_probe == 'rostral', manipulation == 'Non-TGI'),
-                   position = position_nudge(x = -.1), width = .2,
-                   errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
[…]

### 2024-01-17 Manuscript.Rmd
making manuscript and figure revisions

@@
 Enhanced warm and burning ratings during the TGI were observed when cold and warm stimuli were confined within the same dermatome.
-Further, heat perception was enhanced when the cold stimulus projected to the segment caudal to the warm stimulus, compared to the opposite spatial arrangement.
-Our results are consistent with spatial spread and integration of thermosensory information in the spinal cord.
+Further, we found the spatial organisation of warm and cold stimuli within and across dermatomes affected TGI perception.
+Specifically, the heat perception was enhanced when the cold stimulus projected to the segment more caudal to the warm stimulus, compared to the opposite spatial arrangement.
+This suggests the perception of TGI is enhanced when cold afferents are projected to spinal segments positioned caudally in relation to those receiving warm afferents.
+Our results indicate distinct interaction of sensory pathways based on the segmental arrangement of afferent fibres and are consistent with current interpretations of the spread and integration of thermosensory information along the spinal cord.
 
@@
 Forty participants took part in experiment 1 (`r descript_exp1_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp1_gender %>% filter(Gender == "M") %>% .$number` males, mean age = `r descript_exp1_age$mean_age` years old, SD = `r descript_exp1_age$sd_age`, range = `r descript_exp1_age$min_age` - `r descript_exp1_age$max_age`) and another 40 participants in experiment 2 (`r descript_exp2_gender %>% filter(Gender == "F") %>% .$number` females and `r descript_exp2_gender %>% filter(Gender == "M") %>% .$number` males and `r descript_exp2_gender %>% filter(Gender != "M" & Gender != "F") %>% .$number` non-binary, mean age = `r descript_exp2_age$mean_age` years old, SD = `r descript_exp2_age$sd_age`, range = `r descript_exp2_age$min_age` - `r descript_exp2_age$max_age`).
+Data collection for experiments 1 and 2 took place between August - December 2022 and January - May 2023 respectively and there were no participants that took part in both experiments.
 The research methodology complied with the principles set forth in the Declaration of Helsinki and received ethical approval from the Institutional Review Board (IRB) at the Danish Neuroscience Center, Aarhus University, Denmark.
@@
 
-## Stimuli and procedure
+## Stimuli
 
-All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC) controlled by PhysiTemp NTE-3 software (version 5.4b).
+All thermal stimuli were delivered using two NTE-3 Thermal Sensitivity Testers (PhysiTemp Instruments LLC, 10mm in diameter) controlled by PhysiTemp NTE-3 software (version 5.4b).
 The procedure involved measurements of heat and cold pain thresholds, calibration of cold-warm temperature pairs eliciting TGI, and an experimental task where TGI and non-TGI stimuli were applied on dermatomes that mapped onto adjacent or nonadjacent spinal segments.
+The thermodes were heated or cooled to the required stimulus temperature prior to being placed on the participant’s skin.
+If the skin temperature affected the surface temperature of the probe, the experimenter waited to start the trial until the desired temperature was reached.
+The maximum rate of temperature change of the probes was 1ºC/s.
 
@@
 2) stimulus of identical temperature as in the TGI condition with a baseline temperature of 30°C (non-TGI stimuli).
-All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments (Figure 1A and B).
+All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments (Figure 1).
+This arrangement of cold and warm probes on the skin was specifically chosen to be able to explore the spinal mechanisms of the TGI and similar set-ups, using two probes to induce TGI, have been used previously in healthy human participants [@fardo_organization_2018; @defrin_spatial_2008].
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1: A and B) Placement and distance of thermodes on the inner forearm, showing corresponding spinal mapping for all four conditions.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1: (A) An example sequence of an experiment.
+The order of pain threshold blocks 1 and 2 and experimental sessions 1 and 2 were counterbalanced evenly across participants.
+(B) Placement and distance of thermodes on the inner forearm.
+(C) The three Visual Analogue Scales (cold, warm, burning) participants used to report sensation coming from the reference probe, presented in a randomised order for every trial.
+(D) The corresponding spinal mapping of the probe placement for all four conditions.
 Within dermatomes, the relative location of the cold thermode was proximal or distal.
@@
 Within dermatome conditions also included warm and cold thermodes in C6 (not depicted here), as well as T1.
-C) The three VAS participants used to report sensation coming from the reference probe, presented for each trial in a randomised order."}
+The size of the stimulus site in panels C and D probe is not to scale."}
 ggdraw() +
-    draw_image(magick::image_read(file.path("figures","figure1_v2.tiff")), scale = 1)
+    draw_image(magick::image_read(file.path("figures","figure1_v3.png")), scale = 1)
 ```
@@
 
-We measured cold and heat pain thresholds in a stepwise manner, the order of which was counterbalanced across participants.
+An outline of the procedure for each experiment is found in Figure 1A. We measured cold and heat pain thresholds in a stepwise manner, the order of which was counterbalanced across participants.
 For cold pain, a single thermode at a starting temperature of 25ºC was held on the participant's dorsal forearm for five seconds.
@@
 The same steps were repeated for heat pain, but with increasing intervals of 5ºC and with a starting temperature of 35ºC and a maximum temperature of 45ºC.
-The heat pain threshold was identified as the lowest temperature at which the participant reported a painful experience.
+The heat pain threshold was identified as the lowest temperature at which the participant reported a painful experience. Heat and cold pain thresholding procedures were completed once per participant.
 
@@
 2) stimuli were presented, (3) both cold and warm temperatures falling within the innocuous range based on individual cold and heat pain thresholds.
+TGI temperature pairs, starting at 25ºC and 35ºC were presented on the participant’s forearm for 10 seconds.
+After 10 seconds, the participant had to rate the perceived burning (in a VAS scale from 0 - 100) coming from either the cold (experiment 1) or warm (experiment 2) probe.
+If the participant did not rate their perceived burning as above 15 on the scale, the experimenter increased the temperature on the warm probe, and decreased the temperature on the cold probe systematically.
+They then placed the probes at a different location on the forearm and repeated the trial.
+If the participant rated above 15ºC, the temperature combination was repeated another six times.
+To determine the TGI temperatures, the participant needed to rate the probe as above 15 on the burning VAS four times out of six.
+A list of temperatures used to calibrate the TGI stimuli can be found in the Supplementary Materials.
+In situations where the participant did not consistently report burning for temperatures that were below their pain thresholds, the maximum and minimum possible temperatures were used (2ºC below their thresholds).
 For pain threshold measurements and TGI calibration, we positioned the probes within a single dermatome.
+
 To address our experimental questions, we presented the calibrated TGI stimuli, as well as cold-neutral (Exp. 1) or warm-neutral (Exp. 2) non-TGI stimuli using two thermodes.
@@
 
-The two thermodes were positioned on the internal surface of either forearm, with a constant spacing value between 4 and 5 cm in each direction, depending on the participant's forearm size.
+The two thermodes were positioned on the internal surface of either forearm, with a constant spacing of 5 cm in each direction (Fig.
+1B).
+In rare cases where the participant’s forearm was too narrow to position the probes at 5 cm apart across dermatomes, this distance was adjusted either 4.5 or 4 cm.
 The positioning of the thermodes was either within the same dermatome (C6 and T1) or across dermatomes mapped onto non-adjacent spinal segments (i.e. C6 - T1).
@@
 
-f45_plot(include_zero = F)[[1]]
+f45_plot(include_zero = T)[[1]]
 ```
@@
 
-f45_plot(include_zero = F)[[2]]
+f45_plot(include_zero = T)[[2]]
 ```

### 2024-01-17 scripts/plots.R

@@ -69,7 +69,6 @@ make_sPlot = function(vas_meds, h2_sum, VAS_type, title, l_pos){
 }
 
 
-
 # make figure 2
 f2_plot = function(include_zero = T){
   # first experiment 1
@@ -143,7 +142,7 @@ f2_plot = function(include_zero = T){
 }
 
 # plots for hypothesis 1
-make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
+make_plot1 = function(vas_h1_diff, h1_diff_sum, title){
   
   # now plot the difference
   plot = data = vas_h1_diff %>% ggplot(aes(colour = quality)) +
@@ -168,7 +167,7 @@ make_plot1 = function(vas_h1_diff,h1_diff_sum, title){
           axis.title = element_text(size = 11),
           strip.text = element_text(size = 10),
           title = element_text(size=10)) +
-    coord_cartesian(ylim = c(-60,60))+
+    #coord_cartesian(ylim = c(-60,60))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
   plot
@@ -246,7 +245,7 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
           axis.title = element_text(size = 11),
           strip.text = element_text(size = 10),
           title = element_text(size = 10))+
-    coord_cartesian(ylim = c(-60,60))+
+    #coord_cartesian(ylim = c(-60,60))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
   # plot the differences - across
@@ -276,7 +275,7 @@ make_plot2 = function(vas_h2_diff,h2_diff_sum,title){
           axis.title = element_text(size = 11),
           strip.text = element_text(size = 10),
           title = element_text(size = 10))+
-    coord_cartesian(ylim = c(-60,60))+
+    #coord_cartesian(ylim = c(-60,60))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
   experiment1_h2 = h2_diff_within / h2_diff_across

### 2024-01-17 Manuscript.Rmd
editing results

@@
 Proximo-distal coordinates referred to locations on the skin closer to the elbow or the wrist, whereas rostral-caudal coordinates referred to spinal segments closer to the head (C6) or the lower back (T1).
-Spatial arrangements of stimuli are depicted in Figure 1B.
+Spatial arrangements of stimuli are depicted in Figure 1D.
 The order of the stimuli (TGI vs. non-TGI), the dermatome condition (within vs. across) and the relative placement of the colder temperature (proximal vs. distal or rostral vs. caudal) were pseudo-randomised and counterbalanced between participants.
 
-During each trial, the experimenter positioned two thermodes on the participant's skin for 10 seconds, after which participants rated the most intense cold, warm or burning sensation they perceived during the stimulation period using three separated computerised VAS scales.
-VAS scales were presented one at a time on a computer screen and appeared as a horizontal line, anchored at 0, representing no sensation (e.g., no burning), and 100, signifying an extreme sensation (e.g., extreme burning).
+During each trial, the experimenter positioned the two thermodes on the participant’s skin, and then waited for both thermodes to reach within .25ºC of the desired temperatures for each stimulus.
+After ten seconds of stimulation, participants reported their ratings using three sequential VAS scales for each perceptual quality (cold, warm and burning).
+Scales ranged from 0, indicating the lack of the corresponding sensory quality, to 100, indicating an extreme sensation (Fig.
+1C) and were presented in a random order.
 The order of the three VAS scales was randomised across trials and participants had a maximum of eight seconds to respond to each scale.
@@
 Each thermode configuration was tested three consecutive times on each arm, on three different and non-overlapping skin locations.
-An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter when to rearrange the thermode configuration or change arms to stimulate different dermatomes depending on a pseudo-randomisation order.
+An auditory tone of 500Hz lasting 100ms was played to indicate to the experimenter that the trial was over, and that they should rearrange the thermode configuration.
+Two simultaneous tones of the same quality occurred every three trials, indicating that the participant should change arms to stimulate different dermatomes depending on a pseudo-randomisation order.
+Tones were used because the experimenter could not see the screen, therefore it was the most effective way to inform the experimenter when each trial was completed.
 Each of the four experimental conditions was repeated 12 times, with both the right and left forearms stimulated, and a minimum of five trials between the re-stimulation of the same skin location.
@@
 
-An initial pilot study informed the [pre-registered](https://osf.io/4xcn5/) calculation of the sample size.
+An initial pilot study informed the pre-registered (https://osf.io/4xcn5/) calculation of the sample size.
 To test the directional TGI hypothesis with 95% power and detect an effect size for the coefficient of .12 or greater, we determined that we needed a minimum number of 32 TGI-responsive participants.
@@
 
-The findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both qualitative components of the illusion are modulated at the spinal cord level.
-This interpretation is consistent with a previous study using a similar dermatome manipulation [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
-These results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI and highlight the importance of the veridical temperature of the stimulus being judged when assessing thermosensory and burning components of TGI perception.
-
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3: Difference between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) for each VAS rating quality (cold, warm and burning).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3: Thermosensory and burning components of TGI are spinally mediated: The placement of warm and cold stimuli in different dermatomes reduces the experience of the TGI.
+The difference between within and across dermatome conditions are displayed for each type of stimulation (Non-TGI and TGI) for each VAS rating quality (cold, warm and burning).
 Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes.
-A) experiment one where participants judged sensations at the location of the cold thermode and B) experiment two where participants judged sensations at the location of the warm thermode.
-Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals."}
+In experiment one (A), where participants judged sensations at the location of the cold thermode, cold ratings were significantly reduced during TGI when thermodes were placed across dermatomes.
+In experiment two (B), where participants judged sensations at the location of the warm thermode, warm and burning ratings were significantly reduced during TGI.
+Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
+Please note that this figure does not include trial data where VAS =0, this is to reflect the outcome of our statistical model."}
 

### 2024-01-17 Manuscript.Rmd
dealing with missing data in figures

@@
 indent: true
-bibliography: knitting_files/tgi-spine2.bib
+bibliography: knitting_files/proj-tgi-spine2.bib
 csl: knitting_files/pain.csl
@@
                rsample, rstatix, simr, tibble, tidyverse, wesanderson, patchwork, 
-               cowplot, flextable
+               cowplot, flextable, pracma
                )
@@
 Box plots show median and interquartile range.
-Data presented here include trials where VAS ratings equal 0, which are modelled seperately in the main analyses"}
+For completion, the data presented here include trials where VAS ratings equal 0, which are modelled seperately in the main analyses"}
 
@@
 Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
-Please note that this figure does not include trial data where VAS =0, this is to reflect the outcome of our statistical model."}
+Please note that this figure does not include trial data where VAS = 0, this is to reflect the outcome of our statistical model."}
 
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4: Difference between the proximal and distal location of the reference thermode in the within dermatome condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4: Proximodistal bias in cold perception: The spatial location of the warm and cold thermodes within dermatomes affects the perception of cold.
+The difference between the proximal and distal location of the reference thermode in the within dermatome are displayed by condition and by stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
 Higher values show higher ratings when the cold probe is more proximal than the warm probe.
-A) experiment one where participants judged sensations at the location of the cold thermode and B) experiment two where participants judged sensations at the location of the warm thermode.
-Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
+In experiment one (A), where participants judged sensations at the location of the cold thermode, cold and burning ratings were higher when the cold probe was more distal.
+In experiment two (B), where participants judged sensations at the location of the warm thermode, cold ratings were higher when the cold probe was more distal.
+Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals.
+Please note that this figure does not include trial data where VAS =0, this is to reflect the outcome of our statistical model."}
 
-f45_plot(include_zero = T)[[1]]
+f45_plot(include_zero = F)[[1]]
 ```
@@
 5B), participants reported a reduced subjective experience of cold, alongside an enhanced perception of warmth when the cold thermode was applied on a dermatome that mapped onto a more caudal segment.
-The results indicated a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord.
-While reduced cold perception was more specific for TGI stimuli, participants reported enhanced warm and burning perception irrespective of stimulation type.
-Overall these effects are in line with the interpretation that the thermosensory and burning components of the TGI can differ strongly according to the location of cold-warm primary sensory afferents on the spinal cord.
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 5: Difference between the caudal and rostral dermatome conditions and the stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 5: Directional effects of inter-segmental sensory integration: Spatial location of warm and cold thermodes across dermatomes affects the perception of TGI and non-TGI stimuli.
+The difference between the caudal and rostral dermatomes are displayed by conditions and stimulation type (Non-TGI, TGI) for all VAS rating types (cold, warm, burn).
 Higher values represent higher ratings when the cold probe is located in dermatomes that are related to more caudal spinal segments (T1) than the warm probe (C6).
-A) experiment one where participants judged sensations at the location of the cold thermode and B) experiment two where participants judged sensations at the location of the warm thermode.
-Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}
+In experiment one (A), where participants judged sensations at the location of the cold thermode, perception of warm and cold, cold ratings were reduced and burning ratings increased when the cold probe was located in more caudal dermatomes.
+In experiment two (B), where participants judged sensations at the location of the warm thermode, the changes in warm and cold ratings were similar to experiment one but specific to TGI stimuli.
+Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals.
+Please note that this figure does not include trial data where VAS =0, this is to reflect the outcome of our statistical model."}
 
-f45_plot(include_zero = T)[[2]]
+f45_plot(include_zero = F)[[2]]
 ```
@@
 
-The details of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments: (1) reduced cold, enhanced heat and burning sensations when thermosensory integration takes place more focally within a few spinal segments, and (2) clear effects when distinct cold and warm stimuli elicited a differential spatial pattern of neural activity along several spinal cord segments.
+In this study, we showed that organisation of cold and warm primary afferents both within and across segmental locations affects perception of the TGI.
+Our findings suggest that the thermosensory quality of the reference thermode (cold or warm) showed differential sensitivity to thermosensory and painful aspects of the TGI experience, and collectively suggested that both qualitative components of the illusion are modulated at the spinal cord level.
+This interpretation is consistent with a previous study using a similar dermatome manipulation [@fardo_organization_2018], as well as another study showing modulation of heat and pain ratings of TGI stimuli by conditioned pain modulation [@harper_conditioned_2017].
+In addition to this, we found a notably enhanced TGI effect when the cold stimulus induced more caudal activity within the spinal cord.
+
+Whilst the stimuli used to induce TGI in our study are not the conventional alternating warm and cold bars we associated with the thermal ‘grill’, research has shown that the TGI can be induced from a variety of alternating warm-cold patterns on the skin [@li_importance_2009].
+In addition, the stimuli used in our paradigm have been previously established to produce TGI [@defrin_spatial_2008; @fardo_organization_2018].
+Overall these results support the role of spinal processes in the generation of distinct perceptual aspects of the TGI and are in line with the interpretation that the thermosensory and burning components of the TGI can differ strongly according to the location of activated cold-warm primary sensory afferents in the spinal cord.
+They also highlight the importance of the veridical temperature of the stimulus being judged when assessing thermosensory and burning components of TGI perception.
+
+The details of spinal neuroanatomy provide insightful perspectives concerning the two main findings of these experiments (Fig.6): (1) reduced cold, enhanced heat and burning sensations when thermosensory integration takes place more focally within a few spinal segments, and (2) clear effects when distinct cold and warm stimuli elicited a differential spatial pattern of neural activity along several spinal cord segments.
 
@@
 
-Our results indicate that enhanced TGI perception when cold-warm stimuli are applied within dermatomes may be attributed to a confluence of interconnected mechanisms.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 6: Schematic of the spinal neuroanatomy directly associated with warm and cold afferents (A) within the same spinal segment and (B) across two separate spinal segments.
+The Lissaur’s tract is depicted as the peripheral warm and cold afferents that span to neighbouring spinal segments.
+Propriospinal projections from the stimulated segments possibly inhibit responses in neighbouring segments, which means integration of warm and cold sensory signals is more likely within (A) than across (B) dermatomes.
+The black arrow indicates direction of supraspinal structures such as the thalamus."}
+ggdraw() +
+    draw_image(magick::image_read(file.path("figures","figure6.png")), scale = 1)
+```
+
+Our results indicate that enhanced TGI perception when cold-warm stimuli are applied within dermatomes (Fig.
+6A), compared to across dermatomes (Fig.
+6B) may be attributed to a confluence of interconnected mechanisms.
 First, the Lissauer's tract, with its short rostrocaudal span of only one to two segments, aligns with the constraints of individual dermatome boundaries.
@@
 
-# Supplementary material
+# Supplementary methods
+For the TGI calibration procedure, the experimenter followed a set list of cold-warm temperature pairs, at which to test TGI:
 
+1. 27-35ºC
+2. 25-37ºC
+3. 22-38ºC
+4. 20-40ºC
+5. 19-41ºC
+6. 18-42ºC
+7. 17-43ºC
+8. 16-44ºC
+
+The experimenter initially tested the TGI using the first temperature combination.
+If this temperature combination did not produce a burning sensation (above 15/100 on the burning VAS) then the experimenter moved to the second temperature combination.
+The experimenter proceeded down the above list like so until one of two things occurred.
+(1) The participant responded that the temperature combination produced burning (15 on the burning VAS scale) in at least 4/6 trials or (2) temperatures were within 1-2ºC of the participant’s pain thresholds.
+If (1), the experimenter proceeded to the main experiment.
+If (2), the experimenter deviated from the above list to identify a temperature combination that produced TGI whilst remaining within the innocuous range for that participant.
+If the end temperature combination was reached (16-44) and the participant still did not feel TGI, then the temperature of the cold probe was lowered gradually, until either the participant experienced the TGI or the probe was within 1-2ºC of the noxious threshold.
+
+# Supplementary results
 Tables of main effects and interactions for each sensory quality (cold, warm, burning) for experiment 1 and experiment 2.
@@
 \newpage
+
 ## Temperatures by participant

### 2024-01-17 scripts/models.R

@@ -10,8 +10,10 @@ if(rerun){
   experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'))
   experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'))
   
-  df_long_exp1 = experiment1$df_long %>% mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
-  df_long_exp2 = experiment2$df_long %>% mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
+  df_long_exp1 = experiment1$df_long %>% 
+    mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
+  df_long_exp2 = experiment2$df_long %>% 
+    mutate(cold_probe = as.factor(cold_probe), manipulation = as.factor(manipulation))
   
   
   ## Define constrats such that we both get within / across (i.e. distal & proximal vs rostral & caudual)

### 2024-01-17 scripts/plots.R

@@ -136,6 +136,8 @@ f2_plot = function(include_zero = T){
                          widths = c(1,1.4))
   
   s_plot_out
+  ggsave(file.path("figures", "Figure2.png"), plot = s_plot_out, device = NULL, 
+         width = 7.2, height = 5, dpi = 600)
   
   return(s_plot_out)
   
@@ -143,6 +145,9 @@ f2_plot = function(include_zero = T){
 
 # plots for hypothesis 1
 make_plot1 = function(vas_h1_diff, h1_diff_sum, title){
+  
+ 
+  # now turn all NAs into 0, just for visualisation purposes
   
   # now plot the difference
   plot = data = vas_h1_diff %>% ggplot(aes(colour = quality)) +
@@ -167,7 +172,7 @@ make_plot1 = function(vas_h1_diff, h1_diff_sum, title){
           axis.title = element_text(size = 11),
           strip.text = element_text(size = 10),
           title = element_text(size=10)) +
-    #coord_cartesian(ylim = c(-60,60))+
+    coord_cartesian(ylim = c(-60,60))+
     scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) 
   
   plot
@@ -179,9 +184,18 @@ f3_plot = function(include_zero = T){
   
   # experiment 1 file
   
-  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), include_zero = include_zero)
+  experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), 
+                          include_zero = include_zero)
   vas_h1_diff_exp1 = experiment1$vas_h1_diff
   h1_diff_sum_exp1 = experiment1$h1_diff_sum
+  diff_temp <- experiment1$diff_temp
+  
+  # first make sure missing data is included in the plot as 0 for visualisation purposes
+  vas_h1_diff_exp1 <- merge(vas_h1_diff_exp1, diff_temp,
+                            by = c('ID','manipulation','quality'), all.y = TRUE)
+  # make all NAs = 0
+  vas_h1_diff_exp1 <- vas_h1_diff_exp1 %>% 
+    replace_na(list(within = 0, across = 0, difference = 0))
   
   
   h1_diff_plot_exp1 = make_plot1(vas_h1_diff = vas_h1_diff_exp1,
@@ -194,6 +208,14 @@ f3_plot = function(include_zero = T){
[…]

### 2024-01-17 scripts/utility.R

@@ -127,11 +127,12 @@ prep_data = function(file, include_zero = T){
   init_burn <- filter(df_long, quality == 'init')
   all_vas <- filter(df_long, quality != 'init')
   
-  # calculate means
+  # calculate medians and means for plots
   vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
                         median, data = all_vas)
   
   vas_h1 <- aggregate(VAS ~ quality*manipulation*condition*ID, mean, data = vas_meds)
+  
   # change name of manipulation
   vas_h1$manipulation <- factor(vas_h1$manipulation,
                                 labels = c('Non-TGI', 'TGI'))
@@ -139,9 +140,35 @@ prep_data = function(file, include_zero = T){
   h1_sum <- summarySEwithin(data = vas_h1, measurevar = 'VAS',
                             withinvars = c('manipulation', 'quality', 'condition'))
   
+  
   vas_h1_diff <- vas_h1 %>% 
-    pivot_wider(names_from = condition, values_from = VAS) %>% tidyr::replace_na(list(within = 0, across = 0)) %>% 
+    pivot_wider(names_from = condition, values_from = VAS) %>% 
+    tidyr::replace_na(list(within = 0, across = 0)) %>% 
     mutate(difference = within - across)
+  
+  # with !include_zeros nan trials are excluded which leads to missing plot data
+  # these should be replaced with zeros for visualisation purposes 
+  # (which is a true representative of the difference between the actual data anyway)
+  
+  # first, create dataframe with true length for all data
+  nPP <- count(vas_h1_diff, ID)
+  diff_temp <- nPP %>% 
+    slice(rep(row_number(), 6)) %>% 
+    select(-n) %>% 
+    mutate(ID = sort(ID, decreasing = FALSE))
+  
+  quality <- c('cold','warm','burn')
+  manipulation <- c(repmat(1,3,1), repmat(2,3,1))
+  
+  diff_temp$quality <- matrix(rep(quality, 80))
+  diff_temp$manipulation <- matrix(rep(manipulation, 40))
+  
+  diff_temp <- diff_temp %>% 
+    dplyr::mutate(manipulation = recode(manipulation, '1' = 'Non-TGI', '2' = 'TGI'))
+
+  
+# add IDs to 
+  
   # recode quality
   vas_h1_diff$quality <- factor(vas_h1_diff$quality,
[…]

### 2024-01-18 Manuscript.Rmd
final ms changes

@@
 2) stimulus of identical temperature as in the TGI condition with a baseline temperature of 30°C (non-TGI stimuli).
-All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments (Figure 1).
+All stimulation pairs were presented at a fixed distance on the skin, either within the same dermatome or across dermatomes that mapped onto non-adjacent spinal segments (Fig.
+1).
 This arrangement of cold and warm probes on the skin was specifically chosen to be able to explore the spinal mechanisms of the TGI and similar set-ups, using two probes to induce TGI, have been used previously in healthy human participants [@fardo_organization_2018; @defrin_spatial_2008].
@@
 TGI temperature pairs, starting at 25ºC and 35ºC were presented on the participant’s forearm for 10 seconds.
-After 10 seconds, the participant had to rate the perceived burning (in a VAS scale from 0 - 100) coming from either the cold (experiment 1) or warm (experiment 2) probe.
+After 10 seconds, the participant had to rate the perceived burning (in a VAS scale from 0 - 100) coming from either the cold (Exp.
+1) or warm Exp.
+2) probe.
 If the participant did not rate their perceived burning as above 15 on the scale, the experimenter increased the temperature on the warm probe, and decreased the temperature on the cold probe systematically.
 They then placed the probes at a different location on the forearm and repeated the trial.
-If the participant rated above 15ºC, the temperature combination was repeated another six times.
+If the participant rated above 15 on the VAS, the temperature combination was repeated another six times.
 To determine the TGI temperatures, the participant needed to rate the probe as above 15 on the burning VAS four times out of six.
-A list of temperatures used to calibrate the TGI stimuli can be found in the Supplementary Materials.
 In situations where the participant did not consistently report burning for temperatures that were below their pain thresholds, the maximum and minimum possible temperatures were used (2ºC below their thresholds).
@@
 Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals.
-Please note that this figure does not include trial data where VAS = 0, this is to reflect the outcome of our statistical model."}
+Please note that to best reflect the outcome of our zero-inflated statistical model this figure only includes trial data where VAS ratings were greater than 0."}
 
@@
 Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals.
-Please note that this figure does not include trial data where VAS =0, this is to reflect the outcome of our statistical model."}
+Please note that to best reflect the outcome of our zero-inflated statistical model this figure only includes trial data where VAS ratings were greater than 0."}
 
@@
 
-```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 6: Schematic of the spinal neuroanatomy directly associated with warm and cold afferents (A) within the same spinal segment and (B) across two separate spinal segments.
-The Lissaur’s tract is depicted as the peripheral warm and cold afferents that span to neighbouring spinal segments.
-Propriospinal projections from the stimulated segments possibly inhibit responses in neighbouring segments, which means integration of warm and cold sensory signals is more likely within (A) than across (B) dermatomes.
+```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 6: Schematic of the spinal neuroanatomy associated with warm and cold afferents (A) within the same spinal segment and (B) across two separate non-adjacent spinal segments.
+After entering the spinal cord, peripheral warm and cold afferent fibres form collateral branches and synapses above and below the level of entry in neighbouring spinal segments.
+Propriospinal neurons possibly inhibit responses in neighbouring segments (i.e., inter-segmental inhibition), which means integration of warm and cold sensory signals is more likely within (A) than across (B) dermatomes.
+Projection neurons decussate and ascend contralaterally forming the spinothalamic pathway.
 The black arrow indicates direction of supraspinal structures such as the thalamus."}
@@
 We also thank Michael Clements for the collection of pilot data that was instrumental in refining the experimental design.
-This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948788).
+This study was supported by a European Research Council Starting Grant (ERC-2020-StG-948838).
 
@@
 
-# Supplementary methods
-For the TGI calibration procedure, the experimenter followed a set list of cold-warm temperature pairs, at which to test TGI:
-
-1. 27-35ºC
-2. 25-37ºC
-3. 22-38ºC
-4. 20-40ºC
-5. 19-41ºC
-6. 18-42ºC
-7. 17-43ºC
-8. 16-44ºC
-
-The experimenter initially tested the TGI using the first temperature combination.
-If this temperature combination did not produce a burning sensation (above 15/100 on the burning VAS) then the experimenter moved to the second temperature combination.
-The experimenter proceeded down the above list like so until one of two things occurred.
-(1) The participant responded that the temperature combination produced burning (15 on the burning VAS scale) in at least 4/6 trials or (2) temperatures were within 1-2ºC of the participant’s pain thresholds.
-If (1), the experimenter proceeded to the main experiment.
-If (2), the experimenter deviated from the above list to identify a temperature combination that produced TGI whilst remaining within the innocuous range for that participant.
-If the end temperature combination was reached (16-44) and the participant still did not feel TGI, then the temperature of the cold probe was lowered gradually, until either the participant experienced the TGI or the probe was within 1-2ºC of the noxious threshold.
-
-# Supplementary results
+# Supplementary materials
 Tables of main effects and interactions for each sensory quality (cold, warm, burning) for experiment 1 and experiment 2.

### 2024-01-18 scripts/plots.R

@@ -188,10 +188,10 @@ f3_plot = function(include_zero = T){
                           include_zero = include_zero)
   vas_h1_diff_exp1 = experiment1$vas_h1_diff
   h1_diff_sum_exp1 = experiment1$h1_diff_sum
-  diff_temp <- experiment1$diff_temp
+  diff_tmp_h1 <- experiment1$diff_tmp_h1
   
   # first make sure missing data is included in the plot as 0 for visualisation purposes
-  vas_h1_diff_exp1 <- merge(vas_h1_diff_exp1, diff_temp,
+  vas_h1_diff_exp1 <- merge(vas_h1_diff_exp1, diff_tmp_h1,
                             by = c('ID','manipulation','quality'), all.y = TRUE)
   # make all NAs = 0
   vas_h1_diff_exp1 <- vas_h1_diff_exp1 %>% 
@@ -208,10 +208,10 @@ f3_plot = function(include_zero = T){
   experiment2 = prep_data(file.path("data", 'STGI_exp2_compiled-data.csv'), include_zero = include_zero)
   vas_h1_diff_exp2 = experiment2$vas_h1_diff
   h1_diff_sum_exp2 = experiment2$h1_diff_sum
-  diff_temp = experiment2$diff_temp
+  diff_tmp_h1 = experiment2$diff_tmp_h1
   
   # first make sure missing data is included in the plot as 0 for visualisation purposes
-  vas_h1_diff_exp2 <- merge(vas_h1_diff_exp2, diff_temp,
+  vas_h1_diff_exp2 <- merge(vas_h1_diff_exp2, diff_tmp_h1,
                             by = c('ID','manipulation','quality'), all.y = TRUE)
   # make all NAs = 0
   vas_h1_diff_exp2 <- vas_h1_diff_exp2 %>% 
@@ -310,20 +310,40 @@ plot2 = function(include_zero = T){
   experiment1 = prep_data(file.path("data", 'STGI_exp1_compiled-data.csv'), include_zero = include_zero)
   vas_h2_diff_exp1 = experiment1$vas_h2_diff
   h2_diff_sum_exp1 = experiment1$h2_diff_sum
-  diff_temp = experiment1$diff_temp
+  diff_tmp_h2 = experiment1$diff_tmp_h2
   
+  # create full data-frame so NA values = 0
+  # for plotting purposes
+  # first make sure missing data is included in the plot as 0 for visualisation purposes
[…]

### 2024-01-18 scripts/utility.R

@@ -152,7 +152,7 @@ prep_data = function(file, include_zero = T){
   
   # first, create dataframe with true length for all data
   nPP <- count(vas_h1_diff, ID)
-  diff_temp <- nPP %>% 
+  diff_tmp_h1 <- nPP %>% 
     slice(rep(row_number(), 6)) %>% 
     select(-n) %>% 
     mutate(ID = sort(ID, decreasing = FALSE))
@@ -160,10 +160,10 @@ prep_data = function(file, include_zero = T){
   quality <- c('cold','warm','burn')
   manipulation <- c(repmat(1,3,1), repmat(2,3,1))
   
-  diff_temp$quality <- matrix(rep(quality, 80))
-  diff_temp$manipulation <- matrix(rep(manipulation, 40))
+  diff_tmp_h1$quality <- matrix(rep(quality, 80))
+  diff_tmp_h1$manipulation <- matrix(rep(manipulation, 40))
   
-  diff_temp <- diff_temp %>% 
+  diff_tmp_h1 <- diff_tmp_h1 %>% 
     dplyr::mutate(manipulation = recode(manipulation, '1' = 'Non-TGI', '2' = 'TGI'))
 
   
@@ -214,6 +214,18 @@ prep_data = function(file, include_zero = T){
     tidyr::replace_na(list(prox_caud = 0, dist_rost = 0)) %>% 
     mutate(difference = prox_caud - dist_rost)
   
+  #create dataframe of actual length
+  diff_tmp_h2 <- rbind(diff_tmp_h1, diff_tmp_h1) #lengthen
+  diff_tmp_h2 <- diff_tmp_h2 %>% 
+    mutate(ID = sort(ID, decreasing = FALSE))
+  
+  condition <- c(repmat(1,6,1), repmat(2,6,1)) #within across conditions
+  
+  diff_tmp_h2$condition <- matrix(rep(condition, 40))
+  
+  diff_tmp_h2 <- diff_tmp_h2 %>% 
+    dplyr::mutate(condition = recode(condition, '1' = 'within', '2' = 'across'))
+  
   # recode quality
   vas_h2_diff$quality <- factor(vas_h2_diff$quality,
                                 levels = c('cold', 'warm', 'burn'))
@@ -247,7 +259,8 @@ prep_data = function(file, include_zero = T){
               vas_h2_diff = vas_h2_diff,
               h2_diff_sum = h2_diff_sum,
               df_long = df_long,
[…]
